### 2019-07-07 jmiv.tex
changes relecture HT

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage[utf8]{inputenc}
\usepackage{graphicx,subfig}
\usepackage{amstext,amsmath,amssymb,bm,bbm,mathtools}
\usepackage[linesnumbered,lined,boxed,commentsnumbered]{algorithm2e}
\usepackage[export]{adjustbox}
\usepackage{xcolor}

\DeclareMathOperator*{\argmin}{arg\,min}
\DeclarePairedDelimiter\norm{\lVert}{\rVert}%
\DeclarePairedDelimiter\abs{\lvert}{\rvert}%

\definecolor{violet}{rgb}{0.56, 0.0, 1.0}

\newcommand{\todo}[1]{{\textcolor{blue}{#1}}}
\newcommand{\test}[1]{{\textcolor{red}{#1}}}
\newcommand{\jaco}[1]{{\textcolor{green!50!black}{#1}}}
\newcommand{\HT}[1]{{\textcolor{violet}{#1}}}

% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{A\HT{n Elastica-driven} Digital Curve Evolution Model for Image Segmentation\thanks{This  work has  been  partially  funded by CoMeDiC ANR-15-CE40-0006 research grant.}}
  \titlerunning{Digital Curve Evolution by Elastica Energy}
  %\title{Digital Curvature Evolution Models for Image Segmentation\thanks{This  work has  been  partially  funded by CoMeDiC ANR-15-CE40-0006 research grant.}}

\author{Daniel Antunes\inst{1}
Jacques-Olivier Lachaud\inst{1}
Hugues Talbot\inst{2}}
%
\authorrunning{D. Antunes et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Universit{\'e} Savoie Mont Blanc, LAMA, UMR CNRS 5127, F-73376, France
\email{daniel.martins-antunes, jacques-olivier.lachaud@univ-savoie.fr} \and
CentraleSupelec Inria \'equipe OPIS, Universit\'e Paris-Saclay, 9 rue Joliot-Curie, F-91190 Gif-sur-Yvette \\
\email{hugues.talbot@centralesupelec.fr}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}

\keywords{Multigrid convergence  \and Digital estimator \and Curvature \and Shape Optimization \and Image Segmentation.}
\end{abstract}
%
%
%
\setcounter{footnote}{0}
\section{Introduction \todo{(To be extended)}}

Geometric quantities are particularly useful as regularizers in
low-level image analysis, especially when little prior information is
known about the shape of interest. Length penalization is a \HT{well-behaved,} general
purpose regularizer and \HT{many} models \HT{in the literature} make use
of it, from active contours \cite{casseles97geodesic} to level-set
formulations \cite{malladi1995image,malladi1995shape}. Discrete
graph-based variational models have been particularly succesfull to
incorporate length penalization as a penalizer, while keeping the
ability to extract \HT{a} global optimum
\cite{boykov01graphcut,appleton05geodesic}.

However length regularization shows limitations when segmenting
small or thin and elongated objects, as it tends to shrink solutions
or \HT{yields} disconnected solutions. Such drawbacks can be problematic in
image segmentation or image inpainting. It is thus rather natural to
consider curvature (especially squared curvature) \HT{as} a potential
regularizer. Energies involving \HT{both length and} squared curvature are often called
{\em Euler elastica} model (\HT{that} dates back to Euler) or {\em Willmore energy}
($n$-dimensional extension) and have been brought back to attention in
computer vision by Mumford \cite{mumford1994elastica}. A similar
regularizer is also present in the second-order regularizer
of the \HT{original} snake model \cite{kass1988snakes}. \HT{However,
  optimizing models with the Elastica energy is difficult in practice, as it
  is not convex}.

One of the first successful uses of curvature in image processing is
the inpainting algorithm described in \cite{masnou98inpainting}\HT{, where
authors} evaluate the elastica energy along the level lines of a
simply-connected image to reconstruct its occluded parts. The
non-intersection property of level lines \HT{induces} the construction of an
efficient dynamic programming algorithm. \HT{However, }  the curvature energy is \HT{only} coarsely approximated. 
\cite{chan02elasticainpainting} \HT{is} another geometric inpainting method
involving elastica \HT{optimized with level-sets}.

In image segmentation, Zehiry and Grady have shown that injecting
curvature as a regularizer \HT{can help} recover thin and elongated objects
\cite{zehiry10fast}. Similarly Schoenemann {\em et al.}
\cite{schoenemann09linear} have considered the elastica energy in
their ratio-based image segmentation approach. Their global
optimization framework shows the considerable interest of using such
regularizer in common binary image segmentation tasks. However the
time complexity of their algorithm \HT{is prohibitive,} even if
curvature is \HT{again} coarsely approximated.

In fact, it is still a very challenging task to inject curvature in
the context of image segmentation.  
\HT{State-of-art methods are in practice} difficult to optimize and \HT{do not scale}
\cite{zehiry10fast,schoenemann09linear,strandmark11globalframework,nieuwenhuis14efficient}. In
order to achieve reasonable running times, such approaches make use of
coarse curvature estimations for which the approximation error is
\HT{often} unknown. Improving the quality of the curvature estimator has an
important impact on the accuracy of the results, but is
computationally too costly in these methods.

Segmentation methods using Elastica or Willmore energies \HT{generally
reduce to} computing the corresponding flow, i.e. following its
gradient. Well-founded level-set methods involving Willmore energy
\cite{droske2004level} have been used in medical image segmentation
\cite{lim2012introducing}. Another level-set formulation similar to
the Chan-Vese model \HT{was} proposed in \cite{zhu2013image}. Willmore
flow can also be carried out by phase-field models (see
\cite{bretin2015phase}) but they are less suited to image segmentation
since interfaces are blurred in such models. Threshold dynamics can
also be considered for such energies \cite{esedoglu2008threshold} and
has been proposed for image desocclusion \cite{esedoglu2005threshold}.

In this paper we are interested in purely discrete variational segmentation models involving an elastica
energy. Recently, new estimators of curvature along digital contours have been proposed
\cite{roussillon11mdca,coeurjolly13integral,schindele17mdca} with the \HT{desirable} multigrid convergence property. This
motivates us to \HT{propose} models in which they can be used successfully.

\HT{In the remainder, we} investigate the use of the digital integral invariant
curvature estimator \cite{coeurjolly13integral} in a discrete
variational segmentation framework. More precisely, we show how to
incorporate it in a digital flow minimizing its squared
curvature. This model is expressible as a discrete combinatorial
optimization model, which we solve using a classical variant of QPBO
algorithm \cite{rother07qpbo}. \HT{Our solution does not} compute a global
solution to the whole domain, but our approach leads to a digital flow
similar to continuous \HT{Elastica}, as shown by our experiments. We
present an application of the model as a post-processing step in a
segmentation framework, and demonstrate how it can improve standard
results. The code is freely available on
github\footnote{https://www.github.com/danoan/BTools}.

%% In this work, we investigate the use of a more suitable curvature
%% estimator with multigrid convergent property and its application as a
%% boundary regularizer in a digital flow minimizing its squared
%% curvature. Our method decreases the elastica energy of the contour and
%% its evolution is evaluated on several digital flows.

%% Finally, we
%% present an application of the model as a post-processing step in a
%% segmentation framework. The code is freely available on
%% github\footnote{https://www.github.com/danoan/BTools}.

\begin{itemize}
\item{Geometric properties and regularization}
\item{The role of curvature}

  Quote \cite{schoenemann2011elastic} for the interest of using curvature energy when segmenting regions in gradient-based data fitting term. It can look for global optimum within a graph representation of the image. Main problem of their approach is the computational complexity as well as rather coarse approximations of curvature. (Be more precise here).

\item{What are the difficulties in use curvatue as a regularizer (point out convex relaxation approaches) and how a digital approach may help us }
\item{Outline: We present two models that illustrate how digital estimators can be used to minimize the elastica energy on digital sets.  }
\item{\todo{Add related works : geometric priors, binary segmentation, other digital curve evolution models}}
\item{\todo{Talk about Willmore flow with phase field or with threshold dynamics}}

\item{\textbf{Classical work on elastica and Wilmore flow in imaging}}
  \begin{itemize}
  \item{Level lines based disocclusion \cite{masnou98inpainting} }	
  \item{Filling-In by Joint Interpolation of Vector Fields and Gray Levels \cite{ballester01filljoint} }
  \item{Eulers Elastica and Curvature Based Inpaintings \cite{chan02elasticainpainting} }
  \item{Discrete willmore flow \cite{bobenko2005discrete}}
  \item{Introducing Willmore flow into level set segmentation of spinal vertebrae \cite{lim2012introducing}}	
  \end{itemize}

\item{\textbf{Level-sets}}
  \begin{itemize}
  \item{Image processing via level set curvature flow \cite{malladi1995image} }
  \item{Shape Modeling with Front Propagation: A Level Set Approach \cite{malladi1995shape} }	
	\end{itemize}

\item{\textbf{Convex relaxation}}
  \begin{itemize}
  \item{A convex lower semicontinuous approximation of Eulers elastica energy \cite{bredies15convex}}				\item{Introducing Total Curvature for Image Processing \cite{goldluecke11totalcurvature}}
  \end{itemize}

\item{\textbf{Constraint optimization}}
  \begin{itemize}
  \item{Curvature regularity for region-based image segmentation and inpainting: A linear programming relaxation \cite{schoenemann09linear} }	
  \item{A Fast Algorithm for Euler's Elastica Model Using Augmented Lagrangian Method \cite{tai11elastica} }		
  \item{The elastic ratio: Introducing curvature into ratio-based image segmentation \cite{schoenemann2011elastic} }		
  \item{Curvature Regularization for Curves and Surfaces in a Global Optimization Framework \cite{strandmark11globalframework} }
  \end{itemize}

\item{\textbf{Discrete approaches}}
  \begin{itemize}
  \item{Fast global optimization of curvature \cite{zehiry10fast}	}
  \item{Efficient Squared Curvature \cite{nieuwenhuis14efficient} 	}
  \item{Contrast driven {E}lastica for image segmentation \cite{el2016contrast} }	
  \end{itemize}

\end{itemize}

\textit{Outline}. Section two reviews the concept of multigrid
convergence and highlights its importance for the definition of
digital estimators. Next, we describe two convergent estimators used
in this paper, one for tangent and the other for curvature. They are
used in the optimization model and in the definition of the digital
elastica. Section three describes a local combinatorial optimization model
suitable for different curvature estimators. Section four describes the proposed 
curvature evolution model along with several illustrations of digital flows. Section five
explains how to use the evolution model as a post-processing step in
an image segmentation framework.

\section{Multigrid convergent estimators \todo{(Mostly copy/paste)}}

The goal of this section is to  introduce the concept of multigrid convergenc and its potential when analyzing digital images with variational models involving geometric quantities. More precisely we wish to delineate shapes within digital images with some priors related to their unknown continuous geometry. Of course we only observe shape digitizations within images.
%% \begin{itemize}
%% 	\item{Why to use multigrid convergent estimators}
%% 	\item{Multigrid convergence for local estimators}
%% 	\item{Reference to examples of multigrid digital estimators(for curvature, length, tangent)}
%% 	\item{Define the elastica energy estimator}
%% 	\item{\test{(Jaco) see if two opposite II evaluations give convergent curvature}}
%% \end{itemize}

%% \hrulefill

A digital shape is the result of some quantization process over an
object $X$ lying in some continuous space of dimension $2$ (here).
For example, the Gauss digitization of a continuous subset $X$ of the
Euclidean plane $\mathbb{R}^2$ with grid step $h>0$ is defined as
\begin{align*}
	D_h(X) = X \cap (h\mathbb{Z})^2.
\end{align*}

Given a shape $X$ and its digitization $D_h(X)$, a digital estimator $\hat{u}$ for some geometric quantity $u$ is
intended to compute $u(X)$ by using only the digitization. This problem is not well-posed, as the same digital object
could be the digitization of infinitely many objects very different from $X$. Therefore, a characterization of what constitutes
a good estimator is necessary.

Let $u$ be some geometric quantity of $X$ (e.g. tangent, curvature). We wish to devise a digital estimator $\hat{u}$ for
$u$. It is reasonable to state that $\hat{u}$ is a good estimator if $\hat{u}(D_h(X))$ converges to $u(X)$ as we refine
our grid. For example, counting pixels is a convergent estimator for area (with a rescale of $h^2$); but counting
boundary pixels (with a rescale of $h$) is not a convergent estimator for perimeter. Multigrid convergence is the
mathematical tool that makes this definition precise. Given any subset $Z$ of $(h\mathbb{Z})^2$, we can represent it as a
union of axis-aligned squares with edge length $h$ centered on the point of $Z$. The topological boundary of this union
of cubes is called {\em $h$-frontier} of $Z$. When $Z=D_h(X)$, we call it {\em $h$-boundary of $X$} and denote it by
$\partial_h X$.
%% In the following, let the $h$-frontier of $D_h(X)$ to be defined as $\partial D_h(X) = \partial \left( \frac{1}{h} \cdot X \right) \cap \mathbb{Z}^2$.

\begin{definition}[Multigrid convergence for local geometric quantites]
  A local discrete geometric estimator $\hat{u}$ of some geometric
  quantity $u$ is (uniformly) multigrid convergent for the family $\mathbb{X}$ if
  and only if, for any $X \in \mathbb{X}$, there exists a grid step
  $h_X>0$ such that the estimate $\hat{u}(D_h(X),\hat{x},h)$ is
  defined for all $\hat{x} \in \partial_hX$ with $ 0 < h < h_X$, and
  for any $x \in \partial X$,
  \begin{equation*}
    \forall \hat{x} \in  \partial_hX \text{ with } \norm{ \hat{x} - x }_{\infty} \leq h, \norm{ \hat{u}(D_h(X),\hat{x},h) - u(X,x)} \leq \tau_{X}(h),			
  \end{equation*}
  where $\tau_{X}:\mathbb{R}^{+}\setminus\{0\} \rightarrow
  \mathbb{R}^{+}$ has null limit at $0$. This function defines the
  speed of convergence of $\hat{u}$ towards $u$ for $X$.
\end{definition}

For a global geometric quantity (e.g. perimeter, area, volume), the definition remains the same, except that the mapping
between $\partial X$ and $\partial_h X$ is no longer necessary.

Multigrid convergent estimators provide a quality guarantee and should
be preferred over non-multigrid convergent ones. In the next section,
we describe two estimators that are important for our purpose.

\subsection{Tangent and Perimeter Estimators}

The literature presents several perimeter estimators that are multigrid convergent (see
\cite{coeurjolly04comparative,coeurjolly12multigrid} for a review), but in order to define the digital elastica we need a local estimation
of length and we wish that integration over these local length elements gives a multigrid convergent estimator for the
perimeter.

\begin{definition}[Elementary Length]
  Let a digital curve $C$ be represented as a sequence of grid vertices in a grid cell representation of digital objects (in a grid with step $h$). Further, let $\vec{ \hat{v} }$ be a multigrid convergent estimator for the unit tangent vector. The elementary length $\hat{s}(\vec{e})$ at some oriented grid edge $ \vec{e} \in C$ is defined as
  \begin{align*}
    \hat{s}(\vec{e}) = h ~\vec{\hat{v}}(\vec{e}) \cdot \vec{e}.
  \end{align*}
\end{definition}
The integration of the elementary length along the digital curve is a multigrid convergent estimator for perimeter if
one uses the $\lambda$-MST \cite{lachaud07tangent} tangent estimator (see \cite{lachaud06hdr}).

\subsection{Integral Invariant Curvature Estimator}
Generally speaking, an invariant is a function whose value is unaffected by the action
of some group on the elements of the domain.
%% Jaco: trop général, et pas utilisé après
%% Generally speaking, an invariant $\sigma$ is a real-valued function from some space $\Omega$ which value is unaffected by the action
%% of some group $\mathfrak{G}$ on the elements of the domain
%% \begin{align*}
%%   x \in \Omega, g \in \mathfrak{G}, \sigma(x) = v \longleftrightarrow \sigma(g \cdot x ) = v.
%% \end{align*}
Perimeter and curvature are examples of invariants for shapes on
$\mathbb{R}^2$ with respect to the euclidean group of rigid
transformations. Definition of integral area invariant and its link
with curvature is proven in \cite{manay04intinvariant}.

\begin{definition}[Integral area invariant]
  Let $X \subset \mathbb{R}^2$ and $B_r(p)$ the ball of radius $r$ centered at point $p$. Further, let
  $\mathbbm{1}_X(\cdot)$ be the characteristic function of $X$. The integral area invariant $\sigma_{X,r}(\cdot)$ is
  defined as
  \begin{align*}
    \forall p \in \partial X, \quad \sigma_{X,r}(p) = \int_{B_r(p)}{ \mathbbm{1}_X(x) dx}.
  \end{align*}
\end{definition}

The value $\sigma_{X,r}(p)$ is the area of the intersection of the
ball $B_r(p)$ with shape $X$. By approaching the shape at
point $p \in X$, one can rewrite the intersection area
$\sigma_{X,r}(p)$ in the form of the Taylor expansion
\cite{pottman09intinvariant}:
\begin{align*}
  \sigma_{X,r}(p) = \frac{\pi}{2}r^2 - \frac{\kappa(X,p)}{3}r^3 + O(r^4),
\end{align*}

where $\kappa(X,p)$ is the curvature of $X$ at point $p$. By isolating $\kappa$ we can define a curvature estimator

\begin{align}
  \tilde{\kappa}(p) \coloneqq \frac{3}{r^3}\left( \frac{\pi r^2}{2} - \sigma_{X,r}(p) \right),
  \label{eq:curvature_approximation}
\end{align}

Such an approximation is convenient as one can simply devise a multigrid convergent estimator for the area.

\begin{definition}	
  Given a digital shape $D \subset (h \mathbb{Z})^2$,  the area estimatir $\widehat{Area}(D,h)$ is defined as	
  \begin{align}
    \widehat{Area}(D,h) \coloneqq h^2\text{Card}\left( D \right).	
    \label{eq:digital_estimator_area}
  \end{align}
\end{definition}
It is well known that this area estimator is multigrid convergent
(e.g. see \cite{klette2000multigrid}).  In
\cite{coeurjolly13integral}, the authors combine the
approximation\eqref{eq:curvature_approximation} and digital estimator
\eqref{eq:digital_estimator_area} to define a multigrid convergent
estimator for the curvature.

\begin{definition}[Integral Invariant Curvature Estimator]
  Let $D \subset (h \mathbb{Z})^2$ a digital shape. The integral invariant curvature estimator is defined as
  \begin{align*}
    \hat{\kappa}_{r}(D,x,h) \coloneqq \frac{3}{r^3} \left( \frac{\pi r^2}{2} - \widehat{Area} \left( B_{r} ( x ) \cap D, h \right) \right).
    %% \hat{\kappa}_{r}(D,x,h) \coloneqq \frac{3}{r^3} \left( \frac{\pi r^2}{2} - \widehat{Area} \left( B_{r/h} ( \frac{1}{h} \cdot x ) \cap D, h \right) \right).
  \end{align*}
\end{definition}

This estimator is multigrid convergent with speed $O(h^\frac{1}{3})$
for radii chosen as $r=\Theta(h^\frac{1}{3})$.  This estimator is also
robust to noise and can be extended to estimate the mean curvature of
three dimensional shapes.

\subsection{Elastica energy estimator}

In the remaining of this paper we are going to be interested in the minimization of the elastica energy. Given a Euclidean shape $X$ with smooth enough boundary, the elastica is defined as
\begin{align}
  E(X) = \int_{\partial X}{(\alpha + \beta \kappa^2) ds}, \quad \text{for~} \alpha \ge 0, \beta \ge 0.
  \label{eq:elastica}
\end{align}

The digital version of elastica energy approaching the continuous elastica energy is defined as follows (it uses multigrid convergent estimators):
\begin{align}
	\hat{E}( D_h(X) ) = \sum_{\vec{e} \in \partial D_h(X)}{ \hat{s}(\vec{e})\left(\; \alpha + \beta \hat{\kappa}_{r}^2(D_h(X),\dot{\vec{e}},h) \; \right)},
	\label{eq:digital-energy}
\end{align}
where $\dot{\vec{e}}$ denotes the center of the edge $\vec{e}$. In the
expression above, we will substitute an arbitrary subset $Z$ of
$\mathbb{Z}^2$ to $D_h(X)$ since the continuous shape $X$ is unknown.
In the following we omit the grid step $h$ to simplify expressions
(or, putting it differently, we assume that the shape of interest is
rescaled by $1/h$ and we set $h=1$).

\section{Local combinatorial optimization}

The objectives of this section is to show both the potential of minimizing a purely digital elastica energy but also to underline the difficulties of using it in a global combinatorial optimization framework.

Given a digital shape $S^{(0)}$ we describe a process that generates a
sequence $S^{(i)}$ of shapes with non-increasing elastica energy. The
idea is to define a neighborhood of shapes $\mathcal{N}^{(i)}$ to the
shape $S^{(i)}$ and choose the element of $\mathcal{N}^{(i)}$ with
lowest energy.  The process is suited for the integral invariant
estimator but also for other curvature estimators, for example, MDCA
\cite{roussillon11mdca}. As a matter of fact, our experiments have
shown that either estimators induce similar results.

Let $S$ be a $2$-dimensional digital shape. We adopt the cellular-grid model to represent $S$, i.e., pixels and its lower dimensional counterparts, linels and pointels, are part of $S$. In particular, we denote by $\partial S$ the topological boundary of $S$, i.e., the connected sequence of linels such that for each linel we have one of its incident pixels in $S$ and the other not in $S$.

Let $d_{S}:\Omega \rightarrow \mathcal{R}$ be the Euclidean distance transformation with respect to shape $S$. The value $d_S(x)$ gives the Euclidean distance between $x$ and the closest pixel in $S$.

\begin{definition}[m-Ring Set]
Given a digital shape $S\in\Omega$, its distance transformation $d_S$ and natural numbers $m > 0$, the {\em $m$-ring set of $S$} is defined as
\begin{align*}
	\quad R_m(S) &:= R_m^-(S) \; \cup \; R_m^+(S) \\
	&:= \left\{ x \in \Omega \; | \; m-1 < d_S(x) \leq m \right\} \; \cup \;  \left\{ x \in \Omega \; | \; 	m-1 < d_{\overline{S}}(x) \leq m \right\}.
\end{align*}
\end{definition}

Consider the following set of neighbor candidates to $S$:
\begin{align*}
\mathcal{U}(S) = \{ D \; | D \subset R_1(S) \cup S \; \text{and} \; \text{$D$ is connected} \}.
\end{align*}

Such set can be extremely large and its complete exhaustion is prohibitively expensive.  Instead, we explore a subset of it with the help of $n$-glued curves.

An oriented closed curve $C$ is a closed connected sequence of linels with a well-defined interior. A segment of $C$ is a connected subsequence $c \in C$ of its linels.

\begin{figure}
\center
	\subfloat[\label{}]{%
	\includegraphics[scale=0.2]{images/local_search/definitions/model-regions-square.eps}
	}\hspace{40pt}%
	\subfloat[\label{}]{%
	\includegraphics[scale=0.2]{images/local_search/definitions/glued-curve.eps}
	}%	
	\caption{The blue pixels in figure (a) illustrates a $2$-ring set, while the green pixels its inner-pixel boundary. In figure (b) we highlight an element of set $\mathcal{G}_{11}(C_1,C_2)$. The curve segments of $C_1$ and $C_2$ are colored in red and green, while the junction linels in blue.}
\end{figure}

\begin{definition}[Glued Curve]
Given closed curves $C_1,C_2$ agreeing with some orientation $q$, a glued curve is a closed curve  $(c_1,\ell_1,c_2,\ell_2)$ with orientation $q$ and $c_1 \in C_1, c_2 \in C_2$. The linels $\ell_1,\ell_2$ are called junction linels.
\end{definition}

\begin{definition}[$n$-Glued Curve Set]
Given closed curves $C_1,C_2$ with same orientation, its set of $n$-glued curves is defined as
\begin{align*}
	\mathcal{G}_n(C_1,C_2) = \{ (c_1,\ell_1,c_2,\ell_2) \; | \; |c_2|=n \},
\end{align*}
\end{definition}

Let $S_O = ( S \cup R_1^+(S) ) $ and $S_I = ( S \setminus R_1^-(S) ) $, the neighborhood set to shape $S$ is defined as
\begin{align*}
	\mathcal{N}(S,N) = \bigcup_{1 \leq n \leq N} int \big( \mathcal{G}_{n}(\partial S_O, \partial S) \; \big) \cup int \big( \;  \; \mathcal{G}_{n}(\partial S, \partial S_I) \; \big),
\end{align*}

where $int(C)$ is the interior of the shape bounded by the close oriented curve $C$. Algorithm~\ref{alg:local-search} describes the local combinatorial process and Figure~\ref{fig:local-comb-square-results} presents the digital curve evolution when executing this algorithm for two different shapes with $N=20$.

\begin{algorithm}
 \SetKwData{It}{i}
 \SetKwData{MIt}{maxIt}
 \SetKwData{Tol}{tolerance}
 \SetKwData{Delta}{delta}
 \SetKwData{Best}{best} 
 \SetKwInOut{Input}{input}\SetKwInOut{Output}{output}

 \Input{A digital set $S$; the maximum length of glued curves $N$; the maximum number of iterations \MIt; and a stop condition \Tol}
 \BlankLine
 \Delta $\longleftarrow$ \Tol+1\;
 \While{ \It $<$ \MIt \bf{and} \Delta $>$ \Tol  }{
  	\For{$ X \in \mathcal{N}(S^{(i)},N) $}
	{
		\If{ $\hat{E}(X)$ $<$ $\hat{E}(X^\star)$ }
		{
			$X^\star \longleftarrow X$
		}
	}
	\It $\longleftarrow$ \It $+1$\;
	$S^{(i)} \longleftarrow X^\star$\;
	\Delta $\longleftarrow$ $\hat{E}(S^{(i-1)}) - \hat{E}(S^{(i)})$\;	
 }
 \label{alg:local-search} 
 \caption{Local combinatorial optimization for elastica minimization.}
\end{algorithm}

\begin{figure}[!ht]
\center
	\subfloat[h=1.0\label{}]{%
	\includegraphics[scale=0.125]{images/local_search/square/h1/summary-flow.eps}
	}%
	\hspace{10pt}
	\subfloat[h=0.5\label{}]{%
	\includegraphics[scale=0.125]{images/local_search/square/h05/summary-flow.eps}
	}%
	\hspace{10pt}
	\subfloat[h=1.0\label{}]{%
	\includegraphics[scale=0.125]{images/local_search/flower/h1/summary-flow.eps}
	}%
	\hspace{10pt}
	\subfloat[h=0.5\label{}]{%
	\includegraphics[scale=0.125]{images/local_search/flower/h05/summary-flow.eps}
	}%
		\caption{Local combinatorial optimization process results for the square and flower shapes. Shapes displayed at every $2$ iterations for the square and $7$ iterations for the flower.}	
		\label{fig:local-comb-square-results}
\end{figure}

The running time of algorithm \ref{alg:local-search} is summarized in
table \ref{tab:summary-local-comb-rtime}. All the experiments in this paper were executed on a five core $3.4Ghz$ cpu and the number of pixels in the triangle, square and flower shapes are respectively $841,1867,521$ for grid step $h=1.0$. Although its use in practical applications is limited, we
demonstrate that digital estimators are effective in their measurements
and the flows evolve as expected. We observe that it is a
complete digital approach, and we do not suffer from discretization
and rounding problems, a common issue in continuous models.
Furthermore we have checked that this approach works
indifferently with Integral Invariant curvature estimator and
Maximal Digital Circular Arc curvature estimator. So the convergence
of the digital curvature estimator seems to be the cornerstone to
get a digital curve behaving like a continuous elastica.  In the
next section, we explore a more efficient approach.

\begin{figure}
\begin{minipage}[b]{0.5\textwidth}
\center
\includegraphics[scale=0.35]{images/local_search/square-flower.eps}
\caption{Elastica computation along iterations of algorithm \ref{alg:local-search}}
\label{fig:plot-elastica-local-search}
\end{minipage}\hspace{40pt}%
\begin{minipage}[b]{0.45\textwidth}
\center
\captionsetup{type=table}
\begin{tabular}{|l|c|c|}
\hline
& $h=1.0$ & $h=0.5$\\
\hline
Square & 47s (5s/it) & 260s (12s/it)\\
\hline
Flower & 1235s (23s/it)  & 8516s (52s/it)\\
\hline
\end{tabular}
\caption{Running times for the local combinatorial optimization algorithm with $k=1,N=20$. Four threads were used.}
\label{tab:summary-local-comb-rtime}
\end{minipage}
\end{figure}

\section{Digital Curvature Flow}

%	Let $\Omega_C$ be the collection of connected digital sets in $\Omega$. Given a digital shape $S$, we wish to evolve it into a shape $S^\star$ similar to $S$ but with lower digital elastica energy. We recall the digital curvature estimator definition
%	
%\begin{align}
%	\hat{\kappa}^2(y) &= c_1\Big( c_2 - | B_r(y) \cap S | \Big)^2, 
%	\label{eq:curvature-estimator-pixels}
%\end{align}
%
%where $c_1=3/r^6$ and $c_2=\pi r^2/2$. Let $X,Y$ be the set of pixels and linels, respectively, in $\Omega$. We define the following binary model
%		
%\begin{align}
%\text{Minimize}_{x,y} & \sum_{y}{c_1y \Big(c_2 - \sum_{x_j \in B_r(y)}{x_j}\Big)^2	 } + F(S,X_{=1} \cup Y_{=1}) \nonumber \\
%\text{subject to} & \nonumber \\
%& (X_{=1} \cup Y_{=1}) \in \Omega_C, \; x,y \in \{0,1\}^\Omega
%\label{eq:general-binary-formulation}
%\end{align}
%
%
%where $F$ is some measure of similarity, e.g. distance, between initial shape $S$ and candidate solution. Such term is needed, otherwise the uninteresting empty set would be the optimal solution.
%
%Formulation \eqref{eq:general-binary-formulation} is of order four, binary and non-convex. These properties make it a hard optimization problem. We are going to explore an alternative energy, which is a simplification of the former.

%\subsection{A first model}
%
%We note that the elastica can be decreased by attenuating non-flat regions. The idea is to evolve a flow $S^{(i)}$ where $S^{(i+1)}$ is derived from the minimization of the sum of the squared curvature at $S^{(i)}$. We exchange solving a fourth order energy to solve multiple second order problems. We still have to guarantee that solutions are connected. We handle this issue by limiting the optimization region to a subset of $\Omega$, namely the inner pixel boundary of  $S^{(i)}$.

Given a digital shape $S \in \Omega$, the idea is to evolve a flow $S^{(i)}$ where $S^{(i+1)}$ is derived from the minimization of the sum of the squared curvature at $S^{(i)}$. In order to guarantee connectivity, we limit the optimization region to a subset of $\Omega$, namely the inner pixel boundary of  $S^{(i)}$. We also use the notation $| S |$ to denote the cardinal of a digital set $S$.

\subsection{Discrete variational model for discrete curve evolution}

We start by definition the optimization variables.
\begin{definition}[Inner pixel boundary]
Given a digital shape $S$ embedded in a domain $\Omega$, we define its inner pixel boundary set $O(S)$ as
\begin{align*}
	O(S) = \left\{ \: x \; | \; x \in S, |\mathcal{N}_4(x) \cap S|<4 \: \right\},
\end{align*}
where $\mathcal{N}_4(x)$ denotes the $4$-adjacent neighbor set of $x$ (without $x$).
\end{definition}

In other words, each flow iteration decides which pixels in the inner boundary are to be removed and which are to be kept. To simplify notation, we denote the optimization region of $S^{(i)}$ as $O^{(i)}$, and the foreground set as $F^{(i)} = S^{(i)} \setminus O^{(i)}$. We recall the definition of our digital curvature estimator :
\begin{align}
	\hat{\kappa}^2(y) &= c_1\Big( c_2 - | B_r(y) \cap S | \Big)^2, 
	\label{eq:curvature-estimator-pixels}
\end{align}
where $c_1=3/r^6$ and $c_2=\pi r^2/2$.

We define $O_{r}^{(i)}(y) := O^{(i)} \cap B_r(y)$ and an analogous definition holds for $F_{r}^{(i)}(y)$. Expanding \eqref{eq:curvature-estimator-pixels}, we get 
\begin{align*}
  \hat{\kappa}^2(y) &= c_1\Big( c_2 - \sum_{x_j \in B_r(y)} \big( {x_j} + |F_{r}^{(i)}(y)| \big) \Big)^2 \\
   &= c_1 \cdot \Big( C + 2\left( |F_{r}^{(i)}(y)| - c_2 \right) \hspace{-2mm}\sum_{x_j \in O_{r}^{(i)}(y)}\hspace{-2mm}{x_j} + \hspace{-2mm}\sum_{x_j \in O_{r}^{(i)}(y)}\hspace{-2mm}{x_j^2} + \hspace{-2mm}\sum_{ \substack{x_j,x_k \in O_{r}^{(i)}(p) \\ j<k} }\hspace{-2mm}{2x_jx_k}  \Big),
\end{align*}
where $C=c_2^2 - 2c_2 \cdot |F_{r}^{(i)}(y)| + |F_{r}^{(i)}(y)|^2$ is a constant. In
order to be symmetric, the curvature at some linel $y$ is computed on
$R_m(S)$.\todo{Que veux-tu dire?} By ignoring constants and multiplication factors and using
the binary character of the variables, we define the following family
of energies for given parameters $\alpha,\beta \geq 0$.
\begin{align}
  E_m(X,S) =& \sum_{x \in X}{\alpha s(x)} \nonumber \\ 
  & + \sum_{y \in R_m(S)}{ \beta \Big( { (1/2+ |F_{r}^{(i)}(y)|-c_2) \cdot \sum_{x_j \in O_{r}^{(i)}(y)}{x_j} } + \sum_{ \substack{x_j,x_k \in O_{r}^{(i)}(y) \\ j<k} }{x_jx_k} \Big) } \nonumber \\
  & + \sum_{x \in X}{\gamma g(S,x)}
  \label{eq:energy-family}
\end{align}
\todo{Que vaux $X$ ici ?}	
where $g(S,x)$ denotes a similarity term as distance to initial shape $S$ or data fidelity term and $s(x)$ denotes a length penalization term. Each choice of $m$ generates a different flow, which is generaly described in the Digital Curve Evolution (DCE) algorithm \ref{alg:evolution-model}.

\begin{algorithm}[H]
 \SetKwData{It}{i}
 \SetKwData{MIt}{maxIt}
 \SetKwData{Delta}{delta}
 \SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
 \SetKwComment{comment}{//}{}

 \Input{A digital set $S$; The ring number $m$; Length($\alpha$), curvature($\beta$) and similarity($\gamma$) coefficients; the maximum number of iterations \MIt;}
 \BlankLine
 $S^{(i)} \longleftarrow S$\;
 \While{ \It $<$ \MIt  }{ 	
	\comment{Expansion mode}
	\If{ \It is odd }{	 
	 	$X^{(i)} \longleftarrow \argmin_X E_m(X,\overline{S^{(i)}})$\;
 		$S^{(i)} \longleftarrow F^{(i)} + \overline{X^{(i)}}$\;
 		$S^{(i)} \longleftarrow \overline{S^{(i)}}$\;	 	
 	}
	\comment{Shrinking mode} 	
 	\Else{	
	 	$X^{(i)} \longleftarrow \argmin_X E_m(X,S^{(i)})$\; 	
 		$S^{(i)} \longleftarrow F^{(i)} + \overline{X^{(i)}}$\;
 	}

	\It $\longleftarrow$ \It $+1$\;

 }
 \label{alg:evolution-model} 
 \caption{Digital curvature evolution algorithm (DCE).}
\end{algorithm}

Recall that the integral invariant estimator approaches curvature by
computing the difference between half of the area of a chosen ball and
the area of the intersection of this ball with the shape.  In
particular, regions of positive curvature have fewer pixels in their
intersection set than on its complement wrt the estimation ball. This
implies that variables in such regions are labeled one, as the
unbalance grows otherwise. We attenuate curvature if we shift the
center of the estimation ball towards the interior of the shape, which
means removing the labeled one pixels. That is why we take the
complement of the optimization solution.

The same reasoning applies for non-convex parts. Indeed, concave
regions are convex in the shape complement. In the expansion mode we
apply the same reasoning on the image complement, and by doing this we
are able to handle concavities. It is called expansion mode because
the optimization region, in this case, is the outer pixel boundary of
the original shape. Table~\ref{tab:flow-summary} sums up these
arguments.

Length and similarity terms should be properly defined in order to
comply with the complement step of the DCE algorithm. The length
penalization is defined as
\begin{align}
  s(x)=\sum_{x_j \in \mathcal{N}_4(x)}{ t(x_j) }, \quad \text{where } t(x_j) = \left\{\begin{array}{ll}
  (x-x_j)^2, & \text{if } x_j \in O_{r}^{(i)}\\
  (x-0), & \text{if } x_j \in F_{r}^{(i)}\\
  (x-1), & \text{otherwise }
  \end{array}\right.
  \label{eq:length-penalization}
\end{align}

We do not use similarity terms in this section, thus we postpone the
definition of such terms until the description of how DCE can be used
in an image segmentation framework.

\begin{table}
  \center
  \begin{tabular}{|c|c|c|c|} \hline
    shrink mode &    $\kappa \gg 0$ & $\kappa \geq 0$ &  $\kappa < 0$ \\ \hline
    $X$ & $x_k=1$ & $x_k \in \{0,1\}$ & $x_k=0$ \\ \hline
    $S^{(i+1)} \leftarrow S^{(i)} \setminus X$ & eroded & prob. eroded & unchanged  \\ \hline \hline
    expansion mode &    $\bar{\kappa} \gg 0$ & $\bar{\kappa} \geq 0$ & $\bar{\kappa} < 0$ \\ \hline
    $\bar{X}$ & $\bar{x}_k=1$ & $\bar{x}_k \in \{0,1\}$ & $\bar{x}_k=0$ \\ \hline
    $S^{(i+1)} \leftarrow \overline{\bar{S}^{(i)} \setminus \bar{X}}$ & dilated & prob. dilated & unchanged \\ \hline 
  \end{tabular}

  \label{tab:flow-summary}	  
  \caption{  Since the curvature is negated when reversing the curve (i.e. $\bar{\kappa}=-\kappa$), this process can only shrink  convex parts in shrink mode and expand concave parts in expansion mode.}

\end{table}

In figure \ref{fig:m1-square-flow} we see some results for the DCE
algorithm with $m=1$. We observe a global movement towards roundness,
but with several artifacts. We minimize the effects of a jaggy
boundary by setting $\alpha > 0$. Nonetheless, a higher estimation
ball radius creates unstable shapes. In fact, the estimator is very
sensitive in regions of low squared curvature, and it is precisely in
those regions that spurious pixels are created.

\begin{figure}[!ht]
\center
\begin{minipage}[b]{0.33\textwidth}
	\subfloat[$r=3, \alpha=0$\label{}]{%
	\includegraphics[scale=0.2]{images/flow/length-radius-effect/triangle-r3-nolength/summary_flow.eps}
	}%
\end{minipage}%
\begin{minipage}[b]{0.33\textwidth}
	\subfloat[$r=3, \alpha=0.15$\label{}]{%
	\includegraphics[scale=0.2]{images/flow/length-radius-effect/triangle-r3-length0.15/summary_flow.eps}
	}%
\end{minipage}%
\begin{minipage}[b]{0.33\textwidth}
	\subfloat[$r=5, \alpha=0.15$\label{}]{%
	\includegraphics[scale=0.2]{images/flow/length-radius-effect/triangle-r5/summary_flow.eps}
	}%
\end{minipage}%
\caption{The algorithm is very sensitive to the little variations of the estimator, which are particularly important in regions of low squared curvature. Artifacts are somewhat reduced with a length penalization but increases if we use a higher ball radius. }
\label{fig:m1-square-flow}
\end{figure}

\subsection{A more stable model.}
In the previous section we noticed that the algorithm produces shapes
with many artifacts due to the small uncertainties of the estimator
along regions of low squared curvature. We argue that, evaluating the
estimation ball along farther ring sets we avoid those sensitive areas
by focusing the optimization process only on regions with highest
squared curvature value.

%%\jaco{Motivation in digital geometry of why it makes sense to compute things farther.}

\begin{figure}[!ht]
\center
\center
\begin{minipage}[b]{0.33\textwidth}
	\subfloat[$r=5, m=1$\label{}]{%
	\includegraphics[scale=0.2]{images/flow/farther-rings/square-r5-l1/summary_flow.eps}
	}%
\end{minipage}%
\begin{minipage}[b]{0.33\textwidth}
	\subfloat[$r=5, m=2$\label{}]{%
	\includegraphics[scale=0.2]{images/flow/farther-rings/square-r5-l2/summary_flow.eps}
	}%
\end{minipage}%
\begin{minipage}[b]{0.33\textwidth}
	\subfloat[$r=5, m=3$\label{}]{%
	\includegraphics[scale=0.2]{images/flow/farther-rings/square-r5-l3/summary_flow.eps}
	}%
\end{minipage}%
\caption{By positioning the estimation ball on farther rings, we minimize artifacts creation. \label{fig:mx-square-flow}}
\end{figure}

In our experiments, the best results are obtained by executing DCE
algorithm with $m$ equal to $r$, where $r$ is the estimation ball
radius (see figures \ref{fig:mx-square-flow},
\ref{fig:mx-flow-gs-radius-effect} ). In plot
\ref{fig:mx-elastica-plots}, we observe how the elastica energy evolves along
the iterations. If the radius is too large, the elastica energy may increase after some steps. That is what happens for the
triangle, in which the flow converges to a single point.

\begin{figure}[!ht]
\center				
		\setcounter{subfigure}{-3}
		\subfloat[$r=3,h=0.5$]{%
		\subfloat{%
		\includegraphics[scale=0.2]{images/flow/grid-radius-effect/triangle/r3-h0.5/summary_flow.eps}
		}%
		\hspace{15pt}
		\subfloat{%
		\includegraphics[scale=0.15]{images/flow/grid-radius-effect/square/r3-h0.5/summary_flow.eps}}%
		\hspace{15pt}
		\subfloat{%
\includegraphics[scale=0.2]{images/flow/grid-radius-effect/flower/r3-h0.5/summary_flow.eps}}%
		}

		\setcounter{subfigure}{-2}
		\subfloat[$r=5,h=0.5$]{%
		\subfloat{%
		\includegraphics[scale=0.2]{images/flow/grid-radius-effect/triangle/r5-h0.5/summary_flow.eps}
		}%1
		\hspace{15pt}
		\subfloat{%
		\includegraphics[scale=0.15]{images/flow/grid-radius-effect/square/r5-h0.5/summary_flow.eps}}%
		\hspace{15pt}
		\subfloat{%
\includegraphics[scale=0.2]{images/flow/grid-radius-effect/flower/r5-h0.5/summary_flow.eps}}%
		}				
\caption{The choice of radius impacts the flow. In the figures, the flow ceases to evolve for all shapes  when $r=3$ (a). In figure (b), for $r=5$, the triangle evolves to a single point, while the others stop  in an intermediate shape, as in (a). }
\label{fig:mx-flow-gs-radius-effect}
\end{figure}

\begin{figure}[!ht]
\center
\includegraphics[scale=0.5]{images/flow/elastica-energy-plot/r5h05.eps}
\caption{Elastica computation along the iterations for different shapes. If radius is too large, elastica energy may increase after a certain number of iterations. }
\label{fig:mx-elastica-plots}
\end{figure}

\begin{figure}[!ht]
\center
\subfloat[]{%
	\includegraphics[scale=0.5]{images/flow/faster-high-curvature/summary_flow.eps}}\\%
\subfloat[]{%
		\includegraphics[scale=0.25]{images/flow/fill-holes/summary_flow.eps}}%%1
\label{fig:mx-speed-variation-hole-filling}
\caption{High curvature regions evolves faster than lower ones (a). The flow can handle topological changes (b). }
\end{figure}

\subsection{Optimization method}

Let $f$ be a function of $n$ binary variables with unary and pairwise terms, i.e.

\begin{align*}
f(y_1,\cdots, y_n) = \sum_{j}{f_j(y_j)} + \sum_{j < k}{f_{j,k}(y_j,y_k)}.
\end{align*}

Function $f$ is submodular if and only if the following inequality holds for each pairwise term $f_{j,k}$ \cite{kolmogorov04whatenergies}:
\begin{align*}
  \quad f_{j,k}(0,0) + f_{j,k}(1,1) \leq f_{j,k}(0,1) + f_{j,k}(1,0).
\end{align*}

Energy $E_m$ is non-submodular and optimizing it is a difficult
problem, which constrains us to use heuristics and approximation
algorithms. The QPBO method \cite{rother07qpbo} transforms the
original problem in a max-flow/min-cut formulation and returns a full
optimal labeling for submodular energies. For non-submodular energies
the method is guaranteed to return a partial labeling with the
property that the set of labeled variables is part of an optimal
solution. That property is called partial optimality.

In practice, QPBO can leave many pixels unlabeled. There exist two
extensions of QPBO that alleviate this limitation: QPBOI (improve) and
QPBOP (probe). The first is an approximation method that is guaranteed
to not increase the energy, but we lost the property of partial
optimality. The second is an exact method which is reported to label
more variables than QPBO.

The percentage of unlabeled pixels by QPBOP for $E_1$ is quite high,
but the percentage decreases to zero as we set $m$ equal to
$r$. Therefore, we are more confident to take the solution for values
of $m$ close to $r$. However, the way it varies across $m$ values
differs from shape to shape, as is illustrated in figure
\ref{fig:unlabeled-versus-iterations}. We also noticed that, for
$m=r$, all the pixels were labeled. Perhaps this means that our energy
is submodular in this case, but this remains to be proved.

We have used QPBOI to solve $E_m$. Naturally, in the case where all
pixels are labeled by QPBOP, QPBOI returns the same labeling as QPBOP.

\begin{figure}[!htp]
\center
\begin{minipage}[b]{0.5\textwidth}
\subfloat[]{ \includegraphics[scale=0.35]{images/optimization/unlabeled-iterations/radius-3/plot-model-square-concavities-probe.eps}}\\%
\subfloat[]{ \includegraphics[scale=0.35]{images/optimization/unlabeled-iterations/radius-5/plot-model-square-concavities-probe.eps}}\\%
\subfloat[]{ \includegraphics[scale=0.35]{images/optimization/unlabeled-iterations/radius-7/plot-model-square-concavities-probe.eps}}%
\end{minipage}%
\begin{minipage}[b]{0.5\textwidth}
\subfloat[]{ \includegraphics[scale=0.35]{images/optimization/unlabeled-iterations/radius-3/plot-model-flower-concavities-probe.eps}}\\%
\subfloat[]{ \includegraphics[scale=0.35]{images/optimization/unlabeled-iterations/radius-5/plot-model-flower-concavities-probe.eps}}\\%
\subfloat[]{ \includegraphics[scale=0.35]{images/optimization/unlabeled-iterations/radius-7/plot-model-flower-concavities-probe.eps}}%
\end{minipage}
\caption{For each plot, we first produce shapes $\left\{ S^{(i)} \right\}$ executing DCE with $m=r$. Then, for each shape in $\left\{ S^{(i)} \right\}$, we execute one iteration of DCE for different values of $m$ and we count the unlabeled pixels. The number of unlabeled pixels by QPBOP remains high for lower values of $m$, and goes to zero when $m=r$. We observe the same behaviour for different radius values.}
\label{fig:unlabeled-versus-iterations}
\end{figure}

\begin{figure}
\center
\includegraphics[scale=0.5]{images/optimization/pairwise-ratio/plot-pairwiseratio-lowerHigher-concavities-probe.eps}
\caption{We plot the ratio of pairwise terms among all $\binom{|X^{(i)}|}{2}$ combinations. The highest ring has rougly half the number of pairwise terms  than the lowest ring.\label{fig:ratio-pairwise-terms}}
\end{figure}

\todo{You must comment figure~\ref{fig:ratio-pairwise-terms} in the text.}

\section{Application to image segmentation}

We present an application of our digital curve evolution algorithm to supervised image segmentation. The DCE will act as a contour correction method. Here we are going to use a data fidelity term in order to characterize the object of interest. Given foreground and background seeds selected by the user, we derive mixed gaussian distributions  of color intensities $G_f$ and $G_b$, and we define the data fidelity term as

\begin{align}
  g(y) = -(1-y)\log{G_f(I(y))} - y\log{G_b(I(y))}.
  \label{eq:data-fidelity}
\end{align}

We use the DCE algorithm to regularize an initial contour outputed by some segmentation algorithm or delineated by the user. In this application, the similarity term of the DCE
is set to the data fidelity term \eqref{eq:data-fidelity}.

\begin{algorithm}[H]
 \SetKwData{It}{i}
 \SetKwData{MIt}{maxIt}
 \SetKwData{Tol}{tolerance}
 \SetKwData{Delta}{delta}
 \SetKwInOut{Input}{input}\SetKwInOut{Output}{output}
 \SetKwComment{comment}{//}{}

 \Input{An image $I$; seed mask $M$; the estimation ball radius $r$; data $(\gamma)$, length $(\alpha)$ and squared curvature $(\beta)$ weights; initial dilation $d$; stop condition value \Tol; the maximum number of iterations \MIt;}
 \BlankLine

 $S \longleftarrow$ GrabCut($I,M$)\;
 $S^{(0)} \longleftarrow $ dilate($S$,$d$)\; 
 \Delta $\longleftarrow +\infty$\;
 $i \longleftarrow 0$\;
 \While{ \It $<$ \MIt \bf{and} \Delta $>$ \Tol  }{ 	
 	$S^{(i+1)} \longleftarrow $ DCE($S^{(i)},\gamma,\alpha,\beta$)\;
 	\Delta $\longleftarrow |S^{(i)} - S^{(i+1)}|$\;

	\It $\longleftarrow$ \It $+1$\;

 }
 \label{alg:contour-correction} 
 \caption{Contour correction algorithm. \todo{Critère d'arrêt basé sur un nombre de pixels changés !?}}
\end{algorithm}

The algorithm can be initialized by a collection of compact sets, or with the result of a third-party segmentation algorithm, as GrabCut \cite{rother04grabcut}. We include an additional parameter $d$ that dilates the initial sets using a square of side one before executing the flow.

\begin{figure}
\center
\begin{tabular}{ccc}
Seeds & $(\alpha=0, \beta=0.5)$ & $(\alpha=0,\beta=1)$ \\
 	\includegraphics[scale=0.25]{images/segmentation/bc/coala/seeds.png} & 
	\includegraphics[scale=0.25]{images/segmentation/bc/coala/r3/lg0_sq05_dt1_it50.png} & 
	\includegraphics[scale=0.25]{images/segmentation/bc/coala/r3/lg0_sq1_dt1_it50.png} \\

 	\includegraphics[scale=0.25]{images/segmentation/bc/coala/lg0_sq0_dt1_it20.png} & 
	\includegraphics[scale=0.25]{images/segmentation/bc/coala/r3/lg1_sq0_dt1_it50.png} &
	\includegraphics[scale=0.25]{images/segmentation/bc/coala/r3/lg2_sq0_dt1_it50.png} \\

	GrabCut & $(\alpha=0.5, \beta=0)$ & $(\alpha=1, \beta=0)$
\end{tabular}	
\caption{Comparison of squared curvature regularization (first row) and length regularization (second row). }
\label{fig:parameters-influence}
\end{figure}

\begin{figure}
	\center
	\begin{tabular}{ccc}
		GrabCut & Contour Correction & Schoenemann \\
		& $(r=5, \alpha=0.1, \beta=1.0, \gamma=3.0$) & $(\alpha=0.1, \beta=1.0$)\\
		\includegraphics[scale=0.2]{images/segmentation/bc/tiger1/gc-seg.png} &
		\includegraphics[scale=0.2]{images/segmentation/bc/tiger1/corrected-seg.png} &					\includegraphics[scale=0.2]{images/segmentation/schoenemann/tiger1/tiger1-seg.png}\\									
		\includegraphics[scale=0.2]{images/segmentation/bc/snake/gc-seg.png} &
		\includegraphics[scale=0.2]{images/segmentation/bc/snake/corrected-seg.png} &
		\includegraphics[scale=0.2]{images/segmentation/schoenemann/snake/snake-seg.png}\\						
		\includegraphics[scale=0.2]{images/segmentation/bc/man/gc-seg.png} &
		\includegraphics[scale=0.2]{images/segmentation/bc/man/corrected-seg.png} &
		\includegraphics[scale=0.2]{images/segmentation/schoenemann/man/man-seg.png}\\		
		\includegraphics[scale=0.2]{images/segmentation/bc/vase/gc-seg.png} &
		\includegraphics[scale=0.2]{images/segmentation/bc/vase/corrected-seg.png} &					\includegraphics[scale=0.2]{images/segmentation/schoenemann/vase/vase-seg.png}		
	\end{tabular}
	\caption{The proposed method regularizes grabcut contours and returns meaningful results. We can observe the completion feature of curvature in the second row, and we don't suffer from oversegmentation issues as Schoenemann's method. However, our flow may stop in a local optima as in the fourth row, while Schoenemann's is able to extrapolate such solutions.}
	\label{fig:segmentation-results}	
\end{figure}

\begin{figure}
	\center
	\begin{tabular}{ccc}
		GrabCut & Contour Correction & Schoenemann \\
		& $(r=5, \alpha=0.1, \beta=1.0, \gamma=3.0$) & $(\alpha=0.1, \beta=1.0$)\\
		\includegraphics[scale=0.2]{images/segmentation/bc/airplane2/gc-seg.png} &
		\includegraphics[scale=0.2]{images/segmentation/bc/airplane2/corrected-seg.png} &					\includegraphics[scale=0.2]{images/segmentation/schoenemann/airplane2/airplane2-seg.png}\\									
		\includegraphics[scale=0.2]{images/segmentation/bc/bird/gc-seg.png} &
		\includegraphics[scale=0.2]{images/segmentation/bc/bird/corrected-seg.png} &
		\includegraphics[scale=0.2]{images/segmentation/schoenemann/bird/bird-seg.png}\\						
		\includegraphics[scale=0.2]{images/segmentation/bc/camel/gc-seg.png} &
		\includegraphics[scale=0.2]{images/segmentation/bc/camel/corrected-seg.png} &
		\includegraphics[scale=0.2]{images/segmentation/schoenemann/camel/camel-seg.png}\\		
		\includegraphics[scale=0.2]{images/segmentation/bc/rock/gc-seg.png} &
		\includegraphics[scale=0.2]{images/segmentation/bc/rock/corrected-seg.png} &					\includegraphics[scale=0.2]{images/segmentation/schoenemann/rock/rock-seg.png}\\
		\includegraphics[scale=0.2]{images/segmentation/bc/giraffes/gc-seg.png} &
		\includegraphics[scale=0.2]{images/segmentation/bc/giraffes/corrected-seg.png} &					\includegraphics[scale=0.2]{images/segmentation/schoenemann/giraffes/giraffes-seg.png}\\
		\includegraphics[scale=0.2]{images/segmentation/bc/canguru/gc-seg.png} &
		\includegraphics[scale=0.2]{images/segmentation/bc/canguru/corrected-seg.png} &					\includegraphics[scale=0.2]{images/segmentation/schoenemann/canguru/canguru-seg.png}\\		
		\includegraphics[scale=0.2]{images/segmentation/bc/coral/gc-seg.png} &
		\includegraphics[scale=0.2]{images/segmentation/bc/coral/corrected-seg.png} &					\includegraphics[scale=0.2]{images/segmentation/schoenemann/coral/coral-seg.png}\\

	\end{tabular}
	\caption{}
	\label{fig:more-segmentation-results}	
\end{figure}

We evaluate our method using the BSD300 database \cite{martinFTM01berkeley}. All images contains the same number of pixels, the resolution being 321x481 in portrait mode. We compare the results of our method with segmentations given by GrabCut and Schoenemanns's method \cite{schoenemann09linear}. We report an average of $3s$ per flow iteration, and an average of $30$ iterations per image. While GrabCut executes in less than one second, Schoenemann's method may take several hours to complete.

In figure \ref{fig:parameters-influence} we can observe the results of a curvature regularization in comparison with a pure length regularization, and figures \ref{fig:segmentation-results} and \ref{fig:more-segmentation-results} show some segmentation results.

\todo{You must comment on the results.}

\section{Conclusion}\label{sec:conclusion}

We have studied in depth several digital curve evolution models based
on the elastica energy and we have presented an application of one of
them to image segmentation. The processes we have described are
completely digital, and do not suffer from issues that typically
arises in models that passes through a discretization stage, as
rounding. Moreover, the model can handle changes in topology and its
results are competitive with similar approaches while achieving
reasonable running times.

Future developments of this work may include automatization, no more
dependence on seeds selected by the user and automatic choice of ball
estimation radius based on the reach of the shape. One can also think
to extend the DCE algorithm to $3$d, as the integral invariant
estimator preserves its properties in that space. In future works, a
denoising application may be derived by running the flow on the $3$d
shape with data fidelity defined by image intensities or by distance
to initial position.

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{jmiv}

\end{document}

### 2019-07-07 jmiv.tex
changes relecture HT

@@
 \begin{abstract}
-
+  \HT{Geometric priors have been shown to be useful in image segmentation to regularize results. For example, the classical
+    Mumford-Shah functional uses regions perimeter as prior. This has inspired much research in the last few decades,
+    with classical approaches like the Rudin-Osher-Fatemi and most graph-cut formulations, which all use a weighted or
+    binary perimeter prior. It has been observed that this prior is not suitable in many applications, for example for
+    segmenting thin objects or some textures, which may have high perimeter/surface ratio. Mumford observed that an
+    interesting prior for natural objects is the Euler Elastical model, which involves the squared curvature. In other
+    areas of science, researchers have noticed that some physical binarization processes, like emulsion unmixing can be
+    well-approximated by curvature-related flow like the Willmore flow. 
+    However, curvature-related flows are not easy to compute because curvature is difficult to estimate accurately, and the
+    underlying optimisation processes are not convex. In this article, we propose to formulate a digital flow that
+    approximates a curvature-related flow using a multigrid-convergent curvature estimator, within a discrete
+    variational framework. We also present an application of this model as a post-processing step in a segmentation
+    framework.}
 \keywords{Multigrid convergence  \and Digital estimator \and Curvature \and Shape Optimization \and Image Segmentation.}

### 2019-07-07 jmiv.tex
changes relecture HT

@@
 \setcounter{footnote}{0}
-\section{Introduction \todo{(To be extended)}}
+\section{Introduction} %% \todo{(To be extended)}}
 
@@
 regularizer is also present in the second-order regularizer
-of the \HT{original} snake model \cite{kass1988snakes}. \HT{However,
-  optimizing models with the Elastica energy is difficult in practice, as it
-  is not convex}.
-
-One of the first successful uses of curvature in image processing is
-the inpainting algorithm described in \cite{masnou98inpainting}\HT{, where
-authors} evaluate the elastica energy along the level lines of a
-simply-connected image to reconstruct its occluded parts. The
-non-intersection property of level lines \HT{induces} the construction of an
-efficient dynamic programming algorithm. \HT{However, }  the curvature energy is \HT{only} coarsely approximated. 
-\cite{chan02elasticainpainting} \HT{is} another geometric inpainting method
-involving elastica \HT{optimized with level-sets}.
-
-In image segmentation, Zehiry and Grady have shown that injecting
-curvature as a regularizer \HT{can help} recover thin and elongated objects
-\cite{zehiry10fast}. Similarly Schoenemann {\em et al.}
-\cite{schoenemann09linear} have considered the elastica energy in
-their ratio-based image segmentation approach. Their global
-optimization framework shows the considerable interest of using such
-regularizer in common binary image segmentation tasks. However the
-time complexity of their algorithm \HT{is prohibitive,} even if
-curvature is \HT{again} coarsely approximated.
+of the \HT{original} snake model \cite{kass1988snakes}. \HT{Similarly,
+an explicit curvature term was often employed in early level-set methods,
+like~\cite{malladi1995image,malladi1995shape,ballester01filljoint} for segmentation or inpainting,}
+\HT{However, Casselles {\em et al.} in~\cite{casseles97geodesic} observed that these
+terms were not geometric, in the sense that they depended on the discretization}.
+
+The use of curvature for surface regularization was studied in~\cite{bobenko2005discrete},
+although results look promising, authors used an inexact linearized version of the
+square curvature at every step.
+
+One of the first successful uses of \HT{geometric squared} curvature in image processing is the inpainting algorithm
+described in \cite{masnou98inpainting}\HT{, where authors} evaluate the elastica energy along the level lines of a
+simply-connected image to reconstruct its occluded parts. The non-intersection property of level lines \HT{induces} the
+construction of an efficient dynamic programming algorithm. \HT{However, } the curvature energy is \HT{only} coarsely
+approximated.  \cite{chan02elasticainpainting} \HT{is} another geometric inpainting method involving elastica
+\HT{optimized with level-sets}.
+
+In image segmentation, Zehiry and Grady have shown that injecting curvature as a regularizer \HT{can help} recover thin
+and elongated objects \cite{zehiry10fast}. Similarly Schoenemann {\em et al.}  \cite{schoenemann09linear} have
+considered the elastica energy in their ratio-based image segmentation approach. In~\cite{schoenemann2011elastic},
+Schoenemann~{\em et al.} extend ratio-cut approaches to segmentation with a curvature term. Their global optimization
+framework shows the considerable \HT{advantages} of using such regularizer in common binary image segmentation tasks.
+However the time complexity of their algorithm \HT{is prohibitive,} even if curvature is \HT{again} coarsely
+approximated.  In more recent work, Lim {\em et al.} propose an edge-weighted Willmore-like flow to segment
+vertebra~\cite{lim2012introducing} using a level-set formulation.  They observe improved results compared
+to~\cite{casseles97geodesic} and other perimeter-based priors, but observe that a shape prior and a close-enough
+solution must also be provided to achieve good results.
 
@@
 
-  Quote \cite{schoenemann2011elastic} for the interest of using curvature energy when segmenting regions in gradient-based data fitting term.
+%  Quote \cite{schoenemann2011elastic} for the interest of using curvature energy when segmenting regions in gradient-based data fitting term.
 It can look for global optimum within a graph representation of the image.
@@
 
-\item{\textbf{Classical work on elastica and Wilmore flow in imaging}}
-  \begin{itemize}
-  \item{Level lines based disocclusion \cite{masnou98inpainting} }	
-  \item{Filling-In by Joint Interpolation of Vector Fields and Gray Levels \cite{ballester01filljoint} }
-  \item{Eulers Elastica and Curvature Based Inpaintings \cite{chan02elasticainpainting} }
-  \item{Discrete willmore flow \cite{bobenko2005discrete}}
-  \item{Introducing Willmore flow into level set segmentation of spinal vertebrae \cite{lim2012introducing}}	
-  \end{itemize}
-
-\item{\textbf{Level-sets}}
-  \begin{itemize}
-  \item{Image processing via level set curvature flow \cite{malladi1995image} }
-  \item{Shape Modeling with Front Propagation: A Level Set Approach \cite{malladi1995shape} }	
-	\end{itemize}
+%%\item{\textbf{Classical work on elastica and Wilmore flow in imaging}}
+  %%\begin{itemize}
+  %% \item{Level lines based disocclusion \cite{masnou98inpainting} }	%% DONE
+ %%  \item{Filling-In by Joint Interpolation of Vector Fields and Gray Levels \cite{ballester01filljoint} } %% DONE
+ %%  \item{Eulers Elastica and Curvature Based Inpaintings \cite{chan02elasticainpainting} } %% DONE
+ %% \item{Discrete willmore flow \cite{bobenko2005discrete}}
+ %%  \item{Introducing Willmore flow into level set segmentation of spinal vertebrae \cite{lim2012introducing}}	 %%% DONE
+ %% \end{itemize}
+
+%%\item{\textbf{Level-sets}}
+ %% \begin{itemize}
+  %% \item{Image processing via level set curvature flow \cite{malladi1995image} } %% DONE
+  %% \item{Shape Modeling with Front Propagation: A Level Set Approach \cite{malladi1995shape} }	%% DONE
+%%	\end{itemize}
 
@@
   \begin{itemize}
-  \item{A convex lower semicontinuous approximation of Eulers elastica energy \cite{bredies15convex}}				\item{Introducing Total Curvature for Image Processing \cite{goldluecke11totalcurvature}}
+  \item{A convex lower semicontinuous approximation of Eulers elastica energy \cite{bredies15convex}}
+  \item{Introducing Total Curvature for Image Processing \cite{goldluecke11totalcurvature}}
   \end{itemize}
@@
   \item{A Fast Algorithm for Euler's Elastica Model Using Augmented Lagrangian Method \cite{tai11elastica} }		
-  \item{The elastic ratio: Introducing curvature into ratio-based image segmentation \cite{schoenemann2011elastic} }		
+  %%\item{The elastic ratio: Introducing curvature into ratio-based image segmentation \cite{schoenemann2011elastic}
+  %%}		%% DONE
   \item{Curvature Regularization for Curves and Surfaces in a Global Optimization Framework \cite{strandmark11globalframework} }

### 2019-07-07 jmiv.tex
Suggestions acceptance and corrections

@@
 \usepackage[export]{adjustbox}
-\usepackage{xcolor}
+\usepackage[dvipsnames]{xcolor}
 
@@
 \newcommand{\HT}[1]{{\textcolor{violet}{#1}}}
+\newcommand{\daniel}[1]{\textcolor{NavyBlue}{#1}}
 
@@
 %
-\title{A\HT{n Elastica-driven} Digital Curve Evolution Model for Image Segmentation\thanks{This  work has  been  partially  funded by CoMeDiC ANR-15-CE40-0006 research grant.}}
+\title{An Elastica-driven Digital Curve Evolution Model for Image Segmentation\thanks{This  work has  been  partially  funded by CoMeDiC ANR-15-CE40-0006 research grant.}}
   \titlerunning{Digital Curve Evolution by Elastica Energy}
@@
 \begin{abstract}
-  \HT{Geometric priors have been shown to be useful in image segmentation to regularize results. For example, the classical
+  Geometric priors have been shown to be useful in image segmentation to regularize results. For example, the classical
     Mumford-Shah functional uses regions perimeter as prior. This has inspired much research in the last few decades,
@@
     variational framework. We also present an application of this model as a post-processing step in a segmentation
-    framework.}
+    framework.
 \keywords{Multigrid convergence  \and Digital estimator \and Curvature \and Shape Optimization \and Image Segmentation.}
@@
 low-level image analysis, especially when little prior information is
-known about the shape of interest. Length penalization is a \HT{well-behaved,} general
-purpose regularizer and \HT{many} models \HT{in the literature} make use
+known about the shape of interest. Length penalization is a well-behaved, general
+purpose regularizer and many models in the literature make use
 of it, from active contours \cite{casseles97geodesic} to level-set
@@
 graph-based variational models have been particularly succesfull to
-incorporate length penalization as a penalizer, while keeping the
-ability to extract \HT{a} global optimum
+incorporate length penalization, while keeping the
+ability to extract a global optimum
 \cite{boykov01graphcut,appleton05geodesic}.
@@
 small or thin and elongated objects, as it tends to shrink solutions
-or \HT{yields} disconnected solutions. Such drawbacks can be problematic in
+or yields disconnected solutions. Such drawbacks can be problematic in
 image segmentation or image inpainting. It is thus rather natural to
-consider curvature (especially squared curvature) \HT{as} a potential
-regularizer. Energies involving \HT{both length and} squared curvature are often called
-{\em Euler elastica} model (\HT{that} dates back to Euler) or {\em Willmore energy}
+consider curvature (especially squared curvature) as a potential
+regularizer. Energies involving both length and squared curvature are often called
+{\em Euler elastica} model (that dates back to Euler) or {\em Willmore energy}
 ($n$-dimensional extension) and have been brought back to attention in
@@
 regularizer is also present in the second-order regularizer
-of the \HT{original} snake model \cite{kass1988snakes}. \HT{Similarly,
+of the original snake model \cite{kass1988snakes}. Similarly,
 an explicit curvature term was often employed in early level-set methods,
-like~\cite{malladi1995image,malladi1995shape,ballester01filljoint} for segmentation or inpainting,}
-\HT{However, Casselles {\em et al.} in~\cite{casseles97geodesic} observed that these
-terms were not geometric, in the sense that they depended on the discretization}.
+like~\cite{malladi1995image,malladi1995shape,ballester01filljoint} for segmentation or inpainting.
+However, Casselles {\em et al.} in~\cite{casseles97geodesic} observed that these
+terms were not geometric, in the sense that they depended on the discretization.
 
@@
 
-One of the first successful uses of \HT{geometric squared} curvature in image processing is the inpainting algorithm
-described in \cite{masnou98inpainting}\HT{, where authors} evaluate the elastica energy along the level lines of a
-simply-connected image to reconstruct its occluded parts. The non-intersection property of level lines \HT{induces} the
-construction of an efficient dynamic programming algorithm. \HT{However, } the curvature energy is \HT{only} coarsely
-approximated.  \cite{chan02elasticainpainting} \HT{is} another geometric inpainting method involving elastica
-\HT{optimized with level-sets}.
-
-In image segmentation, Zehiry and Grady have shown that injecting curvature as a regularizer \HT{can help} recover thin
+One of the first successful uses of curvature in image processing is the inpainting algorithm
+described in \cite{masnou98inpainting}, where authors evaluate the absolute curvature along the level lines of a simply-connected image to reconstruct its occluded parts.
+The non-intersection property of level lines induces the
+construction of an efficient dynamic programming algorithm. However,  the curvature energy is only coarsely
+approximated.  In \cite{chan02elasticainpainting}, a geometric inpainting method involving elastica
+optimized with level-sets is described.
+
+In image segmentation, Zehiry and Grady have shown that injecting curvature as a regularizer can help recover thin
 and elongated objects \cite{zehiry10fast}. Similarly Schoenemann {\em et al.}  \cite{schoenemann09linear} have
@@
 Schoenemann~{\em et al.} extend ratio-cut approaches to segmentation with a curvature term. Their global optimization
-framework shows the considerable \HT{advantages} of using such regularizer in common binary image segmentation tasks.
-However the time complexity of their algorithm \HT{is prohibitive,} even if curvature is \HT{again} coarsely
+framework shows the considerable advantages of using such regularizer in common binary image segmentation tasks.
+However the time complexity of their algorithm is prohibitive, even if curvature is again coarsely
 approximated.  In more recent work, Lim {\em et al.} propose an edge-weighted Willmore-like flow to segment
@@
 the context of image segmentation.  
-\HT{State-of-art methods are in practice} difficult to optimize and \HT{do not scale}
+State-of-art methods are in practice difficult to optimize and do not scale
 \cite{zehiry10fast,schoenemann09linear,strandmark11globalframework,nieuwenhuis14efficient}. In
@@
 coarse curvature estimations for which the approximation error is
-\HT{often} unknown. Improving the quality of the curvature estimator has an
+often unknown. Improving the quality of the curvature estimator has an
 important impact on the accuracy of the results, but is
@@
 
-Segmentation methods using Elastica or Willmore energies \HT{generally
-reduce to} computing the corresponding flow, i.e. following its
+Segmentation methods using Elastica or Willmore energies generally
+reduce to computing the corresponding flow, i.e. following its
 gradient. Well-founded level-set methods involving Willmore energy
@@
 \cite{lim2012introducing}. Another level-set formulation similar to
-the Chan-Vese model \HT{was} proposed in \cite{zhu2013image}. Willmore
+the Chan-Vese model was proposed in \cite{zhu2013image}. Willmore
 flow can also be carried out by phase-field models (see
@@
 energy. Recently, new estimators of curvature along digital contours have been proposed
-\cite{roussillon11mdca,coeurjolly13integral,schindele17mdca} with the \HT{desirable} multigrid convergence property. This
-motivates us to \HT{propose} models in which they can be used successfully.
-
-\HT{In the remainder, we} investigate the use of the digital integral invariant
+\cite{roussillon11mdca,coeurjolly13integral,schindele17mdca} with the desirable multigrid convergence property. This
+motivates us to propose models in which they can be used successfully.
+
+In the remainder, we investigate the use of the digital integral invariant
 curvature estimator \cite{coeurjolly13integral} in a discrete
@@
 optimization model, which we solve using a classical variant of QPBO
-algorithm \cite{rother07qpbo}. \HT{Our solution does not} compute a global
+algorithm \cite{rother07qpbo}. Our solution does not compute a global
 solution to the whole domain, but our approach leads to a digital flow
-similar to continuous \HT{Elastica}, as shown by our experiments. We
+similar to continuous Elastica, as shown by our experiments. We
 present an application of the model as a post-processing step in a
 segmentation framework, and demonstrate how it can improve standard
-results. The code is freely available on
-github\footnote{https://www.github.com/danoan/BTools}.
-
-%% In this work, we investigate the use of a more suitable curvature
-%% estimator with multigrid convergent property and its application as a
-%% boundary regularizer in a digital flow minimizing its squared
-%% curvature. Our method decreases the elastica energy of the contour and
-%% its evolution is evaluated on several digital flows.
-
-%% Finally, we
-%% present an application of the model as a post-processing step in a
-%% segmentation framework. The code is freely available on
-%% github\footnote{https://www.github.com/danoan/BTools}.
-
-\begin{itemize}
-\item{Geometric properties and regularization}
-\item{The role of curvature}
-
-%  Quote \cite{schoenemann2011elastic} for the interest of using curvature energy when segmenting regions in gradient-based data fitting term.
-It can look for global optimum within a graph representation of the image.
-Main problem of their approach is the computational complexity as well as rather coarse approximations of curvature.
-(Be more precise here).
-
-\item{What are the difficulties in use curvatue as a regularizer (point out convex relaxation approaches) and how a digital approach may help us }
-\item{Outline: We present two models that illustrate how digital estimators can be used to minimize the elastica energy on digital sets.  }
-\item{\todo{Add related works : geometric priors, binary segmentation, other digital curve evolution models}}
-\item{\todo{Talk about Willmore flow with phase field or with threshold dynamics}}
-
-%%\item{\textbf{Classical work on elastica and Wilmore flow in imaging}}
-  %%\begin{itemize}
-  %% \item{Level lines based disocclusion \cite{masnou98inpainting} }	%% DONE
- %%  \item{Filling-In by Joint Interpolation of Vector Fields and Gray Levels \cite{ballester01filljoint} } %% DONE
- %%  \item{Eulers Elastica and Curvature Based Inpaintings \cite{chan02elasticainpainting} } %% DONE
- %% \item{Discrete willmore flow \cite{bobenko2005discrete}}
- %%  \item{Introducing Willmore flow into level set segmentation of spinal vertebrae \cite{lim2012introducing}}	 %%% DONE
- %% \end{itemize}
-
-%%\item{\textbf{Level-sets}}
- %% \begin{itemize}
-  %% \item{Image processing via level set curvature flow \cite{malladi1995image} } %% DONE
-  %% \item{Shape Modeling with Front Propagation: A Level Set Approach \cite{malladi1995shape} }	%% DONE
-%%	\end{itemize}
-
-\item{\textbf{Convex relaxation}}
-  \begin{itemize}
-  \item{A convex lower semicontinuous approximation of Eulers elastica energy \cite{bredies15convex}}
-  \item{Introducing Total Curvature for Image Processing \cite{goldluecke11totalcurvature}}
-  \end{itemize}
-
-\item{\textbf{Constraint optimization}}
-  \begin{itemize}
-  \item{Curvature regularity for region-based image segmentation and inpainting: A linear programming relaxation \cite{schoenemann09linear} }	
-  \item{A Fast Algorithm for Euler's Elastica Model Using Augmented Lagrangian Method \cite{tai11elastica} }		
-  %%\item{The elastic ratio: Introducing curvature into ratio-based image segmentation \cite{schoenemann2011elastic}
-  %%}		%% DONE
-  \item{Curvature Regularization for Curves and Surfaces in a Global Optimization Framework \cite{strandmark11globalframework} }
-  \end{itemize}
-
-\item{\textbf{Discrete approaches}}
-  \begin{itemize}
-  \item{Fast global optimization of curvature \cite{zehiry10fast}	}
-  \item{Efficient Squared Curvature \cite{nieuwenhuis14efficient} 	}
-  \item{Contrast driven {E}lastica for image segmentation \cite{el2016contrast} }	
-  \end{itemize}
-
-\end{itemize}
+results.
+\daniel{This paper is an extended version of a previous work that appeared in \cite{antunes19}.
+We've included a deeper discussion on the optimization method we've used and we present a comparison of our segmentation method with two other related works, and illustrate the results with several examples.
+Moreover, we have included a new local combinatorial optimization approach for elastica minimization.
+Finnaly,  the code produced in this paper is freely available on github\footnote{https://www.github.com/danoan/BTools}.}
 
@@
 
-\section{Multigrid convergent estimators \todo{(Mostly copy/paste)}}
+\section{Multigrid convergent estimators}
 
@@
 Of course we only observe shape digitizations within images.
-%% \begin{itemize}
-%% 	\item{Why to use multigrid convergent estimators}
-%% 	\item{Multigrid convergence for local estimators}
-%% 	\item{Reference to examples of multigrid digital estimators(for curvature, length, tangent)}
-%% 	\item{Define the elastica energy estimator}
-%% 	\item{\test{(Jaco) see if two opposite II evaluations give convergent curvature}}
-%% \end{itemize}
-
-%% \hrulefill
 
@@
 
-\begin{figure}
+\begin{figure}[!h]
 \center
@@
 
-\begin{figure}[!ht]
+\begin{figure}[!h]
 \center
@@
 
-\begin{figure}
+\begin{figure}[!h]
 \begin{minipage}[b]{0.5\textwidth}
@@
   \hat{\kappa}^2(y) &= c_1\Big( c_2 - \sum_{x_j \in B_r(y)} \big( {x_j} + |F_{r}^{(i)}(y)| \big) \Big)^2 \\
-   &= c_1 \cdot \Big( C + 2\left( |F_{r}^{(i)}(y)| - c_2 \right) \hspace{-2mm}\sum_{x_j \in O_{r}^{(i)}(y)}\hspace{-2mm}{x_j} + \hspace{-2mm}\sum_{x_j \in O_{r}^{(i)}(y)}\hspace{-2mm}{x_j^2} + \hspace{-2mm}\sum_{ \substack{x_j,x_k \in O_{r}^{(i)}(p) \\ j<k} }\hspace{-2mm}{2x_jx_k}  \Big),
-\end{align*}
-where $C=c_2^2 - 2c_2 \cdot |F_{r}^{(i)}(y)| + |F_{r}^{(i)}(y)|^2$ is a constant. In
-order to be symmetric, the curvature at some linel $y$ is computed on
-$R_m(S)$.\todo{Que veux-tu dire?} By ignoring constants and multiplication factors and using
+   &= c_1 \cdot \Big( C + 2\left( |F_{r}^{(i)}(y)| - c_2 \right) \hspace{-2mm}\sum_{x_j \in O_{r}^{(i)}(y)}\hspace{-2mm}{x_j} + \hspace{-2mm}\sum_{x_j \in O_{r}^{(i)}(y)}\hspace{-2mm}{x_j^2} + \hspace{-2mm}\sum_{ \substack{x_j,x_k \in O_{r}^{(i)}(y) \\ j<k} }\hspace{-2mm}{2x_jx_k}  \Big),
+\end{align*}
+where $C=c_2^2 - 2c_2 \cdot |F_{r}^{(i)}(y)| + |F_{r}^{(i)}(y)|^2$ is a constant. By ignoring constants and multiplication factors and using
 the binary character of the variables, we define the following family
-of energies for given parameters $\alpha,\beta \geq 0$.
+of energies for given parameters $\alpha,\beta, \gamma \geq 0$.
 \begin{align}
@@
   & + \sum_{y \in R_m(S)}{ \beta \Big( { (1/2+ |F_{r}^{(i)}(y)|-c_2) \cdot \sum_{x_j \in O_{r}^{(i)}(y)}{x_j} } + \sum_{ \substack{x_j,x_k \in O_{r}^{(i)}(y) \\ j<k} }{x_jx_k} \Big) } \nonumber \\
-  & + \sum_{x \in X}{\gamma g(S,x)}
+  & + \sum_{x \in X}{\gamma g(S,x)},
   \label{eq:energy-family}
 \end{align}
-\todo{Que vaux $X$ ici ?}	
 where $g(S,x)$ denotes a similarity term as distance to initial shape $S$ or data fidelity term and $s(x)$ denotes a length penalization term.
@@
 
-  \label{tab:flow-summary}	  
   \caption{  Since the curvature is negated when reversing the curve (i.e.
 $\bar{\kappa}=-\kappa$), this process can only shrink  convex parts in shrink mode and expand concave parts in expansion mode.}
+   \label{tab:flow-summary}
 
@@
 
-In our experiments, the best results are obtained by executing DCE
+\daniel{In our experiments, the best results are obtained by executing DCE
 algorithm with $m$ equal to $r$, where $r$ is the estimation ball
-radius (see figures \ref{fig:mx-square-flow},
-\ref{fig:mx-flow-gs-radius-effect} ). In plot
-\ref{fig:mx-elastica-plots}, we observe how the elastica energy evolves along
-the iterations. If the radius is too large, the elastica energy may increase after some steps. That is what happens for the
-triangle, in which the flow converges to a single point.
-
-\begin{figure}[!ht]
+radius (see figure \ref{fig:mx-square-flow} ).
+We observe that elastica may increase after some iterations if chosen radius is too large, as in the case of the triangle in figure \ref{fig:mx-flow-gs-radius-effect} in which the flow converges to a single point.
+We conjecture that an appropriated value for the radius should be given by the shape reach.
+	The produced flow has no difficulties in handling changes on topology, and it presents different speeds for regions with low and high curvature values, as illustrated in figure \ref{fig:mx-speed-variation-hole-filling}.}
+
+\begin{figure}[hp!]
 \center				
@@
 \includegraphics[scale=0.2]{images/flow/grid-radius-effect/flower/r5-h0.5/summary_flow.eps}}%
+		}\\
+		\subfloat[Elastica evaluation]{%
+		\includegraphics[scale=0.5]{images/flow/elastica-energy-plot/r5h05.eps}						
 		}
@@
 In figure (b), for $r=5$, the triangle evolves to a single point, while the others stop  in an intermediate shape, as in (a).
+In figure (c), we observe that for a given choice of radius, the elastica may increase after a certain number of iterations.
 }
@@
 
-\begin{figure}[!ht]
-\center
-\includegraphics[scale=0.5]{images/flow/elastica-energy-plot/r5h05.eps}
-\caption{Elastica computation along the iterations for different shapes. If radius is too large, elastica energy may increase after a certain number of iterations. }
-\label{fig:mx-elastica-plots}
-\end{figure}
-
-\begin{figure}[!ht]
+\begin{figure}[!h]
 \center
@@
 		\includegraphics[scale=0.25]{images/flow/fill-holes/summary_flow.eps}}%%1
+\caption{High curvature regions evolves faster than lower ones (a). The flow can handle topological changes (b). }
 \label{fig:mx-speed-variation-hole-filling}
-\caption{High curvature regions evolves faster than lower ones (a). The flow can handle topological changes (b). }
 \end{figure}
@@
 \ref{fig:unlabeled-versus-iterations}. We also noticed that, for
-$m=r$, all the pixels were labeled. Perhaps this means that our energy
-is submodular in this case, but this remains to be proved.
+$m=r$, all the pixels were labeled, \daniel{which may indicate that $E_r$ is an an easy 
+instance of the general non-submodular energy $E_m$, but this remains to be proved. The number of pairwise
+terms in $E_r$ is roughly half of those in $E_1$ (see figure \ref{fig:ratio-pairwise-terms}).}
 
@@
 
-\begin{figure}[!htp]
+\begin{figure}[h!]
+\center
+\includegraphics[scale=0.5]{images/optimization/pairwise-ratio/plot-pairwiseratio-lowerHigher-concavities-probe.eps}
+\caption{We plot the ratio of pairwise terms among all $\binom{|X^{(i)}|}{2}$ combinations. The highest ring has rougly half the number of pairwise terms  than the lowest ring.}
+\label{fig:ratio-pairwise-terms}
+\end{figure}
+
+\begin{figure}[hp!]
 \center
@@
 
-\begin{figure}
-\center
-\includegraphics[scale=0.5]{images/optimization/pairwise-ratio/plot-pairwiseratio-lowerHigher-concavities-probe.eps}
-\caption{We plot the ratio of pairwise terms among all $\binom{|X^{(i)}|}{2}$ combinations.
-The highest ring has rougly half the number of pairwise terms  than the lowest ring.\label{fig:ratio-pairwise-terms}}
-\end{figure}
-
-\todo{You must comment figure~\ref{fig:ratio-pairwise-terms} in the text.}
-
 \section{Application to image segmentation}
@@
 
- \Input{An image $I$; seed mask $M$; the estimation ball radius $r$; data $(\gamma)$, length $(\alpha)$ and squared curvature $(\beta)$ weights; initial dilation $d$; stop condition value \Tol; the maximum number of iterations \MIt;}
+ \Input{An image $I$; seed mask $M$; the estimation ball radius $r$; length $(\alpha)$, squared curvature $(\beta)$ and data fidelity $(\gamma)$ coefficients; initial dilation $d$; stop condition value \Tol; the maximum number of iterations \MIt;}
  \BlankLine
@@
  \While{ \It $<$ \MIt \bf{and} \Delta $>$ \Tol  }{ 	
- 	$S^{(i+1)} \longleftarrow $ DCE($S^{(i)},\gamma,\alpha,\beta$)\;
+ 	$S^{(i+1)} \longleftarrow $ DCE($S^{(i)},r,\alpha,\beta,\gamma,2$)\;
  	\Delta $\longleftarrow |S^{(i)} - S^{(i+1)}|$\;
@@
  \label{alg:contour-correction} 
- \caption{Contour correction algorithm. \todo{Critère d'arrêt basé sur un nombre de pixels changés !?}}
+ \caption{Contour correction algorithm.}
 \end{algorithm}
@@
 
-\begin{figure}
+\begin{figure}[ht!]
 \center
@@
 
-\begin{figure}
+\begin{figure}[ht!]
 	\center
@@
 	\end{tabular}
-	\caption{The proposed method regularizes grabcut contours and returns meaningful results.
+	\caption{The proposed method regularizes GrabCut contours and returns meaningful results.
 We can observe the completion feature of curvature in the second row, and we don't suffer from oversegmentation issues as Schoenemann's method.
@@
 
-\begin{figure}
+\begin{figure}[hp!]
 	\center
@@
 
-In figure \ref{fig:parameters-influence} we can observe the results of a curvature regularization in comparison with a pure length regularization, and figures \ref{fig:segmentation-results} and \ref{fig:more-segmentation-results} show some segmentation results.
-
-\todo{You must comment on the results.}
+\daniel{In figure \ref{fig:parameters-influence} we can observe the results of a curvature regularization in comparison with a pure length regularization.
+The curvature can fill gaps and is smoother than the one produced by length only, resulting in more pleasant segmentations.
+In figures \ref{fig:segmentation-results} and \ref{fig:more-segmentation-results} we list several results of our method and we compare them with segmentation produced by GrabCut and Schoenemann's method.
+Our method is successful in producing curvature regularized segmentations and demonstrates the completion property of curvature.
+Moreover, it does not suffer from over segmentation, it is faster than Schoenemann's, and in several opportunities produces better segmentations than GrabCut.}
 

### 2019-07-07 jmiv.tex
avances

--- 2019-07-07 jmiv.tex
@@
 
-Geometric quantities are particularly useful as regularizers in
-low-level image analysis, especially when little prior information is
-known about the shape of interest. Length penalization is a \HT{well-behaved,} general
-purpose regularizer and \HT{many} models \HT{in the literature} make use
-of it, from active contours \cite{casseles97geodesic} to level-set
-formulations \cite{malladi1995image,malladi1995shape}. Discrete
-graph-based variational models have been particularly succesfull to
-incorporate length penalization as a penalizer, while keeping the
-ability to extract \HT{a} global optimum
-\cite{boykov01graphcut,appleton05geodesic}.
-
-However length regularization shows limitations when segmenting
-small or thin and elongated objects, as it tends to shrink solutions
-or \HT{yields} disconnected solutions. Such drawbacks can be problematic in
-image segmentation or image inpainting. It is thus rather natural to
-consider curvature (especially squared curvature) \HT{as} a potential
-regularizer. Energies involving \HT{both length and} squared curvature are often called
-{\em Euler elastica} model (\HT{that} dates back to Euler) or {\em Willmore energy}
-($n$-dimensional extension) and have been brought back to attention in
-computer vision by Mumford \cite{mumford1994elastica}. A similar
-regularizer is also present in the second-order regularizer
-of the \HT{original} snake model \cite{kass1988snakes}. \HT{Similarly,
-an explicit curvature term was often employed in early level-set methods,
-like~\cite{malladi1995image,malladi1995shape,ballester01filljoint} for segmentation or inpainting,}
-\HT{However, Casselles {\em et al.} in~\cite{casseles97geodesic} observed that these
-terms were not geometric, in the sense that they depended on the discretization}.
-
-The use of curvature for surface regularization was studied in~\cite{bobenko2005discrete},
-although results look promising, authors used an inexact linearized version of the
-square curvature at every step.
-
-One of the first successful uses of \HT{geometric squared} curvature in image processing is the inpainting algorithm
+Geometric quantities are particularly useful as regularizers in low-level image analysis, especially when little prior
+information is known about the shape of interest. Length penalization is a \HT{well-behaved,} general purpose
+regularizer and \HT{many} models \HT{in the literature} make use of it, from active contours \cite{casseles97geodesic}
+to level-set formulations \cite{malladi1995image,malladi1995shape}. Discrete graph-based variational models have been
+particularly succesfull to incorporate length penalization as a penalizer, while keeping the ability to extract \HT{a}
+global optimum \cite{boykov01graphcut,appleton05geodesic}.
+
+However length regularization shows limitations when segmenting small or thin and elongated objects, as it tends to
+shrink solutions or \HT{yields} disconnected solutions. Such drawbacks can be problematic in image segmentation, image
+restoration or image inpainting. It is thus rather natural to consider curvature (especially squared curvature) \HT{as}
+a potential regularizer. Energies involving \HT{both length and} squared curvature are often called \HT{the {\em Elastica}}
+model (\HT{that} dates back to Euler) . \HT{The {\em Willmore energy} is its $n$-dimensional extension. These were brought to
+attention} in computer vision by Mumford \cite{mumford1994elastica}. A similar concept is also present in the
+second-order regularizer of the \HT{original} snake model \cite{kass1988snakes}. \HT{Indeed, an explicit curvature
+  term was often employed in early level-set methods, like~\cite{malladi1995image,malladi1995shape,ballester01filljoint}
+  for segmentation or inpainting,} \HT{However, Casselles {\em et al.} in~\cite{casseles97geodesic} observed that these
+  terms as employed were not geometric, in the sense that they depended on the discretization parameters}.
+
+\HT{The use of curvature for surface regularization in the case of the Willmore energy was studied
+  in~\cite{bobenko2005discrete}, although results look promising, authors used an inexact linearized version of the
+  square curvature at every step.}
+
+One of the first successful uses of \HT{geometric, squared} curvature in image processing is the inpainting algorithm
 described in \cite{masnou98inpainting}\HT{, where authors} evaluate the elastica energy along the level lines of a
@@
 However the time complexity of their algorithm \HT{is prohibitive,} even if curvature is \HT{again} coarsely
-approximated.  In more recent work, Lim {\em et al.} propose an edge-weighted Willmore-like flow to segment
+approximated.  \HT{In more recent work, Lim {\em et al.} propose an edge-weighted Willmore-like flow to segment
 vertebra~\cite{lim2012introducing} using a level-set formulation. They observe improved results compared
 to~\cite{casseles97geodesic} and other perimeter-based priors, but observe that a shape prior and a close-enough
-solution must also be provided to achieve good results.
-
-In fact, it is still a very challenging task to inject curvature in
-the context of image segmentation.  
-\HT{State-of-art methods are in practice} difficult to optimize and \HT{do not scale}
-\cite{zehiry10fast,schoenemann09linear,strandmark11globalframework,nieuwenhuis14efficient}. In
-order to achieve reasonable running times, such approaches make use of
-coarse curvature estimations for which the approximation error is
-\HT{often} unknown. Improving the quality of the curvature estimator has an
-important impact on the accuracy of the results, but is
-computationally too costly in these methods.
-
-Segmentation methods using Elastica or Willmore energies \HT{generally
-reduce to} computing the corresponding flow, i.e. following its
-gradient. Well-founded level-set methods involving Willmore energy
-\cite{droske2004level} have been used in medical image segmentation
-\cite{lim2012introducing}. Another level-set formulation similar to
-the Chan-Vese model \HT{was} proposed in \cite{zhu2013image}. Willmore
-flow can also be carried out by phase-field models (see
-\cite{bretin2015phase}) but they are less suited to image segmentation
-since interfaces are blurred in such models. Threshold dynamics can
-also be considered for such energies \cite{esedoglu2008threshold} and
-has been proposed for image desocclusion \cite{esedoglu2005threshold}.
+solution must also be provided to achieve good results.}
+
+In fact, it is still a very challenging task to \HT{efficiently handle} curvature in the context of image segmentation.
+\HT{State-of-art methods are in practice} difficult to optimize and \HT{do not scale easily}
+\cite{zehiry10fast,schoenemann09linear,strandmark11globalframework,nieuwenhuis14efficient}. In order to achieve
+reasonable running times, such approaches make use of coarse curvature estimations for which the approximation error is
+\HT{often} unknown. Improving the quality of the curvature estimator has an important impact on the accuracy of the
+results, but is computationally too costly in these methods.
+
+Segmentation methods using Elastica or Willmore energies \HT{can be formulated via the computation of} corresponding
+flow, i.e. following its gradient. Well-founded level-set methods involving Willmore energy \cite{droske2004level} have
+been used in medical image segmentation \cite{lim2012introducing}. Another level-set formulation similar to the
+Chan-Vese model \HT{was} proposed in \cite{zhu2013image}. Willmore flow can also be carried out by phase-field models
+(see \cite{bretin2015phase}) but they are less suited to image segmentation since interfaces are blurred in such
+models. Threshold dynamics can also be considered for such energies \cite{esedoglu2008threshold} and has been proposed
+for image desocclusion \cite{esedoglu2005threshold}. \HT{However, flow-based methods will always deliver
+  a local minimum, which heavily depend on initialization for good results}.
+
+\HT{In contrast, researchers have sought convex relaxation of curvature-related
+  formulation. In~\cite{goldluecke11totalcurvature}, Goldluecke and Cremers introduce the {\em Total Curvature}, based
+  on the Menger-Melnikov curvature of a measure. The formulation is non-convex but can be relaxed into a well-correlated
+  but non-tight convex one. The relaxed formulation can be used to solve inverse problems including segmentation,
+  however computing a solution is still expensive, requiring signifiant parallelisation efforts with a GPU to achieve
+  acceptable computing times}. \HT{In~\cite{bredies15convex}, Bredies {\em et al.} study a convex approximation of the
+  Elastica energy, using a lifting scheme. Thanks to the lifting, it is not restritcted to binary sets. It shows
+  promising results and can be used for image restoration in addition to inpainting and segmentation. The scheme is
+  however neither tight nor exact, and required 4 dimensions for a 2D approximation. In addition, it does not carry over
+  to $nD$. It also remains computationally expensive.}
 
@@
 
-\HT{In the remainder, we} investigate the use of the digital integral invariant
-curvature estimator \cite{coeurjolly13integral} in a discrete
-variational segmentation framework. More precisely, we show how to
-incorporate it in a digital flow minimizing its squared
-curvature. This model is expressible as a discrete combinatorial
-optimization model, which we solve using a classical variant of QPBO
-algorithm \cite{rother07qpbo}. \HT{Our solution does not} compute a global
-solution to the whole domain, but our approach leads to a digital flow
-similar to continuous \HT{Elastica}, as shown by our experiments. We
-present an application of the model as a post-processing step in a
-segmentation framework, and demonstrate how it can improve standard
-results. The code is freely available on
+\HT{In the remainder, we} investigate the use of the digital integral invariant curvature estimator
+\cite{coeurjolly13integral} in a discrete variational segmentation framework. More precisely, we show how to incorporate
+it in a digital flow minimizing its squared curvature. This model is expressible as a discrete combinatorial
+optimization model, which we solve using a classical variant of QPBO algorithm \cite{rother07qpbo}. \HT{Our solution
+  does not} compute a global solution to the whole domain, but our approach leads to a digital flow similar to
+continuous \HT{Elastica}, as shown by our experiments. We present an application of the model as a post-processing step
+in a segmentation framework, and demonstrate how it can improve standard results. The code is freely available on
 github\footnote{https://www.github.com/danoan/BTools}.
@@
 \begin{itemize}
-\item{Geometric properties and regularization}
-\item{The role of curvature}
+%% \item{Geometric properties and regularization}
+%% \item{The role of curvature}
 
@@
 
-\item{What are the difficulties in use curvatue as a regularizer (point out convex relaxation approaches) and how a digital approach may help us }
+\item{What are the difficulties in use curvature as a regularizer (point out convex relaxation approaches) and how a digital approach may help us }
 \item{Outline: We present two models that illustrate how digital estimators can be used to minimize the elastica energy on digital sets.  }
@@
 
-\item{\textbf{Convex relaxation}}
-  \begin{itemize}
-  \item{A convex lower semicontinuous approximation of Eulers elastica energy \cite{bredies15convex}}
-  \item{Introducing Total Curvature for Image Processing \cite{goldluecke11totalcurvature}}
-  \end{itemize}
+%%\item{\textbf{Convex relaxation}}
+%%  \begin{itemize}
+%%  \item{A convex lower semicontinuous approximation of Eulers elastica energy \cite{bredies15convex}}
+ %% \item{Introducing Total Curvature for Image Processing \cite{goldluecke11totalcurvature}}
+ %% \end{itemize}
 
@@
   \begin{itemize}
-  \item{Curvature regularity for region-based image segmentation and inpainting: A linear programming relaxation \cite{schoenemann09linear} }	
+ %% \item{Curvature regularity for region-based image segmentation and inpainting: A linear programming relaxation \cite{schoenemann09linear} }	
   \item{A Fast Algorithm for Euler's Elastica Model Using Augmented Lagrangian Method \cite{tai11elastica} }		

### 2019-07-07 jmiv.tex

@@
 One of the first successful uses of \HT{geometric, squared} curvature in image processing is the inpainting algorithm
-described in \cite{masnou98inpainting}\HT{, where authors} evaluate the elastica energy along the level lines of a
+described in \cite{masnou98inpainting}\HT{, where authors} evaluate
+the absolute curvature along the level lines of a
 simply-connected image to reconstruct its occluded parts. The non-intersection property of level lines \HT{induces} the
@@
 
-In image segmentation, Zehiry and Grady have shown that injecting curvature as a regularizer \HT{can help} recover thin
+In image segmentation, Zehiry and Grady have shown that injecting curvature as a regularizer can help recover thin
 and elongated objects \cite{zehiry10fast}. Similarly Schoenemann {\em et al.}  \cite{schoenemann09linear} have
@@
 Schoenemann~{\em et al.} extend ratio-cut approaches to segmentation with a curvature term. Their global optimization
+
 framework shows the considerable \HT{advantages} of using such regularizer in common binary image segmentation tasks.
@@
 energy. Recently, new estimators of curvature along digital contours have been proposed
-\cite{roussillon11mdca,coeurjolly13integral,schindele17mdca} with the \HT{desirable} multigrid convergence property. This
-motivates us to \HT{propose} models in which they can be used successfully.
+\cite{roussillon11mdca,coeurjolly13integral,schindele17mdca} with the desirable multigrid convergence property. This
+motivates us to propose models in which they can be used successfully.
 
@@
 continuous \HT{Elastica}, as shown by our experiments. We present an application of the model as a post-processing step
-in a segmentation framework, and demonstrate how it can improve standard results. The code is freely available on
-github\footnote{https://www.github.com/danoan/BTools}.
+in a segmentation framework, and demonstrate how it can improve standard results. 
+\daniel{This paper is an extended version of a previous work that appeared in \cite{antunes19}.
+We've included a deeper discussion on the optimization method we've used and we present a comparison of our segmentation method with two other related works, and illustrate the results with several examples.
+Moreover, we have included a new local combinatorial optimization approach for elastica minimization.
+Finnaly,  the code produced in this paper is freely available on github\footnote{https://www.github.com/danoan/BTools}.}
 

### 2019-07-08 jmiv.tex
fatigue

@@
 
+\subsection{Existing works}
 \HT{The use of curvature for surface regularization in the case of the Willmore energy was studied
@@
 Schoenemann~{\em et al.} extend ratio-cut approaches to segmentation with a curvature term. Their global optimization
-
 framework shows the considerable \HT{advantages} of using such regularizer in common binary image segmentation tasks.
@@
 models. Threshold dynamics can also be considered for such energies \cite{esedoglu2008threshold} and has been proposed
-for image desocclusion \cite{esedoglu2005threshold}. \HT{However, flow-based methods will always deliver
-  a local minimum, which heavily depend on initialization for good results}.
+for image desocclusion \cite{esedoglu2005threshold}. \HT{However, flow-based methods will always deliver a local
+  minimum, which heavily depend on initialization for good results}.  \HT{A similar approach is to formulate the
+  Elastica as a regularization in a variational framework and use operator splitting to optimize it. Tai {\em et
+    al.}~\cite{tai11elastica} and more recently Deng~{\em et al.}~\cite{deng2019new} have proposed this approach, which
+  is well-suited to inverse problem solving. The problem remains non-convex and the nature of the converged iterate
+are not studied, i.e. how close they are to a global optimum.}
 
@@
 
-In this paper we are interested in purely discrete variational segmentation models involving an elastica
-energy. Recently, new estimators of curvature along digital contours have been proposed
+\HT{Discrete approaches have been used to tackle the Elastica difficulties. As noted before~\cite{schoenemann09linear}
+  have linearized a mesh-based approach, which was expanded upon by~\cite{strandmark11globalframework}, while
+  \cite{zehiry10fast} have used a binary solver for a non-submodular approach on a regular square grid of pixels, which
+  was expanded in~\cite{el2016contrast}. In~\cite{nieuwenhuis14efficient} , a specific solver is developed to yield a
+  better solution to an extension of the formulation in~\cite{zehiry10fast}.}
+
+\subsection{Motivation}
+\HT{In spite of the multiplicity of existing approaches, it seems none is currently completely satisfactory. While the
+  sought solution is expected to be very smooth based on geometrical expectations, the mathematical properties
+  of the related operators make this smoothness elusive. Non-convexity and the presence of high-order terms make
+  Elastica difficult to optimize and to approximate, let alone compute efficiently. The computed solution in the
+  literature are rarely evaluated, and the complexity of the proposed solution is often high.}
+
+%%\item{What are the difficulties in use curvature as a regularizer (point out convex relaxation approaches) and how a digital approach may help us }
+%%\item{Outline: We present two models that illustrate how digital estimators can be used to minimize the elastica energy on digital sets.  }
+%%\item{\todo{Add related works : geometric priors, binary segmentation, other digital curve evolution models}}
+%%\item{\todo{Talk about Willmore flow with phase field or with threshold dynamics}}
+
+\HT{Consequently,} we are interested in \HT{studying} purely discrete variational segmentation models involving an
+elastica energy. Recently, new estimators of curvature along digital contours have been proposed
 \cite{roussillon11mdca,coeurjolly13integral,schindele17mdca} with the desirable multigrid convergence property. This
@@
 
-\HT{In the remainder, we} investigate the use of the digital integral invariant curvature estimator
+\HT{In the remainder, we propose to} investigate the use of the digital integral invariant curvature estimator
 \cite{coeurjolly13integral} in a discrete variational segmentation framework. More precisely, we show how to incorporate
@@
 in a segmentation framework, and demonstrate how it can improve standard results. 
-\daniel{This paper is an extended version of a previous work that appeared in \cite{antunes19}.
-We've included a deeper discussion on the optimization method we've used and we present a comparison of our segmentation method with two other related works, and illustrate the results with several examples.
-Moreover, we have included a new local combinatorial optimization approach for elastica minimization.
-Finnaly,  the code produced in this paper is freely available on github\footnote{https://www.github.com/danoan/BTools}.}
-
-%% In this work, we investigate the use of a more suitable curvature
-%% estimator with multigrid convergent property and its application as a
-%% boundary regularizer in a digital flow minimizing its squared
-%% curvature. Our method decreases the elastica energy of the contour and
-%% its evolution is evaluated on several digital flows.
-
-%% Finally, we
-%% present an application of the model as a post-processing step in a
-%% segmentation framework. The code is freely available on
-%% github\footnote{https://www.github.com/danoan/BTools}.
-
-\begin{itemize}
-%% \item{Geometric properties and regularization}
-%% \item{The role of curvature}
-
-%  Quote \cite{schoenemann2011elastic} for the interest of using curvature energy when segmenting regions in gradient-based data fitting term.
-It can look for global optimum within a graph representation of the image.
-Main problem of their approach is the computational complexity as well as rather coarse approximations of curvature.
-(Be more precise here).
-
-\item{What are the difficulties in use curvature as a regularizer (point out convex relaxation approaches) and how a digital approach may help us }
-\item{Outline: We present two models that illustrate how digital estimators can be used to minimize the elastica energy on digital sets.  }
-\item{\todo{Add related works : geometric priors, binary segmentation, other digital curve evolution models}}
-\item{\todo{Talk about Willmore flow with phase field or with threshold dynamics}}
-
-%%\item{\textbf{Classical work on elastica and Wilmore flow in imaging}}
-  %%\begin{itemize}
-  %% \item{Level lines based disocclusion \cite{masnou98inpainting} }	%% DONE
- %%  \item{Filling-In by Joint Interpolation of Vector Fields and Gray Levels \cite{ballester01filljoint} } %% DONE
- %%  \item{Eulers Elastica and Curvature Based Inpaintings \cite{chan02elasticainpainting} } %% DONE
- %% \item{Discrete willmore flow \cite{bobenko2005discrete}}
- %%  \item{Introducing Willmore flow into level set segmentation of spinal vertebrae \cite{lim2012introducing}}	 %%% DONE
- %% \end{itemize}
-
-%%\item{\textbf{Level-sets}}
- %% \begin{itemize}
-  %% \item{Image processing via level set curvature flow \cite{malladi1995image} } %% DONE
-  %% \item{Shape Modeling with Front Propagation: A Level Set Approach \cite{malladi1995shape} }	%% DONE
-%%	\end{itemize}
-
-%%\item{\textbf{Convex relaxation}}
-%%  \begin{itemize}
-%%  \item{A convex lower semicontinuous approximation of Eulers elastica energy \cite{bredies15convex}}
- %% \item{Introducing Total Curvature for Image Processing \cite{goldluecke11totalcurvature}}
- %% \end{itemize}
-
-\item{\textbf{Constraint optimization}}
-  \begin{itemize}
- %% \item{Curvature regularity for region-based image segmentation and inpainting: A linear programming relaxation \cite{schoenemann09linear} }	
-  \item{A Fast Algorithm for Euler's Elastica Model Using Augmented Lagrangian Method \cite{tai11elastica} }		
-  %%\item{The elastic ratio: Introducing curvature into ratio-based image segmentation \cite{schoenemann2011elastic}
-  %%}		%% DONE
-  \item{Curvature Regularization for Curves and Surfaces in a Global Optimization Framework \cite{strandmark11globalframework} }
-  \end{itemize}
-
-\item{\textbf{Discrete approaches}}
-  \begin{itemize}
-  \item{Fast global optimization of curvature \cite{zehiry10fast}	}
-  \item{Efficient Squared Curvature \cite{nieuwenhuis14efficient} 	}
-  \item{Contrast driven {E}lastica for image segmentation \cite{el2016contrast} }	
-  \end{itemize}
-
-\end{itemize}
-
-\textit{Outline}. Section two reviews the concept of multigrid
-convergence and highlights its importance for the definition of
-digital estimators. Next, we describe two convergent estimators used
-in this paper, one for tangent and the other for curvature. They are
-used in the optimization model and in the definition of the digital
-elastica. Section three describes a local combinatorial optimization model
-suitable for different curvature estimators. Section four describes the proposed 
-curvature evolution model along with several illustrations of digital flows. Section five
-explains how to use the evolution model as a post-processing step in
-an image segmentation framework.
+\daniel{This paper is an extended version of a previous work that appeared in \cite{antunes19}. We've included a deeper
+  discussion on the optimization method we've used and we present a comparison of our segmentation method with two other
+  related works, and illustrate the results with several examples. Moreover, we have included a new local combinatorial
+  optimization approach for elastica minimization. Finnaly,  the code produced in this paper is freely available on
+  github\footnote{https://www.github.com/danoan/BTools}.}
+
+\subsection{Outline}.
+Section two reviews the concept of multigrid convergence and highlights its importance for the
+definition of digital estimators. Next, we describe two convergent estimators used in this paper, one for tangent and
+the other for curvature. They are used in the optimization model and in the definition of the digital elastica. Section
+three describes a local combinatorial optimization model suitable for different curvature estimators. Section four
+describes the proposed curvature evolution model along with several illustrations of digital flows. Section five
+explains how to use the evolution model as a post-processing step in an image segmentation framework.
 
@@
 \end{document}
+
+%% for reference
+
+%% In this work, we investigate the use of a more suitable curvature
+%% estimator with multigrid convergent property and its application as a
+%% boundary regularizer in a digital flow minimizing its squared
+%% curvature. Our method decreases the elastica energy of the contour and
+%% its evolution is evaluated on several digital flows.
+
+%% Finally, we
+%% present an application of the model as a post-processing step in a
+%% segmentation framework. The code is freely available on
+%% github\footnote{https://www.github.com/danoan/BTools}.
+
+%\begin{itemize}
+%% \item{Geometric properties and regularization}
+%% \item{The role of curvature}
+
+%  Quote \cite{schoenemann2011elastic} for the interest of using curvature energy when segmenting regions in gradient-based data fitting term.
+It can look for global optimum within a graph representation of the image.
+Main problem of their approach is the computational complexity as well as rather coarse approximations of curvature.
+(Be more precise here).
+
+%%\item{\textbf{Classical work on elastica and Wilmore flow in imaging}}
+  %%\begin{itemize}
+  %% \item{Level lines based disocclusion \cite{masnou98inpainting} }	%% DONE
+ %%  \item{Filling-In by Joint Interpolation of Vector Fields and Gray Levels \cite{ballester01filljoint} } %% DONE
+ %%  \item{Eulers Elastica and Curvature Based Inpaintings \cite{chan02elasticainpainting} } %% DONE
+ %% \item{Discrete willmore flow \cite{bobenko2005discrete}}
+ %%  \item{Introducing Willmore flow into level set segmentation of spinal vertebrae \cite{lim2012introducing}}	 %%% DONE
+ %% \end{itemize}
+
+%%\item{\textbf{Level-sets}}
+ %% \begin{itemize}
+  %% \item{Image processing via level set curvature flow \cite{malladi1995image} } %% DONE
+  %% \item{Shape Modeling with Front Propagation: A Level Set Approach \cite{malladi1995shape} }	%% DONE
+%%	\end{itemize}
+
+%%\item{\textbf{Convex relaxation}}
+%%  \begin{itemize}
+%%  \item{A convex lower semicontinuous approximation of Eulers elastica energy \cite{bredies15convex}}
+ %% \item{Introducing Total Curvature for Image Processing \cite{goldluecke11totalcurvature}}
+ %% \end{itemize}
+
+%\item{\textbf{Constraint optimization}}
+ % \begin{itemize}
+  %% \item{Curvature regularity for region-based image segmentation and inpainting: A linear programming relaxation \cite{schoenemann09linear} }	
+  %% \item{A Fast Algorithm for Euler's Elastica Model Using Augmented Lagrangian Method \cite{tai11elastica} }		
+  %%\item{The elastic ratio: Introducing curvature into ratio-based image segmentation \cite{schoenemann2011elastic}
+  %%}		%% DONE
+ % \end{itemize}
+
+%%\item{\textbf{Discrete approaches}}
+%%  \begin{itemize}
+  %% \item{Fast global optimization of curvature \cite{zehiry10fast}	} %% DONE
+  %%\item{Efficient Squared Curvature \cite{nieuwenhuis14efficient} 	}
+  %%\item{Contrast driven {E}lastica for image segmentation \cite{el2016contrast} }
+  %%\item{Curvature Regularization for Curves and Surfaces in a Global Optimization Framework \cite{strandmark11globalframework} }
+
+ % \end{itemize}
+
+%%\end{itemize}

### 2019-07-08 jmiv.tex
Add jmiv style

@@
 %
-\documentclass[runningheads]{llncs}
+%\documentclass[runningheads]{llncs}
+\documentclass[smallextended]{svjour3}       % onecolumn (second format)
 %
@@
 
-\author{Daniel Antunes\inst{1}
-Jacques-Olivier Lachaud\inst{1}
-Hugues Talbot\inst{2}}
+\author{Daniel Antunes%\inst{1}
+\and Jacques-Olivier Lachaud%\inst{1}
+\and Hugues Talbot%\inst{2}
+}
 %
@@
 %
-\institute{Universit{\'e} Savoie Mont Blanc, LAMA, UMR CNRS 5127, F-73376, France
-\email{daniel.martins-antunes, jacques-olivier.lachaud@univ-savoie.fr} \and
-CentraleSupelec Inria \'equipe OPIS, Universit\'e Paris-Saclay, 9 rue Joliot-Curie, F-91190 Gif-sur-Yvette \\
+\institute{%Universit{\'e} Savoie Mont Blanc, LAMA, UMR CNRS 5127, F-73376, France
+  Daniel Antunes \at
+  Univ. Grenoble Alpes, Univ. Savoie Mont Blanc, CNRS, LAMA, 73000 Chambéry, France \\
+  \email{daniel.martins-antunes@univ-smb.fr} \and
+  Jacques-Olivier~Lachaud \at  Univ. Grenoble Alpes, Univ. Savoie Mont Blanc, CNRS, LAMA, 73000 Chambéry, France \\
+  \email{jacques-olivier.lachaud@univ-smb.fr} \and
+  Hugues Talbot \at CentraleSupelec Inria \'equipe OPIS, Universit\'e Paris-Saclay, 9 rue Joliot-Curie, F-91190 Gif-sur-Yvette \\
   \email{hugues.talbot@centralesupelec.fr}}

### 2019-07-08 jmiv.tex
Relecture intro

@@
   Geometric priors have been shown to be useful in image segmentation to regularize results. For example, the classical
-    Mumford-Shah functional uses regions perimeter as prior. This has inspired much research in the last few decades,
+    Mumford-Shah functional uses region perimeter as prior. This has inspired much research in the last few decades,
     with classical approaches like the Rudin-Osher-Fatemi and most graph-cut formulations, which all use a weighted or
@@
     underlying optimisation processes are not convex. In this article, we propose to formulate a digital flow that
-    approximates a curvature-related flow using a multigrid-convergent curvature estimator, within a discrete
-    variational framework. We also present an application of this model as a post-processing step in a segmentation
+    approximates an Elastica-related flow using a multigrid-convergent curvature estimator, within a discrete
+    variational framework. We also present an application of this model as a post-processing step to a segmentation
     framework.

### 2019-07-08 jmiv.tex
Relecture 1 finie

@@
 
-Geometric quantities are particularly useful as regularizers in low-level image analysis, especially when little prior
-information is known about the shape of interest. Length penalization is a \HT{well-behaved,} general purpose
-regularizer and \HT{many} models \HT{in the literature} make use of it, from active contours \cite{casseles97geodesic}
-to level-set formulations \cite{malladi1995image,malladi1995shape}. Discrete graph-based variational models have been
-particularly succesfull to incorporate length penalization as a penalizer, while keeping the ability to extract \HT{a}
-global optimum \cite{boykov01graphcut,appleton05geodesic}.
-
-However length regularization shows limitations when segmenting small or thin and elongated objects, as it tends to
-shrink solutions or \HT{yields} disconnected solutions. Such drawbacks can be problematic in image segmentation, image
-restoration or image inpainting. It is thus rather natural to consider curvature (especially squared curvature) \HT{as}
-a potential regularizer. Energies involving \HT{both length and} squared curvature are often called \HT{the {\em Elastica}}
-model (\HT{that} dates back to Euler) . \HT{The {\em Willmore energy} is its $n$-dimensional extension. These were brought to
-attention} in computer vision by Mumford \cite{mumford1994elastica}. A similar concept is also present in the
-second-order regularizer of the \HT{original} snake model \cite{kass1988snakes}. \HT{Indeed, an explicit curvature
-  term was often employed in early level-set methods, like~\cite{malladi1995image,malladi1995shape,ballester01filljoint}
-  for segmentation or inpainting,} \HT{However, Casselles {\em et al.} in~\cite{casseles97geodesic} observed that these
-  terms as employed were not geometric, in the sense that they depended on the discretization parameters}.
+Geometric quantities are particularly useful as regularizers in
+low-level image analysis, especially when little prior information is
+known about the shape of interest. Length penalization is a
+well-behaved, general purpose regularizer and many models in the
+literature make use of it, from active contours
+\cite{casseles97geodesic} to level-set formulations
+\cite{malladi1995image,malladi1995shape}. Discrete graph-based
+variational models have been particularly succesful to incorporate
+length penalization as a penalizer, while keeping the ability to
+extract a global optimum \cite{boykov01graphcut,appleton05geodesic}.
+
+However length regularization shows limitations when segmenting small
+or thin and elongated objects, as it tends to shrink solutions or
+yields disconnected solutions. Such drawbacks can be problematic in
+image segmentation, image restoration or image inpainting. It is thus
+rather natural to consider curvature (especially squared curvature) as
+a potential regularizer. Energies involving both length and squared
+curvature are often called the {\em Elastica} model (that dates back
+to Euler). The {\em Willmore energy} is its $n$-dimensional
+extension. These were brought to attention in computer vision by
+Mumford \cite{mumford1994elastica}. A similar concept is also present
+in the second-order regularizer of the original snake model
+\cite{kass1988snakes}.Indeed, an explicit curvature term was often
+employed in early level-set methods,
+like~\cite{malladi1995image,malladi1995shape,ballester01filljoint} for
+segmentation or inpainting. However, Casselles {\em et al.}
+in~\cite{casseles97geodesic} observed that these terms as employed
+were not geometric, in the sense that they depend on the
+discretization parameters.
 
 \subsection{Existing works}
-\HT{The use of curvature for surface regularization in the case of the Willmore energy was studied
-  in~\cite{bobenko2005discrete}, although results look promising, authors used an inexact linearized version of the
-  square curvature at every step.}
-
-One of the first successful uses of \HT{geometric, squared} curvature in image processing is the inpainting algorithm
-described in \cite{masnou98inpainting}\HT{, where authors} evaluate
-the absolute curvature along the level lines of a
-simply-connected image to reconstruct its occluded parts. The non-intersection property of level lines \HT{induces} the
-construction of an efficient dynamic programming algorithm. \HT{However, } the curvature energy is \HT{only} coarsely
-approximated.  \cite{chan02elasticainpainting} \HT{is} another geometric inpainting method involving elastica
-\HT{optimized with level-sets}.
-
-In image segmentation, Zehiry and Grady have shown that injecting curvature as a regularizer can help recover thin
-and elongated objects \cite{zehiry10fast}. Similarly Schoenemann {\em et al.}  \cite{schoenemann09linear} have
-considered the elastica energy in their ratio-based image segmentation approach. In~\cite{schoenemann2011elastic},
-Schoenemann~{\em et al.} extend ratio-cut approaches to segmentation with a curvature term. Their global optimization
-framework shows the considerable \HT{advantages} of using such regularizer in common binary image segmentation tasks.
-However the time complexity of their algorithm \HT{is prohibitive,} even if curvature is \HT{again} coarsely
-approximated.  \HT{In more recent work, Lim {\em et al.} propose an edge-weighted Willmore-like flow to segment
-vertebra~\cite{lim2012introducing} using a level-set formulation. They observe improved results compared
-to~\cite{casseles97geodesic} and other perimeter-based priors, but observe that a shape prior and a close-enough
-solution must also be provided to achieve good results.}
-
-In fact, it is still a very challenging task to \HT{efficiently handle} curvature in the context of image segmentation.
-\HT{State-of-art methods are in practice} difficult to optimize and \HT{do not scale easily}
-\cite{zehiry10fast,schoenemann09linear,strandmark11globalframework,nieuwenhuis14efficient}. In order to achieve
-reasonable running times, such approaches make use of coarse curvature estimations for which the approximation error is
-\HT{often} unknown. Improving the quality of the curvature estimator has an important impact on the accuracy of the
-results, but is computationally too costly in these methods.
-
-Segmentation methods using Elastica or Willmore energies \HT{can be formulated via the computation of} corresponding
-flow, i.e. following its gradient. Well-founded level-set methods involving Willmore energy \cite{droske2004level} have
-been used in medical image segmentation \cite{lim2012introducing}. Another level-set formulation similar to the
-Chan-Vese model \HT{was} proposed in \cite{zhu2013image}. Willmore flow can also be carried out by phase-field models
-(see \cite{bretin2015phase}) but they are less suited to image segmentation since interfaces are blurred in such
-models. Threshold dynamics can also be considered for such energies \cite{esedoglu2008threshold} and has been proposed
-for image desocclusion \cite{esedoglu2005threshold}. \HT{However, flow-based methods will always deliver a local
-  minimum, which heavily depend on initialization for good results}.  \HT{A similar approach is to formulate the
-  Elastica as a regularization in a variational framework and use operator splitting to optimize it. Tai {\em et
-    al.}~\cite{tai11elastica} and more recently Deng~{\em et al.}~\cite{deng2019new} have proposed this approach, which
-  is well-suited to inverse problem solving. The problem remains non-convex and the nature of the converged iterate
-are not studied, i.e. how close they are to a global optimum.}
-
-\HT{In contrast, researchers have sought convex relaxation of curvature-related
+The use of curvature for surface regularization in the case of the
+Willmore energy was studied in~\cite{bobenko2005discrete}. Although
+results look promising, authors used an inexact linearized version of
+the square curvature at every step.
+
+One of the first successful uses of geometric, squared curvature in
+image processing is the inpainting algorithm described in
+\cite{masnou98inpainting}, where authors evaluate the absolute
+curvature along the level lines of a simply-connected image to
+reconstruct its occluded parts. The non-intersection property of level
+lines induces the construction of an efficient dynamic programming
+algorithm. The curvature energy is nevertheless only coarsely
+approximated. We may quote \cite{chan02elasticainpainting} as another
+geometric inpainting method involving elastica, which is optimized with
+level-sets.
+
+In image segmentation, Zehiry and Grady have shown that injecting
+curvature as a regularizer can help recover thin and elongated objects
+\cite{zehiry10fast}. Similarly Schoenemann {\em et al.}
+\cite{schoenemann09linear} have considered the elastica energy in
+their ratio-based image segmentation
+approach. In~\cite{schoenemann2011elastic}, Schoenemann~{\em et al.}
+extend ratio-cut approaches to segmentation with a curvature
+term. Their global optimization framework shows the considerable
+advantages of using such regularizer in common binary image
+segmentation tasks.  However the time complexity of their algorithm
+is prohibitive, even if curvature is again coarsely
+approximated.  In a more recent work, Lim {\em et al.} propose an
+edge-weighted Willmore-like flow to segment
+vertebra~\cite{lim2012introducing} using a level-set
+formulation. They observe improved results compared
+to~\cite{casseles97geodesic} and other perimeter-based priors, but
+observe that a shape prior and a close-enough initialization must also be
+provided to achieve good results.
+
+In fact, it is still a very challenging task to efficiently handle
+curvature in the context of image segmentation.  State-of-art methods
+are in practice difficult to optimize and do not scale easily
+\cite{zehiry10fast,schoenemann09linear,strandmark11globalframework,nieuwenhuis14efficient}. In
+order to achieve reasonable running times, such approaches make use of
+coarse curvature estimations for which the approximation error is
+often unknown. Improving the quality of the curvature estimator has an
+important impact on the accuracy of the results, but is
+computationally too costly in these methods.
+
+Segmentation methods using Elastica or Willmore energies can be
+formulated via the computation of the corresponding flow,
+i.e. following its gradient. Well-founded level-set methods involving
+Willmore energy \cite{droske2004level} have been used in medical image
+segmentation \cite{lim2012introducing}. Another level-set formulation
+similar to the Chan-Vese model was proposed in
+\cite{zhu2013image}. Willmore flow can also be carried out by
+phase-field models (see \cite{bretin2015phase}) but they are less
+suited to image segmentation since interfaces are blurred in such
+models. Threshold dynamics can also be considered for such energies
+\cite{esedoglu2008threshold} and has been proposed for image
+desocclusion \cite{esedoglu2005threshold}. However, flow-based methods
+will always deliver a local minimum, which heavily depend on
+initialization for good results. A similar approach is to formulate
+the Elastica as a regularization in a variational framework and use
+operator splitting to optimize it. Tai {\em et
+  al.}~\cite{tai11elastica} and more recently Deng~{\em et
+  al.}~\cite{deng2019new} have proposed this approach, which is
+well-suited to inverse problem solving. The problem remains non-convex
+and the nature of the converged iterates are not studied, i.e. how
+close they are to a global optimum.
+
+In contrast, researchers have sought convex relaxation of curvature-related
 formulation. In~\cite{goldluecke11totalcurvature}, Goldluecke and Cremers introduce the {\em Total Curvature}, based
 on the Menger-Melnikov curvature of a measure. The formulation is non-convex but can be relaxed into a well-correlated
-  but non-tight convex one. The relaxed formulation can be used to solve inverse problems including segmentation,
-  however computing a solution is still expensive, requiring signifiant parallelisation efforts with a GPU to achieve
-  acceptable computing times}. \HT{In~\cite{bredies15convex}, Bredies {\em et al.} study a convex approximation of the
-  Elastica energy, using a lifting scheme. Thanks to the lifting, it is not restritcted to binary sets. It shows
+but non-tight convex one.
+The relaxed formulation can be used to solve inverse problems including segmentation.
+However computing a solution is still expensive, requiring signifiant parallelisation efforts with a GPU to achieve
+  acceptable computing times. In~\cite{bredies15convex}, Bredies {\em et al.} study a convex approximation of the
+  Elastica energy, using a lifting scheme. Thanks to the lifting, it is not restricted to binary sets. It shows
   promising results and can be used for image restoration in addition to inpainting and segmentation. The scheme is
   however neither tight nor exact, and required 4 dimensions for a 2D approximation. In addition, it does not carry over
-to $nD$. It also remains computationally expensive.}
-
-\HT{Discrete approaches have been used to tackle the Elastica difficulties. As noted before~\cite{schoenemann09linear}
-  have linearized a mesh-based approach, which was expanded upon by~\cite{strandmark11globalframework}, while
-  \cite{zehiry10fast} have used a binary solver for a non-submodular approach on a regular square grid of pixels, which
-  was expanded in~\cite{el2016contrast}. In~\cite{nieuwenhuis14efficient} , a specific solver is developed to yield a
-  better solution to an extension of the formulation in~\cite{zehiry10fast}.}
+to $nD$. It also remains computationally expensive.
+
+Discrete approaches have been used to tackle the Elastica
+difficulties. As noted before, \cite{schoenemann09linear} have
+linearized a mesh-based approach, which was expanded upon
+by~\cite{strandmark11globalframework}, while \cite{zehiry10fast} have
+used a binary solver for a non-submodular approach on a regular square
+grid of pixels, which was expanded
+in~\cite{el2016contrast}. In~\cite{nieuwenhuis14efficient} , a
+specific solver is developed to yield a better solution to an
+extension of the formulation in~\cite{zehiry10fast}.
 
 \subsection{Motivation}
-\HT{In spite of the multiplicity of existing approaches, it seems none is currently completely satisfactory. While the
-  sought solution is expected to be very smooth based on geometrical expectations, the mathematical properties
-  of the related operators make this smoothness elusive. Non-convexity and the presence of high-order terms make
-  Elastica difficult to optimize and to approximate, let alone compute efficiently. The computed solution in the
-  literature are rarely evaluated, and the complexity of the proposed solution is often high.}
+In spite of the multiplicity of existing approaches, it seems none is
+currently completely satisfactory. While the sought solution is
+expected to be very smooth based on geometrical expectations, the
+mathematical properties of the related operators make this smoothness
+elusive. Non-convexity and the presence of high-order terms make
+Elastica difficult to optimize and to approximate, let alone compute
+efficiently. The computed solutions in the literature are rarely
+evaluated, and the complexity of the proposed solution is often high.
 
@@
 
-\HT{Consequently,} we are interested in \HT{studying} purely discrete variational segmentation models involving an
-elastica energy. Recently, new estimators of curvature along digital contours have been proposed
-\cite{roussillon11mdca,coeurjolly13integral,schindele17mdca} with the desirable multigrid convergence property. This
-motivates us to propose models in which they can be used successfully.
-
-\HT{In the remainder, we propose to} investigate the use of the digital integral invariant curvature estimator
-\cite{coeurjolly13integral} in a discrete variational segmentation framework. More precisely, we show how to incorporate
-it in a digital flow minimizing its squared curvature. This model is expressible as a discrete combinatorial
-optimization model, which we solve using a classical variant of QPBO algorithm \cite{rother07qpbo}. \HT{Our solution
-  does not} compute a global solution to the whole domain, but our approach leads to a digital flow similar to
-continuous \HT{Elastica}, as shown by our experiments. We present an application of the model as a post-processing step
-in a segmentation framework, and demonstrate how it can improve standard results. 
-\daniel{This paper is an extended version of a previous work that appeared in \cite{antunes19}. We've included a deeper
-  discussion on the optimization method we've used and we present a comparison of our segmentation method with two other
-  related works, and illustrate the results with several examples. Moreover, we have included a new local combinatorial
-  optimization approach for elastica minimization. Finnaly,  the code produced in this paper is freely available on
-  github\footnote{https://www.github.com/danoan/BTools}.}
-
-\subsection{Outline}.
-Section two reviews the concept of multigrid convergence and highlights its importance for the
-definition of digital estimators. Next, we describe two convergent estimators used in this paper, one for tangent and
-the other for curvature. They are used in the optimization model and in the definition of the digital elastica. Section
-three describes a local combinatorial optimization model suitable for different curvature estimators. Section four
-describes the proposed curvature evolution model along with several illustrations of digital flows. Section five
-explains how to use the evolution model as a post-processing step in an image segmentation framework.
+Consequently, we are interested in studying purely discrete
+variational segmentation models involving an Elastica
+energy. Recently, new estimators of curvature along digital contours
+have been proposed
+\cite{roussillon11mdca,coeurjolly13integral,schindele17mdca} with the
+desirable multigrid convergence property. This motivates us to propose
+models in which they can be used successfully.
+
+In this paper, we propose to investigate the use of the digital
+integral invariant curvature estimator \cite{coeurjolly13integral} in
+a discrete variational segmentation framework. More precisely, we show
+how to incorporate it in a digital flow minimizing its squared
+curvature. This model is expressible as a discrete combinatorial
+optimization model, which we solve using a classical variant of QPBO
+algorithm \cite{rother07qpbo}. Our solution does not compute a global
+solution to the whole domain but a global solution to a band
+surrounding a given shape. Our approach thus leads to a digital flow
+similar to continuous Elastica, as shown by our experiments. We
+present an application of this model as a post-processing step in a
+segmentation framework, and demonstrate how it can improve standard
+results. This paper is an extended version of a previous work that
+appeared in \cite{antunes19}. We have included a deeper discussion on
+our optimization method and we present a more thorough comparison of
+our segmentation method with two other related works. Moreover, we
+have included a new local combinatorial optimization approach for
+elastica minimization, which show that our discrete model is
+well-founded. Finally, the code produced in this paper is freely
+available on github.\footnote{https://www.github.com/danoan/BTools}
+
+\subsection{Outline}
+Section~2 reviews the concept of multigrid convergence and highlights
+its importance for the definition of digital estimators. We describe
+two convergent estimators used in this paper, one that approaches the
+length of elementary discrete contour elements, and the other that
+approaches the curvature of a discrete contour. They are used in the
+optimization model and in the definition of the digital
+elastica. Section~3 describes a local combinatorial optimization model
+suitable for different curvature estimators, that presents interesting
+results but is too costly in practice. Section~4 describes the
+proposed Elastica-driven curvature evolution model along with several
+illustrations of digital flows. Section~5 explains how to use this
+evolution model as a post-processing step in an image segmentation
+framework and compares it to two related approaches. We conclude and
+draw some perspectives to this work in Section~6.
 

### 2019-07-08 cover-letter/cover-letter.tex
Cover letter

\documentclass{article}

\usepackage[utf8]{inputenc}
\usepackage{hyperref,cite}
%\signature{Daniel Antunes, Jacques-Olivier Lachaud, Hugues Talbot}
%\address{}

\begin{document}
%\begin{letter}{}
%\opening{Dear editors:}

Dear editors:\\

With respect to the work in \cite{antunes19}, the authors have included three new contributions. In section three, we describe a new local combinatorial optimization method to evolve a flow driven by the minimization of the digital elastica energy. The method is suitable for two multigrid convergent estimators of curvature, and the results are illustrated with figures and a small discussion about the running time. In section four, we extend the digital evolution model described in \cite{antunes19}. In particular, we generalize the evolution model in and we define a family of energies, each one giving rise to a new evolution model. We've included a discussion with respect to the QPBOP optimization method and how the number of unlabeled pixels varies in the family of energies. Remarkably, QPBOP labels all variables for one of the energies in the family. Finally, in section five, we compared our segmentation method with two other algorithms: GrabCut \cite{rother04grabcut} and Schoenemmans's \cite{schoenemann09linear}, and we illustrate the results with several figures.

\bibliographystyle{plain}
\bibliography{../jmiv.bib}

%\end{letter}

\end{document}

### 2019-07-08 cover-letter/cover-letter.tex
Update cover letter

@@
-\documentclass{article}
+\documentclass{letter}
+%\documentclass{article}
 
@@
 \usepackage{hyperref,cite}
+\usepackage[a4paper, total={7in, 10in}]{geometry}
 %\signature{Daniel Antunes, Jacques-Olivier Lachaud, Hugues Talbot}
@@
 
+\makeatletter
+\newenvironment{thebibliography}[1]
+     {\list{\@biblabel{\@arabic\c@enumiv}}%
+           {\settowidth\labelwidth{\@biblabel{#1}}%
+            \leftmargin\labelwidth
+            \advance\leftmargin\labelsep
+            \usecounter{enumiv}%
+            \let\p@enumiv\@empty
+            \renewcommand\theenumiv{\@arabic\c@enumiv}}%
+      \sloppy
+      \clubpenalty4000
+      \@clubpenalty \clubpenalty
+      \widowpenalty4000%
+      \sfcode`\.\@m}
+     {\def\@noitemerr
+       {\@latex@warning{Empty `thebibliography' environment}}%
+      \endlist}
+\newcommand\newblock{\hskip .11em\@plus.33em\@minus.07em}
+\makeatother
+
+\signature{Daniel Antunes, Jacques-Olivier Lachaud, Hugues Talbot}
 \begin{document}
-%\begin{letter}{}
-%\opening{Dear editors:}
+\begin{letter}{Cover letter for paper ``An Elastica-driven Digital Curve Evolution Model for Image Segmentation''}
+\opening{Dear editors,}
 
-Dear editors:\\
-
-With respect to the work in \cite{antunes19}, the authors have included three new contributions.
+This paper is an extension version of the DGCI'19 paper ``Digital Curvature Evolution Model for Image Segmentation'' \cite{antunes19}.
+We have included three new contributions.
 In section three, we describe a new local combinatorial optimization method to evolve a flow driven by the minimization of the digital elastica energy.
@@
 In section four, we extend the digital evolution model described in \cite{antunes19}.
-In particular, we generalize the evolution model in and we define a family of energies, each one giving rise to a new evolution model.
+In particular, we generalize the curve evolution model  and we define a family of energies, each one giving rise to a new evolution model.
 We've included a discussion with respect to the QPBOP optimization method and how the number of unlabeled pixels varies in the family of energies.
@@
 
+Thank you for your time and consideration.
+
+\closing{Yours Faithfully,}
+
 \bibliographystyle{plain}
 \bibliography{../jmiv.bib}
+
+\end{letter}
 

### 2019-07-08 jmiv.tex
relec HT

@@
   \email{jacques-olivier.lachaud@univ-smb.fr} \and
-  Hugues Talbot \at CentraleSupelec Inria \'equipe OPIS, Universit\'e Paris-Saclay, 9 rue Joliot-Curie, F-91190 Gif-sur-Yvette \\
+  Hugues Talbot \at CentraleSupelec, Inria, Universit\'e Paris-Saclay, 9 rue Joliot-Curie, F-91190 Gif-sur-Yvette \\
   \email{hugues.talbot@centralesupelec.fr}}
@@
 \section{Multigrid convergent estimators}
-
-The goal of this section is to  introduce the concept of multigrid convergenc and its potential when analyzing digital images with variational models involving geometric quantities.
-More precisely we wish to delineate shapes within digital images with some priors related to their unknown continuous geometry.
-Of course we only observe shape digitizations within images.
+Our objective is to delineate shapes within digital images with some priors related to continuous geometry. The goal of
+this section is to introduce the concept of multigrid convergence and its potential when analyzing digital images with
+variational models involving geometric quantities, with the constraint that only digitized shapes are observed.
 

### 2019-07-08 jmiv.tex
fatigue

@@
 approximated. We may quote \cite{chan02elasticainpainting} as another
-geometric inpainting method involving elastica, which is optimized with
+geometric inpainting method involving Elastica, which is optimized with
 level-sets.
@@
 \cite{zehiry10fast}. Similarly Schoenemann {\em et al.}
-\cite{schoenemann09linear} have considered the elastica energy in
+\cite{schoenemann09linear} have considered the Elastica energy in
 their ratio-based image segmentation
@@
 The literature presents several perimeter estimators that are multigrid convergent (see
-\cite{coeurjolly04comparative,coeurjolly12multigrid} for a review), but in order to define the digital elastica we need a local estimation
+\cite{coeurjolly04comparative,coeurjolly12multigrid} for a review), but in order to define the digital Elastica we need a local estimation
 of length and we wish that integration over these local length elements gives a multigrid convergent estimator for the
@@
 \begin{definition}	
-  Given a digital shape $D \subset (h \mathbb{Z})^2$,  the area estimatir $\widehat{Area}(D,h)$ is defined as	
+  Given a digital shape $D \subset (h \mathbb{Z})^2$,  the area estimatir $\widehat{\text{Area}}(D,h)$ is defined as	
   \begin{align}
-    \widehat{Area}(D,h) \coloneqq h^2\text{Card}\left( D \right).	
+    \widehat{\text{Area}}(D,h) \coloneqq h^2\text{Card}\left( D \right).	
     \label{eq:digital_estimator_area}
@@
   \begin{align*}
-    \hat{\kappa}_{r}(D,x,h) \coloneqq \frac{3}{r^3} \left( \frac{\pi r^2}{2} - \widehat{Area} \left( B_{r} ( x ) \cap D, h \right) \right).
+    \hat{\kappa}_{r}(D,x,h) \coloneqq \frac{3}{r^3} \left( \frac{\pi r^2}{2} - \widehat{\text{Area}} \left( B_{r} ( x ) \cap D, h \right) \right).
     %% \hat{\kappa}_{r}(D,x,h) \coloneqq \frac{3}{r^3} \left( \frac{\pi r^2}{2} - \widehat{Area} \left( B_{r/h} ( \frac{1}{h} \cdot x ) \cap D, h \right) \right).
@@
 
-In the remaining of this paper we are going to be interested in the minimization of the elastica energy. Given a Euclidean shape $X$ with smooth enough boundary, the elastica is defined as
+In the remaining of this article, we are considering in the minimization of the Elastica energy. Given a Euclidean shape $X$ with smooth enough boundary, the Elastica is defined as
 \begin{align}
@@
 
-The digital version of elastica energy approaching the continuous elastica energy is defined as follows (it uses multigrid convergent estimators):
+The digital version of Elastica energy approaching the continuous Elastica energy is defined as follows (it uses multigrid convergent estimators):
 \begin{align}
@@
 
-The objectives of this section is to show both the potential of minimizing a purely digital elastica energy but also to underline the difficulties of using it in a global combinatorial optimization framework.
+The objectives of this section is to show both the potential of minimizing a purely digital Elastica energy but also to underline the difficulties of using it in a global combinatorial optimization framework.
 
 Given a digital shape $S^{(0)}$ we describe a process that generates a
-sequence $S^{(i)}$ of shapes with non-increasing elastica energy. The
+sequence $S^{(i)}$ of shapes with non-increasing Elastica energy. The
 idea is to define a neighborhood of shapes $\mathcal{N}^{(i)}$ to the
@@
 
-The running time of algorithm \ref{alg:local-search} is summarized in
-table \ref{tab:summary-local-comb-rtime}.
-All the experiments in this paper were executed on a five core $3.4Ghz$ cpu and the number of pixels in the triangle, square and flower shapes are respectively $841,1867,521$ for grid step $h=1.0$.
-Although its use in practical applications is limited, we
-demonstrate that digital estimators are effective in their measurements
-and the flows evolve as expected. We observe that it is a
-complete digital approach, and we do not suffer from discretization
-and rounding problems, a common issue in continuous models.
-Furthermore we have checked that this approach works
-indifferently with Integral Invariant curvature estimator and
-Maximal Digital Circular Arc curvature estimator. So the convergence
-of the digital curvature estimator seems to be the cornerstone to
-get a digital curve behaving like a continuous elastica.  In the
-next section, we explore a more efficient approach.
+The running time of algorithm \ref{alg:local-search} is summarized in table \ref{tab:summary-local-comb-rtime}. All the
+experiments in this paper were executed on a five-core $3.4Ghz$ CPU and the number of pixels in the triangle, square and
+flower shapes are respectively $841,1867,521$ for grid step $h=1.0$. Although its use in practical applications is
+limited, we demonstrate that digital estimators are effective in their measurements and the flows evolve as expected. We
+observe that it is a complete digital approach, and we do not suffer from discretization and rounding problems, a common
+issue in continuous models.  Furthermore we have checked that this approach works indifferently with Integral Invariant
+curvature estimator and Maximal Digital Circular Arc curvature estimator. So the convergence of the digital curvature
+estimator seems to be the cornerstone to get a digital curve behaving like a continuous Elastica.  In the next section,
+we explore a more efficient approach.
 
@@
 
-Recall that the integral invariant estimator approaches curvature by
-computing the difference between half of the area of a chosen ball and
-the area of the intersection of this ball with the shape.  In
-particular, regions of positive curvature have fewer pixels in their
-intersection set than on its complement wrt the estimation ball. This
-implies that variables in such regions are labeled one, as the
-unbalance grows otherwise. We attenuate curvature if we shift the
-center of the estimation ball towards the interior of the shape, which
-means removing the labeled one pixels. That is why we take the
-complement of the optimization solution.
-
-The same reasoning applies for non-convex parts. Indeed, concave
-regions are convex in the shape complement. In the expansion mode we
-apply the same reasoning on the image complement, and by doing this we
-are able to handle concavities. It is called expansion mode because
-the optimization region, in this case, is the outer pixel boundary of
-the original shape. Table~\ref{tab:flow-summary} sums up these
-arguments.
-
-Length and similarity terms should be properly defined in order to
-comply with the complement step of the DCE algorithm. The length
-penalization is defined as
+Recall that the integral invariant estimator approaches curvature by computing the difference between half of the area
+of a chosen ball and the area of the intersection of this ball with the shape.  In particular, regions of positive
+curvature have fewer pixels in their intersection set than on its complement w.r.t the estimation ball. This implies
+that variables in such regions are labeled with 1, as the unbalance grows otherwise. We attenuate curvature if we shift
+the center of the estimation ball towards the interior of the shape, which means removing the 1-labeled pixels. That is
+why we take the complement of the optimization solution.
+
+The same reasoning applies for non-convex parts. Indeed, concave regions are convex in the shape complement. In the
+expansion mode we apply the same reasoning on the image complement, and by doing this we are able to handle
+concavities. It is called expansion mode because the optimization region, in this case, is the outer pixel boundary of
+the original shape. Table~\ref{tab:flow-summary} sums up these arguments.
+
+Length and similarity terms should be properly defined in order to comply with the complement step of the DCE
+algorithm. The length penalization is defined as
 \begin{align}
@@
 radius (see figure \ref{fig:mx-square-flow} ).
-We observe that elastica may increase after some iterations if chosen radius is too large, as in the case of the triangle in figure \ref{fig:mx-flow-gs-radius-effect} in which the flow converges to a single point.
+We observe that Elastica may increase after some iterations if chosen radius is too large, as in the case of the triangle in figure \ref{fig:mx-flow-gs-radius-effect} in which the flow converges to a single point.
 We conjecture that an appropriated value for the radius should be given by the shape reach.
@@
 We have studied in depth several digital curve evolution models based
-on the elastica energy and we have presented an application of one of
+on the Elastica energy and we have presented an application of one of
 them to image segmentation. The processes we have described are

### 2019-07-08 jmiv.tex
fatigue

@@
 
-We do not use similarity terms in this section, thus we postpone the
-definition of such terms until the description of how DCE can be used
-in an image segmentation framework.
+We do not use similarity terms in this section, thus we postpone the definition of such terms until later in this
+article, with the description of how DCE can be used in an image segmentation framework.
 
@@
 
-In figure \ref{fig:m1-square-flow} we see some results for the DCE
-algorithm with $m=1$. We observe a global movement towards roundness,
-but with several artifacts. We minimize the effects of a jaggy
-boundary by setting $\alpha > 0$. Nonetheless, a higher estimation
-ball radius creates unstable shapes. In fact, the estimator is very
-sensitive in regions of low squared curvature, and it is precisely in
-those regions that spurious pixels are created.
+In figure \ref{fig:m1-square-flow} we see some results for the DCE algorithm with $m=1$. We observe a global evolution
+towards rounder shapes, but with several artifacts. We minimize the effects of a jaggy boundary by setting $\alpha >
+0$. Nonetheless, a higher estimation ball radius creates unstable shapes. In fact, the estimator is very sensitive in
+regions of low squared curvature, and it is precisely in those regions that spurious pixels are created.
 
@@
 \subsection{A more stable model.}
-In the previous section we noticed that the algorithm produces shapes
-with many artifacts due to the small uncertainties of the estimator
-along regions of low squared curvature. We argue that, evaluating the
-estimation ball along farther ring sets we avoid those sensitive areas
-by focusing the optimization process only on regions with highest
-squared curvature value.
+In the previous section we noticed that the algorithm produces shapes with many artifacts due to the small uncertainties
+of the estimator along regions of low squared curvature. We argue that, evaluating the estimation ball along outer
+ring sets we avoid those sensitive areas by focusing the optimization process only on regions with highest squared
+curvature value.
 
@@
 
-\daniel{In our experiments, the best results are obtained by executing DCE
-algorithm with $m$ equal to $r$, where $r$ is the estimation ball
-radius (see figure \ref{fig:mx-square-flow} ).
-We observe that Elastica may increase after some iterations if chosen radius is too large, as in the case of the triangle in figure \ref{fig:mx-flow-gs-radius-effect} in which the flow converges to a single point.
-We conjecture that an appropriated value for the radius should be given by the shape reach.
-	The produced flow has no difficulties in handling changes on topology, and it presents different speeds for regions with low and high curvature values, as illustrated in figure \ref{fig:mx-speed-variation-hole-filling}.}
+\daniel{In our experiments, the best results are obtained by executing DCE algorithm with $m$ equal to $r$, where $r$ is
+  the estimation ball radius (see figure \ref{fig:mx-square-flow} ). We observe that Elastica may increase after some
+  iterations if chosen radius is too large, as in the case of the triangle in figure \ref{fig:mx-flow-gs-radius-effect}
+  in which the flow converges to a single point. We conjecture that an appropriated value for the radius should be given
+  by the shape reach.  The produced flow has no difficulties in handling changes on topology, and it presents different
+  speeds for regions with low and high curvature values, as illustrated in figure
+  \ref{fig:mx-speed-variation-hole-filling}.}
 

### 2019-07-08 jmiv.tex
fatigue

@@
 
-\daniel{In our experiments, the best results are obtained by executing DCE algorithm with $m$ equal to $r$, where $r$ is
+{In our experiments, the best results are obtained by executing DCE algorithm with $m$ equal to $r$, where $r$ is
   the estimation ball radius (see figure \ref{fig:mx-square-flow} ). We observe that Elastica may increase after some
@@
   speeds for regions with low and high curvature values, as illustrated in figure
-  \ref{fig:mx-speed-variation-hole-filling}.}
+  \ref{fig:mx-speed-variation-hole-filling}.
 
@@
 
-Energy $E_m$ is non-submodular and optimizing it is a difficult
-problem, which constrains us to use heuristics and approximation
-algorithms. The QPBO method \cite{rother07qpbo} transforms the
-original problem in a max-flow/min-cut formulation and returns a full
-optimal labeling for submodular energies. For non-submodular energies
-the method is guaranteed to return a partial labeling with the
-property that the set of labeled variables is part of an optimal
+Energy $E_m$ is non-submodular and optimizing it is a difficult problem, which constrains us to use heuristics and
+approximation algorithms. The QPBO method \cite{rother07qpbo} transforms the original problem in a max-flow/min-cut
+formulation and yields a full optimal labeling for submodular energies. For non-submodular energies the method is
+guaranteed to return a partial labeling with the property that the set of labeled variables is part of an optimal
 solution. That property is called partial optimality.
 
-In practice, QPBO can leave many pixels unlabeled. There exist two
-extensions of QPBO that alleviate this limitation: QPBOI (improve) and
-QPBOP (probe). The first is an approximation method that is guaranteed
-to not increase the energy, but we lost the property of partial
-optimality. The second is an exact method which is reported to label
-more variables than QPBO.
-
-The percentage of unlabeled pixels by QPBOP for $E_1$ is quite high,
-but the percentage decreases to zero as we set $m$ equal to
-$r$. Therefore, we are more confident to take the solution for values
-of $m$ close to $r$. However, the way it varies across $m$ values
-differs from shape to shape, as is illustrated in figure
-\ref{fig:unlabeled-versus-iterations}. We also noticed that, for
-$m=r$, all the pixels were labeled, \daniel{which may indicate that $E_r$ is an an easy 
-instance of the general non-submodular energy $E_m$, but this remains to be proved. The number of pairwise
-terms in $E_r$ is roughly half of those in $E_1$ (see figure \ref{fig:ratio-pairwise-terms}).}
-
-We have used QPBOI to solve $E_m$. Naturally, in the case where all
-pixels are labeled by QPBOP, QPBOI returns the same labeling as QPBOP.
+In practice, QPBO can leave many pixels unlabeled. There exist two extensions to QPBO that alleviate this limitation:
+QPBOI (improve) and QPBOP (probe). The first is an approximation method that is guaranteed to not increase the energy,
+but loses the property of partial optimality. The second is an exact method which is reported to label more variables
+than QPBO.
+
+The percentage of unlabeled pixels by QPBOP for $E_1$ is quite high, but the percentage decreases to zero as we set $m$
+equal to $r$. Therefore, we are more confident in taking the solution for values of $m$ close to $r$. However, the way it
+varies across $m$ values differs from shape to shape, as is illustrated in figure
+\ref{fig:unlabeled-versus-iterations}. We also noticed that, for $m=r$, all the pixels were labeled, {which may
+  indicate that $E_r$ is an an easy instance of the general non-submodular energy $E_m$, but this remains to be
+  proved. The number of pairwise terms in $E_r$ is roughly half of those in $E_1$ (see figure
+  \ref{fig:ratio-pairwise-terms}).
+
+  We have used QPBOI to solve $E_m$. Naturally, in the case where all pixels are labeled by QPBOP, QPBOI returns the
+  same labeling as QPBOP.
 

### 2019-07-08 jmiv.tex
fatigue

@@
 
-We present an application of our digital curve evolution algorithm to supervised image segmentation.
-The DCE will act as a contour correction method.
-Here we are going to use a data fidelity term in order to characterize the object of interest.
-Given foreground and background seeds selected by the user, we derive mixed gaussian distributions  of color intensities $G_f$ and $G_b$, and we define the data fidelity term as
+We present an application of our digital curve evolution algorithm to supervised image segmentation. The DCE acts as a
+contour correction method. Here we are going to use a data fidelity term in order to characterize the object of
+interest. Given foreground and background seeds selected by the user, we derive mixed gaussian distributions  of color
+intensities $G_f$ and $G_b$, and we define the data fidelity term as the cross-entropy, i.e.
 

### 2019-07-08 jmiv.tex
fatigue

@@
 elastica. Section~3 describes a local combinatorial optimization model
-suitable for different curvature estimators, that presents interesting
+suitable for several curvature estimators, that presents interesting
 results but is too costly in practice. Section~4 describes the
@@
 The number of unlabeled pixels by QPBOP remains high for lower values of $m$, and goes to zero when $m=r$.
-We observe the same behaviour for different radius values.}
+We observe the same behaviour for varying radius values.}
 \label{fig:unlabeled-versus-iterations}
@@
 We present an application of our digital curve evolution algorithm to supervised image segmentation. The DCE acts as a
-contour correction method. Here we are going to use a data fidelity term in order to characterize the object of
+contour correction method. Here we use a data fidelity term in order to characterize the object of
 interest. Given foreground and background seeds selected by the user, we derive mixed gaussian distributions  of color
@@
 
-\daniel{In figure \ref{fig:parameters-influence} we can observe the results of a curvature regularization in comparison with a pure length regularization.
-The curvature can fill gaps and is smoother than the one produced by length only, resulting in more pleasant segmentations.
-In figures \ref{fig:segmentation-results} and \ref{fig:more-segmentation-results} we list several results of our method and we compare them with segmentation produced by GrabCut and Schoenemann's method.
-Our method is successful in producing curvature regularized segmentations and demonstrates the completion property of curvature.
-Moreover, it does not suffer from over segmentation, it is faster than Schoenemann's, and in several opportunities produces better segmentations than GrabCut.}
+{In figure \ref{fig:parameters-influence} we can observe the results of a curvature regularization in comparison with a
+  pure length regularization. The curvature can fill gaps and is smoother than the one produced by length only,
+  resulting in more pleasant segmentations. In figures \ref{fig:segmentation-results} and
+  \ref{fig:more-segmentation-results} we list several results of our method and we compare them with segmentation
+  produced by GrabCut and Schoenemann's method. Our method is successful in producing curvature regularized
+  segmentations and demonstrates the completion property of curvature. Moreover, it does not suffer from over
+  segmentation, it is much faster than Schoenemann's, and in several opportunities produces better segmentations than
+  GrabCut.
 
@@
 
-We have studied in depth several digital curve evolution models based
-on the Elastica energy and we have presented an application of one of
-them to image segmentation. The processes we have described are
-completely digital, and do not suffer from issues that typically
-arises in models that passes through a discretization stage, as
-rounding. Moreover, the model can handle changes in topology and its
-results are competitive with similar approaches while achieving
-reasonable running times.
-
-Future developments of this work may include automatization, no more
-dependence on seeds selected by the user and automatic choice of ball
-estimation radius based on the reach of the shape. One can also think
-to extend the DCE algorithm to $3$d, as the integral invariant
-estimator preserves its properties in that space. In future works, a
-denoising application may be derived by running the flow on the $3$d
-shape with data fidelity defined by image intensities or by distance
-to initial position.
+We have studied in depth several digital curve evolution models based on a digital version of the Elastica energy and we
+have presented an application to image segmentation. The processes we have described are completely digital, and do not
+suffer from issues that typically arise in models that passes through a discretization stage, such as
+rounding. Moreover, the model can handle changes in topology and its results are competitive with similar approaches
+while achieving reasonable running times.
+
+Future developments of this work will include extending the DCE algorithm to $3$d, as the integral invariant estimator
+is available in higher dimensions. As a result, a denoising application may be derived by lifting the flow to $3$d
+with a data fidelity defined by image intensities or by distance to initial position.
 

### 2019-07-08 cover-letter/cover-letter.tex
relec HT

@@
 
-This paper is an extension version of the DGCI'19 paper ``Digital Curvature Evolution Model for Image Segmentation'' \cite{antunes19}.
-We have included three new contributions.
-In section three, we describe a new local combinatorial optimization method to evolve a flow driven by the minimization of the digital elastica energy.
-The method is suitable for two multigrid convergent estimators of curvature, and the results are illustrated with figures and a small discussion about the running time.
-In section four, we extend the digital evolution model described in \cite{antunes19}.
-In particular, we generalize the curve evolution model  and we define a family of energies, each one giving rise to a new evolution model.
-We've included a discussion with respect to the QPBOP optimization method and how the number of unlabeled pixels varies in the family of energies.
-Remarkably, QPBOP labels all variables for one of the energies in the family.
-Finally, in section five, we compared our segmentation method with two other algorithms: GrabCut \cite{rother04grabcut} and Schoenemmans's \cite{schoenemann09linear}, and we illustrate the results with several figures.
+Our article is an extension version of the DGCI'19 paper ``Digital
+Curvature Evolution Model for Image Segmentation''
+\cite{antunes19}. We have included three new contributions. In section
+three, we describe a new local combinatorial optimization method to
+evolve a flow driven by the minimization of the digital Elastica
+energy. The method is suitable for two multigrid convergent estimators
+of curvature, and the results are illustrated with figures and a small
+discussion about the running time. In section four, we extend the
+digital evolution model described in \cite{antunes19}. In particular,
+we generalize the curve evolution model and we define a family of
+energies, each one giving rise to a new evolution model. We've
+included a discussion with respect to the QPBOP optimization method
+and how the number of unlabeled pixels varies in the family of
+energies. Remarkably, QPBOP labels all variables for one of the
+energies in the family. Finally, in section five, we compared our
+segmentation method with two other algorithms: GrabCut
+\cite{rother04grabcut} and Schoenemmans's \cite{schoenemann09linear},
+and we illustrate the results with several figures.
 

### 2019-07-09 images/local_search/graph-plot.sh
Modified plots

@@ -1,0 +1,85 @@
+#!/usr/bin/env bash
+
+gp_save()
+{
+	printf "set size 1.0, 0.6;
+		set terminal postscript portrait enhanced color dashed lw 2 \"Helvetica\" 20;
+		set key right top;
+		set output \"my-plot.ps\";
+		replot;
+		set terminal x11;
+		set size 1,1;"
+}
+
+gp_plot_config()
+{
+    #set yrange [-0.1:1.1]; 
+    printf "set title '$1';
+    set xlabel 'Iterations';
+    set ylabel 'Elastica ({/Symbol a}=0.1, {/Symbol b}=1)';"
+}
+
+
+gp_add_plot()
+{
+    printf "'$1' u 1:2 w l title '$2',"
+}
+
+gp_last_plot()
+{
+	printf "'$1' u 1:2 w l title '$2';"
+}
+
+
+create_multiplot()
+{
+	fileoutput=$1;shift;
+	plottitle="$1";shift;
+
+	buffer="$(gp_plot_config "$plottitle")plot "
+	i=0
+	num_plots=`expr ${#} / 2 - 1`
+
+	while [ ${i} -lt ${num_plots} ]
+	do
+		subplotDataFile=$1
+		subplotTitle=$2
+		buffer="${buffer}$(gp_add_plot $subplotDataFile $subplotTitle)"
+		shift; shift;
+
+		i=`expr $i + 1`
+	done
+
+	if [ $num_plots -eq 0 ]
+	then
+		buffer="${buffer}$(gp_last_plot $1 $2)"
+	else
+		buffer="${buffer}$(gp_last_plot $1 $2)"
+	fi
+
+	buffer="${buffer}$(gp_save)"
+
+
+	`gnuplot -e "$buffer"`
+	`mv my-plot.ps ${fileoutput}`
+}
+
+
+
+
+BASE_FOLDER=$(realpath $1)
+PLOTS_OUTPUT=$(realpath $2)
+FILENAME_OUTPUT=$3
+
+mkdir -p $PLOTS_OUTPUT
+OUTPUT_PLOT=${PLOTS_OUTPUT}/${FILENAME_OUTPUT}
+
+
+PLOT_STRING="$OUTPUT_PLOT ''"
+PLOT_STRING="${PLOT_STRING} ${BASE_FOLDER}/output/model/h$gs/radius-$radius/$shape/$method/$mode/level-$i.txt m=$i"
+
[…]

### 2019-11-28 jmiv.tex
typos correction

@@
 literature make use of it, from active contours
-\cite{casseles97geodesic} to level-set formulations
+\cite{caseles97geodesic} to level-set formulations
 \cite{malladi1995image,malladi1995shape}. Discrete graph-based
@@
 like~\cite{malladi1995image,malladi1995shape,ballester01filljoint} for
-segmentation or inpainting. However, Casselles {\em et al.}
-in~\cite{casseles97geodesic} observed that these terms as employed
+segmentation or inpainting. However, Caselles {\em et al.}
+in~\cite{caseles97geodesic} observed that these terms as employed
 were not geometric, in the sense that they depend on the
@@
 formulation. They observe improved results compared
-to~\cite{casseles97geodesic} and other perimeter-based priors, but
+to~\cite{caseles97geodesic} and other perimeter-based priors, but
 observe that a shape prior and a close-enough initialization must also be
@@
 \cite{esedoglu2008threshold} and has been proposed for image
-desocclusion \cite{esedoglu2005threshold}. However, flow-based methods
+disocclusion \cite{esedoglu2005threshold}. However, flow-based methods
 will always deliver a local minimum, which heavily depend on
@@
 The relaxed formulation can be used to solve inverse problems including segmentation.
-However computing a solution is still expensive, requiring signifiant parallelisation efforts with a GPU to achieve
+However computing a solution is still expensive, requiring significant parallelisation efforts with a GPU to achieve
   acceptable computing times. In~\cite{bredies15convex}, Bredies {\em et al.} study a convex approximation of the
@@
 grid of pixels, which was expanded
-in~\cite{el2016contrast}. In~\cite{nieuwenhuis14efficient} , a
+in~\cite{el2016contrast}. In~\cite{nieuwenhuis14efficient}, a
 specific solver is developed to yield a better solution to an
@@
 elastica minimization, which show that our discrete model is
-well-founded. Finally, the code produced in this paper is freely
+well-founded. Finally, the code related to this paper is freely
 available on github.\footnote{https://www.github.com/danoan/BTools}
@@
 \begin{definition}	
-  Given a digital shape $D \subset (h \mathbb{Z})^2$,  the area estimatir $\widehat{\text{Area}}(D,h)$ is defined as	
+  Given a digital shape $D \subset (h \mathbb{Z})^2$,  the area estimator $\widehat{\text{Area}}(D,h)$ is defined as	
   \begin{align}
@@
 	}%	
-	\caption{The blue pixels in figure (a) illustrates a $2$-ring set, while the green pixels its inner-pixel boundary.
+	\caption{The blue pixels in figure (a) illustrates a $2$-ring set, while the green pixels form its inner-pixel boundary.
 In figure (b) we highlight an element of set $\mathcal{G}_{11}(C_1,C_2)$.
@@
 \begin{align*}
-	\mathcal{N}(S,N) = \bigcup_{1 \leq n \leq N} int \big( \mathcal{G}_{n}(\partial S_O, \partial S) \; \big) \cup int \big( \;  \; \mathcal{G}_{n}(\partial S, \partial S_I) \; \big),
+	\mathcal{N}(S,N) = \bigcup_{1 \leq n \leq N} int \big(\; \mathcal{G}_{n}( \partial S_O, \partial S) \; \big) \cup int \big( \; \mathcal{G}_{n}(\partial S, \partial S_I) \; \big),
 \end{align*}
@@
  }
+ \caption{Local combinatorial optimization for elastica minimization.}
  \label{alg:local-search} 
- \caption{Local combinatorial optimization for elastica minimization.}
 \end{algorithm}
@@
 where $g(S,x)$ denotes a similarity term as distance to initial shape $S$ or data fidelity term and $s(x)$ denotes a length penalization term.
-Each choice of $m$ generates a different flow, which is generaly described in the Digital Curve Evolution (DCE) algorithm \ref{alg:evolution-model}.
+Each choice of $m$ generates a different flow, which is generally described in the Digital Curve Evolution (DCE) algorithm \ref{alg:evolution-model}.
 
@@
  }
+ \caption{Digital curvature evolution algorithm (DCE).}
  \label{alg:evolution-model}  
- \caption{Digital curvature evolution algorithm (DCE).}
 \end{algorithm}
@@
 {In our experiments, the best results are obtained by executing DCE algorithm with $m$ equal to $r$, where $r$ is
-  the estimation ball radius (see figure \ref{fig:mx-square-flow} ). We observe that Elastica may increase after some
+  the estimation ball radius (see figure \ref{fig:mx-square-flow}). We observe that Elastica may increase after some
   iterations if chosen radius is too large, as in the case of the triangle in figure \ref{fig:mx-flow-gs-radius-effect}
@@
 
-Function $f$ is submodular if and only if the following inequality holds for each pairwise term $f_{j,k}$ \cite{kolmogorov04whatenergies}:
+The function $f$ is submodular if and only if the following inequality holds for each pairwise term $f_{j,k}$ \cite{kolmogorov04whatenergies}:
 \begin{align*}
@@
 
-Energy $E_m$ is non-submodular and optimizing it is a difficult problem, which constrains us to use heuristics and
+The energy $E_m$ is non-submodular and optimizing it is a difficult problem, which constrains us to use heuristics and
 approximation algorithms. The QPBO method \cite{rother07qpbo} transforms the original problem in a max-flow/min-cut
@@
 equal to $r$. Therefore, we are more confident in taking the solution for values of $m$ close to $r$. However, the way it
-varies across $m$ values differs from shape to shape, as is illustrated in figure
+varies across values of $m$ differs from shape to shape, as is illustrated in figure
 \ref{fig:unlabeled-versus-iterations}. We also noticed that, for $m=r$, all the pixels were labeled, {which may
-  indicate that $E_r$ is an an easy instance of the general non-submodular energy $E_m$, but this remains to be
+  indicate that $E_r$ is an easy instance of the general non-submodular energy $E_m$, but this remains to be
   proved. The number of pairwise terms in $E_r$ is roughly half of those in $E_1$ (see figure
@@
 \includegraphics[scale=0.5]{images/optimization/pairwise-ratio/plot-pairwiseratio-lowerHigher-concavities-probe.eps}
-\caption{We plot the ratio of pairwise terms among all $\binom{|X^{(i)}|}{2}$ combinations. The highest ring has rougly half the number of pairwise terms  than the lowest ring.}
+\caption{We plot the ratio of pairwise terms among all $\binom{|X^{(i)}|}{2}$ combinations. The highest ring has roughly half the number of pairwise terms as the lowest ring.}
 \label{fig:ratio-pairwise-terms}
@@
 contour correction method. Here we use a data fidelity term in order to characterize the object of
-interest. Given foreground and background seeds selected by the user, we derive mixed gaussian distributions  of color
+interest. Given foreground and background seeds selected by the user, we derive mixed Gaussian distributions  of color
 intensities $G_f$ and $G_b$, and we define the data fidelity term as the cross-entropy, i.e.
@@
 
-We use the DCE algorithm to regularize an initial contour outputed by some segmentation algorithm or delineated by the user. In this application, the similarity term of the DCE
+We use the DCE algorithm to regularize an initial contour output by some segmentation algorithm or delineated by the user. In this application, the similarity term of the DCE
 is set to the data fidelity term \eqref{eq:data-fidelity}.
@@
 	\caption{The proposed method regularizes GrabCut contours and returns meaningful results.
-We can observe the completion feature of curvature in the second row, and we don't suffer from oversegmentation issues as Schoenemann's method.
-However, our flow may stop in a local optima as in the fourth row, while Schoenemann's is able to extrapolate such solutions.}
+We can observe the completion feature of curvature in the second row, and we don't suffer from over-segmentation issues as Schoenemann's method.
+However, our flow may stop in a local optimum as in the fourth row, while Schoenemann's is able to extrapolate such solutions.}
 	\label{fig:segmentation-results}	
@@
 We evaluate our method using the BSD300 database \cite{martinFTM01berkeley}.
-All images contains the same number of pixels, the resolution being 321x481 in portrait mode.
+All images contain the same number of pixels, the resolution being 321x481 in portrait mode.
 We compare the results of our method with segmentations given by GrabCut and Schoenemanns's method \cite{schoenemann09linear}.
@@
   produced by GrabCut and Schoenemann's method. Our method is successful in producing curvature regularized
-  segmentations and demonstrates the completion property of curvature. Moreover, it does not suffer from over
-  segmentation, it is much faster than Schoenemann's, and in several opportunities produces better segmentations than
+  segmentations and demonstrates the completion property of curvature.
+Moreover, it does not suffer from over-segmentation, it is much faster than Schoenemann's, and in several cases produces better segmentations than
   GrabCut.

### 2019-11-28 jmiv.tex
correction of equation 5 development in section 4.1

@@
 \begin{align*}
-  \hat{\kappa}^2(y) &= c_1\Big( c_2 - \sum_{x_j \in B_r(y)} \big( {x_j} + |F_{r}^{(i)}(y)| \big) \Big)^2 \\
+  \hat{\kappa}^2(y) &= c_1\Big( c_2 - |F_{r}^{(i)}(y)| - \sum_{x_j \in O_r^{(i)}(y)} \big( {x_j}  \big) \Big)^2 \\
    &= c_1 \cdot \Big( C + 2\left( |F_{r}^{(i)}(y)| - c_2 \right) \hspace{-2mm}\sum_{x_j \in O_{r}^{(i)}(y)}\hspace{-2mm}{x_j} + \hspace{-2mm}\sum_{x_j \in O_{r}^{(i)}(y)}\hspace{-2mm}{x_j^2} + \hspace{-2mm}\sum_{ \substack{x_j,x_k \in O_{r}^{(i)}(y) \\ j<k} }\hspace{-2mm}{2x_jx_k}  \Big),

### 2019-11-28 jmiv.tex
Algorithm 2 correction
cellular-grid model figure

@@
 Let $S$ be a $2$-dimensional digital shape.
-We adopt the cellular-grid model to represent $S$, i.e., pixels and its lower dimensional counterparts, linels and pointels, are part of $S$.
+We adopt the cellular-grid model to represent $S$, i.e., pixels and its lower dimensional counterparts, linels and pointels, are part of $S$ (see figure \ref{fig:cellular-grid-model}).
 In particular, we denote by $\partial S$ the topological boundary of $S$, i.e., the connected sequence of linels such that for each linel we have one of its incident pixels in $S$ and the other not in $S$.
+
+\begin{figure}[h!]
+	\center
+	\subfloat[\label{}]{%
+	\includegraphics[scale=2.0]{images/local_search/definitions/flower.png}
+	}\hspace{40pt}%
+	\subfloat[\label{}]{%	
+	\includegraphics[scale=0.3]{images/local_search/definitions/cellular-grid-illustration.eps}
+	}
+	\caption{The flower shape in figure (a) and the cellular-grid model representation in (b) of the rectangle-bounded region.
+In figure (b), pixels are colored in gray, linels in green and pointels in blue.}
+	\label{fig:cellular-grid-model}
+\end{figure}
 
@@
  \BlankLine
- $S^{(i)} \longleftarrow S$\;
+ $S^{(0)} \longleftarrow S$\;
+ $i \longleftarrow 1$\;
  \While{ \It $<$ \MIt  }{ 	
@@
 	\If{ \It is odd }{	 
-	 	$X^{(i)} \longleftarrow \argmin_X E_m(X,\overline{S^{(i)}})$\;
- 		$S^{(i)} \longleftarrow F^{(i)} + \overline{X^{(i)}}$\;
+	 	$X^{(i)} \longleftarrow \argmin_X E_m(X,\overline{S^{(i-1)}})$\;
+ 		$S^{(i)} \longleftarrow F^{(i-1)} + \overline{X^{(i)}}$\;
  		$S^{(i)} \longleftarrow \overline{S^{(i)}}$\;	 	
@@
  	\Else{	
-	 	$X^{(i)} \longleftarrow \argmin_X E_m(X,S^{(i)})$\; 	
- 		$S^{(i)} \longleftarrow F^{(i)} + \overline{X^{(i)}}$\;
+	 	$X^{(i)} \longleftarrow \argmin_X E_m(X,S^{(i-1)})$\; 	
+ 		$S^{(i)} \longleftarrow F^{(i-1)} + \overline{X^{(i)}}$\;
  	}

### 2019-11-28 jmiv.tex
glued curve change in definition

@@
 \begin{definition}[Glued Curve]
-Given closed curves $C_1,C_2$ agreeing with some orientation $q$, a glued curve is a closed curve  $(c_1,\ell_1,c_2,\ell_2)$ with orientation $q$ and $c_1 \in C_1, c_2 \in C_2$.
+Given a closed curve $C_1$ with orientation $q$, and curve $C_2$ with same orientation $q$ such that $C_2$ encloses a region that contains $C_1$, a glued curve is a closed curve  $(c_1,\ell_1,c_2,\ell_2)$ with orientation $q$ and $c_1 \subset C_1, c_2 \subset C_2$.
 The linels $\ell_1,\ell_2$ are called junction linels.

### 2019-11-28 jmiv.tex
edition of glued-curve figure illustration
Definition of interior operator for a set of curves

--- 2019-11-28 jmiv.tex
@@
 
-An oriented closed curve $C$ is a closed connected sequence of linels with a well-defined interior. A segment of $C$ is a connected subsequence $c \in C$ of its linels.
+An oriented closed curve $C$ is a closed connected sequence of linels with a well-defined interior.
+A segment of $C$ is a connected subsequence $c \in C$ of its linels.
+We denote by $int(C)$ the interior of the shape bounded by curve $C$.
+Moreover, for a set of curves $\mathcal{C}$, we define $int(\mathcal{C}) = \bigcup_{C \in \mathcal{C}} int(C) $.
 
@@
 	\subfloat[\label{}]{%
-	\includegraphics[scale=0.2]{images/local_search/definitions/glued-curve.eps}
+	\includegraphics[scale=0.22]{images/local_search/definitions/glued-curve.eps}
 	}%	
@@
 \begin{definition}[Glued Curve]
-Given closed curves $C_1,C_2$ agreeing with some orientation $q$, a glued curve is a closed curve  $(c_1,\ell_1,c_2,\ell_2)$ with orientation $q$ and $c_1 \in C_1, c_2 \in C_2$.
+Given closed curves $C_1,C_2$ agreeing with some orientation $q$ such that $int(C_1) \subset int(C_2)$, a glued curve is a closed curve  $(c_1,\ell_1,c_2,\ell_2)$ with orientation $q$ and $c_1 \subset C_1, c_2 \subset C_2$.
 The linels $\ell_1,\ell_2$ are called junction linels.
@@
 \begin{align*}
-	\mathcal{N}(S,N) = \bigcup_{1 \leq n \leq N} int \big(\; \mathcal{G}_{n}( \partial S_O, \partial S) \; \big) \cup int \big( \; \mathcal{G}_{n}(\partial S, \partial S_I) \; \big),
-\end{align*}
-
-where $int(C)$ is the interior of the shape bounded by the close oriented curve $C$.
+	\mathcal{N}(S,N) = \bigcup_{1 \leq n \leq N} int \big(\; \mathcal{G}_{n}( \partial S_O, \partial S) \; \big) \cup int \big( \; \mathcal{G}_{n}(\partial S, \partial S_I) \; \big).
+\end{align*}
+
 Algorithm~\ref{alg:local-search} describes the local combinatorial process and Figure~\ref{fig:local-comb-square-results} presents the digital curve evolution when executing this algorithm for two different shapes with $N=20$.

### 2019-11-29 jmiv.tex
Change of notation section 3 and 4

@@
 where $\dot{\vec{e}}$ denotes the center of the edge $\vec{e}$. In the
-expression above, we will substitute an arbitrary subset $Z$ of
+expression above, we will substitute an arbitrary subset $S$ of
 $\mathbb{Z}^2$ to $D_h(X)$ since the continuous shape $X$ is unknown.
@@
 
-Let $S$ be a $2$-dimensional digital shape.
+Let $S$ be a $2$-dimensional digital shape embedded in a domain $\Omega \subset \mathbb{Z}^2$.
 We adopt the cellular-grid model to represent $S$, i.e., pixels and its lower dimensional counterparts, linels and pointels, are part of $S$ (see figure \ref{fig:cellular-grid-model}).
@@
 
-Let $d_{S}:\Omega \rightarrow \mathcal{R}$ be the Euclidean distance transformation with respect to shape $S$. The value $d_S(x)$ gives the Euclidean distance between $x$ and the closest pixel in $S$.
+Let $d_{S}:\Omega \rightarrow \mathcal{R}$ be the Euclidean distance transformation with respect to shape $S$. The value $d_S(p)$ gives the Euclidean distance between $p$ and the closest pixel in $S$.
 
@@
 	\quad R_m(S) &:= R_m^-(S) \; \cup \; R_m^+(S) \\
-	&:= \left\{ x \in \Omega \; | \; m-1 < d_S(x) \leq m \right\} \; \cup \;  \left\{ x \in \Omega \; | \; 	m-1 < d_{\overline{S}}(x) \leq m \right\}.
+	&:= \left\{ p \in \Omega \; | \; m-1 < d_S(p) \leq m \right\} \; \cup \;  \left\{ p \in \Omega \; | \; 	m-1 < d_{\overline{S}}(p) \leq m \right\}.
 \end{align*}
@@
  \Delta $\longleftarrow$ \Tol+1\;
+ $i \longleftarrow 0$\;
  \While{ \It $<$ \MIt \bf{and} \Delta $>$ \Tol  }{
@@
 
-Given a digital shape $S \in \Omega$, the idea is to evolve a flow $S^{(i)}$ where $S^{(i+1)}$ is derived from the minimization of the sum of the squared curvature at $S^{(i)}$.
+Given a digital shape $S \subset \Omega \subset \mathbb{Z}^2$, the idea is to evolve a flow $S^{(i)}$ where $S^{(i+1)}$ is derived from the minimization of the sum of the squared curvature at $S^{(i)}$.
 In order to guarantee connectivity, we limit the optimization region to a subset of $\Omega$, namely the inner pixel boundary of  $S^{(i)}$.
@@
 \begin{definition}[Inner pixel boundary]
-Given a digital shape $S$ embedded in a domain $\Omega$, we define its inner pixel boundary set $O(S)$ as
-\begin{align*}
-	O(S) = \left\{ \: x \; | \; x \in S, |\mathcal{N}_4(x) \cap S|<4 \: \right\},
-\end{align*}
-where $\mathcal{N}_4(x)$ denotes the $4$-adjacent neighbor set of $x$ (without $x$).
+Given a digital shape $S$ embedded in a domain $\Omega$, we define its inner pixel boundary set $I(S)$ as
+\begin{align*}
+	I(S) = \left\{ \: p \; | \; p \in S, |\mathcal{N}_4(x) \cap S|<4 \: \right\},
+\end{align*}
+where $\mathcal{N}_4(p)$ denotes the $4$-adjacent neighbor set of $p$ (without $p$).
 \end{definition}
 
-In other words, each flow iteration decides which pixels in the inner boundary are to be removed and which are to be kept.
-To simplify notation, we denote the optimization region of $S^{(i)}$ as $O^{(i)}$, and the foreground set as $F^{(i)} = S^{(i)} \setminus O^{(i)}$.
-We recall the definition of our digital curvature estimator :
+The optimization variables set is defined as
+
+\begin{align*}
+	X(S) = \left\{ x_j \in \{0,1\} \; | \; p_j \in I(S) \right \}.
+\end{align*}
+
+In other words, each flow iteration decides which pixels in the inner boundary are to be removed from $S$ and which are to be kept in $S$.
+To simplify notation, we denote the optimization region of $S^{(i)}$ as $X^{(i)}$, and the foreground set as $F^{(i)} = S^{(i)} \setminus X^{(i)}$.
+We recall the definition of our digital curvature estimator:
 \begin{align}
-	\hat{\kappa}^2(y) &= c_1\Big( c_2 - | B_r(y) \cap S | \Big)^2, 
+	\hat{\kappa}^2(p) &= c_1\Big( c_2 - | B_r(p) \cap S | \Big)^2, 
 	\label{eq:curvature-estimator-pixels}
@@
 
-We define $O_{r}^{(i)}(y) := O^{(i)} \cap B_r(y)$ and an analogous definition holds for $F_{r}^{(i)}(y)$. Expanding \eqref{eq:curvature-estimator-pixels}, we get 
-\begin{align*}
-  \hat{\kappa}^2(y) &= c_1\Big( c_2 - |F_{r}^{(i)}(y)| - \sum_{x_j \in O_r^{(i)}(y)} \big( {x_j}  \big) \Big)^2 \\
-   &= c_1 \cdot \Big( C + 2\left( |F_{r}^{(i)}(y)| - c_2 \right) \hspace{-2mm}\sum_{x_j \in O_{r}^{(i)}(y)}\hspace{-2mm}{x_j} + \hspace{-2mm}\sum_{x_j \in O_{r}^{(i)}(y)}\hspace{-2mm}{x_j^2} + \hspace{-2mm}\sum_{ \substack{x_j,x_k \in O_{r}^{(i)}(y) \\ j<k} }\hspace{-2mm}{2x_jx_k}  \Big),
-\end{align*}
-where $C=c_2^2 - 2c_2 \cdot |F_{r}^{(i)}(y)| + |F_{r}^{(i)}(y)|^2$ is a constant. By ignoring constants and multiplication factors and using
+We define $X_{r}^{(i)}(p) := X^{(i)} \cap B_r(p)$ and an analogous definition holds for $F_{r}^{(i)}(p)$. Expanding \eqref{eq:curvature-estimator-pixels}, we get 
+\begin{align*}
+  \hat{\kappa}^2(p) &= c_1\Big( c_2 - |F_{r}^{(i)}(p)| - \sum_{x_j \in X_r^{(i)}(p)} {x_j} \Big)^2 \\
+   &= c_1 \cdot \Big( C + 2\left( |F_{r}^{(i)}(p)| - c_2 \right) \hspace{-2mm}\sum_{x_j \in X_{r}^{(i)}(p)}\hspace{-2mm}{x_j} + \hspace{-2mm}\sum_{x_j \in X_{r}^{(i)}(p)}\hspace{-2mm}{x_j^2} + \hspace{-2mm}\sum_{ \substack{x_j,x_k \in X_{r}^{(i)}(p) \\ j<k} }\hspace{-2mm}{2x_jx_k}  \Big),
+\end{align*}
+where $C=c_2^2 - 2c_2 \cdot |F_{r}^{(i)}(p)| + |F_{r}^{(i)}(p)|^2$ is a constant. By ignoring constants and multiplication factors and using
 the binary character of the variables, we define the following family
@@
   E_m(X,S) =& \sum_{x \in X}{\alpha s(x)} \nonumber \\ 
-  & + \sum_{y \in R_m(S)}{ \beta \Big( { (1/2+ |F_{r}^{(i)}(y)|-c_2) \cdot \sum_{x_j \in O_{r}^{(i)}(y)}{x_j} } + \sum_{ \substack{x_j,x_k \in O_{r}^{(i)}(y) \\ j<k} }{x_jx_k} \Big) } \nonumber \\
+  & + \sum_{p \in R_m(S)}{ \beta \Big( { (1/2+ |F_{r}^{(i)}(p)|-c_2) \cdot \sum_{x_j \in X_{r}^{(i)}(p)}{x_j} } + \sum_{ \substack{x_j,x_k \in X_{r}^{(i)}(p) \\ j<k} }{x_jx_k} \Big) } \nonumber \\
   & + \sum_{x \in X}{\gamma g(S,x)},
@@
   s(x)=\sum_{x_j \in \mathcal{N}_4(x)}{ t(x_j) }, \quad \text{where } t(x_j) = \left\{\begin{array}{ll}
-  (x-x_j)^2, & \text{if } x_j \in O_{r}^{(i)}\\
+  (x-x_j)^2, & \text{if } x_j \in X_{r}^{(i)}\\
   (x-0), & \text{if } x_j \in F_{r}^{(i)}\\

### 2019-11-29 jmiv.tex
Edition of figure 6
Algorithm 2 notation clarification
precision on dataset images resolution

@@
 	 	$X^{(i)} \longleftarrow \argmin_X E_m(X,\overline{S^{(i-1)}})$\;
- 		$S^{(i)} \longleftarrow F^{(i-1)} + \overline{X^{(i)}}$\;
+ 		$S^{(i)} \longleftarrow F^{(i-1)}_{\overline{S}} + \overline{X^{(i)}}$\;
  		$S^{(i)} \longleftarrow \overline{S^{(i)}}$\;	 	
@@
 	 	$X^{(i)} \longleftarrow \argmin_X E_m(X,S^{(i-1)})$\; 	
- 		$S^{(i)} \longleftarrow F^{(i-1)} + \overline{X^{(i)}}$\;
+ 		$S^{(i)} \longleftarrow F^{(i-1)}_{S} + \overline{X^{(i)}}$\;
  	}
@@
 \begin{minipage}[b]{0.33\textwidth}
-	\subfloat[$r=5, m=2$\label{}]{%
-	\includegraphics[scale=0.2]{images/flow/farther-rings/square-r5-l2/summary_flow.eps}
+	\subfloat[$r=5, m=3$\label{}]{%
+	\includegraphics[scale=0.2]{images/flow/farther-rings/square-r5-l3/summary_flow.eps}
 	}%
@@
 \begin{minipage}[b]{0.33\textwidth}
-	\subfloat[$r=5, m=3$\label{}]{%
-	\includegraphics[scale=0.2]{images/flow/farther-rings/square-r5-l3/summary_flow.eps}
+	\subfloat[$r=5, m=5$\label{}]{%
+	\includegraphics[scale=0.2]{images/flow/farther-rings/square-r5-l5/summary_flow.eps}
 	}%
@@
 We evaluate our method using the BSD300 database \cite{martinFTM01berkeley}.
-All images contain the same number of pixels, the resolution being 321x481 in portrait mode.
+All images contain the same number of pixels, the resolution being 321x481 (481x321) in portrait (landscape) mode.
 We compare the results of our method with segmentations given by GrabCut and Schoenemanns's method \cite{schoenemann09linear}.

### 2019-12-02 jmiv.tex
caption for figure 13
Section 3 high resolution figures

@@
 
-Algorithm~\ref{alg:local-search} describes the local combinatorial process and Figure~\ref{fig:local-comb-square-results} presents the digital curve evolution when executing this algorithm for two different shapes with $N=20$.
+Algorithm~\ref{alg:local-search} describes the local combinatorial process and Figure~\ref{fig:local-comb-square-results} presents the digital curve evolution when executing this algorithm for two different shapes with $N=50$.
 
@@
 	\subfloat[h=1.0\label{}]{%
-	\includegraphics[scale=0.125]{images/local_search/square/h1/summary-flow.eps}
+	\includegraphics[scale=0.125]{images/local_search/square/h1/summary.eps}
 	}%
@@
 	\subfloat[h=0.5\label{}]{%
-	\includegraphics[scale=0.125]{images/local_search/square/h05/summary-flow.eps}
+	\includegraphics[scale=0.125]{images/local_search/square/h05/summary.eps}
 	}%
@@
 	\subfloat[h=1.0\label{}]{%
-	\includegraphics[scale=0.125]{images/local_search/flower/h1/summary-flow.eps}
+	\includegraphics[scale=0.125]{images/local_search/flower/h1/summary.eps}
 	}%
@@
 	\subfloat[h=0.5\label{}]{%
-	\includegraphics[scale=0.125]{images/local_search/flower/h05/summary-flow.eps}
+	\includegraphics[scale=0.125]{images/local_search/flower/h05/summary.eps}
 	}%
-		\caption{Local combinatorial optimization process results for the square and flower shapes. Shapes displayed at every $2$ iterations for the square and $7$ iterations for the flower.}	
+		\caption{Local combinatorial optimization process results for the square and flower shapes. Shapes displayed at every $2$ iterations for the square and $5$ iterations for the flower.}	
 		\label{fig:local-comb-square-results}
@@
 The running time of algorithm \ref{alg:local-search} is summarized in table \ref{tab:summary-local-comb-rtime}. All the
-experiments in this paper were executed on a five-core $3.4Ghz$ CPU and the number of pixels in the triangle, square and
-flower shapes are respectively $841,1867,521$ for grid step $h=1.0$. Although its use in practical applications is
+experiments in this paper were executed on a $32$-core $2.4Ghz$ CPU and the number of pixels in the square and
+flower shapes are respectively $841,1867$ for grid step $h=1.0$. Although its use in practical applications is
 limited, we demonstrate that digital estimators are effective in their measurements and the flows evolve as expected. We
@@
 \includegraphics[scale=0.35]{images/local_search/square-flower.eps}
-\caption{Elastica computation along iterations of algorithm \ref{alg:local-search}}
+\caption{Elastica computation along iterations of algorithm \ref{alg:local-search}. The final shape has energy value closer to the optimal solution $2\pi/5$ (dashed line).}
 \label{fig:plot-elastica-local-search}
@@
 \hline
-Square & 47s (5s/it) & 260s (12s/it)\\
+Square & 4s (0.4s/it) & 77s (3s/it)\\
 \hline
-Flower & 1235s (23s/it)  & 8516s (52s/it)\\
+Flower & 252s (4s/it)  & 3246s (42s/it)\\
 \hline
 \end{tabular}
-\caption{Running times for the local combinatorial optimization algorithm with $k=1,N=20$. Four threads were used.}
+\caption{Running times for the local combinatorial optimization algorithm with $k=1,N=50$. Four threads were used.}
 \label{tab:summary-local-comb-rtime}
@@
 	\end{tabular}
-	\caption{}
+	\caption{Additional comparison results between GrabCut, Schoenemman and Contour correction segmentation methods.}
 	\label{fig:more-segmentation-results}	

### 2019-12-02 images/local_search/graph-plot.sh

@@ -1,85 +1,0 @@
-#!/usr/bin/env bash
-
-gp_save()
-{
-	printf "set size 1.0, 0.6;
-		set terminal postscript portrait enhanced color dashed lw 2 \"Helvetica\" 20;
-		set key right top;
-		set output \"my-plot.ps\";
-		replot;
-		set terminal x11;
-		set size 1,1;"
-}
-
-gp_plot_config()
-{
-    #set yrange [-0.1:1.1]; 
-    printf "set title '$1';
-    set xlabel 'Iterations';
-    set ylabel 'Elastica ({/Symbol a}=0.1, {/Symbol b}=1)';"
-}
-
-
-gp_add_plot()
-{
-    printf "'$1' u 1:2 w l title '$2',"
-}
-
-gp_last_plot()
-{
-	printf "'$1' u 1:2 w l title '$2';"
-}
-
-
-create_multiplot()
-{
-	fileoutput=$1;shift;
-	plottitle="$1";shift;
-
-	buffer="$(gp_plot_config "$plottitle")plot "
-	i=0
-	num_plots=`expr ${#} / 2 - 1`
-
-	while [ ${i} -lt ${num_plots} ]
-	do
-		subplotDataFile=$1
-		subplotTitle=$2
-		buffer="${buffer}$(gp_add_plot $subplotDataFile $subplotTitle)"
-		shift; shift;
-
-		i=`expr $i + 1`
-	done
-
-	if [ $num_plots -eq 0 ]
-	then
-		buffer="${buffer}$(gp_last_plot $1 $2)"
-	else
-		buffer="${buffer}$(gp_last_plot $1 $2)"
-	fi
-
-	buffer="${buffer}$(gp_save)"
-
-
-	`gnuplot -e "$buffer"`
-	`mv my-plot.ps ${fileoutput}`
-}
-
-
-
-
-BASE_FOLDER=$(realpath $1)
-PLOTS_OUTPUT=$(realpath $2)
-FILENAME_OUTPUT=$3
-
-mkdir -p $PLOTS_OUTPUT
-OUTPUT_PLOT=${PLOTS_OUTPUT}/${FILENAME_OUTPUT}
-
-
-PLOT_STRING="$OUTPUT_PLOT ''"
-PLOT_STRING="${PLOT_STRING} ${BASE_FOLDER}/output/model/h$gs/radius-$radius/$shape/$method/$mode/level-$i.txt m=$i"
-
[…]

### 2019-12-05 jmiv.tex
Fix wrong parameter value in plot
Further clarification of inversing the solution in section 4

@@
 
-Given a digital shape $S \subset \Omega \subset \mathbb{Z}^2$, the idea is to evolve a flow $S^{(i)}$ where $S^{(i+1)}$ is derived from the minimization of the sum of the squared curvature at $S^{(i)}$.
+Given a digital shape $S \subset \Omega \subset \mathbb{Z}^2$, the goal is to evolve a flow $S^{(i)}$ where $S^{(i+1)}$ has lower digital elastica than its precedent.
+
+We observe that the integral invariant estimator \eqref{eq:curvature_approximation} is originaly designed to be evaluated on the digital boundary of some shape, which is the unknown of our problem.
+Enforcing this restriction implies to incorporate topological information in the form of constraints or penalization terms in the same lines of \cite{schoenemann09linear}, but such approach would result in a third order model, which we prefer to avoid.
+Instead, we are going to exploit the II estimator definition in order to create a flow that evolves proportionally to the squared curvature of the current shape.
+
  In order to guarantee connectivity, we limit the optimization region to a subset of $\Omega$, namely the inner pixel boundary of  $S^{(i)}$.
@@
 
-We start by definition the optimization variables.
+We start by defining the optimization variables.
 \begin{definition}[Inner pixel boundary]
@@
 
+We remark that the minimization of \eqref{eq:energy-family} for $S^{(i)}$ is not sufficient to derive the next shape $S^{(i+1)}$ because topolical information is not included in the model.
+Instead, the minimization of \eqref{eq:energy-family} is used as a guide.
 Recall that the integral invariant estimator approaches curvature by computing the difference between half of the area
@@
 		\subfloat[Elastica evaluation]{%
-		\includegraphics[scale=0.5]{images/flow/elastica-energy-plot/r5h05.eps}						
+		\includegraphics[scale=0.5]{images/flow/elastica-energy-plot/square-flower-triangle.eps}						
 		}

### 2019-12-05 jmiv.tex
Corrections section 3

@@
 flower shapes are respectively $841,1867$ for grid step $h=1.0$. Although its use in practical applications is
-limited, we demonstrate that digital estimators are effective in their measurements and the flows evolve as expected. We
+limited, we demonstrate that digital estimators are effective in their measurements and the flows evolve as expected.
+In particular, the digital elastica energy for the experiments in figure \ref{fig:local-comb-square-results} approaches the global optimum (figure  \ref{fig:plot-elastica-local-search}).
+We
 observe that it is a complete digital approach, and we do not suffer from discretization and rounding problems, a common
@@
 \includegraphics[scale=0.35]{images/local_search/square-flower.eps}
-\caption{Elastica computation along iterations of algorithm \ref{alg:local-search}. The final shape has energy value closer to the optimal solution $2\pi/5$ (dashed line).}
+\caption{Elastica computation along iterations of algorithm \ref{alg:local-search}. The final shape has energy value closer to the optimal value $2\pi/5$ (dashed line).}
 \label{fig:plot-elastica-local-search}

### 2019-12-05 jmiv.tex
Fix image in figure 11
int(C2) included in int(C1)

@@
 \begin{definition}[Glued Curve]
-Given closed curves $C_1,C_2$ agreeing with some orientation $q$ such that $int(C_1) \subset int(C_2)$, a glued curve is a closed curve  $(c_1,\ell_1,c_2,\ell_2)$ with orientation $q$ and $c_1 \subset C_1, c_2 \subset C_2$.
+Given closed curves $C_1,C_2$ agreeing with some orientation $q$ such that $int(C_2) \subset int(C_1)$, a glued curve is a closed curve  $(c_1,\ell_1,c_2,\ell_2)$ with orientation $q$ and $c_1 \subset C_1, c_2 \subset C_2$.
 The linels $\ell_1,\ell_2$ are called junction linels.
@@
 
- 	\includegraphics[scale=0.25]{images/segmentation/bc/coala/lg0_sq0_dt1_it20.png} & 
+ 	\includegraphics[scale=0.25]{images/segmentation/bc/coala/grabcut-seg.png} & 
 	\includegraphics[scale=0.25]{images/segmentation/bc/coala/r3/lg1_sq0_dt1_it50.png} &

### 2019-12-13 jmiv.tex
Modify definitions in section 3; new figure for the ring-set

@@
 
-Let $d_{S}:\Omega \rightarrow \mathcal{R}$ be the Euclidean distance transformation with respect to shape $S$. The value $d_S(p)$ gives the Euclidean distance between $p$ and the closest pixel in $S$.
+Let $d_{S}:\Omega \rightarrow \mathcal{R}$ be the signed Euclidean distance transformation with respect to shape $S$.
+The value $d_S(p)$ gives the Euclidean distance between $p \notin S$ and the closest pixel in $S$.
+For points $p \in S$, $d_S(p)$ gives the distance between $p$ and the closest pixel not in $S$.
+The \emph{$m$-level set of $S$}
 
 \begin{definition}[m-Ring Set]
-Given a digital shape $S\in\Omega$, its distance transformation $d_S$ and natural numbers $m > 0$, the {\em $m$-ring set of $S$} is defined as
-\begin{align*}
-	\quad R_m(S) &:= R_m^-(S) \; \cup \; R_m^+(S) \\
-	&:= \left\{ p \in \Omega \; | \; m-1 < d_S(p) \leq m \right\} \; \cup \;  \left\{ p \in \Omega \; | \; 	m-1 < d_{\overline{S}}(p) \leq m \right\}.
+Given a digital shape $S\in\Omega$, its signed distance transformation $d_S$ and natural number $m \neq 0$, the {\em $m$-ring set of $S$} is defined as
+\begin{align*}
+	\mathcal{R}_m(S) &:= \mathcal{L}_m \cup \mathcal{L}_{-m},
+\end{align*}
+where
+\begin{align*}
+	\mathcal{L}_m(S) &:= \left\{ \quad \begin{array}{cc}
+		\left\{ p \in \Omega \; | \; m-1 < d_S(p) \leq m \right\} & , \quad m>0\\
+		\left\{ p \in \Omega \; | \; m+1 > d_S(p) \geq m \right\} & , \quad m<0
+		\end{array} \right.
 \end{align*}
@@
 
-Such set can be extremely large and its complete exhaustion is prohibitively expensive.  Instead, we explore a subset of it with the help of $n$-glued curves.
-
-An oriented closed curve $C$ is a closed connected sequence of linels with a well-defined interior.
-A segment of $C$ is a connected subsequence $c \in C$ of its linels.
-We denote by $int(C)$ the interior of the shape bounded by curve $C$.
-Moreover, for a set of curves $\mathcal{C}$, we define $int(\mathcal{C}) = \bigcup_{C \in \mathcal{C}} int(C) $.
+Such set can be extremely large and its complete exhaustion is prohibitively expensive.  Instead, we are going to use a subset of it.
+
+\begin{definition}[$n$-neighborhood]
+	Given a digital shape $S \in \Omega$, its $n$-neighborhood $\mathcal{N}_n(S)$ is defined as the set of digital shapes that can be built from $S$ by adding or removing a sequence of $n$ connected pixels in $R_1(S)$.
+\end{definition}
 
@@
 	\subfloat[\label{}]{%
-	\includegraphics[scale=0.2]{images/local_search/definitions/model-regions-square.eps}
+	\includegraphics[scale=0.03]{images/local_search/definitions/R3.pdf}
 	}\hspace{40pt}%
@@
 	}%	
-	\caption{The blue pixels in figure (a) illustrates a $2$-ring set, while the green pixels form its inner-pixel boundary.
-In figure (b) we highlight an element of set $\mathcal{G}_{11}(C_1,C_2)$.
-The curve segments of $C_1$ and $C_2$ are colored in red and green, while the junction linels in blue.}
-\end{figure}
-
-\begin{definition}[Glued Curve]
-Given closed curves $C_1,C_2$ agreeing with some orientation $q$ such that $int(C_2) \subset int(C_1)$, a glued curve is a closed curve  $(c_1,\ell_1,c_2,\ell_2)$ with orientation $q$ and $c_1 \subset C_1, c_2 \subset C_2$.
-The linels $\ell_1,\ell_2$ are called junction linels.
-\end{definition}
-
-\begin{definition}[$n$-Glued Curve Set]
-Given closed curves $C_1,C_2$ with same orientation, its set of $n$-glued curves is defined as
-\begin{align*}
-	\mathcal{G}_n(C_1,C_2) = \{ (c_1,\ell_1,c_2,\ell_2) \; | \; |c_2|=n \},
-\end{align*}
-\end{definition}
-
-Let $S_O = ( S \cup R_1^+(S) ) $ and $S_I = ( S \setminus R_1^-(S) ) $, the neighborhood set to shape $S$ is defined as
-\begin{align*}
-	\mathcal{N}(S,N) = \bigcup_{1 \leq n \leq N} int \big(\; \mathcal{G}_{n}( \partial S_O, \partial S) \; \big) \cup int \big( \; \mathcal{G}_{n}(\partial S, \partial S_I) \; \big).
-\end{align*}
-
-Algorithm~\ref{alg:local-search} describes the local combinatorial process and Figure~\ref{fig:local-comb-square-results} presents the digital curve evolution when executing this algorithm for two different shapes with $N=50$.
+	\caption{The blue pixels in figure (a) illustrates a $3$-ring set. In figure (b) we highlight the contour of an element of set $\mathcal{N}_{11}$.}
+\end{figure}
+
+Algorithm~\ref{alg:local-search} describes the local combinatorial process and Figure~\ref{fig:local-comb-square-results} presents the digital curve evolution when executing this algorithm for two different shapes with $n=50$.
 
@@
 
- \Input{A digital set $S$; the maximum length of glued curves $N$; the maximum number of iterations \MIt; and a stop condition \Tol}
+ \Input{A digital set $S$; the neighborhood parameter $n$; the maximum number of iterations \MIt; and a stop condition \Tol}
  \BlankLine
@@
  \While{ \It $<$ \MIt \bf{and} \Delta $>$ \Tol  }{
-  	\For{$ X \in \mathcal{N}(S^{(i)},N) $}
+  	\For{$ X \in \mathcal{N}_n(S^{(i)}) $}
 	{

### 2019-12-13 jmiv.tex
New figure in section 4

@@
 \end{tabular}
-\caption{Running times for the local combinatorial optimization algorithm with $k=1,N=50$. Four threads were used.}
+\caption{Running times for the local combinatorial optimization algorithm with $k=1,n=50$. Four threads were used.}
 \label{tab:summary-local-comb-rtime}
@@
 
-Given a digital shape $S \subset \Omega \subset \mathbb{Z}^2$, the goal is to evolve a flow $S^{(i)}$ where $S^{(i+1)}$ has lower digital elastica than its precedent.
+Given a digital shape $S \subset \Omega \subset \mathbb{Z}^2$, the goal is to compute a flow $S^{(i)}$ where $S^{(i+1)}$ has lower digital elastica than its precedent.
 
 We observe that the integral invariant estimator \eqref{eq:curvature_approximation} is originaly designed to be evaluated on the digital boundary of some shape, which is the unknown of our problem.
-Enforcing this restriction implies to incorporate topological information in the form of constraints or penalization terms in the same lines of \cite{schoenemann09linear}, but such approach would result in a third order model, which we prefer to avoid.
-Instead, we are going to exploit the II estimator definition in order to create a flow that evolves proportionally to the squared curvature of the current shape.
+Injecting contour information leads to a third order model, which we prefer to avoid.
+Instead, we are going to exploit the II estimator definition in order to compute a flow that evolves proportionally to the squared curvature of the current shape.
 
@@
 
+\begin{figure}
+\begin{minipage}{0.5\textwidth}
+\center
+\includegraphics[scale=0.1]{images/flow/contour-information/before-opt.pdf}
+\label{fig:contour-info-1}
+\end{minipage}%
+\begin{minipage}{0.5\textwidth}
+\center
+\includegraphics[scale=0.1]{images/flow/contour-information/after-opt.pdf}
+\label{fig:contour-info-2}
+\end{minipage}%
+\caption{Directly using the optimization result of \eqref{eq:energy-family} doesn't decrease squared curvature because contour information is not present in the energy.}
+\label{fig:contour-info}
+\end{figure}
+
 \begin{algorithm}[H]
@@
 
-We remark that the minimization of \eqref{eq:energy-family} for $S^{(i)}$ is not sufficient to derive the next shape $S^{(i+1)}$ because topolical information is not included in the model.
-Instead, the minimization of \eqref{eq:energy-family} is used as a guide.
+We emphasize that the minimization of \eqref{eq:energy-family} for $S^{(i)}$ is not sufficient to derive the next shape $S^{(i+1)}$ because topolical information is not included in the model (see figure \ref{fig:contour-info}).
 Recall that the integral invariant estimator approaches curvature by computing the difference between half of the area

### 2019-12-13 jmiv.tex
Enclose changes with revision tag (colored red)

@@
 \newcommand{\daniel}[1]{\textcolor{NavyBlue}{#1}}
+\newcommand{\revision}[1]{\textcolor{red}{#1}}
 
@@
 like~\cite{malladi1995image,malladi1995shape,ballester01filljoint} for
-segmentation or inpainting. However, Caselles {\em et al.}
+segmentation or inpainting. However, \revision{Caselles} {\em et al.}
 in~\cite{caseles97geodesic} observed that these terms as employed
@@
 \cite{esedoglu2008threshold} and has been proposed for image
-disocclusion \cite{esedoglu2005threshold}. However, flow-based methods
+\revision{disocclusion} \cite{esedoglu2005threshold}. However, flow-based methods
 will always deliver a local minimum, which heavily depend on
@@
 elastica minimization, which show that our discrete model is
-well-founded. Finally, the code related to this paper is freely
+well-founded. Finally, \revision{the code related to} this paper is freely
 available on github.\footnote{https://www.github.com/danoan/BTools}
@@
 \begin{definition}	
-  Given a digital shape $D \subset (h \mathbb{Z})^2$,  the area estimator $\widehat{\text{Area}}(D,h)$ is defined as	
+  Given a digital shape $D \subset (h \mathbb{Z})^2$,  the area \revision{estimator} $\widehat{\text{Area}}(D,h)$ is defined as	
   \begin{align}
@@
 where $\dot{\vec{e}}$ denotes the center of the edge $\vec{e}$. In the
-expression above, we will substitute an arbitrary subset $S$ of
+expression above, we will substitute an arbitrary subset \revision{$S$} of
 $\mathbb{Z}^2$ to $D_h(X)$ since the continuous shape $X$ is unknown.
@@
 
-Let $S$ be a $2$-dimensional digital shape embedded in a domain $\Omega \subset \mathbb{Z}^2$.
-We adopt the cellular-grid model to represent $S$, i.e., pixels and its lower dimensional counterparts, linels and pointels, are part of $S$ (see figure \ref{fig:cellular-grid-model}).
+\revision{Let $S$ be a $2$-dimensional digital shape embedded in a domain $\Omega \subset \mathbb{Z}^2$}.
+We adopt the cellular-grid model to represent $S$, i.e., pixels and its lower dimensional counterparts, linels and pointels, are part of $S$ \revision{(see figure \ref{fig:cellular-grid-model})}.
 In particular, we denote by $\partial S$ the topological boundary of $S$, i.e., the connected sequence of linels such that for each linel we have one of its incident pixels in $S$ and the other not in $S$.
@@
 	}
-	\caption{The flower shape in figure (a) and the cellular-grid model representation in (b) of the rectangle-bounded region.
-In figure (b), pixels are colored in gray, linels in green and pointels in blue.}
+	\caption{\revision{The flower shape in figure (a) and the cellular-grid model representation in (b) of the rectangle-bounded region.
+In figure (b), pixels are colored in gray, linels in green and pointels in blue.}}
 	\label{fig:cellular-grid-model}
@@
 
-Let $d_{S}:\Omega \rightarrow \mathcal{R}$ be the signed Euclidean distance transformation with respect to shape $S$.
-The value $d_S(p)$ gives the Euclidean distance between $p \notin S$ and the closest pixel in $S$.
-For points $p \in S$, $d_S(p)$ gives the distance between $p$ and the closest pixel not in $S$.
-The \emph{$m$-level set of $S$}
+Let $d_{S}:\Omega \rightarrow \mathcal{R}$ be the \revision{signed} Euclidean distance transformation with respect to shape $S$.
+The value $d_S(p)$ gives the Euclidean distance between \revision{$p \notin S$ and the closest pixel in $S$.
+For points $p \in S$, $d_S(p)$ gives the distance between $p$ and the closest pixel not in $S$.}
 
 \begin{definition}[m-Ring Set]
+\revision{
 Given a digital shape $S\in\Omega$, its signed distance transformation $d_S$ and natural number $m \neq 0$, the {\em $m$-ring set of $S$} is defined as
@@
 		\end{array} \right.
-\end{align*}
+\end{align*}}
 \end{definition}
@@
 \begin{definition}[$n$-neighborhood]
+\revision{
 	Given a digital shape $S \in \Omega$, its $n$-neighborhood $\mathcal{N}_n(S)$ is defined as the set of digital shapes that can be built from $S$ by adding or removing a sequence of $n$ connected pixels in $R_1(S)$.
+}
 \end{definition}
@@
 	}%	
-	\caption{The blue pixels in figure (a) illustrates a $3$-ring set. In figure (b) we highlight the contour of an element of set $\mathcal{N}_{11}$.}
+	\caption{\revision{The blue pixels in figure (a) illustrates a $3$-ring set. In figure (b) we highlight the contour of an element of set $\mathcal{N}_{11}$.}}
 \end{figure}
@@
 	}%
-		\caption{Local combinatorial optimization process results for the square and flower shapes. Shapes displayed at every $2$ iterations for the square and $5$ iterations for the flower.}	
+		\caption{\revision{Local combinatorial optimization process results for the square and flower shapes. Shapes displayed at every $2$ iterations for the square and $5$ iterations for the flower.}}	
 		\label{fig:local-comb-square-results}
@@
 The running time of algorithm \ref{alg:local-search} is summarized in table \ref{tab:summary-local-comb-rtime}. All the
-experiments in this paper were executed on a $32$-core $2.4Ghz$ CPU and the number of pixels in the square and
-flower shapes are respectively $841,1867$ for grid step $h=1.0$. Although its use in practical applications is
+experiments in this paper were executed on a \revision{$32$-core $2.4Ghz$ CPU and the number of pixels in the square and
+flower shapes are respectively $841,1867$ for grid step $h=1.0$}. Although its use in practical applications is
 limited, we demonstrate that digital estimators are effective in their measurements and the flows evolve as expected.
-In particular, the digital elastica energy for the experiments in figure \ref{fig:local-comb-square-results} approaches the global optimum (figure  \ref{fig:plot-elastica-local-search}).
+\revision{In particular, the digital elastica energy for the experiments in figure \ref{fig:local-comb-square-results} approaches the global optimum (figure  \ref{fig:plot-elastica-local-search})}.
 We
@@
 \includegraphics[scale=0.35]{images/local_search/square-flower.eps}
-\caption{Elastica computation along iterations of algorithm \ref{alg:local-search}. The final shape has energy value closer to the optimal value $2\pi/5$ (dashed line).}
+\caption{Elastica computation along iterations of algorithm \ref{alg:local-search}. \revision{The final shape has energy value closer to the optimal value $2\pi/5$ (dashed line)}.}
 \label{fig:plot-elastica-local-search}
@@
 \begin{minipage}[b]{0.45\textwidth}
+\revision{
 \center
@@
 \end{tabular}
-\caption{Running times for the local combinatorial optimization algorithm with $k=1,n=50$. Four threads were used.}
+}
+\caption{Running times for the local combinatorial optimization algorithm with $k=1,\revision{n=50}$. Four threads were used.}
 \label{tab:summary-local-comb-rtime}
@@
 
+\revision{
 We observe that the integral invariant estimator \eqref{eq:curvature_approximation} is originaly designed to be evaluated on the digital boundary of some shape, which is the unknown of our problem.
 Injecting contour information leads to a third order model, which we prefer to avoid.
-Instead, we are going to exploit the II estimator definition in order to compute a flow that evolves proportionally to the squared curvature of the current shape.
+Instead, we are going to exploit the II estimator definition in order to compute a flow that evolves proportionally to the squared curvature of the current shape.}
 
@@
 \begin{definition}[Inner pixel boundary]
-Given a digital shape $S$ embedded in a domain $\Omega$, we define its inner pixel boundary set $I(S)$ as
-\begin{align*}
-	I(S) = \left\{ \: p \; | \; p \in S, |\mathcal{N}_4(x) \cap S|<4 \: \right\},
+
+Given a digital shape $S$ embedded in a domain $\Omega$, we define its inner pixel boundary set \revision{$I(S)$} as
+\begin{align*}
+	\revision{I(S)} = \left\{ \: p \; | \; p \in S, |\mathcal{N}_4(x) \cap S|<4 \: \right\},
 \end{align*}
@@
 
-The optimization variables set is defined as
-
-\begin{align*}
+\revision{
+The optimization variables set is defined as}
+
+\begin{align*}
+\revision{
 	X(S) = \left\{ x_j \in \{0,1\} \; | \; p_j \in I(S) \right \}.
+}
 \end{align*}
@@
 \end{minipage}%
-\caption{Directly using the optimization result of \eqref{eq:energy-family} doesn't decrease squared curvature because contour information is not present in the energy.}
+\caption{ \revision{Directly using the optimization result of \eqref{eq:energy-family} doesn't decrease squared curvature because contour information is not present in the energy.}}
 \label{fig:contour-info}
@@
 	 	$X^{(i)} \longleftarrow \argmin_X E_m(X,\overline{S^{(i-1)}})$\;
- 		$S^{(i)} \longleftarrow F^{(i-1)}_{\overline{S}} + \overline{X^{(i)}}$\;
+ 		$S^{(i)} \longleftarrow \revision{F^{(i-1)}_{\overline{S}}} + \overline{X^{(i)}}$\;
  		$S^{(i)} \longleftarrow \overline{S^{(i)}}$\;	 	
@@
 
-We emphasize that the minimization of \eqref{eq:energy-family} for $S^{(i)}$ is not sufficient to derive the next shape $S^{(i+1)}$ because topolical information is not included in the model (see figure \ref{fig:contour-info}).
+\revision{
+We emphasize that the minimization of \eqref{eq:energy-family} for $S^{(i)}$ is not sufficient to derive the next shape $S^{(i+1)}$ because topolical information is not included in the model (see figure \ref{fig:contour-info})}.
 Recall that the integral invariant estimator approaches curvature by computing the difference between half of the area
@@
 \begin{minipage}[b]{0.33\textwidth}
-	\subfloat[$r=5, m=5$\label{}]{%
+	\subfloat[\revision{$r=5, m=5$}\label{}]{%
 	\includegraphics[scale=0.2]{images/flow/farther-rings/square-r5-l5/summary_flow.eps}
@@
 		}\\
-		\subfloat[Elastica evaluation]{%
+		\subfloat[\revision{Elastica evaluation}]{%
 		\includegraphics[scale=0.5]{images/flow/elastica-energy-plot/square-flower-triangle.eps}						
@@
 \begin{tabular}{ccc}
-Seeds & $(\alpha=0, \beta=0.5)$ & $(\alpha=0,\beta=1)$ \\
+\revision{Seeds} & $(\alpha=0, \beta=0.5)$ & $(\alpha=0,\beta=1)$ \\
  	\includegraphics[scale=0.25]{images/segmentation/bc/coala/seeds.png} & 
@@
 
-	GrabCut & $(\alpha=0.5, \beta=0)$ & $(\alpha=1, \beta=0)$
+	\revision{GrabCut} & $(\alpha=0.5, \beta=0)$ & $(\alpha=1, \beta=0)$
 \end{tabular}	
@@
 	\end{tabular}
-	\caption{Additional comparison results between GrabCut, Schoenemman and Contour correction segmentation methods.}
+	\caption{\revision{Additional comparison results between GrabCut, Schoenemman and Contour correction segmentation methods.}}
 	\label{fig:more-segmentation-results}	
@@
 We evaluate our method using the BSD300 database \cite{martinFTM01berkeley}.
-All images contain the same number of pixels, the resolution being 321x481 (481x321) in portrait (landscape) mode.
+All images contain the same number of pixels, \revision{the resolution being 321x481 (481x321) in portrait (landscape) mode}.
 We compare the results of our method with segmentations given by GrabCut and Schoenemanns's method \cite{schoenemann09linear}.

### 2019-12-13 jmiv.tex
Further corrections

@@
 
-Let $d_{S}:\Omega \rightarrow \mathcal{R}$ be the \revision{signed} Euclidean distance transformation with respect to shape $S$.
+Let $d_{S}:\Omega \rightarrow \mathbb{R}$ be the \revision{signed} Euclidean distance transformation with respect to shape $S$.
 The value $d_S(p)$ gives the Euclidean distance between \revision{$p \notin S$ and the closest pixel in $S$.
@@
 \begin{align*}
-	\mathcal{R}_m(S) &:= \mathcal{L}_m \cup \mathcal{L}_{-m},
+	R_m(S) &:= L_m \cup L_{-m},
 \end{align*}
@@
 \begin{align*}
-	\mathcal{L}_m(S) &:= \left\{ \quad \begin{array}{cc}
+	L_m(S) &:= \left\{ \quad \begin{array}{cc}
 		\left\{ p \in \Omega \; | \; m-1 < d_S(p) \leq m \right\} & , \quad m>0\\
@@
 
-Algorithm~\ref{alg:local-search} describes the local combinatorial process and Figure~\ref{fig:local-comb-square-results} presents the digital curve evolution when executing this algorithm for two different shapes with $n=50$.
+Algorithm~\ref{alg:local-search} describes the local combinatorial process and Figure~\ref{fig:local-comb-square-results} presents the digital curve evolution when executing this algorithm for two different shapes with \revision{$n=50$}.
 
@@
 
-Given a digital shape $S \subset \Omega \subset \mathbb{Z}^2$, the goal is to compute a flow $S^{(i)}$ where $S^{(i+1)}$ has lower digital elastica than its precedent.
-
 \revision{
+Given a digital shape $S \subset \Omega \subset \mathbb{Z}^2$, the goal is to compute a flow $S^{(i)}$ where $S^{(i+1)}$ has lower digital elastica $S^{(i)}$.
+
 We observe that the integral invariant estimator \eqref{eq:curvature_approximation} is originaly designed to be evaluated on the digital boundary of some shape, which is the unknown of our problem.
@@
 \revision{
-We emphasize that the minimization of \eqref{eq:energy-family} for $S^{(i)}$ is not sufficient to derive the next shape $S^{(i+1)}$ because topolical information is not included in the model (see figure \ref{fig:contour-info})}.
+We emphasize that the minimization of \eqref{eq:energy-family} for $S^{(i)}$ is not sufficient to derive the next shape $S^{(i+1)}$ because contour information is not included in the model (see figure \ref{fig:contour-info})}.
 Recall that the integral invariant estimator approaches curvature by computing the difference between half of the area

### 2019-12-15 jmiv.tex
fix issue with \revision

@@
 \revision{
-Given a digital shape $S \subset \Omega \subset \mathbb{Z}^2$, the goal is to compute a flow $S^{(i)}$ where $S^{(i+1)}$ has lower digital elastica $S^{(i)}$.
-
-We observe that the integral invariant estimator \eqref{eq:curvature_approximation} is originaly designed to be evaluated on the digital boundary of some shape, which is the unknown of our problem.
+Given a digital shape $S \subset \Omega \subset \mathbb{Z}^2$, the goal is to compute a flow $S^{(i)}$ where $S^{(i+1)}$ has lower digital elastica $S^{(i)}$.}
+
+\revision{We observe that the integral invariant estimator \eqref{eq:curvature_approximation} is originaly designed to be evaluated on the digital boundary of the shape, which is the unknown of our problem.
 Injecting contour information leads to a third order model, which we prefer to avoid.

### 2019-12-16 answer-to-reviewers/answer-to-reviewers.tex
answers

\documentclass[12pt]{article}
\usepackage{a4wide}
\usepackage{amsmath,amssymb}

\title{Response to reviewers}
\date{}

\begin{document}
\maketitle

We thank the reviewers for their time, consideration and thoughtful comments. Our article has been amended
according to their recommendations. Our replies follow.

\section{Reviewer \#1}

\paragraph{This is an interesting contribution to digital processing of images. Alternative approaches to discretization of elastica based on polygonal approximations for discrete elastica and their convergence issues could be mentioned for comparison}

~\\
Thanks.

\section{Reviewer \#2}

\subsection{General comments}
The manuscript discusses discrete estimators for geometric quantities,
especially curvature, with so-called "multigrid convergence" to ensure
their suitability for the discretization of geometric energy functionals.
On this basis, it derives purely discrete optimization procedures for
segmentation (used for post-processing graph-cut-based segmentation in the
experimental part) and shows the viability of the approach by an experimental
validation.

The idea and theory laid out in the paper are interesting and appealing; the
experimental validation, on a level for a paper with accent on theory, is
convincing. The manuscript extends the work from the preceding DGCI paper
by the same authors in a reasonable and substantial way. I clearly support
publication of the paper.

Most of the text is written in good style and well comprehensible; however,
Section 4.1 with the core variational model is hard to read and needs some
additional clarifications as set forth in the detailed comments below.
Therefore I propose to accept the paper conditional on a major revision.

\subsection{Comments}

\textbf{8:14--16 Probably a reference for "the cellular-grid model" may be in place.
Moreover, some short explanation would be welcom regarding the basic
components, especially "linels" and "pointels". I can guess what a linel is
but what are pointels, i.e., how do they differ from points?}

~\\
$\rightarrow$ An additional figure and further explanation was incorporated in the manuscript.
~\\

\textbf{8:42--44 I guess for gluing curves, some hypothesis on $C_1, C_2$ and/or $c_1, c_2$
is needed, so they can actually be connected by linels. This should be added.
Moreover, I understand that $c_1$ and $c_2$ are clipped from $C_1$ and $C_2$ but the
$\in$ symbol (=element of a set?!) does not express this well. $\subset$ or
$\subseteq$ would be better but would still need some constraining sentence.}

~\\
$\rightarrow$ We agree. We assume that region enclosed by $C_2$ is contained in the region enclosed by $C_1$. The hypothesis was included in the manuscript.
~\\

\textbf{9:21--26 In the unnumbered displayed equation int is applied to sets of curves (according to Def. 8) but it is only explained in the text what int is for a single curve. Some explanation is needed how this transfers to sets of curves, in order for the reader to interpret the unnumbered displayed equation.}

→ Indeed, an extension of the operator int(.) for set of curves is needed. The extended definition was included in the manuscript.

Section 4.1: This was the part that I had really difficulties to warp my mind
around. As this is the central theoretical section, the reader should be
guided here with utmost clarity.

Starting with 11:18, it is (as I understand) meant that the "optimization
region: $O^{(i)}$ is the inner pixel boundary set of the i-th iterate $S^{(i)}$
according to Def. 9. This could be stated explicitly to assure the reader they
are on the right track of understanding.

→ We’ve modified the presentation in section 4 in order to clarify this point.

On the transition from (5) to the unnumbered displayed equation starting 11:29, I find that the notation is somewhat confusing. As far as I infer, the $x_i$ are used in a duplicate meaning: On one hand, $x_j\in B_r(y)$ indicates that $x_j$ are pixels from the discrete neighborhood (set) $B_r(y)$. On the other hand, they are summed which does not make sense for pixels; it seems in the summation $x_j$ actually stands short-hand for $1_X(x_j)$, i.e., the membership of pixel $x_j$ in the set $X$ which is optimized by minimizing $E_m(X,S)$ from eq. (6) later on. Using $1_X(x_j)$ all the time would be too cumbersome, I agree, but it would definitely be better to use different symbols for pixels (elements of $B_r$) and the optimization variables. At any rate, the meaning of these variables needs to be stated, along with explicitly clarifying their relation to X, and the role of X as pixel subset of $O^{(i)}$ to be optimized.

→ That's correct. We hope that the modifications done in presentation of section four will clarify this point.

Next, I conjecture that the first line of the unnumbered equation at 11:29
needs a minor correction: The opening bracket after the $\sum$ symbol should
probably go before the $\sum$ symbol so the $|F_r^{(i)}(y)|$ is not included
in the summation.

→ That's correct. Fixed!

Moreover, the summation should be over $O_r^{(i)}(y)$ as in the following line because otherwise the pixels j in the foreground would be counted twice, once with their $x_j$ in the sum over $B_r(y)$ and a second time lumped up in the $|F_r|$ expression. (Of course, one can argue that $X$ is a subset of $O^{(i)}$, thus the $x_j$ -- actually $1_X(x_j)$ -- are zero for pixels outside S and in the foreground set; but despite formal correctness, this would be confusing. Better define $1_X(x_j)$ only within $O^{(i)}$.)

→ That's also correct. Fixed!

Next, I stumbled over Algorithm 1. In the expansion mode, I wonder whether $F^{(i)}$ in Line 6 is the foreground set of $S^{(i)}$ as defined in the text, or whether it is tacitly assumed that, since in Line 5 the energy $E_m$ was written for the complement set $\bar{S^{(i)}}$, $F^{(i)}$ is in fact the set of non-boundary pixels of $\bar{S}$. To me it appears most plausible that the latter is meant but this needs to be made clear somehow.

→ That's correct! In the expansion mode, $F$ represents the foreground pixels of $\bar{S}$. We changed the notation to make this point clear.

Finally, the paragraphs 12:26--41 provide a heuristic reasoning why to use the complement of optimization sets $X^{(i)}$ in the algorithm. However, if (5) indeed is a discrete approximation of the squared curvature, and $E_m$ then discretizes a continuous energy involving the squared curvature, and $E_m$ is minimized to find $X$, the reduction of the (modulus of the) curvature should be achieved using $X$, not $\bar{X}$. The heuristics in 12:26--41 seem plausible in themselves but somewhere here is a contradiction. Using stringent energy minimization and then, by a heuristic argument, just the inverse of the result, would put the entire theoretical approach at question. It might be that this is somehow related with the placement of $y$ in $E_m$ off the actual shape boundary (on the ring sets $R_m$) but from what I read I cannot see how the contradiction is resolved. As the experiments demonstrate that the method actually works, I think this can be clarified by careful additional explanations, or minor corrections in the formulas.

→ We included a paragraph in the text clarifying this point. To sum up, we cannot use directly the minimization of energy $E_m$ because we are not incorporating topological information into the model, which would lead to a third order model that we wish to avoid. The heuristic comes up to solve this issue of not having topological information in the model.

\subsection{MINOR TYPOS ETC.}

[List of suggestions and corrections]
→ We thank you for your careful reading! The grammar corrections and style suggestions were very appreciated.

\section{Reviewer \#3}

Digital analogs of continuous definitions related mathematical image analysis are interesting. From these point of views, the present paper is interesting. However, some revisions are requested, since the relations among some sections are unclear. Also, graphical expressions of definitions and equations for digital setting are requested, since these figures make non-experts in digital geometry accessible to the paper by comparing with classical definitions.

\subsection{Comments}

Cross references are incorrect. Algorithm 1 is cited as algorithm 11 in the manuscript.
Please check latex file of your manuscript.

→ Thank you for pointing out. Corrections were made.

Eq. (4) is proposed in this paper.
"Gradient flow" like evolution of digital planar boundary which minimises energy of eq. (4).
For the understanding of the differences and similarity between definitions for eqs. (3) and (4),
step-by-step graphical descriptions of definitions and equations in section 2 are preferable.

→ Not sure to comply with this request or not. I’m not sure what to answer

Second paragraph insection3 describes the main mathematical idea for curve evolution in digital space. In the process selection of the local neighbourhood is essential in your proposal. The graphical explanation is preferable. These descriptions provide the necessity of the distance transform in the local operations.

→ New figures were included in section 3. We they will help clarify this point.

In algorithm 1 (11) $X^\ast$ s.t .$\hat{E}(X)< E(X^ast)$ is searched, how can you mathematically guarantee $\hat{E}(X)< E(X^\ast)$? Please describe why such $X^{\ast}$ exists.

→ It may not exist! If the neighborhood is exhausted and such X* is not found, the algorithm stops. In particular, the shapes S(i) and S(i-1) will be the same, hence delta will be zero and there will be no next iteration.

4. Relation between section 3 and section 4 is unclear.
Please describe relations between the Elastica minimisation motion and curvature flow.
Is the curvature flow of yours is derived as curve evolution process?
If so, please describe the derivation step-by-step
If not, please clarify the relation of them in your manuscript.

→ Section 3 plays two roles. The first is to validate the use of multigrid convergent estimator in an optimization model. In particular, the experiments in section 3 converged to the theoretical global optimum. However, the model in section 3 is of limited use in practice, but since we were successful in proving its pertinence, we can use this model as a base of comparison for other digital models. For example, comparing the results achieved for the model in section 3 with those achieved for the model proposed in section 4, which is more likely to be used in practice.

\end{document}

### 2019-12-16 answer-to-reviewers/answer-to-reviewers.tex
revision comments

@@
 We thank the reviewers for their time, consideration and thoughtful comments. Our article has been amended
-according to their recommendations. Our replies follow.
+according to their recommendations. Changes in the text are highlighted in red. In addition, our replies follow.
 
@@
 
-→ Indeed, an extension of the operator int(.) for set of curves is needed. The extended definition was included in the manuscript.
+~\\
+$\rightarrow$ Indeed, an extension of the operator int(.) for set of curves is needed. The extended definition was included in the manuscript.
+~\\
 
-Section 4.1: This was the part that I had really difficulties to warp my mind
+\textbf{Section 4.1: This was the part that I had really difficulties to warp my mind
 around. As this is the central theoretical section, the reader should be
-guided here with utmost clarity.
+guided here with utmost clarity.}
 
-Starting with 11:18, it is (as I understand) meant that the "optimization
+\textbf{Starting with 11:18, it is (as I understand) meant that the "optimization
 region: $O^{(i)}$ is the inner pixel boundary set of the i-th iterate $S^{(i)}$
 according to Def. 9. This could be stated explicitly to assure the reader they
-are on the right track of understanding.
+are on the right track of understanding.}
 
-→ We’ve modified the presentation in section 4 in order to clarify this point.
+~\\
+$\rightarrow$ We have modified the presentation in section 4 in order to clarify this point.
+~\\
 
-On the transition from (5) to the unnumbered displayed equation starting 11:29, I find that the notation is somewhat confusing.
+\textbf{On the transition from (5) to the unnumbered displayed equation starting 11:29, I find that the notation is somewhat confusing.
 As far as I infer, the $x_i$ are used in a duplicate meaning: On one hand, $x_j\in B_r(y)$ indicates that $x_j$ are pixels from the discrete neighborhood (set) $B_r(y)$.
@@
 Using $1_X(x_j)$ all the time would be too cumbersome, I agree, but it would definitely be better to use different symbols for pixels (elements of $B_r$) and the optimization variables.
-At any rate, the meaning of these variables needs to be stated, along with explicitly clarifying their relation to X, and the role of X as pixel subset of $O^{(i)}$ to be optimized.
+At any rate, the meaning of these variables needs to be stated, along with explicitly clarifying their relation to X, and the role of X as pixel subset of $O^{(i)}$ to be optimized.}
 
-→ That's correct. We hope that the modifications done in presentation of section four will clarify this point.
+~\\
+$\rightarrow$ We agree. We hope that the modifications implemented in the presentation of section four will clarify this point.
+~\\
 

### 2019-12-16 answer-to-reviewers/answer-to-reviewers.tex
Update answers-to-reviewers

@@
 ~\\
-Thanks.
+In section 5, we compare our segmentation model with the work of \cite{schoenemann09linear} which uses a discretization of curvature proposed in \cite{bruckstein96} which $\Gamma$-convergence is proved in \cite{bruckstein01}.
+We remark that our approach never leaves the digital domain, in other words, is purely digital and it doesn't rely in any curve representation.
+The notions of multigrid convergence and $\Gamma$-convergence are not easily comparable, as the former is especially designed for digital data.
+In this sense, multigrid convergence is more appropriated in our case as our main object of interest are digital images.
+~\\
 
@@
 ~\\
-$\rightarrow$ We agree. We assume that region enclosed by $C_2$ is contained in the region enclosed by $C_1$. The hypothesis was included in the manuscript.
+$\rightarrow$ We agree. In fact, the former presentation included gratuitous technical difficulties. We've decided to change the presentation to an equivalent one, easier to read.
 ~\\
@@
 ~\\
-$\rightarrow$ Indeed, an extension of the operator int(.) for set of curves is needed. The extended definition was included in the manuscript.
+$\rightarrow$ Indeed, an extension of the operator int(.) for set of curves was necessary.
+However, as said in the previous answer, the presentation of this section has changed, and such definition is no more needed.
 ~\\
@@
 
-Next, I conjecture that the first line of the unnumbered equation at 11:29
+\textbf{Next, I conjecture that the first line of the unnumbered equation at 11:29
 needs a minor correction: The opening bracket after the $\sum$ symbol should
-probably go before the $\sum$ symbol so the $|F_r^{(i)}(y)|$ is not included
-in the summation.
+probably go before the $\sum$ symbol so the $|F_r^{(i)}(y)|$ is not included in the summation. }
 
-→ That's correct. Fixed!
+~\\
+$\rightarrow$ That's correct. Fixed!
+~\\
 
-Moreover, the summation should be over $O_r^{(i)}(y)$ as in the following line because otherwise the pixels j in the foreground would be counted twice, once with their $x_j$ in the sum over $B_r(y)$ and a second time lumped up in the $|F_r|$ expression.
+\textbf{Moreover, the summation should be over $O_r^{(i)}(y)$ as in the following line because otherwise the pixels j in the foreground would be counted twice, once with their $x_j$ in the sum over $B_r(y)$ and a second time lumped up in the $|F_r|$ expression.
 (Of course, one can argue that $X$ is a subset of $O^{(i)}$, thus the $x_j$ -- actually $1_X(x_j)$ -- are zero for pixels outside S and in the foreground set; but despite formal correctness, this would be confusing.
-Better define $1_X(x_j)$ only within $O^{(i)}$.)
+Better define $1_X(x_j)$ only within $O^{(i)}$.) }
 
-→ That's also correct. Fixed!
+~\\
+$\rightarrow$ That's also correct. Fixed!
+~\\
 
-Next, I stumbled over Algorithm 1.
+\textbf{Next, I stumbled over Algorithm 1.
 In the expansion mode, I wonder whether $F^{(i)}$ in Line 6 is the foreground set of $S^{(i)}$ as defined in the text, or whether it is tacitly assumed that, since in Line 5 the energy $E_m$ was written for the complement set $\bar{S^{(i)}}$, $F^{(i)}$ is in fact the set of non-boundary pixels of $\bar{S}$.
-To me it appears most plausible that the latter is meant but this needs to be made clear somehow.
+To me it appears most plausible that the latter is meant but this needs to be made clear somehow.}
 
-→ That's correct! In the expansion mode, $F$ represents the foreground pixels of $\bar{S}$. We changed the notation to make this point clear.
+~\\
+$\rightarrow$ That's correct! In the expansion mode, $F$ represents the foreground pixels of $\bar{S}$. We changed the notation to make this point clear.
+~\\
 
-Finally, the paragraphs 12:26--41 provide a heuristic reasoning why to use the complement of optimization sets $X^{(i)}$ in the algorithm.
+\textbf{Finally, the paragraphs 12:26--41 provide a heuristic reasoning why to use the complement of optimization sets $X^{(i)}$ in the algorithm.
 However, if (5) indeed is a discrete approximation of the squared curvature, and $E_m$ then discretizes a continuous energy involving the squared curvature, and $E_m$ is minimized to find $X$, the reduction of the (modulus of the) curvature should be achieved using $X$, not $\bar{X}$.
@@
 It might be that this is somehow related with the placement of $y$ in $E_m$ off the actual shape boundary (on the ring sets $R_m$) but from what I read I cannot see how the contradiction is resolved.
-As the experiments demonstrate that the method actually works, I think this can be clarified by careful additional explanations, or minor corrections in the formulas.
+As the experiments demonstrate that the method actually works, I think this can be clarified by careful additional explanations, or minor corrections in the formulas.}
 
-→ We included a paragraph in the text clarifying this point.
-To sum up, we cannot use directly the minimization of energy $E_m$ because we are not incorporating topological information into the model, which would lead to a third order model that we wish to avoid.
-The heuristic comes up to solve this issue of not having topological information in the model.
+~\\
+$\rightarrow$ We included a paragraph in the text clarifying this point.
+To sum up, we cannot use directly the minimization of energy $E_m$ because we are not incorporating contour information into the model, which would lead to a third order energy that we wish to avoid.
+The heuristic comes up to solve this issue of not having contour information in the model.
+~\\
 
@@
 [List of suggestions and corrections]
-→ We thank you for your careful reading! The grammar corrections and style suggestions were very appreciated.
+~\\
+
+$\rightarrow$ We thank you for your careful reading! The grammar corrections and style suggestions were very appreciated.
+~\\
 
@@
 
-Cross references are incorrect. Algorithm 1 is cited as algorithm 11 in the manuscript.
-Please check latex file of your manuscript.
+\textbf{Cross references are incorrect. Algorithm 1 is cited as algorithm 11 in the manuscript.
+Please check latex file of your manuscript.}
 
-→ Thank you for pointing out. Corrections were made.
+~\\
+$\rightarrow$ Thank you for pointing out. Corrections were made.
+~\\
 
-Eq. (4) is proposed in this paper.
+~\\
+\textbf{Eq. (4) is proposed in this paper.
 "Gradient flow" like evolution of digital planar boundary which minimises energy of eq. (4).
 For the understanding of the differences and similarity between definitions for eqs. (3) and (4),
-step-by-step graphical descriptions of definitions and equations in section 2 are preferable.
+step-by-step graphical descriptions of definitions and equations in section 2 are preferable.}
 
-→ Not sure to comply with this request or not. I’m not sure what to answer
+~\\
+$\rightarrow$ Not sure to comply with this request or not. I’m not sure what to answer
+~\\
 
-Second paragraph insection3 describes the main mathematical idea for curve evolution in digital space.
+\textbf{Second paragraph insection3 describes the main mathematical idea for curve evolution in digital space.
 In the process selection of the local neighbourhood is essential in your proposal.
 The graphical explanation is preferable.
-These descriptions provide the necessity of the distance transform in the local operations.
+These descriptions provide the necessity of the distance transform in the local operations.}
 
-→ New figures were included in section 3. We they will help clarify this point.
+~\\
+$\rightarrow$ New figures were included in section 3. We they will help clarify this point.
+~\\
 
-In algorithm 1 (11) $X^\ast$ s.t .$\hat{E}(X)< E(X^ast)$ is searched, how can you mathematically guarantee $\hat{E}(X)< E(X^\ast)$? Please describe why such $X^{\ast}$ exists.
+\textbf{In algorithm 1 (11) $X^\ast$ s.t .$\hat{E}(X)< E(X^ast)$ is searched, how can you mathematically guarantee $\hat{E}(X)< E(X^\ast)$? Please describe why such $X^{\ast}$ exists.}
 
-→ It may not exist!
+~\\
+$\rightarrow$ It may not exist!
 If the neighborhood is exhausted and such X* is not found, the algorithm stops.
 In particular, the shapes S(i) and S(i-1) will be the same, hence delta will be zero and there will be no next iteration.
+~\\
 
-4. Relation between section 3 and section 4 is unclear.
+\textbf{Relation between section 3 and section 4 is unclear.
 Please describe relations between the Elastica minimisation motion and curvature flow.
@@
 If so, please describe the derivation step-by-step
-If not, please clarify the relation of them in your manuscript.
+If not, please clarify the relation of them in your manuscript.}
 
-→ Section 3 plays two roles.
+~\\
+$\rightarrow$ Section 3 plays two roles.
 The first is to validate the use of multigrid convergent estimator in an optimization model.
@@
 For example, comparing the results achieved for the model in section 3 with those achieved for the model proposed in section 4, which is more likely to be used in practice.
+~\\
+
+\bibliographystyle{plain}
+\bibliography{answers.bib}
 

### 2019-12-16 jmiv.tex
Typos, notation, style corrections

--- 2019-12-13 jmiv.tex
@@
 \usepackage[export]{adjustbox}
+\usepackage{array}
 \usepackage[dvipsnames]{xcolor}
@@
   and only if, for any $X \in \mathbb{X}$, there exists a grid step
-  $h_X>0$ such that the estimate $\hat{u}(D_h(X),\hat{x},h)$ is
-  defined for all $\hat{x} \in \partial_hX$ with $ 0 < h < h_X$, and
+  $h_X>0$ such that the estimate $\hat{u}(D_h(X), \revision{p},h)$ is
+  defined for all $\revision{p} \in \partial_hX$ with $ 0 < h < h_X$, and
   for any $x \in \partial X$,
   \begin{equation*}
-    \forall \hat{x} \in  \partial_hX \text{ with } \norm{ \hat{x} - x }_{\infty} \leq h, \norm{ \hat{u}(D_h(X),\hat{x},h) - u(X,x)} \leq \tau_{X}(h),			
+    \forall \revision{p} \in  \partial_hX \text{ with } \norm{ \revision{p} - x }_{\infty} \leq h, \norm{ \hat{u}(D_h(X),\revision{p},h) - u(X,x)} \leq \tau_{X}(h),			
   \end{equation*}
@@
   \begin{align*}
-    \hat{\kappa}_{r}(D,x,h) \coloneqq \frac{3}{r^3} \left( \frac{\pi r^2}{2} - \widehat{\text{Area}} \left( B_{r} ( x ) \cap D, h \right) \right).
+    \hat{\kappa}_{r}(D,\revision{p},h) \coloneqq \frac{3}{r^3} \left( \frac{\pi r^2}{2} - \widehat{\text{Area}} \left( B_{r} ( \revision{p} ) \cap D, h \right) \right).
     %% \hat{\kappa}_{r}(D,x,h) \coloneqq \frac{3}{r^3} \left( \frac{\pi r^2}{2} - \widehat{Area} \left( B_{r/h} ( \frac{1}{h} \cdot x ) \cap D, h \right) \right).
@@
 
-Algorithm~\ref{alg:local-search} describes the local combinatorial process and Figure~\ref{fig:local-comb-square-results} presents the digital curve evolution when executing this algorithm for two different shapes with \revision{$n=50$}.
+Algorithm~\ref{alg:local-search} describes the local combinatorial process and Figure~\ref{fig:local-comb-square-results} presents the digital curve evolution when executing this algorithm for two different shapes with \revision{$0 \leq n \leq 50$}.
 
@@
 	}%
-		\caption{\revision{Local combinatorial optimization process results for the square and flower shapes. Shapes displayed at every $2$ iterations for the square and $5$ iterations for the flower.}}	
+		\caption{\revision{Local combinatorial optimization process results using II estimator with radius $7$ for the square and flower shapes.
+Shapes displayed at every $2$ iterations for the square and $5$ iterations for the flower.}}
 		\label{fig:local-comb-square-results}
@@
 }
-\caption{Running times for the local combinatorial optimization algorithm with $k=1,\revision{n=50}$. Four threads were used.}
+\caption{Running times for the local combinatorial optimization algorithm with $\revision{ 0 \leq n \leq 50}$. Thirty two threads were used.}
 \label{tab:summary-local-comb-rtime}
@@
 \revision{
-Given a digital shape $S \subset \Omega \subset \mathbb{Z}^2$, the goal is to compute a flow $S^{(i)}$ where $S^{(i+1)}$ has lower digital elastica $S^{(i)}$.
-
-We observe that the integral invariant estimator \eqref{eq:curvature_approximation} is originaly designed to be evaluated on the digital boundary of some shape, which is the unknown of our problem.
+Given a digital shape $S \subset \Omega \subset \mathbb{Z}^2$, the goal is to compute a flow $S^{(i)}$ where $S^{(i+1)}$ has lower digital elastica than $S^{(i)}$.}
+
+\revision{We observe that the integral invariant estimator \eqref{eq:curvature_approximation} is originally designed to be evaluated on the digital boundary of the shape, which is the unknown of our problem.
 Injecting contour information leads to a third order model, which we prefer to avoid.
@@
 
+\subsection{Discrete variational model for discrete curve evolution}
+
+\revision{We assume an ordering in $\Omega$, i.e., there exists a bijective function $\omega : \Omega \rightarrow \{1 \cdots |\Omega| \}$.
+Moreover, we associate to every pixel in $\Omega$ a binary variable grouped in the set $X(\Omega)$}
+
+\begin{align*}
+	\revision{X(\Omega) := \left\{ x_{\omega(p)} \in \{0,1\} \; | \; p \in \Omega \right\}.}
+\end{align*}
+
+\revision{We extend the definition for every subset $P \in \Omega$, i.e.,}
+
+\begin{align*}
+	\revision{X(P) := \left\{ x_{\omega(p)} \in \{0,1\} \; | \; p \in P \right\}.}
+\end{align*}
+
 In order to guarantee connectivity, we limit the optimization region to a subset of $\Omega$, namely the inner pixel boundary of  $S^{(i)}$.
@@
 
-\subsection{Discrete variational model for discrete curve evolution}
-
-We start by defining the optimization variables.
 \begin{definition}[Inner pixel boundary]
@@
 \begin{align*}
-	\revision{I(S)} = \left\{ \: p \; | \; p \in S, |\mathcal{N}_4(x) \cap S|<4 \: \right\},
+	\revision{I(S)} := \left\{ \: p \; | \; p \in S, |\mathcal{N}_4(x) \cap S|<4 \: \right\},
 \end{align*}
@@
 
+\revision{To simplify notation, the inner pixel boundary of $S^{(i)}$ is simply denoted $I^{(i)}$. At each iteration, the set $X^{(i)}$ of optimization variables is defined as}
+
+\begin{align*}
 \revision{
-The optimization variables set is defined as}
-
-\begin{align*}
-\revision{
-	X(S) = \left\{ x_j \in \{0,1\} \; | \; p_j \in I(S) \right \}.
-}
-\end{align*}
-
-In other words, each flow iteration decides which pixels in the inner boundary are to be removed from $S$ and which are to be kept in $S$.
-To simplify notation, we denote the optimization region of $S^{(i)}$ as $X^{(i)}$, and the foreground set as $F^{(i)} = S^{(i)} \setminus X^{(i)}$.
+	X^{(i)} := X(I^{(i)}).
+}
+\end{align*}
+
+In other words, each flow iteration decides which pixels in the inner boundary are to be removed from \revision{$S^{(i)}$} and which are to be kept in \revision{$S^{(i)}$}.
 We recall the definition of our digital curvature estimator:
 \begin{align}
-	\hat{\kappa}^2(p) &= c_1\Big( c_2 - | B_r(p) \cap S | \Big)^2, 
+	\hat{\kappa}^2(p) &= c_1\Big( c_2 - | B_r(p) \cap S^{\revision{(i)}} | \Big)^2, 
 	\label{eq:curvature-estimator-pixels}
@@
 
-We define $X_{r}^{(i)}(p) := X^{(i)} \cap B_r(p)$ and an analogous definition holds for $F_{r}^{(i)}(p)$. Expanding \eqref{eq:curvature-estimator-pixels}, we get 
+\revision{The following sets are important in the expansion of $\eqref{eq:curvature-estimator-pixels}$.}
+
+\revision{
+\begin{align*}
+	F_r^{(i)}(p) &:= \big( S^{(i)} \setminus I^{(i)} \big) \cap B_r(p)\\
+	I_r^{(i)}(p) &:= I^{(i)} \cap B_r(p) \\
+	X_r^{(i)}(p) &:= X\big( I_r^{(i)}(p) \big).
+\end{align*}
+}
+
+Expanding \eqref{eq:curvature-estimator-pixels}, we get
+
 \begin{align*}
   \hat{\kappa}^2(p) &= c_1\Big( c_2 - |F_{r}^{(i)}(p)| - \sum_{x_j \in X_r^{(i)}(p)} {x_j} \Big)^2 \\
-   &= c_1 \cdot \Big( C + 2\left( |F_{r}^{(i)}(p)| - c_2 \right) \hspace{-2mm}\sum_{x_j \in X_{r}^{(i)}(p)}\hspace{-2mm}{x_j} + \hspace{-2mm}\sum_{x_j \in X_{r}^{(i)}(p)}\hspace{-2mm}{x_j^2} + \hspace{-2mm}\sum_{ \substack{x_j,x_k \in X_{r}^{(i)}(p) \\ j<k} }\hspace{-2mm}{2x_jx_k}  \Big),
+   &= c_1 \Big( C + 2\left( |F_{r}^{(i)}(p)| - c_2 \right) \hspace{-2mm}\sum_{x_j \in X_{r}^{(i)}(p)}\hspace{-2mm}{x_j} + \hspace{-2mm}\sum_{x_j \in X_{r}^{(i)}(p)}\hspace{-2mm}{x_j^2} + \hspace{-2mm}\sum_{ \substack{x_j,x_k \in X_{r}^{(i)}(p) \\ j<k} }\hspace{-2mm}{2x_jx_k}  \Big),
 \end{align*}
@@
 \begin{align}
-  E_m(X,S) =& \sum_{x \in X}{\alpha s(x)} \nonumber \\ 
-  & + \sum_{p \in R_m(S)}{ \beta \Big( { (1/2+ |F_{r}^{(i)}(p)|-c_2) \cdot \sum_{x_j \in X_{r}^{(i)}(p)}{x_j} } + \sum_{ \substack{x_j,x_k \in X_{r}^{(i)}(p) \\ j<k} }{x_jx_k} \Big) } \nonumber \\
-  & + \sum_{x \in X}{\gamma g(S,x)},
+  E_m(X^{\revision{(i)}},S^{\revision{(i)}}) =& \sum_{x \in X^{\revision{(i)}}}{\alpha s(x)} + \nonumber \\ 
+  & \sum_{ \substack{p \in \\ R_m(S^{\revision{(i)}})}}{ \revision{2c_1} \beta  \Big( { (1/2+ |F_{r}^{(i)}(p)|-c_2) \cdot \sum_{ \substack{ x_j \in \\ X_{r}^{(i)}(p)}}{x_j} } + \sum_{ \substack{j<k, \\ x_j,x_k \in \\ X_{r}^{(i)}(p) } }{x_jx_k} \Big) } + \nonumber \\
+  & \sum_{x \in X^{\revision{(i)}}}{\gamma g(S^{\revision{(i)}},x)},
   \label{eq:energy-family}
 \end{align}
-where $g(S,x)$ denotes a similarity term as distance to initial shape $S$ or data fidelity term and $s(x)$ denotes a length penalization term.
+where $g(S,x)$ denotes a \revision{data term (e.g., distance to initial shape $S$ or fidelity to data)} and $s(x)$ denotes a length penalization term.
 Each choice of $m$ generates a different flow, which is generally described in the Digital Curve Evolution (DCE) algorithm \ref{alg:evolution-model}.
@@
 
- \Input{A digital set $S$; The ring number $m$; Length($\alpha$), curvature($\beta$) and similarity($\gamma$) coefficients; the maximum number of iterations \MIt;}
+ \Input{A digital set $S$; The ring number $m$; Length($\alpha$), curvature($\beta$) and \revision{data}($\gamma$) coefficients; the maximum number of iterations \MIt;}
  \BlankLine
@@
 	 	$X^{(i)} \longleftarrow \argmin_X E_m(X,\overline{S^{(i-1)}})$\;
- 		$S^{(i)} \longleftarrow \revision{F^{(i-1)}_{\overline{S}}} + \overline{X^{(i)}}$\;
- 		$S^{(i)} \longleftarrow \overline{S^{(i)}}$\;	 	
+ 		$\revision{S^{(i)} \longleftarrow \overline{ F^{(i-1)}_{\overline{S}} + \overline{X^{(i)}}}}$\;
  	}
@@
 
-Length and similarity terms should be properly defined in order to comply with the complement step of the DCE
+Length and \revision{data} terms should be properly defined in order to comply with the complement step of the DCE
 algorithm. The length penalization is defined as
@@
 
-We do not use similarity terms in this section, thus we postpone the definition of such terms until later in this
+We do not use \revision{data} terms in this section, thus we postpone the definition of such terms until later in this
 article, with the description of how DCE can be used in an image segmentation framework.
@@
   \center
+  \setlength{\extrarowheight}{0.5em}
   \begin{tabular}{|c|c|c|c|} \hline
@@
 towards rounder shapes, but with several artifacts. We minimize the effects of a jaggy boundary by setting $\alpha >
-0$. Nonetheless, a higher estimation ball radius creates unstable shapes. In fact, the estimator is very sensitive in
+0$. Nonetheless, a \revision{higher radius of the estimation ball} creates unstable shapes. In fact, the estimator is very sensitive in
 regions of low squared curvature, and it is precisely in those regions that spurious pixels are created.
@@
 In the previous section we noticed that the algorithm produces shapes with many artifacts due to the small uncertainties
-of the estimator along regions of low squared curvature. We argue that, evaluating the estimation ball along outer
+of the estimator along regions of low squared curvature. We argue that, \revision{by} evaluating the estimation ball along outer
 ring sets we avoid those sensitive areas by focusing the optimization process only on regions with highest squared
@@
 
-\begin{figure}[hp!]
+\begin{figure}[]
 \center
@@
 
-We use the DCE algorithm to regularize an initial contour output by some segmentation algorithm or delineated by the user. In this application, the similarity term of the DCE
+We use the DCE algorithm to regularize an initial contour output by some segmentation algorithm or delineated by the user. In this application, the \revision{data} term of the DCE
 is set to the data fidelity term \eqref{eq:data-fidelity}.
@@
 	\begin{tabular}{ccc}
-		GrabCut & Contour Correction & Schoenemann \\
-		& $(r=5, \alpha=0.1, \beta=1.0, \gamma=3.0$) & $(\alpha=0.1, \beta=1.0$)\\
+		GrabCut & Schoenemann & Contour Correction \\
+		& $(\alpha=0.1, \beta=1.0$) & $(r=5, \alpha=0.1, \beta=1.0, \gamma=3.0$)\\
 		\includegraphics[scale=0.2]{images/segmentation/bc/tiger1/gc-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/bc/tiger1/corrected-seg.png} &					\includegraphics[scale=0.2]{images/segmentation/schoenemann/tiger1/tiger1-seg.png}\\									
+	\includegraphics[scale=0.2]{images/segmentation/schoenemann/tiger1/tiger1-seg.png}&
+		\includegraphics[scale=0.2]{images/segmentation/bc/tiger1/corrected-seg.png}\\									
 		\includegraphics[scale=0.2]{images/segmentation/bc/snake/gc-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/bc/snake/corrected-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/schoenemann/snake/snake-seg.png}\\						
+		\includegraphics[scale=0.2]{images/segmentation/schoenemann/snake/snake-seg.png} &
+		\includegraphics[scale=0.2]{images/segmentation/bc/snake/corrected-seg.png}\\
 		\includegraphics[scale=0.2]{images/segmentation/bc/man/gc-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/bc/man/corrected-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/schoenemann/man/man-seg.png}\\		
+		\includegraphics[scale=0.2]{images/segmentation/schoenemann/man/man-seg.png} &
+		\includegraphics[scale=0.2]{images/segmentation/bc/man/corrected-seg.png}\\		
 		\includegraphics[scale=0.2]{images/segmentation/bc/vase/gc-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/bc/vase/corrected-seg.png} &					\includegraphics[scale=0.2]{images/segmentation/schoenemann/vase/vase-seg.png}		
+		\includegraphics[scale=0.2]{images/segmentation/schoenemann/vase/vase-seg.png} &
+		\includegraphics[scale=0.2]{images/segmentation/bc/vase/corrected-seg.png}		
 	\end{tabular}
-	\caption{The proposed method regularizes GrabCut contours and returns meaningful results.
-We can observe the completion feature of curvature in the second row, and we don't suffer from over-segmentation issues as Schoenemann's method.
+	\caption{The proposed method regularizes GrabCut \cite{rother04grabcut} contours and returns meaningful results.
+We can observe the completion feature of curvature in the second row, and we don't suffer from over-segmentation issues as Schoenemann's method \cite{schoenemann09linear}.
 However, our flow may stop in a local optimum as in the fourth row, while Schoenemann's is able to extrapolate such solutions.}
@@
 	\begin{tabular}{ccc}
-		GrabCut & Contour Correction & Schoenemann \\
-		& $(r=5, \alpha=0.1, \beta=1.0, \gamma=3.0$) & $(\alpha=0.1, \beta=1.0$)\\
+		GrabCut & Schoenemann & Contour Correction \\
+		& $(\alpha=0.1, \beta=1.0$) & $(r=5, \alpha=0.1, \beta=1.0, \gamma=3.0$)\\
 		\includegraphics[scale=0.2]{images/segmentation/bc/airplane2/gc-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/bc/airplane2/corrected-seg.png} &					\includegraphics[scale=0.2]{images/segmentation/schoenemann/airplane2/airplane2-seg.png}\\									
+		\includegraphics[scale=0.2]{images/segmentation/schoenemann/airplane2/airplane2-seg.png} &
+		\includegraphics[scale=0.2]{images/segmentation/bc/airplane2/corrected-seg.png}\\						
 		\includegraphics[scale=0.2]{images/segmentation/bc/bird/gc-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/bc/bird/corrected-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/schoenemann/bird/bird-seg.png}\\						
+		\includegraphics[scale=0.2]{images/segmentation/schoenemann/bird/bird-seg.png} &
+		\includegraphics[scale=0.2]{images/segmentation/bc/bird/corrected-seg.png}\\				
 		\includegraphics[scale=0.2]{images/segmentation/bc/camel/gc-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/bc/camel/corrected-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/schoenemann/camel/camel-seg.png}\\		
+		\includegraphics[scale=0.2]{images/segmentation/schoenemann/camel/camel-seg.png} &
+		\includegraphics[scale=0.2]{images/segmentation/bc/camel/corrected-seg.png}\\	
 		\includegraphics[scale=0.2]{images/segmentation/bc/rock/gc-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/bc/rock/corrected-seg.png} &					\includegraphics[scale=0.2]{images/segmentation/schoenemann/rock/rock-seg.png}\\
+		\includegraphics[scale=0.2]{images/segmentation/schoenemann/rock/rock-seg.png} &
+		\includegraphics[scale=0.2]{images/segmentation/bc/rock/corrected-seg.png} \\		
 		\includegraphics[scale=0.2]{images/segmentation/bc/giraffes/gc-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/bc/giraffes/corrected-seg.png} &					\includegraphics[scale=0.2]{images/segmentation/schoenemann/giraffes/giraffes-seg.png}\\
+		\includegraphics[scale=0.2]{images/segmentation/schoenemann/giraffes/giraffes-seg.png} &
+		\includegraphics[scale=0.2]{images/segmentation/bc/giraffes/corrected-seg.png} \\		
 		\includegraphics[scale=0.2]{images/segmentation/bc/canguru/gc-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/bc/canguru/corrected-seg.png} &					\includegraphics[scale=0.2]{images/segmentation/schoenemann/canguru/canguru-seg.png}\\		
+		\includegraphics[scale=0.2]{images/segmentation/schoenemann/canguru/canguru-seg.png} &
+		\includegraphics[scale=0.2]{images/segmentation/bc/canguru/corrected-seg.png} \\		
 		\includegraphics[scale=0.2]{images/segmentation/bc/coral/gc-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/bc/coral/corrected-seg.png} &					\includegraphics[scale=0.2]{images/segmentation/schoenemann/coral/coral-seg.png}\\
-
+		\includegraphics[scale=0.2]{images/segmentation/schoenemann/coral/coral-seg.png} &
+		\includegraphics[scale=0.2]{images/segmentation/bc/coral/corrected-seg.png}								
 	\end{tabular}
-	\caption{\revision{Additional comparison results between GrabCut, Schoenemman and Contour correction segmentation methods.}}
+	\caption{\revision{Additional comparison results between GrabCut \cite{rother04grabcut}, Schoenemman  \cite{schoenemann09linear} and Contour correction segmentation methods.}}
 	\label{fig:more-segmentation-results}	

### 2019-12-17 jmiv.tex
Simplification of opt vars definition
Mispelling corrections; bib file for reviewers answers

@@
 known about the shape of interest. Length penalization is a
-well-behaved, general purpose regularizer and many models in the
+well-behaved, general\revision{-}purpose regularizer and many models in the
 literature make use of it, from active contours
@@
 \cite{malladi1995image,malladi1995shape}. Discrete graph-based
-variational models have been particularly succesful to incorporate
-length penalization as a penalizer, while keeping the ability to
+variational models have been particularly succes\revision{s}ful to incorporate
+length penalization as a penalizer while keeping the ability to
 extract a global optimum \cite{boykov01graphcut,appleton05geodesic}.
 
-However length regularization shows limitations when segmenting small
+However, length regularization shows limitations when segmenting small
 or thin and elongated objects, as it tends to shrink solutions or
@@
 in the second-order regularizer of the original snake model
-\cite{kass1988snakes}.Indeed, an explicit curvature term was often
+\cite{kass1988snakes}. Indeed, an explicit curvature term was often
 employed in early level-set methods,
@@
 Willmore energy was studied in~\cite{bobenko2005discrete}. Although
-results look promising, authors used an inexact linearized version of
+results look promising, \revision{the} authors used an inexact linearized version of
 the square curvature at every step.
 
-One of the first successful uses of geometric, squared curvature in
+One of the first successful uses of curvature in
 image processing is the inpainting algorithm described in
@@
 curvature as a regularizer can help recover thin and elongated objects
-\cite{zehiry10fast}. Similarly Schoenemann {\em et al.}
+\cite{zehiry10fast}. Similarly, Schoenemann {\em et al.}
 \cite{schoenemann09linear} have considered the Elastica energy in
@@
 advantages of using such regularizer in common binary image
-segmentation tasks.  However the time complexity of their algorithm
+segmentation tasks.  However, the time complexity of their algorithm
 is prohibitive, even if curvature is again coarsely
@@
 computationally too costly in these methods.
+\revision{Moreover, parametric approaches to Elastica  as snakes and splines depend on the choice of anchor points and  multigrid convergence hasn't been proven for them.}
 
@@
 well-suited to inverse problem solving. The problem remains non-convex
-and the nature of the converged iterates are not studied, i.e. how
+and the nature of the converged iterates is not studied, i.e. how
 close they are to a global optimum.
@@
   Elastica energy, using a lifting scheme. Thanks to the lifting, it is not restricted to binary sets. It shows
-  promising results and can be used for image restoration in addition to inpainting and segmentation. The scheme is
-  however neither tight nor exact, and required 4 dimensions for a 2D approximation. In addition, it does not carry over
+  promising results and can be used for image restoration in addition to inpainting and segmentation. The scheme is,
+  however, neither tight nor exact, and required 4 dimensions for a 2D approximation. In addition, it does not carry over
 to $nD$. It also remains computationally expensive.
@@
 evaluated, and the complexity of the proposed solution is often high.
-
-%%\item{What are the difficulties in use curvature as a regularizer (point out convex relaxation approaches) and how a digital approach may help us }
-%%\item{Outline: We present two models that illustrate how digital estimators can be used to minimize the elastica energy on digital sets.  }
-%%\item{\todo{Add related works : geometric priors, binary segmentation, other digital curve evolution models}}
-%%\item{\todo{Talk about Willmore flow with phase field or with threshold dynamics}}
 
@@
 present an application of this model as a post-processing step in a
-segmentation framework, and demonstrate how it can improve standard
+segmentation framework and demonstrate how it can improve standard
 results. This paper is an extended version of a previous work that
@@
 have included a new local combinatorial optimization approach for
-elastica minimization, which show that our discrete model is
+Elastica minimization, which shows that our discrete model is
 well-founded. Finally, \revision{the code related to} this paper is freely
-available on github.\footnote{https://www.github.com/danoan/BTools}
+available on GitHub.\footnote{https://www.github.com/danoan/BTools}
 
@@
 optimization model and in the definition of the digital
-elastica. Section~3 describes a local combinatorial optimization model
+Elastica. Section~3 describes a local combinatorial optimization model
 suitable for several curvature estimators, that presents interesting
@@
 of some group on the elements of the domain.
-%% Jaco: trop général, et pas utilisé après
-%% Generally speaking, an invariant $\sigma$ is a real-valued function from some space $\Omega$ which value is unaffected by the action
-%% of some group $\mathfrak{G}$ on the elements of the domain
-%% \begin{align*}
-%%   x \in \Omega, g \in \mathfrak{G}, \sigma(x) = v \longleftrightarrow \sigma(g \cdot x ) = v.
-%% \end{align*}
+
 Perimeter and curvature are examples of invariants for shapes on
-$\mathbb{R}^2$ with respect to the euclidean group of rigid
+$\mathbb{R}^2$ with respect to the Euclidean group of rigid
 transformations. Definition of integral area invariant and its link
@@
 
-In the remaining of this article, we are considering in the minimization of the Elastica energy. Given a Euclidean shape $X$ with smooth enough boundary, the Elastica is defined as
+In the remaining of this article, we are considering the minimization of the Elastica energy. Given a Euclidean shape $X$ with smooth enough boundary, the Elastica is defined as
 \begin{align}
@@
 $\mathbb{Z}^2$ to $D_h(X)$ since the continuous shape $X$ is unknown.
-In the following we omit the grid step $h$ to simplify expressions
+In the following, we omit the grid step $h$ to simplify expressions
 (or, putting it differently, we assume that the shape of interest is
@@
 \cite{roussillon11mdca}. As a matter of fact, our experiments have
-shown that either estimators induce similar results.
+shown that either estimator induce similar results.
 
@@
  }
- \caption{Local combinatorial optimization for elastica minimization.}
+ \caption{Local combinatorial optimization for \revision{E}lastica minimization.}
  \label{alg:local-search} 
@@
 observe that it is a complete digital approach, and we do not suffer from discretization and rounding problems, a common
-issue in continuous models.  Furthermore we have checked that this approach works indifferently with Integral Invariant
+issue in continuous models.  Furthermore, we have checked that this approach works indifferently with Integral Invariant
 curvature estimator and Maximal Digital Circular Arc curvature estimator. So the convergence of the digital curvature
@@
 \includegraphics[scale=0.35]{images/local_search/square-flower.eps}
-\caption{Elastica computation along iterations of algorithm \ref{alg:local-search}. \revision{The final shape has energy value closer to the optimal value $2\pi/5$ (dashed line)}.}
+\caption{Digital elastica computation along iterations of algorithm \ref{alg:local-search}. \revision{The final shape has energy value closer to the optimal value $2\pi/5$ (dashed line)}.}
 \label{fig:plot-elastica-local-search}
@@
 
-%	Let $\Omega_C$ be the collection of connected digital sets in $\Omega$.
-Given a digital shape $S$, we wish to evolve it into a shape $S^\star$ similar to $S$ but with lower digital elastica energy.
-We recall the digital curvature estimator definition
-%	
-%\begin{align}
-%	\hat{\kappa}^2(y) &= c_1\Big( c_2 - | B_r(y) \cap S | \Big)^2, 
-%	\label{eq:curvature-estimator-pixels}
-%\end{align}
-%
-%where $c_1=3/r^6$ and $c_2=\pi r^2/2$. Let $X,Y$ be the set of pixels and linels, respectively, in $\Omega$. We define the following binary model
-%		
-%\begin{align}
-%\text{Minimize}_{x,y} & \sum_{y}{c_1y \Big(c_2 - \sum_{x_j \in B_r(y)}{x_j}\Big)^2	 } + F(S,X_{=1} \cup Y_{=1}) \nonumber \\
-%\text{subject to} & \nonumber \\
-%& (X_{=1} \cup Y_{=1}) \in \Omega_C, \; x,y \in \{0,1\}^\Omega
-%\label{eq:general-binary-formulation}
-%\end{align}
-%
-%
-%where $F$ is some measure of similarity, e.g. distance, between initial shape $S$ and candidate solution. Such term is needed, otherwise the uninteresting empty set would be the optimal solution.
-%
-%Formulation \eqref{eq:general-binary-formulation} is of order four, binary and non-convex.
-These properties make it a hard optimization problem.
-We are going to explore an alternative energy, which is a simplification of the former.
-
-%\subsection{A first model}
-%
-%We note that the elastica can be decreased by attenuating non-flat regions.
-The idea is to evolve a flow $S^{(i)}$ where $S^{(i+1)}$ is derived from the minimization of the sum of the squared curvature at $S^{(i)}$.
-We exchange solving a fourth order energy to solve multiple second order problems.
-We still have to guarantee that solutions are connected.
-We handle this issue by limiting the optimization region to a subset of $\Omega$, namely the inner pixel boundary of  $S^{(i)}$.
-
 \revision{
@@
 \revision{We observe that the integral invariant estimator \eqref{eq:curvature_approximation} is originally designed to be evaluated on the digital boundary of the shape, which is the unknown of our problem.
-Injecting contour information leads to a third order model, which we prefer to avoid.
-Instead, we are going to exploit the II estimator definition in order to compute a flow that evolves proportionally to the squared curvature of the current shape.}
+Injecting contour information leads to a third-order model, which we prefer to avoid.
+Instead, we are going to exploit the II estimator definition to compute a flow that evolves proportionally to the squared curvature of the current shape.}
 
@@
 \revision{We assume an ordering in $\Omega$, i.e., there exists a bijective function $\omega : \Omega \rightarrow \{1 \cdots |\Omega| \}$.
-Moreover, we associate to every pixel in $\Omega$ a binary variable grouped in the set $X(\Omega)$}
-
-\begin{align*}
-	\revision{X(\Omega) := \left\{ x_{\omega(p)} \in \{0,1\} \; | \; p \in \Omega \right\}.}
-\end{align*}
-
-\revision{We extend the definition for every subset $P \in \Omega$, i.e.,}
+Moreover, we associate to any subset $P \subset \Omega$ the set of binary variables $X(P)$ defined as}
 
@@
 
-%%\jaco{Motivation in digital geometry of why it makes sense to compute things farther.}
-
 \begin{figure}[!h]
@@
 {In our experiments, the best results are obtained by executing DCE algorithm with $m$ equal to $r$, where $r$ is
-  the estimation ball radius (see figure \ref{fig:mx-square-flow}). We observe that Elastica may increase after some
+  the estimation ball radius (see figure \ref{fig:mx-square-flow}). We observe that digital elastica may increase after some
   iterations if chosen radius is too large, as in the case of the triangle in figure \ref{fig:mx-flow-gs-radius-effect}
@@
 		}\\
-		\subfloat[\revision{Elastica evaluation}]{%
+		\subfloat[\revision{Digital elastica evaluation}]{%
 		\includegraphics[scale=0.5]{images/flow/elastica-energy-plot/square-flower-triangle.eps}						
@@
 In figure (b), for $r=5$, the triangle evolves to a single point, while the others stop  in an intermediate shape, as in (a).
-In figure (c), we observe that for a given choice of radius, the elastica may increase after a certain number of iterations.
+In figure (c), we observe that for a given choice of radius, the digital elastica may increase after a certain number of iterations.
 }
@@
 interest. Given foreground and background seeds selected by the user, we derive mixed Gaussian distributions of color
-intensities $G_f$ and $G_b$, and we define the data fidelity term as the cross-entropy, i.e.
+intensities $G_f$,$G_b$, and we define the data fidelity term as the cross-entropy, i.e.
 
@@
 We have studied in depth several digital curve evolution models based on a digital version of the Elastica energy and we
-have presented an application to image segmentation. The processes we have described are completely digital, and do not
-suffer from issues that typically arise in models that passes through a discretization stage, such as
+have presented an application to image segmentation. The processes we have described are completely digital and do not
+suffer from issues that typically arise in models that pass through a discretization stage, such as
 rounding. Moreover, the model can handle changes in topology and its results are competitive with similar approaches
@@
 \end{document}
-
-%% for reference
-
-%% In this work, we investigate the use of a more suitable curvature
-%% estimator with multigrid convergent property and its application as a
-%% boundary regularizer in a digital flow minimizing its squared
-%% curvature. Our method decreases the elastica energy of the contour and
-%% its evolution is evaluated on several digital flows.
-
-%% Finally, we
-%% present an application of the model as a post-processing step in a
-%% segmentation framework. The code is freely available on
-%% github\footnote{https://www.github.com/danoan/BTools}.
-
-%\begin{itemize}
-%% \item{Geometric properties and regularization}
-%% \item{The role of curvature}
-
-%  Quote \cite{schoenemann2011elastic} for the interest of using curvature energy when segmenting regions in gradient-based data fitting term.
-It can look for global optimum within a graph representation of the image.
-Main problem of their approach is the computational complexity as well as rather coarse approximations of curvature.
-(Be more precise here).
-
-%%\item{\textbf{Classical work on elastica and Wilmore flow in imaging}}
-  %%\begin{itemize}
-  %% \item{Level lines based disocclusion \cite{masnou98inpainting} }	%% DONE
- %%  \item{Filling-In by Joint Interpolation of Vector Fields and Gray Levels \cite{ballester01filljoint} } %% DONE
- %%  \item{Eulers Elastica and Curvature Based Inpaintings \cite{chan02elasticainpainting} } %% DONE
- %% \item{Discrete willmore flow \cite{bobenko2005discrete}}
- %%  \item{Introducing Willmore flow into level set segmentation of spinal vertebrae \cite{lim2012introducing}}	 %%% DONE
- %% \end{itemize}
-
-%%\item{\textbf{Level-sets}}
- %% \begin{itemize}
-  %% \item{Image processing via level set curvature flow \cite{malladi1995image} } %% DONE
-  %% \item{Shape Modeling with Front Propagation: A Level Set Approach \cite{malladi1995shape} }	%% DONE
-%%	\end{itemize}
-
-%%\item{\textbf{Convex relaxation}}
-%%  \begin{itemize}
-%%  \item{A convex lower semicontinuous approximation of Eulers elastica energy \cite{bredies15convex}}
- %% \item{Introducing Total Curvature for Image Processing \cite{goldluecke11totalcurvature}}
- %% \end{itemize}
-
-%\item{\textbf{Constraint optimization}}
- % \begin{itemize}
-  %% \item{Curvature regularity for region-based image segmentation and inpainting: A linear programming relaxation \cite{schoenemann09linear} }	
-  %% \item{A Fast Algorithm for Euler's Elastica Model Using Augmented Lagrangian Method \cite{tai11elastica} }		
-  %%\item{The elastic ratio: Introducing curvature into ratio-based image segmentation \cite{schoenemann2011elastic}
-  %%}		%% DONE
- % \end{itemize}
-
-%%\item{\textbf{Discrete approaches}}
-%%  \begin{itemize}
-  %% \item{Fast global optimization of curvature \cite{zehiry10fast}	} %% DONE
-  %%\item{Efficient Squared Curvature \cite{nieuwenhuis14efficient} 	}
-  %%\item{Contrast driven {E}lastica for image segmentation \cite{el2016contrast} }
-  %%\item{Curvature Regularization for Curves and Surfaces in a Global Optimization Framework \cite{strandmark11globalframework} }
-
- % \end{itemize}
-
-%%\end{itemize}

### 2019-12-18 jmiv.tex
h=0.25 figures; dashed lines in plots

@@
 computationally too costly in these methods.
-\revision{Moreover, parametric approaches to Elastica  as snakes and splines depend on the choice of anchor points and  multigrid convergence hasn't been proven for them.}
+\revision{Moreover, parametric approaches to Elastica  as snakes and splines are way to sensitive to the choice of anchor points and  multigrid convergence hasn't been proven for them.}
 
@@
 	\center
-	\subfloat[h=1.0\label{}]{%
-	\includegraphics[scale=0.125]{images/local_search/square/h1/summary.eps}
-	}%
-	\hspace{10pt}
-	\subfloat[h=0.5\label{}]{%
-	\includegraphics[scale=0.125]{images/local_search/square/h05/summary.eps}
-	}%
-	\hspace{10pt}
-	\subfloat[h=1.0\label{}]{%
-	\includegraphics[scale=0.125]{images/local_search/flower/h1/summary.eps}
-	}%
-	\hspace{10pt}
-	\subfloat[h=0.5\label{}]{%
-	\includegraphics[scale=0.125]{images/local_search/flower/h05/summary.eps}
-	}%
-		\caption{\revision{Local combinatorial optimization process results using II estimator with radius $7$ for the square and flower shapes.
-Shapes displayed at every $2$ iterations for the square and $5$ iterations for the flower.}}
+	\begin{tabular}{ccc}
+		$h=1.0$ & $h=0.5$ & $h=0.25$\\
+		\includegraphics[scale=0.2]{images/local_search/square/h1/summary.eps} & \includegraphics[scale=0.2]{images/local_search/square/h05/summary.eps} & \includegraphics[scale=0.2]{images/local_search/square/h025/summary.eps} \\
+		\includegraphics[scale=0.2]{images/local_search/flower/h1/summary.eps} & \includegraphics[scale=0.2]{images/local_search/flower/h05/summary.eps} & \includegraphics[scale=0.2]{images/local_search/flower/h025/summary.eps}
+	\end{tabular}	
+		\caption{\revision{Local combinatorial optimization process results using II estimator with radius $5$ for the square and flower shapes. Shapes are displayed at every $5$ iterations.}}	
 		\label{fig:local-comb-square-results}		
@@
 experiments in this paper were executed on a \revision{$32$-core $2.4Ghz$ CPU and the number of pixels in the square and
-flower shapes are respectively $841,1867$ for grid step $h=1.0$}. Although its use in practical applications is
+flower shapes are respectively $841,1641$ for grid step $h=1.0$}. Although its use in practical applications is
 limited, we demonstrate that digital estimators are effective in their measurements and the flows evolve as expected.
@@
 
-\begin{figure}[!h]
-\begin{minipage}[b]{0.5\textwidth}
-\center
-\includegraphics[scale=0.35]{images/local_search/square-flower.eps}
-\caption{Digital elastica computation along iterations of algorithm \ref{alg:local-search}. \revision{The final shape has energy value closer to the optimal value $2\pi/5$ (dashed line)}.}
-\label{fig:plot-elastica-local-search}
-\end{minipage}\hspace{40pt}%
-\begin{minipage}[b]{0.45\textwidth}
+\begin{figure}
+	\center
+	\captionsetup{type=table}	
 	\revision{
-\center
-\captionsetup{type=table}
-\begin{tabular}{|l|c|c|}
+	\begin{tabular}{|c|c|c|}
 	\hline
-& $h=1.0$ & $h=0.5$\\
+	& Square & Flower \\
 	\hline
-Square & 4s (0.4s/it) & 77s (3s/it)\\
+	$h=1.0$ & 4s & 124s \\
 	\hline
-Flower & 252s (4s/it)  & 3246s (42s/it)\\
+	$h=0.5$ & 77s & 1924s\\
+	\hline
+	$h=0.25$ & 1886s & 28445s\\
 	\hline
@@
 	}
-\caption{Running times for the local combinatorial optimization algorithm with $\revision{ 0 \leq n \leq 50}$. Thirty two threads were used.}
+	\caption{Running times for the local combinatorial optimization algorithm with $0 \leq n \leq 50$. Thirty two threads were used.}
 	\label{tab:summary-local-comb-rtime}
-\end{minipage}
+\end{figure}
+
+\begin{figure}[!h]
+\center
+\subfloat[\label{}]{\includegraphics[scale=0.6]{images/local_search/square.eps}}
+\subfloat[\label{}]{\includegraphics[scale=0.6]{images/local_search/flower.eps}}
+\caption{Digital elastica computation along iterations of algorithm \ref{alg:local-search}.
+\revision{The final shape has energy value closer to the optimal value $2\pi/5$ (thin horizontal dashed line)}.}
+\label{fig:plot-elastica-local-search}
 \end{figure}
@@
 
-\begin{algorithm}[H]
+\begin{algorithm}
  \SetKwData{It}{i}
@@
 		}\\
-		\subfloat[\revision{Digital elastica evaluation}]{%
+		\subfloat[\revision{Digital elastica evaluation ($r=5,h=0.5$)}]{%
 		\includegraphics[scale=0.5]{images/flow/elastica-energy-plot/square-flower-triangle.eps}						
@@
 
-\begin{figure}[h!]
+\begin{figure}
 \center

### 2019-12-18 jmiv.tex
Notation adjusts

@@
 In other words, each flow iteration decides which pixels in the inner boundary are to be removed from \revision{$S^{(i)}$} and which are to be kept in \revision{$S^{(i)}$}.
-We recall the definition of our digital curvature estimator:
+We recall the definition of the II digital curvature estimator:
 \begin{align}
@@
 \begin{align*}
-	F_r^{(i)}(p) &:= \big( S^{(i)} \setminus I^{(i)} \big) \cap B_r(p)\\
+	F^{(i)} &:= S^{(i)} \setminus I^{(i)} \\
+	F_r^{(i)}(p) &:= F^{(i)} \cap B_r(p)\\
 	I_r^{(i)}(p) &:= I^{(i)} \cap B_r(p) \\
@@
 algorithm. The length penalization is defined as
+\revision{
 \begin{align}
-  s(x)=\sum_{x_j \in \mathcal{N}_4(x)}{ t(x_j) }, \quad \text{where } t(x_j) = \left\{\begin{array}{ll}
-  (x-x_j)^2, & \text{if } x_j \in X_{r}^{(i)}\\
-  (x-0), & \text{if } x_j \in F_{r}^{(i)}\\
-  (x-1), & \text{otherwise }
+  s(x_{w(p)})=\sum_{q \in \mathcal{N}_4(p)}{ t(q) }, \quad \text{where } t(q) = \left\{\begin{array}{ll}
+  (x_{w(p)}-x_{w(q)})^2, & \text{if } q \in I^{(i)}\\
+  (x_{w(p)}-0), & \text{if } q \in F^{(i)}\\
+  (x_{w(p)}-1), & \text{otherwise }
   \end{array}\right.
   \label{eq:length-penalization}
-\end{align}
+\end{align}}
 
@@
 \begin{align}
-  g(y) = -(1-y)\log{G_f(I(y))} - y\log{G_b(I(y))}.
+  g(\revision{x_{w(p)}}) = -(1-\revision{x_{w(p)}})\log{G_f(p)} - \revision{x_{w(p)}}\log{G_b(p)}.
   \label{eq:data-fidelity}

### 2019-12-18 answer-to-reviewers/answer-to-reviewers.tex
Update answer to reviewers

@@
 In section 5, we compare our segmentation model with the work of \cite{schoenemann09linear} which uses a discretization of curvature proposed in \cite{bruckstein96} which $\Gamma$-convergence is proved in \cite{bruckstein01}.
-We remark that our approach never leaves the digital domain, in other words, is purely digital and it doesn't rely in any curve representation.
-The notions of multigrid convergence and $\Gamma$-convergence are not easily comparable, as the former is especially designed for digital data.
-In this sense, multigrid convergence is more appropriated in our case as our main object of interest are digital images.
+We remark that our approach never leaves the digital domain, in other words, it's purely digital and it doesn't rely on any curve representation.
+The notions of multigrid convergence and $\Gamma$-convergence are not easily comparable.
+The former is specially designed for digital data, hence more appropriated in our case as our main object is a digital image.
 ~\\

### 2019-12-18 jmiv.tex
Mispelling

@@
 computationally too costly in these methods.
-\revision{Moreover, parametric approaches to Elastica  as snakes and splines are way to sensitive to the choice of anchor points and  multigrid convergence hasn't been proven for them.}
+\revision{Moreover, parametric approaches to Elastica  as snakes and splines are too sensitive to the choice of anchor points and multigrid convergence hasn't been proven for them.}
 

### 2019-12-18 answer-to-reviewers/answer-to-reviewers.tex
Update answer to reviewer #1

@@
 
-~\\
-In section 5, we compare our segmentation model with the work of \cite{schoenemann09linear} which uses a discretization of curvature proposed in \cite{bruckstein96} which $\Gamma$-convergence is proved in \cite{bruckstein01}.
-We remark that our approach never leaves the digital domain, in other words, it's purely digital and it doesn't rely on any curve representation.
-The notions of multigrid convergence and $\Gamma$-convergence are not easily comparable.
-The former is specially designed for digital data, hence more appropriated in our case as our main object is a digital image.
-~\\
+~\\ In section 5, we indeed compare our segmentation model with the
+work of \cite{schoenemann09linear}, which uses a polygonal
+approximation of discrete elastica. In this work, the curvature is
+estimated with a simple formula involving angle and edge lengths at
+polygon vertices as proposed in \cite{bruckstein96}. This discrete
+elastica problem with fixed end-points is proven to be
+$\Gamma$-convergent toward the continuous elastica problem in
+\cite{bruckstein01}. However it is not straightforward to include
+image date term in these work, since the optimization variables of the
+polygonal approximation are not related to the digital domain. For
+instance, one could also use splines approximation with exact
+curvature information and the same kind of approach would have the
+same pros and cons.
+
+We remark that our approach never leaves the digital domain. In other
+words, it is purely digital and it does not rely on any curve
+representation. With this approach, all the optimization variables are
+related to the digital domain, and we can thus optimize in the same
+process data terms and elastica terms. Hence there is no alternate
+minimization involved.
+
+Finally, the notions of multigrid convergence and $\Gamma$-convergence
+are not easily comparable. The former concerns the accuracy of an
+estimation, the latter concerns a sequence of minimizers. The former
+is specifically designed for digital data, hence more appropriated in
+our case as our main objects of interest are digital images.  ~\\
 

### 2019-12-19 jmiv.tex
Improve plots visibility

@@
 \center
-\subfloat[\label{}]{\includegraphics[scale=0.6]{images/local_search/square.eps}}
-\subfloat[\label{}]{\includegraphics[scale=0.6]{images/local_search/flower.eps}}
+\subfloat[\label{}]{\includegraphics[scale=0.32]{images/local_search/square.eps}}
+\subfloat[\label{}]{\includegraphics[scale=0.32]{images/local_search/flower.eps}}
 \caption{Digital elastica computation along iterations of algorithm \ref{alg:local-search}.
-\revision{The final shape has energy value closer to the optimal value $2\pi/5$ (thin horizontal dashed line)}.}
+\revision{The final shape has energy value close to the optimal value $2\pi/5$ (thin horizontal dashed line)}.}
 \label{fig:plot-elastica-local-search}

### 2019-12-20 answer-to-reviewers/answer-to-reviewers.tex
Intro parametric approaches

@@
 \cite{bruckstein01}. However it is not straightforward to include
-image date term in these work, since the optimization variables of the
+image data term in this work, since the optimization variables of the
 polygonal approximation are not related to the digital domain. For

### 2019-12-20 jmiv.tex
Intro parametric approaches

@@
 coarse curvature estimations for which the approximation error is
-often unknown. Improving the quality of the curvature estimator has an
-important impact on the accuracy of the results, but is
-computationally too costly in these methods.
-\revision{Moreover, parametric approaches to Elastica  as snakes and splines are too sensitive to the choice of anchor points and multigrid convergence hasn't been proven for them.}
+often unknown.
+\revision{In the segmentation method of \cite{schoenemann09linear}, for example, the curvature is estimated by a simple formula involving angles and edge lengths at polygon vertices.
+The quality of the estimation is higly influenced by the number of vertices and where they are located along the curve.
+More important, in this estimator, the curve representation lies in the continuous domain and the properties of such estimator are not immediately valid when the curve is translated to the digital domain.
+In particular, it is not straightforward to include a image data term in this model without adding extra assumptions about the curve representation.
+One could use a spline approximation with exact curvature information and the same kind of approach would have the same pros and cons.} Improving the quality of the curvature estimator has an important impact on the accuracy of the results, \revision{but we should use the appropriate tools to evaluate its quality.
+In the context of measurements in digital data, this tool is multigrid convergence.}
+
+%Improving the quality of the curvature estimator has an
+%important impact on the accuracy of the results, but is
+%computationally too costly in these methods.
+
+%\revision{Moreover, parametric approaches to Elastica  as snakes and splines are too sensitive to the choice of anchor points and multigrid convergence hasn't been proven for them.}
 

### 2019-12-21 jmiv.tex
Fix n-neighborhood definition

@@
 \revision{
-	Given a digital shape $S \in \Omega$, its $n$-neighborhood $\mathcal{N}_n(S)$ is defined as the set of digital shapes that can be built from $S$ by adding or removing a sequence of $n$ connected pixels in $R_1(S)$.
+	Given a digital shape $S \in \Omega$, its $n$-neighborhood $\mathcal{N}_n(S)$ is defined as the set of digital shapes that can be built from $S$ by adding or removing a sequence of $k \in [0,n]$ connected pixels in $R_1(S)$.
 }
@@
 
-Algorithm~\ref{alg:local-search} describes the local combinatorial process and Figure~\ref{fig:local-comb-square-results} presents the digital curve evolution when executing this algorithm for two different shapes with \revision{$0 \leq n \leq 50$}.
+Algorithm~\ref{alg:local-search} describes the local combinatorial process and Figure~\ref{fig:local-comb-square-results} presents the digital curve evolution when executing this algorithm for two different shapes with \revision{$n=50$}.
 
@@
 	}
-	\caption{Running times for the local combinatorial optimization algorithm with $0 \leq n \leq 50$. Thirty two threads were used.}
+	\caption{Running times for the local combinatorial optimization algorithm with $n=50$. Thirty two threads were used.}
 	\label{tab:summary-local-comb-rtime}

### 2020-01-06 jmiv.tex
no useful change

--- 2019-12-19 jmiv.tex
@@
 %
-%\documentclass[runningheads]{llncs}
-\documentclass[smallextended]{svjour3}       % onecolumn (second format)
+\documentclass[runningheads]{llncs}
 %
@@
 \usepackage[export]{adjustbox}
-\usepackage{array}
-\usepackage[dvipsnames]{xcolor}
+\usepackage{xcolor}
 
@@
 \newcommand{\HT}[1]{{\textcolor{violet}{#1}}}
-\newcommand{\daniel}[1]{\textcolor{NavyBlue}{#1}}
-\newcommand{\revision}[1]{\textcolor{red}{#1}}
 
@@
 %
-\title{An Elastica-driven Digital Curve Evolution Model for Image Segmentation\thanks{This  work has  been  partially  funded by CoMeDiC ANR-15-CE40-0006 research grant.}}
+\title{A\HT{n Elastica-driven} Digital Curve Evolution Model for Image Segmentation\thanks{This  work has  been  partially  funded by CoMeDiC ANR-15-CE40-0006 research grant.}}
   \titlerunning{Digital Curve Evolution by Elastica Energy}
@@
 
-\author{Daniel Antunes%\inst{1}
-\and Jacques-Olivier Lachaud%\inst{1}
-\and Hugues Talbot%\inst{2}
-}
+\author{Daniel Antunes\inst{1}
+Jacques-Olivier Lachaud\inst{1}
+Hugues Talbot\inst{2}}
 %
@@
 %
-\institute{%Universit{\'e} Savoie Mont Blanc, LAMA, UMR CNRS 5127, F-73376, France
-  Daniel Antunes \at
-  Univ. Grenoble Alpes, Univ. Savoie Mont Blanc, CNRS, LAMA, 73000 Chambéry, France \\
-  \email{daniel.martins-antunes@univ-smb.fr} \and
-  Jacques-Olivier~Lachaud \at  Univ. Grenoble Alpes, Univ. Savoie Mont Blanc, CNRS, LAMA, 73000 Chambéry, France \\
-  \email{jacques-olivier.lachaud@univ-smb.fr} \and
-  Hugues Talbot \at CentraleSupelec, Inria, Universit\'e Paris-Saclay, 9 rue Joliot-Curie, F-91190 Gif-sur-Yvette \\
+\institute{Universit{\'e} Savoie Mont Blanc, LAMA, UMR CNRS 5127, F-73376, France
+\email{daniel.martins-antunes, jacques-olivier.lachaud@univ-savoie.fr} \and
+CentraleSupelec Inria \'equipe OPIS, Universit\'e Paris-Saclay, 9 rue Joliot-Curie, F-91190 Gif-sur-Yvette \\
 \email{hugues.talbot@centralesupelec.fr}}
@@
 \begin{abstract}
-  Geometric priors have been shown to be useful in image segmentation to regularize results. For example, the classical
-    Mumford-Shah functional uses region perimeter as prior. This has inspired much research in the last few decades,
+  \HT{Geometric priors have been shown to be useful in image segmentation to regularize results. For example, the classical
+    Mumford-Shah functional uses regions perimeter as prior. This has inspired much research in the last few decades,
     with classical approaches like the Rudin-Osher-Fatemi and most graph-cut formulations, which all use a weighted or
@@
     underlying optimisation processes are not convex. In this article, we propose to formulate a digital flow that
-    approximates an Elastica-related flow using a multigrid-convergent curvature estimator, within a discrete
-    variational framework. We also present an application of this model as a post-processing step to a segmentation
-    framework.
+    approximates a curvature-related flow using a multigrid-convergent curvature estimator, within a discrete
+    variational framework. We also present an application of this model as a post-processing step in a segmentation
+    framework.}
 \keywords{Multigrid convergence  \and Digital estimator \and Curvature \and Shape Optimization \and Image Segmentation.}
@@
 low-level image analysis, especially when little prior information is
-known about the shape of interest. Length penalization is a
-well-behaved, general\revision{-}purpose regularizer and many models in the
-literature make use of it, from active contours
-\cite{caseles97geodesic} to level-set formulations
-\cite{malladi1995image,malladi1995shape}. Discrete graph-based
-variational models have been particularly succes\revision{s}ful to incorporate
-length penalization as a penalizer while keeping the ability to
-extract a global optimum \cite{boykov01graphcut,appleton05geodesic}.
-
-However, length regularization shows limitations when segmenting small
-or thin and elongated objects, as it tends to shrink solutions or
-yields disconnected solutions. Such drawbacks can be problematic in
-image segmentation, image restoration or image inpainting. It is thus
-rather natural to consider curvature (especially squared curvature) as
-a potential regularizer. Energies involving both length and squared
-curvature are often called the {\em Elastica} model (that dates back
-to Euler). The {\em Willmore energy} is its $n$-dimensional
-extension. These were brought to attention in computer vision by
-Mumford \cite{mumford1994elastica}. A similar concept is also present
-in the second-order regularizer of the original snake model
-\cite{kass1988snakes}. Indeed, an explicit curvature term was often
-employed in early level-set methods,
-like~\cite{malladi1995image,malladi1995shape,ballester01filljoint} for
-segmentation or inpainting. However, \revision{Caselles} {\em et al.}
-in~\cite{caseles97geodesic} observed that these terms as employed
-were not geometric, in the sense that they depend on the
-discretization parameters.
-
-\subsection{Existing works}
-The use of curvature for surface regularization in the case of the
-Willmore energy was studied in~\cite{bobenko2005discrete}. Although
-results look promising, \revision{the} authors used an inexact linearized version of
-the square curvature at every step.
-
-One of the first successful uses of curvature in
-image processing is the inpainting algorithm described in
-\cite{masnou98inpainting}, where authors evaluate the absolute
-curvature along the level lines of a simply-connected image to
-reconstruct its occluded parts. The non-intersection property of level
-lines induces the construction of an efficient dynamic programming
-algorithm. The curvature energy is nevertheless only coarsely
-approximated. We may quote \cite{chan02elasticainpainting} as another
-geometric inpainting method involving Elastica, which is optimized with
-level-sets.
-
-In image segmentation, Zehiry and Grady have shown that injecting
-curvature as a regularizer can help recover thin and elongated objects
-\cite{zehiry10fast}. Similarly, Schoenemann {\em et al.}
-\cite{schoenemann09linear} have considered the Elastica energy in
-their ratio-based image segmentation
-approach. In~\cite{schoenemann2011elastic}, Schoenemann~{\em et al.}
-extend ratio-cut approaches to segmentation with a curvature
-term. Their global optimization framework shows the considerable
-advantages of using such regularizer in common binary image
-segmentation tasks.  However, the time complexity of their algorithm
-is prohibitive, even if curvature is again coarsely
-approximated.  In a more recent work, Lim {\em et al.} propose an
-edge-weighted Willmore-like flow to segment
-vertebra~\cite{lim2012introducing} using a level-set
-formulation. They observe improved results compared
-to~\cite{caseles97geodesic} and other perimeter-based priors, but
-observe that a shape prior and a close-enough initialization must also be
-provided to achieve good results.
-
-In fact, it is still a very challenging task to efficiently handle
-curvature in the context of image segmentation.  State-of-art methods
-are in practice difficult to optimize and do not scale easily
+known about the shape of interest. Length penalization is a \HT{well-behaved,} general
+purpose regularizer and \HT{many} models \HT{in the literature} make use
+of it, from active contours \cite{casseles97geodesic} to level-set
+formulations \cite{malladi1995image,malladi1995shape}. Discrete
+graph-based variational models have been particularly succesfull to
+incorporate length penalization as a penalizer, while keeping the
+ability to extract \HT{a} global optimum
+\cite{boykov01graphcut,appleton05geodesic}.
+
+However length regularization shows limitations when segmenting
+small or thin and elongated objects, as it tends to shrink solutions
+or \HT{yields} disconnected solutions. Such drawbacks can be problematic in
+image segmentation or image inpainting. It is thus rather natural to
+consider curvature (especially squared curvature) \HT{as} a potential
+regularizer. Energies involving \HT{both length and} squared curvature are often called
+{\em Euler elastica} model (\HT{that} dates back to Euler) or {\em Willmore energy}
+($n$-dimensional extension) and have been brought back to attention in
+computer vision by Mumford \cite{mumford1994elastica}. A similar
+regularizer is also present in the second-order regularizer
+of the \HT{original} snake model \cite{kass1988snakes}. \HT{Similarly,
+an explicit curvature term was often employed in early level-set methods,
+like~\cite{malladi1995image,malladi1995shape,ballester01filljoint} for segmentation or inpainting,}
+\HT{However, Casselles {\em et al.} in~\cite{casseles97geodesic} observed that these
+terms were not geometric, in the sense that they depended on the discretization}.
+
+The use of curvature for surface regularization was studied in~\cite{bobenko2005discrete},
+although results look promising, authors used an inexact linearized version of the
+square curvature at every step.
+
+One of the first successful uses of \HT{geometric squared} curvature in image processing is the inpainting algorithm
+described in \cite{masnou98inpainting}\HT{, where authors} evaluate the elastica energy along the level lines of a
+simply-connected image to reconstruct its occluded parts. The non-intersection property of level lines \HT{induces} the
+construction of an efficient dynamic programming algorithm. \HT{However, } the curvature energy is \HT{only} coarsely
+approximated.  \cite{chan02elasticainpainting} \HT{is} another geometric inpainting method involving elastica
+\HT{optimized with level-sets}.
+
+In image segmentation, Zehiry and Grady have shown that injecting curvature as a regularizer \HT{can help} recover thin
+and elongated objects \cite{zehiry10fast}. Similarly Schoenemann {\em et al.}  \cite{schoenemann09linear} have
+considered the elastica energy in their ratio-based image segmentation approach. \HT{ In~\cite{schoenemann2011elastic},
+Schoenemann~{\em et al.} extend ratio-cut approaches to segmentation with a curvature term.} Their global optimization
+framework shows the considerable \HT{advantages} of using such regularizer in common binary image segmentation tasks.
+However the time complexity of their algorithm \HT{is prohibitive,} even if curvature is \HT{again} coarsely
+approximated.  \HT{In more recent work, Lim {\em et al.} propose an edge-weighted Willmore-like flow to segment
+vertebra~\cite{lim2012introducing} using a level-set formulation.  They observe improved results compared
+to~\cite{casseles97geodesic} and other perimeter-based priors, but observe that a shape prior and a close-enough
+solution must also be provided to achieve good results.}
+
+In fact, it is still a very challenging task to inject curvature in
+the context of image segmentation.  
+\HT{State-of-art methods are in practice} difficult to optimize and \HT{do not scale}
 \cite{zehiry10fast,schoenemann09linear,strandmark11globalframework,nieuwenhuis14efficient}. In
@@
 coarse curvature estimations for which the approximation error is
-often unknown. Improving the quality of the curvature estimator has an
+\HT{often} unknown. Improving the quality of the curvature estimator has an
 important impact on the accuracy of the results, but is
 computationally too costly in these methods.
-\revision{Moreover, parametric approaches to Elastica  as snakes and splines are too sensitive to the choice of anchor points and multigrid convergence hasn't been proven for them.}
-
-Segmentation methods using Elastica or Willmore energies can be
-formulated via the computation of the corresponding flow,
-i.e. following its gradient. Well-founded level-set methods involving
-Willmore energy \cite{droske2004level} have been used in medical image
-segmentation \cite{lim2012introducing}. Another level-set formulation
-similar to the Chan-Vese model was proposed in
-\cite{zhu2013image}. Willmore flow can also be carried out by
-phase-field models (see \cite{bretin2015phase}) but they are less
-suited to image segmentation since interfaces are blurred in such
-models. Threshold dynamics can also be considered for such energies
-\cite{esedoglu2008threshold} and has been proposed for image
-\revision{disocclusion} \cite{esedoglu2005threshold}. However, flow-based methods
-will always deliver a local minimum, which heavily depend on
-initialization for good results. A similar approach is to formulate
-the Elastica as a regularization in a variational framework and use
-operator splitting to optimize it. Tai {\em et
-  al.}~\cite{tai11elastica} and more recently Deng~{\em et
-  al.}~\cite{deng2019new} have proposed this approach, which is
-well-suited to inverse problem solving. The problem remains non-convex
-and the nature of the converged iterates is not studied, i.e. how
-close they are to a global optimum.
-
-In contrast, researchers have sought convex relaxation of curvature-related
-formulation. In~\cite{goldluecke11totalcurvature}, Goldluecke and Cremers introduce the {\em Total Curvature}, based
-on the Menger-Melnikov curvature of a measure. The formulation is non-convex but can be relaxed into a well-correlated
-but non-tight convex one.
-The relaxed formulation can be used to solve inverse problems including segmentation.
-However computing a solution is still expensive, requiring significant parallelisation efforts with a GPU to achieve
-  acceptable computing times. In~\cite{bredies15convex}, Bredies {\em et al.} study a convex approximation of the
-  Elastica energy, using a lifting scheme. Thanks to the lifting, it is not restricted to binary sets. It shows
-  promising results and can be used for image restoration in addition to inpainting and segmentation. The scheme is,
-  however, neither tight nor exact, and required 4 dimensions for a 2D approximation. In addition, it does not carry over
-to $nD$. It also remains computationally expensive.
-
-Discrete approaches have been used to tackle the Elastica
-difficulties. As noted before, \cite{schoenemann09linear} have
-linearized a mesh-based approach, which was expanded upon
-by~\cite{strandmark11globalframework}, while \cite{zehiry10fast} have
-used a binary solver for a non-submodular approach on a regular square
-grid of pixels, which was expanded
-in~\cite{el2016contrast}. In~\cite{nieuwenhuis14efficient}, a
-specific solver is developed to yield a better solution to an
-extension of the formulation in~\cite{zehiry10fast}.
-
-\subsection{Motivation}
-In spite of the multiplicity of existing approaches, it seems none is
-currently completely satisfactory. While the sought solution is
-expected to be very smooth based on geometrical expectations, the
-mathematical properties of the related operators make this smoothness
-elusive. Non-convexity and the presence of high-order terms make
-Elastica difficult to optimize and to approximate, let alone compute
-efficiently. The computed solutions in the literature are rarely
-evaluated, and the complexity of the proposed solution is often high.
-
-Consequently, we are interested in studying purely discrete
-variational segmentation models involving an Elastica
-energy. Recently, new estimators of curvature along digital contours
-have been proposed
-\cite{roussillon11mdca,coeurjolly13integral,schindele17mdca} with the
-desirable multigrid convergence property. This motivates us to propose
-models in which they can be used successfully.
-
-In this paper, we propose to investigate the use of the digital
-integral invariant curvature estimator \cite{coeurjolly13integral} in
-a discrete variational segmentation framework. More precisely, we show
-how to incorporate it in a digital flow minimizing its squared
+
+Segmentation methods using Elastica or Willmore energies \HT{generally
+reduce to} computing the corresponding flow, i.e. following its
+gradient. Well-founded level-set methods involving Willmore energy
+\cite{droske2004level} have been used in medical image segmentation
+\cite{lim2012introducing}. Another level-set formulation similar to
+the Chan-Vese model \HT{was} proposed in \cite{zhu2013image}. Willmore
+flow can also be carried out by phase-field models (see
+\cite{bretin2015phase}) but they are less suited to image segmentation
+since interfaces are blurred in such models. Threshold dynamics can
+also be considered for such energies \cite{esedoglu2008threshold} and
+has been proposed for image desocclusion \cite{esedoglu2005threshold}.
+
+In this paper we are interested in purely discrete variational segmentation models involving an elastica
+energy. Recently, new estimators of curvature along digital contours have been proposed
+\cite{roussillon11mdca,coeurjolly13integral,schindele17mdca} with the \HT{desirable} multigrid convergence property. This
+motivates us to \HT{propose} models in which they can be used successfully.
+
+\HT{In the remainder, we} investigate the use of the digital integral invariant
+curvature estimator \cite{coeurjolly13integral} in a discrete
+variational segmentation framework. More precisely, we show how to
+incorporate it in a digital flow minimizing its squared
 curvature. This model is expressible as a discrete combinatorial
 optimization model, which we solve using a classical variant of QPBO
-algorithm \cite{rother07qpbo}. Our solution does not compute a global
-solution to the whole domain but a global solution to a band
-surrounding a given shape. Our approach thus leads to a digital flow
-similar to continuous Elastica, as shown by our experiments. We
-present an application of this model as a post-processing step in a
-segmentation framework and demonstrate how it can improve standard
-results. This paper is an extended version of a previous work that
-appeared in \cite{antunes19}. We have included a deeper discussion on
-our optimization method and we present a more thorough comparison of
-our segmentation method with two other related works. Moreover, we
-have included a new local combinatorial optimization approach for
-Elastica minimization, which shows that our discrete model is
-well-founded. Finally, \revision{the code related to} this paper is freely
-available on GitHub.\footnote{https://www.github.com/danoan/BTools}
-
-\subsection{Outline}
-Section~2 reviews the concept of multigrid convergence and highlights
-its importance for the definition of digital estimators. We describe
-two convergent estimators used in this paper, one that approaches the
-length of elementary discrete contour elements, and the other that
-approaches the curvature of a discrete contour. They are used in the
-optimization model and in the definition of the digital
-Elastica. Section~3 describes a local combinatorial optimization model
-suitable for several curvature estimators, that presents interesting
-results but is too costly in practice. Section~4 describes the
-proposed Elastica-driven curvature evolution model along with several
-illustrations of digital flows. Section~5 explains how to use this
-evolution model as a post-processing step in an image segmentation
-framework and compares it to two related approaches. We conclude and
-draw some perspectives to this work in Section~6.
-
-\section{Multigrid convergent estimators}
-Our objective is to delineate shapes within digital images with some priors related to continuous geometry. The goal of
-this section is to introduce the concept of multigrid convergence and its potential when analyzing digital images with
-variational models involving geometric quantities, with the constraint that only digitized shapes are observed.
+algorithm \cite{rother07qpbo}. \HT{Our solution does not} compute a global
+solution to the whole domain, but our approach leads to a digital flow
+similar to continuous \HT{Elastica}, as shown by our experiments. We
+present an application of the model as a post-processing step in a
+segmentation framework, and demonstrate how it can improve standard
+results. The code is freely available on
+github\footnote{https://www.github.com/danoan/BTools}.
+
+%% In this work, we investigate the use of a more suitable curvature
+%% estimator with multigrid convergent property and its application as a
+%% boundary regularizer in a digital flow minimizing its squared
+%% curvature. Our method decreases the elastica energy of the contour and
+%% its evolution is evaluated on several digital flows.
+
+%% Finally, we
+%% present an application of the model as a post-processing step in a
+%% segmentation framework. The code is freely available on
+%% github\footnote{https://www.github.com/danoan/BTools}.
+
+\begin{itemize}
+\item{Geometric properties and regularization}
+\item{The role of curvature}
+
+%  Quote \cite{schoenemann2011elastic} for the interest of using curvature energy when segmenting regions in gradient-based data fitting term.
+It can look for global optimum within a graph representation of the image.
+Main problem of their approach is the computational complexity as well as rather coarse approximations of curvature.
+(Be more precise here).
+
+\item{What are the difficulties in use curvatue as a regularizer (point out convex relaxation approaches) and how a digital approach may help us }
+\item{Outline: We present two models that illustrate how digital estimators can be used to minimize the elastica energy on digital sets.  }
+\item{\todo{Add related works : geometric priors, binary segmentation, other digital curve evolution models}}
+\item{\todo{Talk about Willmore flow with phase field or with threshold dynamics}}
+
+%%\item{\textbf{Classical work on elastica and Wilmore flow in imaging}}
+  %%\begin{itemize}
+  %% \item{Level lines based disocclusion \cite{masnou98inpainting} }	%% DONE
+ %%  \item{Filling-In by Joint Interpolation of Vector Fields and Gray Levels \cite{ballester01filljoint} } %% DONE
+ %%  \item{Eulers Elastica and Curvature Based Inpaintings \cite{chan02elasticainpainting} } %% DONE
+ %% \item{Discrete willmore flow \cite{bobenko2005discrete}}
+ %%  \item{Introducing Willmore flow into level set segmentation of spinal vertebrae \cite{lim2012introducing}}	 %%% DONE
+ %% \end{itemize}
+
+%%\item{\textbf{Level-sets}}
+ %% \begin{itemize}
+  %% \item{Image processing via level set curvature flow \cite{malladi1995image} } %% DONE
+  %% \item{Shape Modeling with Front Propagation: A Level Set Approach \cite{malladi1995shape} }	%% DONE
+%%	\end{itemize}
+
+\item{\textbf{Convex relaxation}}
+  \begin{itemize}
+  \item{A convex lower semicontinuous approximation of Eulers elastica energy \cite{bredies15convex}}
+  \item{Introducing Total Curvature for Image Processing \cite{goldluecke11totalcurvature}}
+  \end{itemize}
+
+\item{\textbf{Constraint optimization}}
+  \begin{itemize}
+  \item{Curvature regularity for region-based image segmentation and inpainting: A linear programming relaxation \cite{schoenemann09linear} }	
+  \item{A Fast Algorithm for Euler's Elastica Model Using Augmented Lagrangian Method \cite{tai11elastica} }		
+  %%\item{The elastic ratio: Introducing curvature into ratio-based image segmentation \cite{schoenemann2011elastic}
+  %%}		%% DONE
+  \item{Curvature Regularization for Curves and Surfaces in a Global Optimization Framework \cite{strandmark11globalframework} }
+  \end{itemize}
+
+\item{\textbf{Discrete approaches}}
+  \begin{itemize}
+  \item{Fast global optimization of curvature \cite{zehiry10fast}	}
+  \item{Efficient Squared Curvature \cite{nieuwenhuis14efficient} 	}
+  \item{Contrast driven {E}lastica for image segmentation \cite{el2016contrast} }	
+  \end{itemize}
+
+\end{itemize}
+
+\textit{Outline}. Section two reviews the concept of multigrid
+convergence and highlights its importance for the definition of
+digital estimators. Next, we describe two convergent estimators used
+in this paper, one for tangent and the other for curvature. They are
+used in the optimization model and in the definition of the digital
+elastica. Section three describes a local combinatorial optimization model
+suitable for different curvature estimators. Section four describes the proposed 
+curvature evolution model along with several illustrations of digital flows. Section five
+explains how to use the evolution model as a post-processing step in
+an image segmentation framework.
+
+\section{Multigrid convergent estimators \todo{(Mostly copy/paste)}}
+
+The goal of this section is to  introduce the concept of multigrid convergenc and its potential when analyzing digital images with variational models involving geometric quantities.
+More precisely we wish to delineate shapes within digital images with some priors related to their unknown continuous geometry.
+Of course we only observe shape digitizations within images.
+%% \begin{itemize}
+%% 	\item{Why to use multigrid convergent estimators}
+%% 	\item{Multigrid convergence for local estimators}
+%% 	\item{Reference to examples of multigrid digital estimators(for curvature, length, tangent)}
+%% 	\item{Define the elastica energy estimator}
+%% 	\item{\test{(Jaco) see if two opposite II evaluations give convergent curvature}}
+%% \end{itemize}
+
+%% \hrulefill
 
@@
   and only if, for any $X \in \mathbb{X}$, there exists a grid step
-  $h_X>0$ such that the estimate $\hat{u}(D_h(X), \revision{p},h)$ is
-  defined for all $\revision{p} \in \partial_hX$ with $ 0 < h < h_X$, and
+  $h_X>0$ such that the estimate $\hat{u}(D_h(X),\hat{x},h)$ is
+  defined for all $\hat{x} \in \partial_hX$ with $ 0 < h < h_X$, and
   for any $x \in \partial X$,
   \begin{equation*}
-    \forall \revision{p} \in  \partial_hX \text{ with } \norm{ \revision{p} - x }_{\infty} \leq h, \norm{ \hat{u}(D_h(X),\revision{p},h) - u(X,x)} \leq \tau_{X}(h),			
+    \forall \hat{x} \in  \partial_hX \text{ with } \norm{ \hat{x} - x }_{\infty} \leq h, \norm{ \hat{u}(D_h(X),\hat{x},h) - u(X,x)} \leq \tau_{X}(h),			
   \end{equation*}
@@
 The literature presents several perimeter estimators that are multigrid convergent (see
-\cite{coeurjolly04comparative,coeurjolly12multigrid} for a review), but in order to define the digital Elastica we need a local estimation
+\cite{coeurjolly04comparative,coeurjolly12multigrid} for a review), but in order to define the digital elastica we need a local estimation
 of length and we wish that integration over these local length elements gives a multigrid convergent estimator for the
@@
 of some group on the elements of the domain.
-
+%% Jaco: trop général, et pas utilisé après
+%% Generally speaking, an invariant $\sigma$ is a real-valued function from some space $\Omega$ which value is unaffected by the action
+%% of some group $\mathfrak{G}$ on the elements of the domain
+%% \begin{align*}
+%%   x \in \Omega, g \in \mathfrak{G}, \sigma(x) = v \longleftrightarrow \sigma(g \cdot x ) = v.
+%% \end{align*}
 Perimeter and curvature are examples of invariants for shapes on
-$\mathbb{R}^2$ with respect to the Euclidean group of rigid
+$\mathbb{R}^2$ with respect to the euclidean group of rigid
 transformations. Definition of integral area invariant and its link
@@
 \begin{definition}	
-  Given a digital shape $D \subset (h \mathbb{Z})^2$,  the area \revision{estimator} $\widehat{\text{Area}}(D,h)$ is defined as	
+  Given a digital shape $D \subset (h \mathbb{Z})^2$,  the area estimatir $\widehat{Area}(D,h)$ is defined as	
   \begin{align}
-    \widehat{\text{Area}}(D,h) \coloneqq h^2\text{Card}\left( D \right).	
+    \widehat{Area}(D,h) \coloneqq h^2\text{Card}\left( D \right).	
     \label{eq:digital_estimator_area}
@@
   \begin{align*}
-    \hat{\kappa}_{r}(D,\revision{p},h) \coloneqq \frac{3}{r^3} \left( \frac{\pi r^2}{2} - \widehat{\text{Area}} \left( B_{r} ( \revision{p} ) \cap D, h \right) \right).
+    \hat{\kappa}_{r}(D,x,h) \coloneqq \frac{3}{r^3} \left( \frac{\pi r^2}{2} - \widehat{Area} \left( B_{r} ( x ) \cap D, h \right) \right).
     %% \hat{\kappa}_{r}(D,x,h) \coloneqq \frac{3}{r^3} \left( \frac{\pi r^2}{2} - \widehat{Area} \left( B_{r/h} ( \frac{1}{h} \cdot x ) \cap D, h \right) \right).
@@
 
-In the remaining of this article, we are considering the minimization of the Elastica energy. Given a Euclidean shape $X$ with smooth enough boundary, the Elastica is defined as
+In the remaining of this paper we are going to be interested in the minimization of the elastica energy. Given a Euclidean shape $X$ with smooth enough boundary, the elastica is defined as
 \begin{align}
@@
 
-The digital version of Elastica energy approaching the continuous Elastica energy is defined as follows (it uses multigrid convergent estimators):
+The digital version of elastica energy approaching the continuous elastica energy is defined as follows (it uses multigrid convergent estimators):
 \begin{align}
@@
 where $\dot{\vec{e}}$ denotes the center of the edge $\vec{e}$. In the
-expression above, we will substitute an arbitrary subset \revision{$S$} of
+expression above, we will substitute an arbitrary subset $Z$ of
 $\mathbb{Z}^2$ to $D_h(X)$ since the continuous shape $X$ is unknown.
-In the following, we omit the grid step $h$ to simplify expressions
+In the following we omit the grid step $h$ to simplify expressions
 (or, putting it differently, we assume that the shape of interest is
@@
 
-The objectives of this section is to show both the potential of minimizing a purely digital Elastica energy but also to underline the difficulties of using it in a global combinatorial optimization framework.
+The objectives of this section is to show both the potential of minimizing a purely digital elastica energy but also to underline the difficulties of using it in a global combinatorial optimization framework.
 
 Given a digital shape $S^{(0)}$ we describe a process that generates a
-sequence $S^{(i)}$ of shapes with non-increasing Elastica energy. The
+sequence $S^{(i)}$ of shapes with non-increasing elastica energy. The
 idea is to define a neighborhood of shapes $\mathcal{N}^{(i)}$ to the
@@
 \cite{roussillon11mdca}. As a matter of fact, our experiments have
-shown that either estimator induce similar results.
-
-\revision{Let $S$ be a $2$-dimensional digital shape embedded in a domain $\Omega \subset \mathbb{Z}^2$}.
-We adopt the cellular-grid model to represent $S$, i.e., pixels and its lower dimensional counterparts, linels and pointels, are part of $S$ \revision{(see figure \ref{fig:cellular-grid-model})}.
+shown that either estimators induce similar results.
+
+Let $S$ be a $2$-dimensional digital shape.
+We adopt the cellular-grid model to represent $S$, i.e., pixels and its lower dimensional counterparts, linels and pointels, are part of $S$.
 In particular, we denote by $\partial S$ the topological boundary of $S$, i.e., the connected sequence of linels such that for each linel we have one of its incident pixels in $S$ and the other not in $S$.
 
-\begin{figure}[h!]
+Let $d_{S}:\Omega \rightarrow \mathcal{R}$ be the Euclidean distance transformation with respect to shape $S$. The value $d_S(x)$ gives the Euclidean distance between $x$ and the closest pixel in $S$.
+
+\begin{definition}[m-Ring Set]
+Given a digital shape $S\in\Omega$, its distance transformation $d_S$ and natural numbers $m > 0$, the {\em $m$-ring set of $S$} is defined as
+\begin{align*}
+	\quad R_m(S) &:= R_m^-(S) \; \cup \; R_m^+(S) \\
+	&:= \left\{ x \in \Omega \; | \; m-1 < d_S(x) \leq m \right\} \; \cup \;  \left\{ x \in \Omega \; | \; 	m-1 < d_{\overline{S}}(x) \leq m \right\}.
+\end{align*}
+\end{definition}
+
+Consider the following set of neighbor candidates to $S$:
+\begin{align*}
+\mathcal{U}(S) = \{ D \; | D \subset R_1(S) \cup S \; \text{and} \; \text{$D$ is connected} \}.
+\end{align*}
+
+Such set can be extremely large and its complete exhaustion is prohibitively expensive.  Instead, we explore a subset of it with the help of $n$-glued curves.
+
+An oriented closed curve $C$ is a closed connected sequence of linels with a well-defined interior. A segment of $C$ is a connected subsequence $c \in C$ of its linels.
+
+\begin{figure}
 \center
 	\subfloat[\label{}]{%
-	\includegraphics[scale=2.0]{images/local_search/definitions/flower.png}
+	\includegraphics[scale=0.2]{images/local_search/definitions/model-regions-square.eps}
 	}\hspace{40pt}%
 	\subfloat[\label{}]{%
-	\includegraphics[scale=0.3]{images/local_search/definitions/cellular-grid-illustration.eps}
-	}
-	\caption{\revision{The flower shape in figure (a) and the cellular-grid model representation in (b) of the rectangle-bounded region.
-In figure (b), pixels are colored in gray, linels in green and pointels in blue.}}
-	\label{fig:cellular-grid-model}
-\end{figure}
-
-Let $d_{S}:\Omega \rightarrow \mathbb{R}$ be the \revision{signed} Euclidean distance transformation with respect to shape $S$.
-The value $d_S(p)$ gives the Euclidean distance between \revision{$p \notin S$ and the closest pixel in $S$.
-For points $p \in S$, $d_S(p)$ gives the distance between $p$ and the closest pixel not in $S$.}
-
-\begin{definition}[m-Ring Set]
-\revision{
-Given a digital shape $S\in\Omega$, its signed distance transformation $d_S$ and natural number $m \neq 0$, the {\em $m$-ring set of $S$} is defined as
-\begin{align*}
-	R_m(S) &:= L_m \cup L_{-m},
-\end{align*}
-where
-\begin{align*}
-	L_m(S) &:= \left\{ \quad \begin{array}{cc}
-		\left\{ p \in \Omega \; | \; m-1 < d_S(p) \leq m \right\} & , \quad m>0\\
-		\left\{ p \in \Omega \; | \; m+1 > d_S(p) \geq m \right\} & , \quad m<0
-		\end{array} \right.
-\end{align*}}
+	\includegraphics[scale=0.2]{images/local_search/definitions/glued-curve.eps}
+	}%	
+	\caption{The blue pixels in figure (a) illustrates a $2$-ring set, while the green pixels its inner-pixel boundary.
+In figure (b) we highlight an element of set $\mathcal{G}_{11}(C_1,C_2)$.
+The curve segments of $C_1$ and $C_2$ are colored in red and green, while the junction linels in blue.}
+\end{figure}
+
+\begin{definition}[Glued Curve]
+Given closed curves $C_1,C_2$ agreeing with some orientation $q$, a glued curve is a closed curve  $(c_1,\ell_1,c_2,\ell_2)$ with orientation $q$ and $c_1 \in C_1, c_2 \in C_2$.
+The linels $\ell_1,\ell_2$ are called junction linels.
 \end{definition}
 
-Consider the following set of neighbor candidates to $S$:
-\begin{align*}
-\mathcal{U}(S) = \{ D \; | D \subset R_1(S) \cup S \; \text{and} \; \text{$D$ is connected} \}.
-\end{align*}
-
-Such set can be extremely large and its complete exhaustion is prohibitively expensive.  Instead, we are going to use a subset of it.
-
-\begin{definition}[$n$-neighborhood]
-\revision{
-	Given a digital shape $S \in \Omega$, its $n$-neighborhood $\mathcal{N}_n(S)$ is defined as the set of digital shapes that can be built from $S$ by adding or removing a sequence of $n$ connected pixels in $R_1(S)$.
-}
+\begin{definition}[$n$-Glued Curve Set]
+Given closed curves $C_1,C_2$ with same orientation, its set of $n$-glued curves is defined as
+\begin{align*}
+	\mathcal{G}_n(C_1,C_2) = \{ (c_1,\ell_1,c_2,\ell_2) \; | \; |c_2|=n \},
+\end{align*}
 \end{definition}
 
-\begin{figure}[!h]
-\center
-	\subfloat[\label{}]{%
-	\includegraphics[scale=0.03]{images/local_search/definitions/R3.pdf}
-	}\hspace{40pt}%
-	\subfloat[\label{}]{%
-	\includegraphics[scale=0.22]{images/local_search/definitions/glued-curve.eps}
-	}%	
-	\caption{\revision{The blue pixels in figure (a) illustrates a $3$-ring set. In figure (b) we highlight the contour of an element of set $\mathcal{N}_{11}$.}}
-\end{figure}
-
-Algorithm~\ref{alg:local-search} describes the local combinatorial process and Figure~\ref{fig:local-comb-square-results} presents the digital curve evolution when executing this algorithm for two different shapes with \revision{$0 \leq n \leq 50$}.
+Let $S_O = ( S \cup R_1^+(S) ) $ and $S_I = ( S \setminus R_1^-(S) ) $, the neighborhood set to shape $S$ is defined as
+\begin{align*}
+	\mathcal{N}(S,N) = \bigcup_{1 \leq n \leq N} int \big( \mathcal{G}_{n}(\partial S_O, \partial S) \; \big) \cup int \big( \;  \; \mathcal{G}_{n}(\partial S, \partial S_I) \; \big),
+\end{align*}
+
+where $int(C)$ is the interior of the shape bounded by the close oriented curve $C$.
+Algorithm~\ref{alg:local-search} describes the local combinatorial process and Figure~\ref{fig:local-comb-square-results} presents the digital curve evolution when executing this algorithm for two different shapes with $N=20$.
 
@@
 
- \Input{A digital set $S$; the neighborhood parameter $n$; the maximum number of iterations \MIt; and a stop condition \Tol}
+ \Input{A digital set $S$; the maximum length of glued curves $N$; the maximum number of iterations \MIt; and a stop condition \Tol}
  \BlankLine
  \Delta $\longleftarrow$ \Tol+1\;
- $i \longleftarrow 0$\;
  \While{ \It $<$ \MIt \bf{and} \Delta $>$ \Tol  }{
-  	\For{$ X \in \mathcal{N}_n(S^{(i)}) $}
+  	\For{$ X \in \mathcal{N}(S^{(i)},N) $}
 	{
@@
  }
- \caption{Local combinatorial optimization for \revision{E}lastica minimization.}
  \label{alg:local-search} 
+ \caption{Local combinatorial optimization for elastica minimization.}
 \end{algorithm}
 
-\begin{figure}[!h]
-	\center
-	\begin{tabular}{ccc}
-		$h=1.0$ & $h=0.5$ & $h=0.25$\\
-		\includegraphics[scale=0.2]{images/local_search/square/h1/summary.eps} & \includegraphics[scale=0.2]{images/local_search/square/h05/summary.eps} & \includegraphics[scale=0.2]{images/local_search/square/h025/summary.eps} \\
-		\includegraphics[scale=0.2]{images/local_search/flower/h1/summary.eps} & \includegraphics[scale=0.2]{images/local_search/flower/h05/summary.eps} & \includegraphics[scale=0.2]{images/local_search/flower/h025/summary.eps}
-	\end{tabular}	
-		\caption{\revision{Local combinatorial optimization process results using II estimator with radius $5$ for the square and flower shapes. Shapes are displayed at every $5$ iterations.}}	
+\begin{figure}[!ht]
+\center
+	\subfloat[h=1.0\label{}]{%
+	\includegraphics[scale=0.125]{images/local_search/square/h1/summary-flow.eps}
+	}%
+	\hspace{10pt}
+	\subfloat[h=0.5\label{}]{%
+	\includegraphics[scale=0.125]{images/local_search/square/h05/summary-flow.eps}
+	}%
+	\hspace{10pt}
+	\subfloat[h=1.0\label{}]{%
+	\includegraphics[scale=0.125]{images/local_search/flower/h1/summary-flow.eps}
+	}%
+	\hspace{10pt}
+	\subfloat[h=0.5\label{}]{%
+	\includegraphics[scale=0.125]{images/local_search/flower/h05/summary-flow.eps}
+	}%
+		\caption{Local combinatorial optimization process results for the square and flower shapes. Shapes displayed at every $2$ iterations for the square and $7$ iterations for the flower.}	
 		\label{fig:local-comb-square-results}
@@
 
-The running time of algorithm \ref{alg:local-search} is summarized in table \ref{tab:summary-local-comb-rtime}. All the
-experiments in this paper were executed on a \revision{$32$-core $2.4Ghz$ CPU and the number of pixels in the square and
-flower shapes are respectively $841,1641$ for grid step $h=1.0$}. Although its use in practical applications is
-limited, we demonstrate that digital estimators are effective in their measurements and the flows evolve as expected.
-\revision{In particular, the digital elastica energy for the experiments in figure \ref{fig:local-comb-square-results} approaches the global optimum (figure  \ref{fig:plot-elastica-local-search})}.
-We
-observe that it is a complete digital approach, and we do not suffer from discretization and rounding problems, a common
-issue in continuous models.  Furthermore, we have checked that this approach works indifferently with Integral Invariant
-curvature estimator and Maximal Digital Circular Arc curvature estimator. So the convergence of the digital curvature
-estimator seems to be the cornerstone to get a digital curve behaving like a continuous Elastica.  In the next section,
-we explore a more efficient approach.
+The running time of algorithm \ref{alg:local-search} is summarized in
+table \ref{tab:summary-local-comb-rtime}.
+All the experiments in this paper were executed on a five core $3.4Ghz$ cpu and the number of pixels in the triangle, square and flower shapes are respectively $841,1867,521$ for grid step $h=1.0$.
+Although its use in practical applications is limited, we
+demonstrate that digital estimators are effective in their measurements
+and the flows evolve as expected. We observe that it is a
+complete digital approach, and we do not suffer from discretization
+and rounding problems, a common issue in continuous models.
+Furthermore we have checked that this approach works
+indifferently with Integral Invariant curvature estimator and
+Maximal Digital Circular Arc curvature estimator. So the convergence
+of the digital curvature estimator seems to be the cornerstone to
+get a digital curve behaving like a continuous elastica.  In the
+next section, we explore a more efficient approach.
 
 \begin{figure}
+\begin{minipage}[b]{0.5\textwidth}
+\center
+\includegraphics[scale=0.35]{images/local_search/square-flower.eps}
+\caption{Elastica computation along iterations of algorithm \ref{alg:local-search}}
+\label{fig:plot-elastica-local-search}
+\end{minipage}\hspace{40pt}%
+\begin{minipage}[b]{0.45\textwidth}
 \center
 \captionsetup{type=table}
-	\revision{
-	\begin{tabular}{|c|c|c|}
+\begin{tabular}{|l|c|c|}
 \hline
-	& Square & Flower \\
+& $h=1.0$ & $h=0.5$\\
 \hline
-	$h=1.0$ & 4s & 124s \\
+Square & 47s (5s/it) & 260s (12s/it)\\
 \hline
-	$h=0.5$ & 77s & 1924s\\
-	\hline
-	$h=0.25$ & 1886s & 28445s\\
+Flower & 1235s (23s/it)  & 8516s (52s/it)\\
 \hline
 \end{tabular}
-	}
-	\caption{Running times for the local combinatorial optimization algorithm with $0 \leq n \leq 50$. Thirty two threads were used.}
+\caption{Running times for the local combinatorial optimization algorithm with $k=1,N=20$. Four threads were used.}
 \label{tab:summary-local-comb-rtime}
-\end{figure}
-
-\begin{figure}[!h]
-\center
-\subfloat[\label{}]{\includegraphics[scale=0.32]{images/local_search/square.eps}}
-\subfloat[\label{}]{\includegraphics[scale=0.32]{images/local_search/flower.eps}}
-\caption{Digital elastica computation along iterations of algorithm \ref{alg:local-search}.
-\revision{The final shape has energy value close to the optimal value $2\pi/5$ (thin horizontal dashed line)}.}
-\label{fig:plot-elastica-local-search}
+\end{minipage}
 \end{figure}
@@
 
-\revision{
-Given a digital shape $S \subset \Omega \subset \mathbb{Z}^2$, the goal is to compute a flow $S^{(i)}$ where $S^{(i+1)}$ has lower digital elastica than $S^{(i)}$.}
-
-\revision{We observe that the integral invariant estimator \eqref{eq:curvature_approximation} is originally designed to be evaluated on the digital boundary of the shape, which is the unknown of our problem.
-Injecting contour information leads to a third-order model, which we prefer to avoid.
-Instead, we are going to exploit the II estimator definition to compute a flow that evolves proportionally to the squared curvature of the current shape.}
-
-\subsection{Discrete variational model for discrete curve evolution}
-
-\revision{We assume an ordering in $\Omega$, i.e., there exists a bijective function $\omega : \Omega \rightarrow \{1 \cdots |\Omega| \}$.
-Moreover, we associate to any subset $P \subset \Omega$ the set of binary variables $X(P)$ defined as}
-
-\begin{align*}
-	\revision{X(P) := \left\{ x_{\omega(p)} \in \{0,1\} \; | \; p \in P \right\}.}
-\end{align*}
-
+%	Let $\Omega_C$ be the collection of connected digital sets in $\Omega$.
+Given a digital shape $S$, we wish to evolve it into a shape $S^\star$ similar to $S$ but with lower digital elastica energy.
+We recall the digital curvature estimator definition
+%	
+%\begin{align}
+%	\hat{\kappa}^2(y) &= c_1\Big( c_2 - | B_r(y) \cap S | \Big)^2, 
+%	\label{eq:curvature-estimator-pixels}
+%\end{align}
+%
+%where $c_1=3/r^6$ and $c_2=\pi r^2/2$. Let $X,Y$ be the set of pixels and linels, respectively, in $\Omega$. We define the following binary model
+%		
+%\begin{align}
+%\text{Minimize}_{x,y} & \sum_{y}{c_1y \Big(c_2 - \sum_{x_j \in B_r(y)}{x_j}\Big)^2	 } + F(S,X_{=1} \cup Y_{=1}) \nonumber \\
+%\text{subject to} & \nonumber \\
+%& (X_{=1} \cup Y_{=1}) \in \Omega_C, \; x,y \in \{0,1\}^\Omega
+%\label{eq:general-binary-formulation}
+%\end{align}
+%
+%
+%where $F$ is some measure of similarity, e.g. distance, between initial shape $S$ and candidate solution. Such term is needed, otherwise the uninteresting empty set would be the optimal solution.
+%
+%Formulation \eqref{eq:general-binary-formulation} is of order four, binary and non-convex.
+These properties make it a hard optimization problem.
+We are going to explore an alternative energy, which is a simplification of the former.
+
+%\subsection{A first model}
+%
+%We note that the elastica can be decreased by attenuating non-flat regions.
+The idea is to evolve a flow $S^{(i)}$ where $S^{(i+1)}$ is derived from the minimization of the sum of the squared curvature at $S^{(i)}$.
+We exchange solving a fourth order energy to solve multiple second order problems.
+We still have to guarantee that solutions are connected.
+We handle this issue by limiting the optimization region to a subset of $\Omega$, namely the inner pixel boundary of  $S^{(i)}$.
+
+Given a digital shape $S \in \Omega$, the idea is to evolve a flow $S^{(i)}$ where $S^{(i+1)}$ is derived from the minimization of the sum of the squared curvature at $S^{(i)}$.
 In order to guarantee connectivity, we limit the optimization region to a subset of $\Omega$, namely the inner pixel boundary of  $S^{(i)}$.
@@
 
+\subsection{Discrete variational model for discrete curve evolution}
+
+We start by definition the optimization variables.
 \begin{definition}[Inner pixel boundary]
-
-Given a digital shape $S$ embedded in a domain $\Omega$, we define its inner pixel boundary set \revision{$I(S)$} as
-\begin{align*}
-	\revision{I(S)} := \left\{ \: p \; | \; p \in S, |\mathcal{N}_4(x) \cap S|<4 \: \right\},
-\end{align*}
-where $\mathcal{N}_4(p)$ denotes the $4$-adjacent neighbor set of $p$ (without $p$).
+Given a digital shape $S$ embedded in a domain $\Omega$, we define its inner pixel boundary set $O(S)$ as
+\begin{align*}
+	O(S) = \left\{ \: x \; | \; x \in S, |\mathcal{N}_4(x) \cap S|<4 \: \right\},
+\end{align*}
+where $\mathcal{N}_4(x)$ denotes the $4$-adjacent neighbor set of $x$ (without $x$).
 \end{definition}
 
-\revision{To simplify notation, the inner pixel boundary of $S^{(i)}$ is simply denoted $I^{(i)}$. At each iteration, the set $X^{(i)}$ of optimization variables is defined as}
-
-\begin{align*}
-\revision{
-	X^{(i)} := X(I^{(i)}).
-}
-\end{align*}
-
-In other words, each flow iteration decides which pixels in the inner boundary are to be removed from \revision{$S^{(i)}$} and which are to be kept in \revision{$S^{(i)}$}.
-We recall the definition of the II digital curvature estimator:
+In other words, each flow iteration decides which pixels in the inner boundary are to be removed and which are to be kept.
+To simplify notation, we denote the optimization region of $S^{(i)}$ as $O^{(i)}$, and the foreground set as $F^{(i)} = S^{(i)} \setminus O^{(i)}$.
+We recall the definition of our digital curvature estimator :
 \begin{align}
-	\hat{\kappa}^2(p) &= c_1\Big( c_2 - | B_r(p) \cap S^{\revision{(i)}} | \Big)^2, 
+	\hat{\kappa}^2(y) &= c_1\Big( c_2 - | B_r(y) \cap S | \Big)^2, 
 	\label{eq:curvature-estimator-pixels}
@@
 
-\revision{The following sets are important in the expansion of $\eqref{eq:curvature-estimator-pixels}$.}
-
-\revision{
-\begin{align*}
-	F^{(i)} &:= S^{(i)} \setminus I^{(i)} \\
-	F_r^{(i)}(p) &:= F^{(i)} \cap B_r(p)\\
-	I_r^{(i)}(p) &:= I^{(i)} \cap B_r(p) \\
-	X_r^{(i)}(p) &:= X\big( I_r^{(i)}(p) \big).
-\end{align*}
-}
-
-Expanding \eqref{eq:curvature-estimator-pixels}, we get
-
-\begin{align*}
-  \hat{\kappa}^2(p) &= c_1\Big( c_2 - |F_{r}^{(i)}(p)| - \sum_{x_j \in X_r^{(i)}(p)} {x_j} \Big)^2 \\
-   &= c_1 \Big( C + 2\left( |F_{r}^{(i)}(p)| - c_2 \right) \hspace{-2mm}\sum_{x_j \in X_{r}^{(i)}(p)}\hspace{-2mm}{x_j} + \hspace{-2mm}\sum_{x_j \in X_{r}^{(i)}(p)}\hspace{-2mm}{x_j^2} + \hspace{-2mm}\sum_{ \substack{x_j,x_k \in X_{r}^{(i)}(p) \\ j<k} }\hspace{-2mm}{2x_jx_k}  \Big),
-\end{align*}
-where $C=c_2^2 - 2c_2 \cdot |F_{r}^{(i)}(p)| + |F_{r}^{(i)}(p)|^2$ is a constant. By ignoring constants and multiplication factors and using
+We define $O_{r}^{(i)}(y) := O^{(i)} \cap B_r(y)$ and an analogous definition holds for $F_{r}^{(i)}(y)$. Expanding \eqref{eq:curvature-estimator-pixels}, we get 
+\begin{align*}
+  \hat{\kappa}^2(y) &= c_1\Big( c_2 - \sum_{x_j \in B_r(y)} \big( {x_j} + |F_{r}^{(i)}(y)| \big) \Big)^2 \\
+   &= c_1 \cdot \Big( C + 2\left( |F_{r}^{(i)}(y)| - c_2 \right) \hspace{-2mm}\sum_{x_j \in O_{r}^{(i)}(y)}\hspace{-2mm}{x_j} + \hspace{-2mm}\sum_{x_j \in O_{r}^{(i)}(y)}\hspace{-2mm}{x_j^2} + \hspace{-2mm}\sum_{ \substack{x_j,x_k \in O_{r}^{(i)}(p) \\ j<k} }\hspace{-2mm}{2x_jx_k}  \Big),
+\end{align*}
+where $C=c_2^2 - 2c_2 \cdot |F_{r}^{(i)}(y)| + |F_{r}^{(i)}(y)|^2$ is a constant. In
+order to be symmetric, the curvature at some linel $y$ is computed on
+$R_m(S)$.\todo{Que veux-tu dire?} By ignoring constants and multiplication factors and using
 the binary character of the variables, we define the following family
-of energies for given parameters $\alpha,\beta, \gamma \geq 0$.
+of energies for given parameters $\alpha,\beta \geq 0$.
 \begin{align}
-  E_m(X^{\revision{(i)}},S^{\revision{(i)}}) =& \sum_{x \in X^{\revision{(i)}}}{\alpha s(x)} + \nonumber \\ 
-  & \sum_{ \substack{p \in \\ R_m(S^{\revision{(i)}})}}{ \revision{2c_1} \beta  \Big( { (1/2+ |F_{r}^{(i)}(p)|-c_2) \cdot \sum_{ \substack{ x_j \in \\ X_{r}^{(i)}(p)}}{x_j} } + \sum_{ \substack{j<k, \\ x_j,x_k \in \\ X_{r}^{(i)}(p) } }{x_jx_k} \Big) } + \nonumber \\
-  & \sum_{x \in X^{\revision{(i)}}}{\gamma g(S^{\revision{(i)}},x)},
+  E_m(X,S) =& \sum_{x \in X}{\alpha s(x)} \nonumber \\ 
+  & + \sum_{y \in R_m(S)}{ \beta \Big( { (1/2+ |F_{r}^{(i)}(y)|-c_2) \cdot \sum_{x_j \in O_{r}^{(i)}(y)}{x_j} } + \sum_{ \substack{x_j,x_k \in O_{r}^{(i)}(y) \\ j<k} }{x_jx_k} \Big) } \nonumber \\
+  & + \sum_{x \in X}{\gamma g(S,x)}
   \label{eq:energy-family}
 \end{align}
-where $g(S,x)$ denotes a \revision{data term (e.g., distance to initial shape $S$ or fidelity to data)} and $s(x)$ denotes a length penalization term.
-Each choice of $m$ generates a different flow, which is generally described in the Digital Curve Evolution (DCE) algorithm \ref{alg:evolution-model}.
-
-\begin{figure}
-\begin{minipage}{0.5\textwidth}
-\center
-\includegraphics[scale=0.1]{images/flow/contour-information/before-opt.pdf}
-\label{fig:contour-info-1}
-\end{minipage}%
-\begin{minipage}{0.5\textwidth}
-\center
-\includegraphics[scale=0.1]{images/flow/contour-information/after-opt.pdf}
-\label{fig:contour-info-2}
-\end{minipage}%
-\caption{ \revision{Directly using the optimization result of \eqref{eq:energy-family} doesn't decrease squared curvature because contour information is not present in the energy.}}
-\label{fig:contour-info}
-\end{figure}
-
-\begin{algorithm}
+\todo{Que vaux $X$ ici ?}	
+where $g(S,x)$ denotes a similarity term as distance to initial shape $S$ or data fidelity term and $s(x)$ denotes a length penalization term.
+Each choice of $m$ generates a different flow, which is generaly described in the Digital Curve Evolution (DCE) algorithm \ref{alg:evolution-model}.
+
+\begin{algorithm}[H]
  \SetKwData{It}{i}
@@
 
- \Input{A digital set $S$; The ring number $m$; Length($\alpha$), curvature($\beta$) and \revision{data}($\gamma$) coefficients; the maximum number of iterations \MIt;}
+ \Input{A digital set $S$; The ring number $m$; Length($\alpha$), curvature($\beta$) and similarity($\gamma$) coefficients; the maximum number of iterations \MIt;}
  \BlankLine
- $S^{(0)} \longleftarrow S$\;
- $i \longleftarrow 1$\;
+ $S^{(i)} \longleftarrow S$\;
  \While{ \It $<$ \MIt  }{ 	
@@
 	\If{ \It is odd }{	 
-	 	$X^{(i)} \longleftarrow \argmin_X E_m(X,\overline{S^{(i-1)}})$\;
- 		$\revision{S^{(i)} \longleftarrow \overline{ F^{(i-1)}_{\overline{S}} + \overline{X^{(i)}}}}$\;
+	 	$X^{(i)} \longleftarrow \argmin_X E_m(X,\overline{S^{(i)}})$\;
+ 		$S^{(i)} \longleftarrow F^{(i)} + \overline{X^{(i)}}$\;
+ 		$S^{(i)} \longleftarrow \overline{S^{(i)}}$\;	 	
  	}
@@
  	\Else{	
-	 	$X^{(i)} \longleftarrow \argmin_X E_m(X,S^{(i-1)})$\; 	
- 		$S^{(i)} \longleftarrow F^{(i-1)}_{S} + \overline{X^{(i)}}$\;
+	 	$X^{(i)} \longleftarrow \argmin_X E_m(X,S^{(i)})$\; 	
+ 		$S^{(i)} \longleftarrow F^{(i)} + \overline{X^{(i)}}$\;
  	}
@@
  }
+ \label{alg:evolution-model} 
  \caption{Digital curvature evolution algorithm (DCE).}
- \label{alg:evolution-model}  
 \end{algorithm}
 
-\revision{
-We emphasize that the minimization of \eqref{eq:energy-family} for $S^{(i)}$ is not sufficient to derive the next shape $S^{(i+1)}$ because contour information is not included in the model (see figure \ref{fig:contour-info})}.
-Recall that the integral invariant estimator approaches curvature by computing the difference between half of the area
-of a chosen ball and the area of the intersection of this ball with the shape.  In particular, regions of positive
-curvature have fewer pixels in their intersection set than on its complement w.r.t the estimation ball. This implies
-that variables in such regions are labeled with 1, as the unbalance grows otherwise. We attenuate curvature if we shift
-the center of the estimation ball towards the interior of the shape, which means removing the 1-labeled pixels. That is
-why we take the complement of the optimization solution.
-
-The same reasoning applies for non-convex parts. Indeed, concave regions are convex in the shape complement. In the
-expansion mode we apply the same reasoning on the image complement, and by doing this we are able to handle
-concavities. It is called expansion mode because the optimization region, in this case, is the outer pixel boundary of
-the original shape. Table~\ref{tab:flow-summary} sums up these arguments.
-
-Length and \revision{data} terms should be properly defined in order to comply with the complement step of the DCE
-algorithm. The length penalization is defined as
-\revision{
+Recall that the integral invariant estimator approaches curvature by
+computing the difference between half of the area of a chosen ball and
+the area of the intersection of this ball with the shape.  In
+particular, regions of positive curvature have fewer pixels in their
+intersection set than on its complement wrt the estimation ball. This
+implies that variables in such regions are labeled one, as the
+unbalance grows otherwise. We attenuate curvature if we shift the
+center of the estimation ball towards the interior of the shape, which
+means removing the labeled one pixels. That is why we take the
+complement of the optimization solution.
+
+The same reasoning applies for non-convex parts. Indeed, concave
+regions are convex in the shape complement. In the expansion mode we
+apply the same reasoning on the image complement, and by doing this we
+are able to handle concavities. It is called expansion mode because
+the optimization region, in this case, is the outer pixel boundary of
+the original shape. Table~\ref{tab:flow-summary} sums up these
+arguments.
+
+Length and similarity terms should be properly defined in order to
+comply with the complement step of the DCE algorithm. The length
+penalization is defined as
 \begin{align}
-  s(x_{w(p)})=\sum_{q \in \mathcal{N}_4(p)}{ t(q) }, \quad \text{where } t(q) = \left\{\begin{array}{ll}
-  (x_{w(p)}-x_{w(q)})^2, & \text{if } q \in I^{(i)}\\
-  (x_{w(p)}-0), & \text{if } q \in F^{(i)}\\
-  (x_{w(p)}-1), & \text{otherwise }
+  s(x)=\sum_{x_j \in \mathcal{N}_4(x)}{ t(x_j) }, \quad \text{where } t(x_j) = \left\{\begin{array}{ll}
+  (x-x_j)^2, & \text{if } x_j \in O_{r}^{(i)}\\
+  (x-0), & \text{if } x_j \in F_{r}^{(i)}\\
+  (x-1), & \text{otherwise }
   \end{array}\right.
   \label{eq:length-penalization}
-\end{align}}
-
-We do not use \revision{data} terms in this section, thus we postpone the definition of such terms until later in this
-article, with the description of how DCE can be used in an image segmentation framework.
+\end{align}
+
+We do not use similarity terms in this section, thus we postpone the
+definition of such terms until the description of how DCE can be used
+in an image segmentation framework.
 
@@
   \center
-  \setlength{\extrarowheight}{0.5em}
   \begin{tabular}{|c|c|c|c|} \hline
@@
 
+  \label{tab:flow-summary}	  
   \caption{  Since the curvature is negated when reversing the curve (i.e.
 $\bar{\kappa}=-\kappa$), this process can only shrink  convex parts in shrink mode and expand concave parts in expansion mode.}
-   \label{tab:flow-summary}
 
@@
 
-In figure \ref{fig:m1-square-flow} we see some results for the DCE algorithm with $m=1$. We observe a global evolution
-towards rounder shapes, but with several artifacts. We minimize the effects of a jaggy boundary by setting $\alpha >
-0$. Nonetheless, a \revision{higher radius of the estimation ball} creates unstable shapes. In fact, the estimator is very sensitive in
-regions of low squared curvature, and it is precisely in those regions that spurious pixels are created.
-
-\begin{figure}[!h]
+In figure \ref{fig:m1-square-flow} we see some results for the DCE
+algorithm with $m=1$. We observe a global movement towards roundness,
+but with several artifacts. We minimize the effects of a jaggy
+boundary by setting $\alpha > 0$. Nonetheless, a higher estimation
+ball radius creates unstable shapes. In fact, the estimator is very
+sensitive in regions of low squared curvature, and it is precisely in
+those regions that spurious pixels are created.
+
+\begin{figure}[!ht]
 \center
@@
 \subsection{A more stable model.}
-In the previous section we noticed that the algorithm produces shapes with many artifacts due to the small uncertainties
-of the estimator along regions of low squared curvature. We argue that, \revision{by} evaluating the estimation ball along outer
-ring sets we avoid those sensitive areas by focusing the optimization process only on regions with highest squared
-curvature value.
-
-\begin{figure}[!h]
+In the previous section we noticed that the algorithm produces shapes
+with many artifacts due to the small uncertainties of the estimator
+along regions of low squared curvature. We argue that, evaluating the
+estimation ball along farther ring sets we avoid those sensitive areas
+by focusing the optimization process only on regions with highest
+squared curvature value.
+
+%%\jaco{Motivation in digital geometry of why it makes sense to compute things farther.}
+
+\begin{figure}[!ht]
 \center
@@
 	\includegraphics[scale=0.2]{images/flow/farther-rings/square-r5-l1/summary_flow.eps}
+	}%
+\end{minipage}%
+\begin{minipage}[b]{0.33\textwidth}
+	\subfloat[$r=5, m=2$\label{}]{%
+	\includegraphics[scale=0.2]{images/flow/farther-rings/square-r5-l2/summary_flow.eps}
 	}%
@@
 \end{minipage}%
-\begin{minipage}[b]{0.33\textwidth}
-	\subfloat[\revision{$r=5, m=5$}\label{}]{%
-	\includegraphics[scale=0.2]{images/flow/farther-rings/square-r5-l5/summary_flow.eps}
-	}%
-\end{minipage}%
 \caption{By positioning the estimation ball on farther rings, we minimize artifacts creation. \label{fig:mx-square-flow}}
@@
 
-{In our experiments, the best results are obtained by executing DCE algorithm with $m$ equal to $r$, where $r$ is
-  the estimation ball radius (see figure \ref{fig:mx-square-flow}). We observe that digital elastica may increase after some
-  iterations if chosen radius is too large, as in the case of the triangle in figure \ref{fig:mx-flow-gs-radius-effect}
-  in which the flow converges to a single point. We conjecture that an appropriated value for the radius should be given
-  by the shape reach.  The produced flow has no difficulties in handling changes on topology, and it presents different
-  speeds for regions with low and high curvature values, as illustrated in figure
-  \ref{fig:mx-speed-variation-hole-filling}.
-
-\begin{figure}[hp!]
+In our experiments, the best results are obtained by executing DCE
+algorithm with $m$ equal to $r$, where $r$ is the estimation ball
+radius (see figures \ref{fig:mx-square-flow},
+\ref{fig:mx-flow-gs-radius-effect} ). In plot
+\ref{fig:mx-elastica-plots}, we observe how the elastica energy evolves along
+the iterations. If the radius is too large, the elastica energy may increase after some steps. That is what happens for the
+triangle, in which the flow converges to a single point.
+
+\begin{figure}[!ht]
 \center				
@@
 \includegraphics[scale=0.2]{images/flow/grid-radius-effect/flower/r5-h0.5/summary_flow.eps}}%
-		}\\
-		\subfloat[\revision{Digital elastica evaluation ($r=5,h=0.5$)}]{%
-		\includegraphics[scale=0.5]{images/flow/elastica-energy-plot/square-flower-triangle.eps}						
 		}				
@@
 In figure (b), for $r=5$, the triangle evolves to a single point, while the others stop  in an intermediate shape, as in (a).
-In figure (c), we observe that for a given choice of radius, the digital elastica may increase after a certain number of iterations.
 }
@@
 
-\begin{figure}[!h]
+\begin{figure}[!ht]
+\center
+\includegraphics[scale=0.5]{images/flow/elastica-energy-plot/r5h05.eps}
+\caption{Elastica computation along the iterations for different shapes. If radius is too large, elastica energy may increase after a certain number of iterations. }
+\label{fig:mx-elastica-plots}
+\end{figure}
+
+\begin{figure}[!ht]
 \center
@@
 		\includegraphics[scale=0.25]{images/flow/fill-holes/summary_flow.eps}}%%1
+\label{fig:mx-speed-variation-hole-filling}
 \caption{High curvature regions evolves faster than lower ones (a). The flow can handle topological changes (b). }
-\label{fig:mx-speed-variation-hole-filling}
 \end{figure}
@@
 
-The function $f$ is submodular if and only if the following inequality holds for each pairwise term $f_{j,k}$ \cite{kolmogorov04whatenergies}:
+Function $f$ is submodular if and only if the following inequality holds for each pairwise term $f_{j,k}$ \cite{kolmogorov04whatenergies}:
 \begin{align*}
@@
 
-The energy $E_m$ is non-submodular and optimizing it is a difficult problem, which constrains us to use heuristics and
-approximation algorithms. The QPBO method \cite{rother07qpbo} transforms the original problem in a max-flow/min-cut
-formulation and yields a full optimal labeling for submodular energies. For non-submodular energies the method is
-guaranteed to return a partial labeling with the property that the set of labeled variables is part of an optimal
+Energy $E_m$ is non-submodular and optimizing it is a difficult
+problem, which constrains us to use heuristics and approximation
+algorithms. The QPBO method \cite{rother07qpbo} transforms the
+original problem in a max-flow/min-cut formulation and returns a full
+optimal labeling for submodular energies. For non-submodular energies
+the method is guaranteed to return a partial labeling with the
+property that the set of labeled variables is part of an optimal
 solution. That property is called partial optimality.
 
-In practice, QPBO can leave many pixels unlabeled. There exist two extensions to QPBO that alleviate this limitation:
-QPBOI (improve) and QPBOP (probe). The first is an approximation method that is guaranteed to not increase the energy,
-but loses the property of partial optimality. The second is an exact method which is reported to label more variables
-than QPBO.
-
-The percentage of unlabeled pixels by QPBOP for $E_1$ is quite high, but the percentage decreases to zero as we set $m$
-equal to $r$. Therefore, we are more confident in taking the solution for values of $m$ close to $r$. However, the way it
-varies across values of $m$ differs from shape to shape, as is illustrated in figure
-\ref{fig:unlabeled-versus-iterations}. We also noticed that, for $m=r$, all the pixels were labeled, {which may
-  indicate that $E_r$ is an easy instance of the general non-submodular energy $E_m$, but this remains to be
-  proved. The number of pairwise terms in $E_r$ is roughly half of those in $E_1$ (see figure
-  \ref{fig:ratio-pairwise-terms}).
-
-  We have used QPBOI to solve $E_m$. Naturally, in the case where all pixels are labeled by QPBOP, QPBOI returns the
-  same labeling as QPBOP.
-
-\begin{figure}
-\center
-\includegraphics[scale=0.5]{images/optimization/pairwise-ratio/plot-pairwiseratio-lowerHigher-concavities-probe.eps}
-\caption{We plot the ratio of pairwise terms among all $\binom{|X^{(i)}|}{2}$ combinations. The highest ring has roughly half the number of pairwise terms as the lowest ring.}
-\label{fig:ratio-pairwise-terms}
-\end{figure}
-
-\begin{figure}[]
+In practice, QPBO can leave many pixels unlabeled. There exist two
+extensions of QPBO that alleviate this limitation: QPBOI (improve) and
+QPBOP (probe). The first is an approximation method that is guaranteed
+to not increase the energy, but we lost the property of partial
+optimality. The second is an exact method which is reported to label
+more variables than QPBO.
+
+The percentage of unlabeled pixels by QPBOP for $E_1$ is quite high,
+but the percentage decreases to zero as we set $m$ equal to
+$r$. Therefore, we are more confident to take the solution for values
+of $m$ close to $r$. However, the way it varies across $m$ values
+differs from shape to shape, as is illustrated in figure
+\ref{fig:unlabeled-versus-iterations}. We also noticed that, for
+$m=r$, all the pixels were labeled. Perhaps this means that our energy
+is submodular in this case, but this remains to be proved.
+
+We have used QPBOI to solve $E_m$. Naturally, in the case where all
+pixels are labeled by QPBOP, QPBOI returns the same labeling as QPBOP.
+
+\begin{figure}[!htp]
 \center
@@
 The number of unlabeled pixels by QPBOP remains high for lower values of $m$, and goes to zero when $m=r$.
-We observe the same behaviour for varying radius values.}
+We observe the same behaviour for different radius values.}
 \label{fig:unlabeled-versus-iterations}
@@
 
+\begin{figure}
+\center
+\includegraphics[scale=0.5]{images/optimization/pairwise-ratio/plot-pairwiseratio-lowerHigher-concavities-probe.eps}
+\caption{We plot the ratio of pairwise terms among all $\binom{|X^{(i)}|}{2}$ combinations.
+The highest ring has rougly half the number of pairwise terms  than the lowest ring.\label{fig:ratio-pairwise-terms}}
+\end{figure}
+
+\todo{You must comment figure~\ref{fig:ratio-pairwise-terms} in the text.}
+
 \section{Application to image segmentation}
 
-We present an application of our digital curve evolution algorithm to supervised image segmentation. The DCE acts as a
-contour correction method. Here we use a data fidelity term in order to characterize the object of
-interest. Given foreground and background seeds selected by the user, we derive mixed Gaussian distributions of color
-intensities $G_f$,$G_b$, and we define the data fidelity term as the cross-entropy, i.e.
+We present an application of our digital curve evolution algorithm to supervised image segmentation.
+The DCE will act as a contour correction method.
+Here we are going to use a data fidelity term in order to characterize the object of interest.
+Given foreground and background seeds selected by the user, we derive mixed gaussian distributions  of color intensities $G_f$ and $G_b$, and we define the data fidelity term as
 
 \begin{align}
-  g(\revision{x_{w(p)}}) = -(1-\revision{x_{w(p)}})\log{G_f(p)} - \revision{x_{w(p)}}\log{G_b(p)}.
+  g(y) = -(1-y)\log{G_f(I(y))} - y\log{G_b(I(y))}.
   \label{eq:data-fidelity}
@@
 
-We use the DCE algorithm to regularize an initial contour output by some segmentation algorithm or delineated by the user. In this application, the \revision{data} term of the DCE
+We use the DCE algorithm to regularize an initial contour outputed by some segmentation algorithm or delineated by the user. In this application, the similarity term of the DCE
 is set to the data fidelity term \eqref{eq:data-fidelity}.
 
-\begin{algorithm}
+\begin{algorithm}[H]
  \SetKwData{It}{i}
@@
 
- \Input{An image $I$; seed mask $M$; the estimation ball radius $r$; length $(\alpha)$, squared curvature $(\beta)$ and data fidelity $(\gamma)$ coefficients; initial dilation $d$; stop condition value \Tol; the maximum number of iterations \MIt;}
+ \Input{An image $I$; seed mask $M$; the estimation ball radius $r$; data $(\gamma)$, length $(\alpha)$ and squared curvature $(\beta)$ weights; initial dilation $d$; stop condition value \Tol; the maximum number of iterations \MIt;}
  \BlankLine
@@
  \While{ \It $<$ \MIt \bf{and} \Delta $>$ \Tol  }{ 	
- 	$S^{(i+1)} \longleftarrow $ DCE($S^{(i)},r,\alpha,\beta,\gamma,2$)\;
+ 	$S^{(i+1)} \longleftarrow $ DCE($S^{(i)},\gamma,\alpha,\beta$)\;
  	\Delta $\longleftarrow |S^{(i)} - S^{(i+1)}|$\;
@@
  \label{alg:contour-correction} 
- \caption{Contour correction algorithm.}
+ \caption{Contour correction algorithm. \todo{Critère d'arrêt basé sur un nombre de pixels changés !?}}
 \end{algorithm}
@@
 
-\begin{figure}[ht!]
+\begin{figure}
 \center
 \begin{tabular}{ccc}
-\revision{Seeds} & $(\alpha=0, \beta=0.5)$ & $(\alpha=0,\beta=1)$ \\
+Seeds & $(\alpha=0, \beta=0.5)$ & $(\alpha=0,\beta=1)$ \\
  	\includegraphics[scale=0.25]{images/segmentation/bc/coala/seeds.png} & 
@@
 
- 	\includegraphics[scale=0.25]{images/segmentation/bc/coala/grabcut-seg.png} & 
+ 	\includegraphics[scale=0.25]{images/segmentation/bc/coala/lg0_sq0_dt1_it20.png} & 
 	\includegraphics[scale=0.25]{images/segmentation/bc/coala/r3/lg1_sq0_dt1_it50.png} &
@@
 
-	\revision{GrabCut} & $(\alpha=0.5, \beta=0)$ & $(\alpha=1, \beta=0)$
+	GrabCut & $(\alpha=0.5, \beta=0)$ & $(\alpha=1, \beta=0)$
 \end{tabular}	
@@
 
-\begin{figure}[ht!]
+\begin{figure}
 	\center
 	\begin{tabular}{ccc}
-		GrabCut & Schoenemann & Contour Correction \\
-		& $(\alpha=0.1, \beta=1.0$) & $(r=5, \alpha=0.1, \beta=1.0, \gamma=3.0$)\\
+		GrabCut & Contour Correction & Schoenemann \\
+		& $(r=5, \alpha=0.1, \beta=1.0, \gamma=3.0$) & $(\alpha=0.1, \beta=1.0$)\\
 		\includegraphics[scale=0.2]{images/segmentation/bc/tiger1/gc-seg.png} &
-	\includegraphics[scale=0.2]{images/segmentation/schoenemann/tiger1/tiger1-seg.png}&
-		\includegraphics[scale=0.2]{images/segmentation/bc/tiger1/corrected-seg.png}\\									
+		\includegraphics[scale=0.2]{images/segmentation/bc/tiger1/corrected-seg.png} &					\includegraphics[scale=0.2]{images/segmentation/schoenemann/tiger1/tiger1-seg.png}\\									
 		\includegraphics[scale=0.2]{images/segmentation/bc/snake/gc-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/schoenemann/snake/snake-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/bc/snake/corrected-seg.png}\\
+		\includegraphics[scale=0.2]{images/segmentation/bc/snake/corrected-seg.png} &
+		\includegraphics[scale=0.2]{images/segmentation/schoenemann/snake/snake-seg.png}\\						
 		\includegraphics[scale=0.2]{images/segmentation/bc/man/gc-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/schoenemann/man/man-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/bc/man/corrected-seg.png}\\		
+		\includegraphics[scale=0.2]{images/segmentation/bc/man/corrected-seg.png} &
+		\includegraphics[scale=0.2]{images/segmentation/schoenemann/man/man-seg.png}\\		
 		\includegraphics[scale=0.2]{images/segmentation/bc/vase/gc-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/schoenemann/vase/vase-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/bc/vase/corrected-seg.png}		
+		\includegraphics[scale=0.2]{images/segmentation/bc/vase/corrected-seg.png} &					\includegraphics[scale=0.2]{images/segmentation/schoenemann/vase/vase-seg.png}		
 	\end{tabular}
-	\caption{The proposed method regularizes GrabCut \cite{rother04grabcut} contours and returns meaningful results.
-We can observe the completion feature of curvature in the second row, and we don't suffer from over-segmentation issues as Schoenemann's method \cite{schoenemann09linear}.
-However, our flow may stop in a local optimum as in the fourth row, while Schoenemann's is able to extrapolate such solutions.}
+	\caption{The proposed method regularizes grabcut contours and returns meaningful results.
+We can observe the completion feature of curvature in the second row, and we don't suffer from oversegmentation issues as Schoenemann's method.
+However, our flow may stop in a local optima as in the fourth row, while Schoenemann's is able to extrapolate such solutions.}
 	\label{fig:segmentation-results}	
@@
 
-\begin{figure}[hp!]
+\begin{figure}
 	\center
 	\begin{tabular}{ccc}
-		GrabCut & Schoenemann & Contour Correction \\
-		& $(\alpha=0.1, \beta=1.0$) & $(r=5, \alpha=0.1, \beta=1.0, \gamma=3.0$)\\
+		GrabCut & Contour Correction & Schoenemann \\
+		& $(r=5, \alpha=0.1, \beta=1.0, \gamma=3.0$) & $(\alpha=0.1, \beta=1.0$)\\
 		\includegraphics[scale=0.2]{images/segmentation/bc/airplane2/gc-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/schoenemann/airplane2/airplane2-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/bc/airplane2/corrected-seg.png}\\						
+		\includegraphics[scale=0.2]{images/segmentation/bc/airplane2/corrected-seg.png} &					\includegraphics[scale=0.2]{images/segmentation/schoenemann/airplane2/airplane2-seg.png}\\									
 		\includegraphics[scale=0.2]{images/segmentation/bc/bird/gc-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/schoenemann/bird/bird-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/bc/bird/corrected-seg.png}\\				
+		\includegraphics[scale=0.2]{images/segmentation/bc/bird/corrected-seg.png} &
+		\includegraphics[scale=0.2]{images/segmentation/schoenemann/bird/bird-seg.png}\\						
 		\includegraphics[scale=0.2]{images/segmentation/bc/camel/gc-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/schoenemann/camel/camel-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/bc/camel/corrected-seg.png}\\	
+		\includegraphics[scale=0.2]{images/segmentation/bc/camel/corrected-seg.png} &
+		\includegraphics[scale=0.2]{images/segmentation/schoenemann/camel/camel-seg.png}\\		
 		\includegraphics[scale=0.2]{images/segmentation/bc/rock/gc-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/schoenemann/rock/rock-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/bc/rock/corrected-seg.png} \\		
+		\includegraphics[scale=0.2]{images/segmentation/bc/rock/corrected-seg.png} &					\includegraphics[scale=0.2]{images/segmentation/schoenemann/rock/rock-seg.png}\\
 		\includegraphics[scale=0.2]{images/segmentation/bc/giraffes/gc-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/schoenemann/giraffes/giraffes-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/bc/giraffes/corrected-seg.png} \\		
+		\includegraphics[scale=0.2]{images/segmentation/bc/giraffes/corrected-seg.png} &					\includegraphics[scale=0.2]{images/segmentation/schoenemann/giraffes/giraffes-seg.png}\\
 		\includegraphics[scale=0.2]{images/segmentation/bc/canguru/gc-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/schoenemann/canguru/canguru-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/bc/canguru/corrected-seg.png} \\		
+		\includegraphics[scale=0.2]{images/segmentation/bc/canguru/corrected-seg.png} &					\includegraphics[scale=0.2]{images/segmentation/schoenemann/canguru/canguru-seg.png}\\		
 		\includegraphics[scale=0.2]{images/segmentation/bc/coral/gc-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/schoenemann/coral/coral-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/bc/coral/corrected-seg.png}								
+		\includegraphics[scale=0.2]{images/segmentation/bc/coral/corrected-seg.png} &					\includegraphics[scale=0.2]{images/segmentation/schoenemann/coral/coral-seg.png}\\
+
 	\end{tabular}
-	\caption{\revision{Additional comparison results between GrabCut \cite{rother04grabcut}, Schoenemman  \cite{schoenemann09linear} and Contour correction segmentation methods.}}
+	\caption{}
 	\label{fig:more-segmentation-results}	
@@
 We evaluate our method using the BSD300 database \cite{martinFTM01berkeley}.
-All images contain the same number of pixels, \revision{the resolution being 321x481 (481x321) in portrait (landscape) mode}.
+All images contains the same number of pixels, the resolution being 321x481 in portrait mode.
 We compare the results of our method with segmentations given by GrabCut and Schoenemanns's method \cite{schoenemann09linear}.
@@
 
-{In figure \ref{fig:parameters-influence} we can observe the results of a curvature regularization in comparison with a
-  pure length regularization. The curvature can fill gaps and is smoother than the one produced by length only,
-  resulting in more pleasant segmentations. In figures \ref{fig:segmentation-results} and
-  \ref{fig:more-segmentation-results} we list several results of our method and we compare them with segmentation
-  produced by GrabCut and Schoenemann's method. Our method is successful in producing curvature regularized
-  segmentations and demonstrates the completion property of curvature.
-Moreover, it does not suffer from over-segmentation, it is much faster than Schoenemann's, and in several cases produces better segmentations than
-  GrabCut.
+In figure \ref{fig:parameters-influence} we can observe the results of a curvature regularization in comparison with a pure length regularization, and figures \ref{fig:segmentation-results} and \ref{fig:more-segmentation-results} show some segmentation results.
+
+\todo{You must comment on the results.}
 
@@
 
-We have studied in depth several digital curve evolution models based on a digital version of the Elastica energy and we
-have presented an application to image segmentation. The processes we have described are completely digital and do not
-suffer from issues that typically arise in models that pass through a discretization stage, such as
-rounding. Moreover, the model can handle changes in topology and its results are competitive with similar approaches
-while achieving reasonable running times.
-
-Future developments of this work will include extending the DCE algorithm to $3$d, as the integral invariant estimator
-is available in higher dimensions. As a result, a denoising application may be derived by lifting the flow to $3$d
-with a data fidelity defined by image intensities or by distance to initial position.
+We have studied in depth several digital curve evolution models based
+on the elastica energy and we have presented an application of one of
+them to image segmentation. The processes we have described are
+completely digital, and do not suffer from issues that typically
+arises in models that passes through a discretization stage, as
+rounding. Moreover, the model can handle changes in topology and its
+results are competitive with similar approaches while achieving
+reasonable running times.
+
+Future developments of this work may include automatization, no more
+dependence on seeds selected by the user and automatic choice of ball
+estimation radius based on the reach of the shape. One can also think
+to extend the DCE algorithm to $3$d, as the integral invariant
+estimator preserves its properties in that space. In future works, a
+denoising application may be derived by running the flow on the $3$d
+shape with data fidelity defined by image intensities or by distance
+to initial position.
 

### 2020-01-06 jmiv.tex

@@
 %
-\title{A\HT{n Elastica-driven} Digital Curve Evolution Model for Image Segmentation\thanks{This  work has  been  partially  funded by CoMeDiC ANR-15-CE40-0006 research grant.}}
+\title{An Elastica-driven Digital Curve Evolution Model for Image Segmentation\thanks{This  work has  been  partially  funded by CoMeDiC ANR-15-CE40-0006 research grant.}}
 \titlerunning{Digital Curve Evolution by Elastica Energy}
@@
 %
-\institute{Universit{\'e} Savoie Mont Blanc, LAMA, UMR CNRS 5127, F-73376, France
-\email{daniel.martins-antunes, jacques-olivier.lachaud@univ-savoie.fr} \and
-CentraleSupelec Inria \'equipe OPIS, Universit\'e Paris-Saclay, 9 rue Joliot-Curie, F-91190 Gif-sur-Yvette \\
+\institute{%Universit{\'e} Savoie Mont Blanc, LAMA, UMR CNRS 5127, F-73376, France
+  Daniel Antunes \at
+  Univ. Grenoble Alpes, Univ. Savoie Mont Blanc, CNRS, LAMA, 73000 Chambéry, France \\
+  \email{daniel.martins-antunes@univ-smb.fr} \and
+  Jacques-Olivier~Lachaud \at  Univ. Grenoble Alpes, Univ. Savoie Mont Blanc, CNRS, LAMA, 73000 Chambéry, France \\
+  \email{jacques-olivier.lachaud@univ-smb.fr} \and
+  Hugues Talbot \at CentraleSupelec, Inria, Universit\'e Paris-Saclay, 9 rue Joliot-Curie, F-91190 Gif-sur-Yvette \\
   \email{hugues.talbot@centralesupelec.fr}}
@@
 \begin{abstract}
-  \HT{Geometric priors have been shown to be useful in image segmentation to regularize results. For example, the classical
-    Mumford-Shah functional uses regions perimeter as prior. This has inspired much research in the last few decades,
+  Geometric priors have been shown to be useful in image segmentation to regularize results. For example, the classical
+    Mumford-Shah functional uses region perimeter as prior. This has inspired much research in the last few decades,
     with classical approaches like the Rudin-Osher-Fatemi and most graph-cut formulations, which all use a weighted or
@@
     underlying optimisation processes are not convex. In this article, we propose to formulate a digital flow that
-    approximates a curvature-related flow using a multigrid-convergent curvature estimator, within a discrete
-    variational framework. We also present an application of this model as a post-processing step in a segmentation
-    framework.}
+    approximates an Elastica-related flow using a multigrid-convergent curvature estimator, within a discrete
+    variational framework. We also present an application of this model as a post-processing step to a segmentation
+    framework.
 \keywords{Multigrid convergence  \and Digital estimator \and Curvature \and Shape Optimization \and Image Segmentation.}
@@
 \HT{State-of-art methods are in practice} difficult to optimize and \HT{do not scale}
+=======
+known about the shape of interest. Length penalization is a
+well-behaved, general purpose regularizer and many models in the
+literature make use of it, from active contours
+\cite{casseles97geodesic} to level-set formulations
+\cite{malladi1995image,malladi1995shape}. Discrete graph-based
+variational models have been particularly succesful to incorporate
+length penalization as a penalizer, while keeping the ability to
+extract a global optimum \cite{boykov01graphcut,appleton05geodesic}.
+
+However length regularization shows limitations when segmenting small
+or thin and elongated objects, as it tends to shrink solutions or
+yields disconnected solutions. Such drawbacks can be problematic in
+image segmentation, image restoration or image inpainting. It is thus
+rather natural to consider curvature (especially squared curvature) as
+a potential regularizer. Energies involving both length and squared
+curvature are often called the {\em Elastica} model (that dates back
+to Euler). The {\em Willmore energy} is its $n$-dimensional
+extension. These were brought to attention in computer vision by
+Mumford \cite{mumford1994elastica}. A similar concept is also present
+in the second-order regularizer of the original snake model
+\cite{kass1988snakes}.Indeed, an explicit curvature term was often
+employed in early level-set methods,
+like~\cite{malladi1995image,malladi1995shape,ballester01filljoint} for
+segmentation or inpainting. However, Casselles {\em et al.}
+in~\cite{casseles97geodesic} observed that these terms as employed
+were not geometric, in the sense that they depend on the
+discretization parameters.
+
+\subsection{Existing works}
+The use of curvature for surface regularization in the case of the
+Willmore energy was studied in~\cite{bobenko2005discrete}. Although
+results look promising, authors used an inexact linearized version of
+the square curvature at every step.
+
+One of the first successful uses of geometric, squared curvature in
+image processing is the inpainting algorithm described in
+\cite{masnou98inpainting}, where authors evaluate the absolute
+curvature along the level lines of a simply-connected image to
+reconstruct its occluded parts. The non-intersection property of level
+lines induces the construction of an efficient dynamic programming
+algorithm. The curvature energy is nevertheless only coarsely
+approximated. We may quote \cite{chan02elasticainpainting} as another
+geometric inpainting method involving Elastica, which is optimized with
+level-sets.
+
+In image segmentation, Zehiry and Grady have shown that injecting
+curvature as a regularizer can help recover thin and elongated objects
+\cite{zehiry10fast}. Similarly Schoenemann {\em et al.}
+\cite{schoenemann09linear} have considered the Elastica energy in
+their ratio-based image segmentation
+approach. In~\cite{schoenemann2011elastic}, Schoenemann~{\em et al.}
+extend ratio-cut approaches to segmentation with a curvature
+term. Their global optimization framework shows the considerable
+advantages of using such regularizer in common binary image
+segmentation tasks.  However the time complexity of their algorithm
+is prohibitive, even if curvature is again coarsely
+approximated.  In a more recent work, Lim {\em et al.} propose an
+edge-weighted Willmore-like flow to segment
+vertebra~\cite{lim2012introducing} using a level-set
+formulation. They observe improved results compared
+to~\cite{casseles97geodesic} and other perimeter-based priors, but
+observe that a shape prior and a close-enough initialization must also be
+provided to achieve good results.
+
+In fact, it is still a very challenging task to efficiently handle
+curvature in the context of image segmentation.  State-of-art methods
+are in practice difficult to optimize and do not scale easily
 \cite{zehiry10fast,schoenemann09linear,strandmark11globalframework,nieuwenhuis14efficient}. In
@@
 
-Segmentation methods using Elastica or Willmore energies \HT{generally
-reduce to} computing the corresponding flow, i.e. following its
-gradient. Well-founded level-set methods involving Willmore energy
-\cite{droske2004level} have been used in medical image segmentation
-\cite{lim2012introducing}. Another level-set formulation similar to
-the Chan-Vese model \HT{was} proposed in \cite{zhu2013image}. Willmore
-flow can also be carried out by phase-field models (see
-\cite{bretin2015phase}) but they are less suited to image segmentation
-since interfaces are blurred in such models. Threshold dynamics can
-also be considered for such energies \cite{esedoglu2008threshold} and
-has been proposed for image desocclusion \cite{esedoglu2005threshold}.
-
-In this paper we are interested in purely discrete variational segmentation models involving an elastica
-energy. Recently, new estimators of curvature along digital contours have been proposed
-\cite{roussillon11mdca,coeurjolly13integral,schindele17mdca} with the \HT{desirable} multigrid convergence property. This
-motivates us to \HT{propose} models in which they can be used successfully.
-
-\HT{In the remainder, we} investigate the use of the digital integral invariant
-curvature estimator \cite{coeurjolly13integral} in a discrete
-variational segmentation framework. More precisely, we show how to
-incorporate it in a digital flow minimizing its squared
+Segmentation methods using Elastica or Willmore energies can be
+formulated via the computation of the corresponding flow,
+i.e. following its gradient. Well-founded level-set methods involving
+Willmore energy \cite{droske2004level} have been used in medical image
+segmentation \cite{lim2012introducing}. Another level-set formulation
+similar to the Chan-Vese model was proposed in
+\cite{zhu2013image}. Willmore flow can also be carried out by
+phase-field models (see \cite{bretin2015phase}) but they are less
+suited to image segmentation since interfaces are blurred in such
+models. Threshold dynamics can also be considered for such energies
+\cite{esedoglu2008threshold} and has been proposed for image
+desocclusion \cite{esedoglu2005threshold}. However, flow-based methods
+will always deliver a local minimum, which heavily depend on
+initialization for good results. A similar approach is to formulate
+the Elastica as a regularization in a variational framework and use
+operator splitting to optimize it. Tai {\em et
+  al.}~\cite{tai11elastica} and more recently Deng~{\em et
+  al.}~\cite{deng2019new} have proposed this approach, which is
+well-suited to inverse problem solving. The problem remains non-convex
+and the nature of the converged iterates are not studied, i.e. how
+close they are to a global optimum.
+
+In contrast, researchers have sought convex relaxation of curvature-related
+formulation. In~\cite{goldluecke11totalcurvature}, Goldluecke and Cremers introduce the {\em Total Curvature}, based
+on the Menger-Melnikov curvature of a measure. The formulation is non-convex but can be relaxed into a well-correlated
+but non-tight convex one.
+The relaxed formulation can be used to solve inverse problems including segmentation.
+However computing a solution is still expensive, requiring signifiant parallelisation efforts with a GPU to achieve
+  acceptable computing times. In~\cite{bredies15convex}, Bredies {\em et al.} study a convex approximation of the
+  Elastica energy, using a lifting scheme. Thanks to the lifting, it is not restricted to binary sets. It shows
+  promising results and can be used for image restoration in addition to inpainting and segmentation. The scheme is
+  however neither tight nor exact, and required 4 dimensions for a 2D approximation. In addition, it does not carry over
+to $nD$. It also remains computationally expensive.
+
+Discrete approaches have been used to tackle the Elastica
+difficulties. As noted before, \cite{schoenemann09linear} have
+linearized a mesh-based approach, which was expanded upon
+by~\cite{strandmark11globalframework}, while \cite{zehiry10fast} have
+used a binary solver for a non-submodular approach on a regular square
+grid of pixels, which was expanded
+in~\cite{el2016contrast}. In~\cite{nieuwenhuis14efficient} , a
+specific solver is developed to yield a better solution to an
+extension of the formulation in~\cite{zehiry10fast}.
+
+\subsection{Motivation}
+In spite of the multiplicity of existing approaches, it seems none is
+currently completely satisfactory. While the sought solution is
+expected to be very smooth based on geometrical expectations, the
+mathematical properties of the related operators make this smoothness
+elusive. Non-convexity and the presence of high-order terms make
+Elastica difficult to optimize and to approximate, let alone compute
+efficiently. The computed solutions in the literature are rarely
+evaluated, and the complexity of the proposed solution is often high.
+
+%%\item{What are the difficulties in use curvature as a regularizer (point out convex relaxation approaches) and how a digital approach may help us }
+%%\item{Outline: We present two models that illustrate how digital estimators can be used to minimize the elastica energy on digital sets.  }
+%%\item{\todo{Add related works : geometric priors, binary segmentation, other digital curve evolution models}}
+%%\item{\todo{Talk about Willmore flow with phase field or with threshold dynamics}}
+
+Consequently, we are interested in studying purely discrete
+variational segmentation models involving an Elastica
+energy. Recently, new estimators of curvature along digital contours
+have been proposed
+\cite{roussillon11mdca,coeurjolly13integral,schindele17mdca} with the
+desirable multigrid convergence property. This motivates us to propose
+models in which they can be used successfully.
+
+In this paper, we propose to investigate the use of the digital
+integral invariant curvature estimator \cite{coeurjolly13integral} in
+a discrete variational segmentation framework. More precisely, we show
+how to incorporate it in a digital flow minimizing its squared
 curvature. This model is expressible as a discrete combinatorial
 optimization model, which we solve using a classical variant of QPBO
-algorithm \cite{rother07qpbo}. \HT{Our solution does not} compute a global
-solution to the whole domain, but our approach leads to a digital flow
-similar to continuous \HT{Elastica}, as shown by our experiments. We
-present an application of the model as a post-processing step in a
+algorithm \cite{rother07qpbo}. Our solution does not compute a global
+solution to the whole domain but a global solution to a band
+surrounding a given shape. Our approach thus leads to a digital flow
+similar to continuous Elastica, as shown by our experiments. We
+present an application of this model as a post-processing step in a
 segmentation framework, and demonstrate how it can improve standard
-results. The code is freely available on
-github\footnote{https://www.github.com/danoan/BTools}.
-
-%% In this work, we investigate the use of a more suitable curvature
-%% estimator with multigrid convergent property and its application as a
-%% boundary regularizer in a digital flow minimizing its squared
-%% curvature. Our method decreases the elastica energy of the contour and
-%% its evolution is evaluated on several digital flows.
-
-%% Finally, we
-%% present an application of the model as a post-processing step in a
-%% segmentation framework. The code is freely available on
-%% github\footnote{https://www.github.com/danoan/BTools}.
-
-\begin{itemize}
-\item{Geometric properties and regularization}
-\item{The role of curvature}
-
-%  Quote \cite{schoenemann2011elastic} for the interest of using curvature energy when segmenting regions in gradient-based data fitting term.
-It can look for global optimum within a graph representation of the image.
-Main problem of their approach is the computational complexity as well as rather coarse approximations of curvature.
-(Be more precise here).
-
-\item{What are the difficulties in use curvatue as a regularizer (point out convex relaxation approaches) and how a digital approach may help us }
-\item{Outline: We present two models that illustrate how digital estimators can be used to minimize the elastica energy on digital sets.  }
-\item{\todo{Add related works : geometric priors, binary segmentation, other digital curve evolution models}}
-\item{\todo{Talk about Willmore flow with phase field or with threshold dynamics}}
-
-%%\item{\textbf{Classical work on elastica and Wilmore flow in imaging}}
-  %%\begin{itemize}
-  %% \item{Level lines based disocclusion \cite{masnou98inpainting} }	%% DONE
- %%  \item{Filling-In by Joint Interpolation of Vector Fields and Gray Levels \cite{ballester01filljoint} } %% DONE
- %%  \item{Eulers Elastica and Curvature Based Inpaintings \cite{chan02elasticainpainting} } %% DONE
- %% \item{Discrete willmore flow \cite{bobenko2005discrete}}
- %%  \item{Introducing Willmore flow into level set segmentation of spinal vertebrae \cite{lim2012introducing}}	 %%% DONE
- %% \end{itemize}
-
-%%\item{\textbf{Level-sets}}
- %% \begin{itemize}
-  %% \item{Image processing via level set curvature flow \cite{malladi1995image} } %% DONE
-  %% \item{Shape Modeling with Front Propagation: A Level Set Approach \cite{malladi1995shape} }	%% DONE
-%%	\end{itemize}
-
-\item{\textbf{Convex relaxation}}
-  \begin{itemize}
-  \item{A convex lower semicontinuous approximation of Eulers elastica energy \cite{bredies15convex}}
-  \item{Introducing Total Curvature for Image Processing \cite{goldluecke11totalcurvature}}
-  \end{itemize}
-
-\item{\textbf{Constraint optimization}}
-  \begin{itemize}
-  \item{Curvature regularity for region-based image segmentation and inpainting: A linear programming relaxation \cite{schoenemann09linear} }	
-  \item{A Fast Algorithm for Euler's Elastica Model Using Augmented Lagrangian Method \cite{tai11elastica} }		
-  %%\item{The elastic ratio: Introducing curvature into ratio-based image segmentation \cite{schoenemann2011elastic}
-  %%}		%% DONE
-  \item{Curvature Regularization for Curves and Surfaces in a Global Optimization Framework \cite{strandmark11globalframework} }
-  \end{itemize}
-
-\item{\textbf{Discrete approaches}}
-  \begin{itemize}
-  \item{Fast global optimization of curvature \cite{zehiry10fast}	}
-  \item{Efficient Squared Curvature \cite{nieuwenhuis14efficient} 	}
-  \item{Contrast driven {E}lastica for image segmentation \cite{el2016contrast} }	
-  \end{itemize}
-
-\end{itemize}
-
-\textit{Outline}. Section two reviews the concept of multigrid
-convergence and highlights its importance for the definition of
-digital estimators. Next, we describe two convergent estimators used
-in this paper, one for tangent and the other for curvature. They are
-used in the optimization model and in the definition of the digital
-elastica. Section three describes a local combinatorial optimization model
-suitable for different curvature estimators. Section four describes the proposed 
-curvature evolution model along with several illustrations of digital flows. Section five
-explains how to use the evolution model as a post-processing step in
-an image segmentation framework.
-
-\section{Multigrid convergent estimators \todo{(Mostly copy/paste)}}
-
-The goal of this section is to  introduce the concept of multigrid convergenc and its potential when analyzing digital images with variational models involving geometric quantities.
-More precisely we wish to delineate shapes within digital images with some priors related to their unknown continuous geometry.
-Of course we only observe shape digitizations within images.
-%% \begin{itemize}
-%% 	\item{Why to use multigrid convergent estimators}
-%% 	\item{Multigrid convergence for local estimators}
-%% 	\item{Reference to examples of multigrid digital estimators(for curvature, length, tangent)}
-%% 	\item{Define the elastica energy estimator}
-%% 	\item{\test{(Jaco) see if two opposite II evaluations give convergent curvature}}
-%% \end{itemize}
-
-%% \hrulefill
+results. This paper is an extended version of a previous work that
+appeared in \cite{antunes19}. We have included a deeper discussion on
+our optimization method and we present a more thorough comparison of
+our segmentation method with two other related works. Moreover, we
+have included a new local combinatorial optimization approach for
+elastica minimization, which show that our discrete model is
+well-founded. Finally, the code produced in this paper is freely
+available on github.\footnote{https://www.github.com/danoan/BTools}
+
+\subsection{Outline}
+Section~2 reviews the concept of multigrid convergence and highlights
+its importance for the definition of digital estimators. We describe
+two convergent estimators used in this paper, one that approaches the
+length of elementary discrete contour elements, and the other that
+approaches the curvature of a discrete contour. They are used in the
+optimization model and in the definition of the digital
+elastica. Section~3 describes a local combinatorial optimization model
+suitable for several curvature estimators, that presents interesting
+results but is too costly in practice. Section~4 describes the
+proposed Elastica-driven curvature evolution model along with several
+illustrations of digital flows. Section~5 explains how to use this
+evolution model as a post-processing step in an image segmentation
+framework and compares it to two related approaches. We conclude and
+draw some perspectives to this work in Section~6.
+
+\section{Multigrid convergent estimators}
+Our objective is to delineate shapes within digital images with some priors related to continuous geometry. The goal of
+this section is to introduce the concept of multigrid convergence and its potential when analyzing digital images with
+variational models involving geometric quantities, with the constraint that only digitized shapes are observed.
 
@@
 
-The running time of algorithm \ref{alg:local-search} is summarized in
-table \ref{tab:summary-local-comb-rtime}.
-All the experiments in this paper were executed on a five core $3.4Ghz$ cpu and the number of pixels in the triangle, square and flower shapes are respectively $841,1867,521$ for grid step $h=1.0$.
-Although its use in practical applications is limited, we
-demonstrate that digital estimators are effective in their measurements
-and the flows evolve as expected. We observe that it is a
-complete digital approach, and we do not suffer from discretization
-and rounding problems, a common issue in continuous models.
-Furthermore we have checked that this approach works
-indifferently with Integral Invariant curvature estimator and
-Maximal Digital Circular Arc curvature estimator. So the convergence
-of the digital curvature estimator seems to be the cornerstone to
-get a digital curve behaving like a continuous elastica.  In the
-next section, we explore a more efficient approach.
-
-\begin{figure}
+The running time of algorithm \ref{alg:local-search} is summarized in table \ref{tab:summary-local-comb-rtime}. All the
+experiments in this paper were executed on a five-core $3.4Ghz$ CPU and the number of pixels in the triangle, square and
+flower shapes are respectively $841,1867,521$ for grid step $h=1.0$. Although its use in practical applications is
+limited, we demonstrate that digital estimators are effective in their measurements and the flows evolve as expected. We
+observe that it is a complete digital approach, and we do not suffer from discretization and rounding problems, a common
+issue in continuous models.  Furthermore we have checked that this approach works indifferently with Integral Invariant
+curvature estimator and Maximal Digital Circular Arc curvature estimator. So the convergence of the digital curvature
+estimator seems to be the cornerstone to get a digital curve behaving like a continuous Elastica.  In the next section,
+we explore a more efficient approach.
+
+\begin{figure}[!h]
 \begin{minipage}[b]{0.5\textwidth}
@@
 
-In figure \ref{fig:m1-square-flow} we see some results for the DCE
-algorithm with $m=1$. We observe a global movement towards roundness,
-but with several artifacts. We minimize the effects of a jaggy
-boundary by setting $\alpha > 0$. Nonetheless, a higher estimation
-ball radius creates unstable shapes. In fact, the estimator is very
-sensitive in regions of low squared curvature, and it is precisely in
-those regions that spurious pixels are created.
-
-\begin{figure}[!ht]
+In figure \ref{fig:m1-square-flow} we see some results for the DCE algorithm with $m=1$. We observe a global evolution
+towards rounder shapes, but with several artifacts. We minimize the effects of a jaggy boundary by setting $\alpha >
+0$. Nonetheless, a higher estimation ball radius creates unstable shapes. In fact, the estimator is very sensitive in
+regions of low squared curvature, and it is precisely in those regions that spurious pixels are created.
+
+\begin{figure}[!h]
 \center
@@
 
-In our experiments, the best results are obtained by executing DCE
-algorithm with $m$ equal to $r$, where $r$ is the estimation ball
-radius (see figures \ref{fig:mx-square-flow},
-\ref{fig:mx-flow-gs-radius-effect} ). In plot
-\ref{fig:mx-elastica-plots}, we observe how the elastica energy evolves along
-the iterations. If the radius is too large, the elastica energy may increase after some steps. That is what happens for the
-triangle, in which the flow converges to a single point.
-
-\begin{figure}[!ht]
+{In our experiments, the best results are obtained by executing DCE algorithm with $m$ equal to $r$, where $r$ is
+  the estimation ball radius (see figure \ref{fig:mx-square-flow} ). We observe that Elastica may increase after some
+  iterations if chosen radius is too large, as in the case of the triangle in figure \ref{fig:mx-flow-gs-radius-effect}
+  in which the flow converges to a single point. We conjecture that an appropriated value for the radius should be given
+  by the shape reach.  The produced flow has no difficulties in handling changes on topology, and it presents different
+  speeds for regions with low and high curvature values, as illustrated in figure
+  \ref{fig:mx-speed-variation-hole-filling}.
+
+\begin{figure}[hp!]
 \center				
@@
 
-Energy $E_m$ is non-submodular and optimizing it is a difficult
-problem, which constrains us to use heuristics and approximation
-algorithms. The QPBO method \cite{rother07qpbo} transforms the
-original problem in a max-flow/min-cut formulation and returns a full
-optimal labeling for submodular energies. For non-submodular energies
-the method is guaranteed to return a partial labeling with the
-property that the set of labeled variables is part of an optimal
+Energy $E_m$ is non-submodular and optimizing it is a difficult problem, which constrains us to use heuristics and
+approximation algorithms. The QPBO method \cite{rother07qpbo} transforms the original problem in a max-flow/min-cut
+formulation and yields a full optimal labeling for submodular energies. For non-submodular energies the method is
+guaranteed to return a partial labeling with the property that the set of labeled variables is part of an optimal
 solution. That property is called partial optimality.
 
-In practice, QPBO can leave many pixels unlabeled. There exist two
-extensions of QPBO that alleviate this limitation: QPBOI (improve) and
-QPBOP (probe). The first is an approximation method that is guaranteed
-to not increase the energy, but we lost the property of partial
-optimality. The second is an exact method which is reported to label
-more variables than QPBO.
-
-The percentage of unlabeled pixels by QPBOP for $E_1$ is quite high,
-but the percentage decreases to zero as we set $m$ equal to
-$r$. Therefore, we are more confident to take the solution for values
-of $m$ close to $r$. However, the way it varies across $m$ values
-differs from shape to shape, as is illustrated in figure
-\ref{fig:unlabeled-versus-iterations}. We also noticed that, for
-$m=r$, all the pixels were labeled. Perhaps this means that our energy
-is submodular in this case, but this remains to be proved.
-
-We have used QPBOI to solve $E_m$. Naturally, in the case where all
-pixels are labeled by QPBOP, QPBOI returns the same labeling as QPBOP.
-
-\begin{figure}[!htp]
+In practice, QPBO can leave many pixels unlabeled. There exist two extensions to QPBO that alleviate this limitation:
+QPBOI (improve) and QPBOP (probe). The first is an approximation method that is guaranteed to not increase the energy,
+but loses the property of partial optimality. The second is an exact method which is reported to label more variables
+than QPBO.
+
+The percentage of unlabeled pixels by QPBOP for $E_1$ is quite high, but the percentage decreases to zero as we set $m$
+equal to $r$. Therefore, we are more confident in taking the solution for values of $m$ close to $r$. However, the way it
+varies across $m$ values differs from shape to shape, as is illustrated in figure
+\ref{fig:unlabeled-versus-iterations}. We also noticed that, for $m=r$, all the pixels were labeled, {which may
+  indicate that $E_r$ is an an easy instance of the general non-submodular energy $E_m$, but this remains to be
+  proved. The number of pairwise terms in $E_r$ is roughly half of those in $E_1$ (see figure
+  \ref{fig:ratio-pairwise-terms}).
+
+  We have used QPBOI to solve $E_m$. Naturally, in the case where all pixels are labeled by QPBOP, QPBOI returns the
+  same labeling as QPBOP.
+
+\begin{figure}[h!]
+\center
+\includegraphics[scale=0.5]{images/optimization/pairwise-ratio/plot-pairwiseratio-lowerHigher-concavities-probe.eps}
+\caption{We plot the ratio of pairwise terms among all $\binom{|X^{(i)}|}{2}$ combinations. The highest ring has rougly half the number of pairwise terms  than the lowest ring.}
+\label{fig:ratio-pairwise-terms}
+\end{figure}
+
+\begin{figure}[hp!]
 \center
@@
 
-\begin{figure}
-\center
-\includegraphics[scale=0.5]{images/optimization/pairwise-ratio/plot-pairwiseratio-lowerHigher-concavities-probe.eps}
-\caption{We plot the ratio of pairwise terms among all $\binom{|X^{(i)}|}{2}$ combinations.
-The highest ring has rougly half the number of pairwise terms  than the lowest ring.\label{fig:ratio-pairwise-terms}}
-\end{figure}
-
-\todo{You must comment figure~\ref{fig:ratio-pairwise-terms} in the text.}
-
 \section{Application to image segmentation}
 
-We present an application of our digital curve evolution algorithm to supervised image segmentation.
-The DCE will act as a contour correction method.
-Here we are going to use a data fidelity term in order to characterize the object of interest.
-Given foreground and background seeds selected by the user, we derive mixed gaussian distributions  of color intensities $G_f$ and $G_b$, and we define the data fidelity term as
+We present an application of our digital curve evolution algorithm to supervised image segmentation. The DCE acts as a
+contour correction method. Here we use a data fidelity term in order to characterize the object of
+interest. Given foreground and background seeds selected by the user, we derive mixed gaussian distributions  of color
+intensities $G_f$ and $G_b$, and we define the data fidelity term as the cross-entropy, i.e.
 
@@
 
-In figure \ref{fig:parameters-influence} we can observe the results of a curvature regularization in comparison with a pure length regularization, and figures \ref{fig:segmentation-results} and \ref{fig:more-segmentation-results} show some segmentation results.
-
-\todo{You must comment on the results.}
+{In figure \ref{fig:parameters-influence} we can observe the results of a curvature regularization in comparison with a
+  pure length regularization. The curvature can fill gaps and is smoother than the one produced by length only,
+  resulting in more pleasant segmentations. In figures \ref{fig:segmentation-results} and
+  \ref{fig:more-segmentation-results} we list several results of our method and we compare them with segmentation
+  produced by GrabCut and Schoenemann's method. Our method is successful in producing curvature regularized
+  segmentations and demonstrates the completion property of curvature. Moreover, it does not suffer from over
+  segmentation, it is much faster than Schoenemann's, and in several opportunities produces better segmentations than
+  GrabCut.
 
@@
 
-We have studied in depth several digital curve evolution models based
-on the elastica energy and we have presented an application of one of
-them to image segmentation. The processes we have described are
-completely digital, and do not suffer from issues that typically
-arises in models that passes through a discretization stage, as
-rounding. Moreover, the model can handle changes in topology and its
-results are competitive with similar approaches while achieving
-reasonable running times.
-
-Future developments of this work may include automatization, no more
-dependence on seeds selected by the user and automatic choice of ball
-estimation radius based on the reach of the shape. One can also think
-to extend the DCE algorithm to $3$d, as the integral invariant
-estimator preserves its properties in that space. In future works, a
-denoising application may be derived by running the flow on the $3$d
-shape with data fidelity defined by image intensities or by distance
-to initial position.
+We have studied in depth several digital curve evolution models based on a digital version of the Elastica energy and we
+have presented an application to image segmentation. The processes we have described are completely digital, and do not
+suffer from issues that typically arise in models that passes through a discretization stage, such as
+rounding. Moreover, the model can handle changes in topology and its results are competitive with similar approaches
+while achieving reasonable running times.
+
+Future developments of this work will include extending the DCE algorithm to $3$d, as the integral invariant estimator
+is available in higher dimensions. As a result, a denoising application may be derived by lifting the flow to $3$d
+with a data fidelity defined by image intensities or by distance to initial position.
 

### 2020-01-07 answer-to-reviewers/answer-to-reviewers.tex
revision version

@@
 
-~\\ In section 5, we indeed compare our segmentation model with the
+~\\
+~\\
+$\rightarrow$ In section 5, we indeed compare our segmentation model with the
 work of \cite{schoenemann09linear}, which uses a polygonal
@@
 Finally, the notions of multigrid convergence and $\Gamma$-convergence
-are not easily comparable. The former concerns the accuracy of an
-estimation, the latter concerns a sequence of minimizers. The former
-is specifically designed for digital data, hence more appropriated in
-our case as our main objects of interest are digital images.  ~\\
+are not related. The former concerns the accuracy of an
+estimation, and is specifically designed for digital data, hence more appropriated in
+our case as our main objects of interest are digital images.  The latter concerns a
+sequence of minimizers especially in the continuous domain.~\\
 
@@
 ~\\
-$\rightarrow$ We agree. In fact, the former presentation included gratuitous technical difficulties. We've decided to change the presentation to an equivalent one, easier to read.
+$\rightarrow$ We agree. In fact, the former presentation included unnecessary technical difficulties. We decided to change the presentation to an equivalent one, easier to read.
 ~\\
@@
 ~\\
-$\rightarrow$ Indeed, an extension of the operator int(.) for set of curves was necessary.
-However, as said in the previous answer, the presentation of this section has changed, and such definition is no more needed.
+$\rightarrow$ Indeed, an extension of the operator int(.) for set of curves was necessary. However, as said in the
+previous answer, the presentation of this section has changed, and this definition is no longer needed.
 ~\\
@@
 ~\\
-$\rightarrow$ Not sure to comply with this request or not. I’m not sure what to answer
+$\rightarrow$ We have significantly changed, and hopefully simplified our description also taking into account the
+other reviewers' comments.
 ~\\

### 2020-01-07 jmiv.tex
revision version

--- 2019-12-21 jmiv.tex
@@
 \revision{
-	Given a digital shape $S \in \Omega$, its $n$-neighborhood $\mathcal{N}_n(S)$ is defined as the set of digital shapes that can be built from $S$ by adding or removing a sequence of $k \in [0,n]$ connected pixels in $R_1(S)$.
+	Given a digital shape $S \in \Omega$, its $n$-neigh\-bor\-hood $\mathcal{N}_n(S)$ is defined as the set of digital shapes that can be built from $S$ by adding or removing a sequence of $k \in [0,n]$ connected pixels in $R_1(S)$.
 }

### 2020-01-07 answer-to-reviewers/answer-to-reviewers.tex
jmiv revision

@@
 ~\\
-$\rightarrow$ We have significantly changed, and hopefully simplified our description also taking into account the
-other reviewers' comments.
+$\rightarrow$ We are not quite sure what the reviewer is asking here. Optimisation of the Elastica (equation (3)) in the
+continuous domain is itself a complex problem that has been studied by Mumford and others. In section 3 we conduct a
+minimization of equation (4) only, which is the discrete equivalent of equation (3). We hope that the new explanations
+and figures in section 3 answer the reviewer's concerns.
 ~\\
@@
 ~\\
-$\rightarrow$ New figures were included in section 3. We they will help clarify this point.
+$\rightarrow$ New figures were included in section 3. We hope they will help clarify this point.
 ~\\
@@
 $\rightarrow$ It may not exist!
-If the neighborhood is exhausted and such X* is not found, the algorithm stops.
-In particular, the shapes S(i) and S(i-1) will be the same, hence delta will be zero and there will be no next iteration.
+If the neighborhood is exhausted and such X* is not found, the algorithm simply stops.
+Specifically, the shapes S(i) and S(i-1) will be the same, hence delta will be zero and there will be no next iteration.
 ~\\

### 2020-01-07 Revision/Biographies/biographies.tex
bibliographies

\documentstyle[a4]{paper}

\begin{document}
\paragraph{Daniel Antunes}
A brilliant PhD student from Brazil.

\paragraph{Jacques-Olivier Lachaud}
A splendid researcher, great mentor and fast friend.

\paragraph{Hugues Talbot}
Hugues Talbot received the Habilitation from Universite Paris-Est in 2013, the PhD from \'Ecole des Mines de Paris in
1993 and the engineering degree from Ecole Centrale de Paris in 1989. He was principal research scientist at CSIRO,
Sydney, from 1994 to 2004. He is now a professor at CentraleSupelec, Universite Paris-Saclay and member of the Inria
OPIS team. He is the co-author of 6 books and over 200 articles in the area of mathematical morphology, discrete
geometry, combinatorial and continuous optimization.
\end{document}

### 2020-01-07 Revision/Biographies/biographies.tex
Add bio jol

@@
 \paragraph{Jacques-Olivier Lachaud}
-A splendid researcher, great mentor and fast friend.
+Jacques-Olivier Lachaud graduated from ENSIMAG engineering school in
+Computer Science in 1994 and received a Ph.D. degree in computer
+science from Joseph Fourier University (Grenoble, France) in 1998 and
+the Habilitation from University Bordeaux 1 in 2006. He is now a
+Professor of Computer Science at the University Savoie Mont Blanc
+(Chambéry, France) and works in the laboratory of mathematics
+(LAMA). His research interests are in image analysis and geometry
+processing, more specifically deformable models, energy-minimizing
+techniques, digital geometry and topology. He has written over 100
+articles in international journals and conferences on these topics.
+%% JO :-D A splendid researcher, great mentor and fast friend.
 

### 2020-01-07 Revision/Biographies/biographies.tex
biographie daniel

--- 2020-01-07 Revision/Biographies/biographies.tex
@@
 \paragraph{Daniel Antunes}
-A brilliant PhD student from Brazil.
+Daniel Antunes received his B.S.
+in computer science from the Universidade Federal do Rio de Janeiro, Brazil (2014) and his M.S.
+in  computer science from Université Paris-Est, France (2016).
+Since February 2017 he is a Ph.D student at the LAMA laboratory at Université Savoie Mont Blanc, France.
+His research interest is focused on digital geometry and combinatorial optimization applied to image analysis.
 

### 2020-01-07 Revision/Biographies/biographies.tex
biographie daniel

--- 2020-01-07 Revision/Biographies/biographies.tex
@@
 \paragraph{Daniel Antunes}
-A brilliant PhD student from Brazil.
+Daniel Antunes received his B.S.
+in computer science from the Universidade Federal do Rio de Janeiro, Brazil (2014) and his M.S.
+in  computer science from Universit\'e Paris-Est, France (2016).
+Since February 2017 he is a Ph.D student in the laboratory of mathematics (LAMA) at Universit\'e Savoie Mont Blanc, France.
+His research interests is focused on digital geometry and combinatorial optimization applied to image analysis.
 

### 2020-01-08 Revision/Biographies/biographies.tex
photos

@@
 \paragraph{Hugues Talbot}
-Hugues Talbot received the Habilitation from Universite Paris-Est in 2013, the PhD from \'Ecole des Mines de Paris in
-1993 and the engineering degree from Ecole Centrale de Paris in 1989. He was principal research scientist at CSIRO,
-Sydney, from 1994 to 2004. He is now a professor at CentraleSupelec, Universite Paris-Saclay and member of the Inria
-OPIS team. He is the co-author of 6 books and over 200 articles in the area of mathematical morphology, discrete
-geometry, combinatorial and continuous optimization.
+Hugues Talbot received the Habilitation from Universite Paris-Est in
+2013, the PhD from \'Ecole des Mines de Paris in 1993 and the
+engineering degree from Ecole Centrale de Paris in 1989. He was
+principal research scientist at CSIRO, Sydney, from 1994 to 2004; and
+a professor in computer science at ESIEE Paris from 2004 to 2018. He
+is now a professor in the mathematics department at CentraleSupelec,
+Universite Paris-Saclay and member of the Inria OPIS team. He is the
+co-author or co-editor of 7 books and over 250 articles in the area of
+mathematical morphology, discrete geometry, combinatorial and
+continuous optimization.
 \end{document}

### 2020-05-20 Revision/Biographies/biographies.tex
flat-file revision version

@@
 principal research scientist at CSIRO, Sydney, from 1994 to 2004; and
-a professor in computer science at ESIEE Paris from 2004 to 2018. He
-is now a professor in the mathematics department at CentraleSupelec,
-Universite Paris-Saclay and member of the Inria OPIS team. He is the
-co-author or co-editor of 7 books and over 250 articles in the area of
-mathematical morphology, discrete geometry, combinatorial and
-continuous optimization.
+a professor in computer science at ESIEE Paris, Universit\'e Paris-Est
+from 2004 to 2018. He is now a professor in the mathematics department
+at CentraleSupelec, Universite Paris-Saclay and member of the Inria
+OPIS team. He is the co-author or co-editor of 7 books and over 250
+articles in the area of mathematical morphology, discrete geometry,
+combinatorial and continuous optimization.
 \end{document}

### 2020-05-20 Revision/R1_latex/manuscript.tex
flat-file revision version
revision continued

--- 2020-01-07 jmiv.tex
@@
 More important, in this estimator, the curve representation lies in the continuous domain and the properties of such estimator are not immediately valid when the curve is translated to the digital domain.
-In particular, it is not straightforward to include a image data term in this model without adding extra assumptions about the curve representation.
+In particular, it is not straightforward to include an image data term in this model without adding extra assumptions about the curve representation.
 One could use a spline approximation with exact curvature information and the same kind of approach would have the same pros and cons.} Improving the quality of the curvature estimator has an important impact on the accuracy of the results, \revision{but we should use the appropriate tools to evaluate its quality.
@@
 	\subfloat[\label{}]{%
-	\includegraphics[scale=2.0]{images/local_search/definitions/flower.png}
+	\includegraphics[scale=2.0]{flower.png}
 	}\hspace{40pt}%
 	\subfloat[\label{}]{%	
-	\includegraphics[scale=0.3]{images/local_search/definitions/cellular-grid-illustration.eps}
+	\includegraphics[scale=0.3]{cellular-grid-illustration.eps}
 	}
@@
 	\subfloat[\label{}]{%
-	\includegraphics[scale=0.03]{images/local_search/definitions/R3.pdf}
+	\includegraphics[scale=0.03]{R3.pdf}
 	}\hspace{40pt}%
 	\subfloat[\label{}]{%
-	\includegraphics[scale=0.22]{images/local_search/definitions/glued-curve.eps}
+	\includegraphics[scale=0.22]{glued-curve.eps}
 	}%	

### 2020-05-20 Revision/R1_latex/manuscript.tex
Finish the flat-file version

@@
 	\subfloat[\label{}]{%
-	\includegraphics[scale=2.0]{flower.png}
+	\includegraphics[scale=2.0]{local_search_definitions_flower.png}
 	}\hspace{40pt}%
 	\subfloat[\label{}]{%	
-	\includegraphics[scale=0.3]{cellular-grid-illustration.eps}
+	\includegraphics[scale=0.3]{local_search_definitions_cellular-grid-illustration.eps}
 	}
@@
 	\subfloat[\label{}]{%
-	\includegraphics[scale=0.03]{R3.pdf}
+	\includegraphics[scale=0.03]{local_search_definitions_R3.eps}
 	}\hspace{40pt}%
 	\subfloat[\label{}]{%
-	\includegraphics[scale=0.22]{glued-curve.eps}
+	\includegraphics[scale=0.22]{local_search_definitions_glued-curve.eps}
 	}%	
@@
 		$h=1.0$ & $h=0.5$ & $h=0.25$\\
-		\includegraphics[scale=0.2]{images/local_search/square/h1/summary.eps} & \includegraphics[scale=0.2]{images/local_search/square/h05/summary.eps} & \includegraphics[scale=0.2]{images/local_search/square/h025/summary.eps} \\
-		\includegraphics[scale=0.2]{images/local_search/flower/h1/summary.eps} & \includegraphics[scale=0.2]{images/local_search/flower/h05/summary.eps} & \includegraphics[scale=0.2]{images/local_search/flower/h025/summary.eps}
+		\includegraphics[scale=0.2]{local_search_square_h1_summary.eps} & \includegraphics[scale=0.2]{local_search_square_h05_summary.eps} & \includegraphics[scale=0.2]{local_search_square_h025_summary.eps} \\
+		\includegraphics[scale=0.2]{local_search_flower_h1_summary.eps} & \includegraphics[scale=0.2]{local_search_flower_h05_summary.eps} & \includegraphics[scale=0.2]{local_search_flower_h025_summary.eps}
 	\end{tabular}	
@@
 \center
-\subfloat[\label{}]{\includegraphics[scale=0.32]{images/local_search/square.eps}}
-\subfloat[\label{}]{\includegraphics[scale=0.32]{images/local_search/flower.eps}}
+\subfloat[\label{}]{\includegraphics[scale=0.32]{local_search_square.eps}}
+\subfloat[\label{}]{\includegraphics[scale=0.32]{local_search_flower.eps}}
 \caption{Digital elastica computation along iterations of algorithm \ref{alg:local-search}.
@@
 \center
-\includegraphics[scale=0.1]{images/flow/contour-information/before-opt.pdf}
+\includegraphics[scale=0.1]{flow_contour-information_before-opt.eps}
 \label{fig:contour-info-1}
@@
 \center
-\includegraphics[scale=0.1]{images/flow/contour-information/after-opt.pdf}
+\includegraphics[scale=0.1]{flow_contour-information_after-opt.eps}
 \label{fig:contour-info-2}
@@
 	\subfloat[$r=3, \alpha=0$\label{}]{%
-	\includegraphics[scale=0.2]{images/flow/length-radius-effect/triangle-r3-nolength/summary_flow.eps}
+	\includegraphics[scale=0.2]{flow_length-radius-effect_triangle-r3-nolength_summary_flow.eps}
 	}%
@@
 	\subfloat[$r=3, \alpha=0.15$\label{}]{%
-	\includegraphics[scale=0.2]{images/flow/length-radius-effect/triangle-r3-length0.15/summary_flow.eps}
+	\includegraphics[scale=0.2]{flow_length-radius-effect_triangle-r3-length015_summary_flow.eps}
 	}%
@@
 	\subfloat[$r=5, \alpha=0.15$\label{}]{%
-	\includegraphics[scale=0.2]{images/flow/length-radius-effect/triangle-r5/summary_flow.eps}
+	\includegraphics[scale=0.2]{flow_length-radius-effect_triangle-r5_summary_flow.eps}
 	}%
@@
 	\subfloat[$r=5, m=1$\label{}]{%
-	\includegraphics[scale=0.2]{images/flow/farther-rings/square-r5-l1/summary_flow.eps}
+	\includegraphics[scale=0.2]{flow_farther-rings_square-r5-l1_summary_flow.eps}
 	}%
@@
 	\subfloat[$r=5, m=3$\label{}]{%
-	\includegraphics[scale=0.2]{images/flow/farther-rings/square-r5-l3/summary_flow.eps}
+	\includegraphics[scale=0.2]{flow_farther-rings_square-r5-l3_summary_flow.eps}
 	}%
@@
 	\subfloat[\revision{$r=5, m=5$}\label{}]{%
-	\includegraphics[scale=0.2]{images/flow/farther-rings/square-r5-l5/summary_flow.eps}
+	\includegraphics[scale=0.2]{flow_farther-rings_square-r5-l5_summary_flow.eps}
 	}%
@@
 		\subfloat{%
-		\includegraphics[scale=0.2]{images/flow/grid-radius-effect/triangle/r3-h0.5/summary_flow.eps}
+		\includegraphics[scale=0.2]{flow_grid-radius-effect_triangle_r3-h05_summary_flow.eps}
 		}%
@@
 		\subfloat{%
-		\includegraphics[scale=0.15]{images/flow/grid-radius-effect/square/r3-h0.5/summary_flow.eps}}%
+		\includegraphics[scale=0.15]{flow_grid-radius-effect_square_r3-h05_summary_flow.eps}}%
 		\hspace{15pt}
 		\subfloat{%
-\includegraphics[scale=0.2]{images/flow/grid-radius-effect/flower/r3-h0.5/summary_flow.eps}}%
+\includegraphics[scale=0.2]{flow_grid-radius-effect_flower_r3-h05_summary_flow.eps}}%
 		}
@@
 		\subfloat{%
-		\includegraphics[scale=0.2]{images/flow/grid-radius-effect/triangle/r5-h0.5/summary_flow.eps}
+		\includegraphics[scale=0.2]{flow_grid-radius-effect_triangle_r5-h05_summary_flow.eps}
 		}%1
@@
 		\subfloat{%
-		\includegraphics[scale=0.15]{images/flow/grid-radius-effect/square/r5-h0.5/summary_flow.eps}}%
+		\includegraphics[scale=0.15]{flow_grid-radius-effect_square_r5-h05_summary_flow.eps}}%
 		\hspace{15pt}
 		\subfloat{%
-\includegraphics[scale=0.2]{images/flow/grid-radius-effect/flower/r5-h0.5/summary_flow.eps}}%
+\includegraphics[scale=0.2]{flow_grid-radius-effect_flower_r5-h05_summary_flow.eps}}%
 		}\\
 		\subfloat[\revision{Digital elastica evaluation ($r=5,h=0.5$)}]{%
-		\includegraphics[scale=0.5]{images/flow/elastica-energy-plot/square-flower-triangle.eps}						
+		\includegraphics[scale=0.5]{flow_elastica-energy-plot_square-flower-triangle.eps}						
 		}
@@
 \subfloat[]{%
-	\includegraphics[scale=0.5]{images/flow/faster-high-curvature/summary_flow.eps}}\\%
+	\includegraphics[scale=0.5]{flow_faster-high-curvature_summary_flow.eps}}\\%
 \subfloat[]{%
-		\includegraphics[scale=0.25]{images/flow/fill-holes/summary_flow.eps}}%%1
+		\includegraphics[scale=0.25]{flow_fill-holes_summary_flow.eps}}%%1
 \caption{High curvature regions evolves faster than lower ones (a). The flow can handle topological changes (b). }
@@
 \center
-\includegraphics[scale=0.5]{images/optimization/pairwise-ratio/plot-pairwiseratio-lowerHigher-concavities-probe.eps}
+\includegraphics[scale=0.5]{optimization_pairwise-ratio_plot-pairwiseratio-lowerHigher-concavities-probe.eps}
 \caption{We plot the ratio of pairwise terms among all $\binom{|X^{(i)}|}{2}$ combinations. The highest ring has roughly half the number of pairwise terms as the lowest ring.}
@@
 \begin{minipage}[b]{0.5\textwidth}
-\subfloat[]{ \includegraphics[scale=0.35]{images/optimization/unlabeled-iterations/radius-3/plot-model-square-concavities-probe.eps}}\\%
-\subfloat[]{ \includegraphics[scale=0.35]{images/optimization/unlabeled-iterations/radius-5/plot-model-square-concavities-probe.eps}}\\%
-\subfloat[]{ \includegraphics[scale=0.35]{images/optimization/unlabeled-iterations/radius-7/plot-model-square-concavities-probe.eps}}%
+\subfloat[]{ \includegraphics[scale=0.35]{optimization_unlabeled-iterations_radius-3_plot-model-square-concavities-probe.eps}}\\%
+\subfloat[]{ \includegraphics[scale=0.35]{optimization_unlabeled-iterations_radius-5_plot-model-square-concavities-probe.eps}}\\%
+\subfloat[]{ \includegraphics[scale=0.35]{optimization_unlabeled-iterations_radius-7_plot-model-square-concavities-probe.eps}}%
 \end{minipage}%
 \begin{minipage}[b]{0.5\textwidth}
-\subfloat[]{ \includegraphics[scale=0.35]{images/optimization/unlabeled-iterations/radius-3/plot-model-flower-concavities-probe.eps}}\\%
-\subfloat[]{ \includegraphics[scale=0.35]{images/optimization/unlabeled-iterations/radius-5/plot-model-flower-concavities-probe.eps}}\\%
-\subfloat[]{ \includegraphics[scale=0.35]{images/optimization/unlabeled-iterations/radius-7/plot-model-flower-concavities-probe.eps}}%
+\subfloat[]{ \includegraphics[scale=0.35]{optimization_unlabeled-iterations_radius-3_plot-model-flower-concavities-probe.eps}}\\%
+\subfloat[]{ \includegraphics[scale=0.35]{optimization_unlabeled-iterations_radius-5_plot-model-flower-concavities-probe.eps}}\\%
+\subfloat[]{ \includegraphics[scale=0.35]{optimization_unlabeled-iterations_radius-7_plot-model-flower-concavities-probe.eps}}%
 \end{minipage}
@@
 \revision{Seeds} & $(\alpha=0, \beta=0.5)$ & $(\alpha=0,\beta=1)$ \\
- 	\includegraphics[scale=0.25]{images/segmentation/bc/coala/seeds.png} & 
-	\includegraphics[scale=0.25]{images/segmentation/bc/coala/r3/lg0_sq05_dt1_it50.png} & 
-	\includegraphics[scale=0.25]{images/segmentation/bc/coala/r3/lg0_sq1_dt1_it50.png} \\
-
- 	\includegraphics[scale=0.25]{images/segmentation/bc/coala/grabcut-seg.png} & 
-	\includegraphics[scale=0.25]{images/segmentation/bc/coala/r3/lg1_sq0_dt1_it50.png} &
-	\includegraphics[scale=0.25]{images/segmentation/bc/coala/r3/lg2_sq0_dt1_it50.png} \\
+ 	\includegraphics[scale=0.25]{segmentation_bc_coala_seeds.png} & 
+	\includegraphics[scale=0.25]{segmentation_bc_coala_r3_lg0_sq05_dt1_it50.png} & 
+	\includegraphics[scale=0.25]{segmentation_bc_coala_r3_lg0_sq1_dt1_it50.png} \\
+
+ 	\includegraphics[scale=0.25]{segmentation_bc_coala_grabcut-seg.png} & 
+	\includegraphics[scale=0.25]{segmentation_bc_coala_r3_lg1_sq0_dt1_it50.png} &
+	\includegraphics[scale=0.25]{segmentation_bc_coala_r3_lg2_sq0_dt1_it50.png} \\
 
@@
 		& $(\alpha=0.1, \beta=1.0$) & $(r=5, \alpha=0.1, \beta=1.0, \gamma=3.0$)\\
-		\includegraphics[scale=0.2]{images/segmentation/bc/tiger1/gc-seg.png} &
-	\includegraphics[scale=0.2]{images/segmentation/schoenemann/tiger1/tiger1-seg.png}&
-		\includegraphics[scale=0.2]{images/segmentation/bc/tiger1/corrected-seg.png}\\									
-		\includegraphics[scale=0.2]{images/segmentation/bc/snake/gc-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/schoenemann/snake/snake-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/bc/snake/corrected-seg.png}\\
-		\includegraphics[scale=0.2]{images/segmentation/bc/man/gc-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/schoenemann/man/man-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/bc/man/corrected-seg.png}\\		
-		\includegraphics[scale=0.2]{images/segmentation/bc/vase/gc-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/schoenemann/vase/vase-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/bc/vase/corrected-seg.png}		
+		\includegraphics[scale=0.2]{segmentation_bc_tiger1_gc-seg.png} &
+	\includegraphics[scale=0.2]{segmentation_schoenemann_tiger1_tiger1-seg.png}&
+		\includegraphics[scale=0.2]{segmentation_bc_tiger1_corrected-seg.png}\\									
+		\includegraphics[scale=0.2]{segmentation_bc_snake_gc-seg.png} &
+		\includegraphics[scale=0.2]{segmentation_schoenemann_snake_snake-seg.png} &
+		\includegraphics[scale=0.2]{segmentation_bc_snake_corrected-seg.png}\\
+		\includegraphics[scale=0.2]{segmentation_bc_man_gc-seg.png} &
+		\includegraphics[scale=0.2]{segmentation_schoenemann_man_man-seg.png} &
+		\includegraphics[scale=0.2]{segmentation_bc_man_corrected-seg.png}\\		
+		\includegraphics[scale=0.2]{segmentation_bc_vase_gc-seg.png} &
+		\includegraphics[scale=0.2]{segmentation_schoenemann_vase_vase-seg.png} &
+		\includegraphics[scale=0.2]{segmentation_bc_vase_corrected-seg.png}		
 	\end{tabular}
@@
 		& $(\alpha=0.1, \beta=1.0$) & $(r=5, \alpha=0.1, \beta=1.0, \gamma=3.0$)\\
-		\includegraphics[scale=0.2]{images/segmentation/bc/airplane2/gc-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/schoenemann/airplane2/airplane2-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/bc/airplane2/corrected-seg.png}\\						
-		\includegraphics[scale=0.2]{images/segmentation/bc/bird/gc-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/schoenemann/bird/bird-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/bc/bird/corrected-seg.png}\\				
-		\includegraphics[scale=0.2]{images/segmentation/bc/camel/gc-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/schoenemann/camel/camel-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/bc/camel/corrected-seg.png}\\	
-		\includegraphics[scale=0.2]{images/segmentation/bc/rock/gc-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/schoenemann/rock/rock-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/bc/rock/corrected-seg.png} \\		
-		\includegraphics[scale=0.2]{images/segmentation/bc/giraffes/gc-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/schoenemann/giraffes/giraffes-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/bc/giraffes/corrected-seg.png} \\		
-		\includegraphics[scale=0.2]{images/segmentation/bc/canguru/gc-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/schoenemann/canguru/canguru-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/bc/canguru/corrected-seg.png} \\		
-		\includegraphics[scale=0.2]{images/segmentation/bc/coral/gc-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/schoenemann/coral/coral-seg.png} &
-		\includegraphics[scale=0.2]{images/segmentation/bc/coral/corrected-seg.png}								
+		\includegraphics[scale=0.2]{segmentation_bc_airplane2_gc-seg.png} &
+		\includegraphics[scale=0.2]{segmentation_schoenemann_airplane2_airplane2-seg.png} &
+		\includegraphics[scale=0.2]{segmentation_bc_airplane2_corrected-seg.png}\\						
+		\includegraphics[scale=0.2]{segmentation_bc_bird_gc-seg.png} &
+		\includegraphics[scale=0.2]{segmentation_schoenemann_bird_bird-seg.png} &
+		\includegraphics[scale=0.2]{segmentation_bc_bird_corrected-seg.png}\\				
+		\includegraphics[scale=0.2]{segmentation_bc_camel_gc-seg.png} &
+		\includegraphics[scale=0.2]{segmentation_schoenemann_camel_camel-seg.png} &
+		\includegraphics[scale=0.2]{segmentation_bc_camel_corrected-seg.png}\\	
+		\includegraphics[scale=0.2]{segmentation_bc_rock_gc-seg.png} &
+		\includegraphics[scale=0.2]{segmentation_schoenemann_rock_rock-seg.png} &
+		\includegraphics[scale=0.2]{segmentation_bc_rock_corrected-seg.png} \\		
+		\includegraphics[scale=0.2]{segmentation_bc_giraffes_gc-seg.png} &
+		\includegraphics[scale=0.2]{segmentation_schoenemann_giraffes_giraffes-seg.png} &
+		\includegraphics[scale=0.2]{segmentation_bc_giraffes_corrected-seg.png} \\		
+		\includegraphics[scale=0.2]{segmentation_bc_canguru_gc-seg.png} &
+		\includegraphics[scale=0.2]{segmentation_schoenemann_canguru_canguru-seg.png} &
+		\includegraphics[scale=0.2]{segmentation_bc_canguru_corrected-seg.png} \\		
+		\includegraphics[scale=0.2]{segmentation_bc_coral_gc-seg.png} &
+		\includegraphics[scale=0.2]{segmentation_schoenemann_coral_coral-seg.png} &
+		\includegraphics[scale=0.2]{segmentation_bc_coral_corrected-seg.png}								
 	\end{tabular}
@@
 \bibliographystyle{splncs04}
-\bibliography{jmiv}
+\bibliography{manuscript}
 

### 2020-05-20 Revision/R1_latex/manuscript.tex
Convert eps figures to pdf

@@
 	\subfloat[\label{}]{%	
-	\includegraphics[scale=0.3]{local_search_definitions_cellular-grid-illustration.eps}
+	\includegraphics[scale=0.3]{local_search_definitions_cellular-grid-illustration.pdf}
 	}
@@
 	\subfloat[\label{}]{%
-	\includegraphics[scale=0.03]{local_search_definitions_R3.eps}
+	\includegraphics[scale=0.03]{local_search_definitions_R3.pdf}
 	}\hspace{40pt}%
 	\subfloat[\label{}]{%
-	\includegraphics[scale=0.22]{local_search_definitions_glued-curve.eps}
+	\includegraphics[scale=0.22]{local_search_definitions_glued-curve.pdf}
 	}%	
@@
 		$h=1.0$ & $h=0.5$ & $h=0.25$\\
-		\includegraphics[scale=0.2]{local_search_square_h1_summary.eps} & \includegraphics[scale=0.2]{local_search_square_h05_summary.eps} & \includegraphics[scale=0.2]{local_search_square_h025_summary.eps} \\
-		\includegraphics[scale=0.2]{local_search_flower_h1_summary.eps} & \includegraphics[scale=0.2]{local_search_flower_h05_summary.eps} & \includegraphics[scale=0.2]{local_search_flower_h025_summary.eps}
+		\includegraphics[scale=0.2]{local_search_square_h1_summary.pdf} & \includegraphics[scale=0.2]{local_search_square_h05_summary.pdf} & \includegraphics[scale=0.2]{local_search_square_h025_summary.pdf} \\
+		\includegraphics[scale=0.2]{local_search_flower_h1_summary.pdf} & \includegraphics[scale=0.2]{local_search_flower_h05_summary.pdf} & \includegraphics[scale=0.2]{local_search_flower_h025_summary.pdf}
 	\end{tabular}	
@@
 \center
-\subfloat[\label{}]{\includegraphics[scale=0.32]{local_search_square.eps}}
-\subfloat[\label{}]{\includegraphics[scale=0.32]{local_search_flower.eps}}
+\subfloat[\label{}]{\includegraphics[scale=0.32]{local_search_square.pdf}}
+\subfloat[\label{}]{\includegraphics[scale=0.32]{local_search_flower.pdf}}
 \caption{Digital elastica computation along iterations of algorithm \ref{alg:local-search}.
@@
 \center
-\includegraphics[scale=0.1]{flow_contour-information_before-opt.eps}
+\includegraphics[scale=0.1]{flow_contour-information_before-opt.pdf}
 \label{fig:contour-info-1}
@@
 \center
-\includegraphics[scale=0.1]{flow_contour-information_after-opt.eps}
+\includegraphics[scale=0.1]{flow_contour-information_after-opt.pdf}
 \label{fig:contour-info-2}
@@
 	\subfloat[$r=3, \alpha=0$\label{}]{%
-	\includegraphics[scale=0.2]{flow_length-radius-effect_triangle-r3-nolength_summary_flow.eps}
+	\includegraphics[scale=0.2]{flow_length-radius-effect_triangle-r3-nolength_summary_flow.pdf}
 	}%
@@
 	\subfloat[$r=3, \alpha=0.15$\label{}]{%
-	\includegraphics[scale=0.2]{flow_length-radius-effect_triangle-r3-length015_summary_flow.eps}
+	\includegraphics[scale=0.2]{flow_length-radius-effect_triangle-r3-length015_summary_flow.pdf}
 	}%
@@
 	\subfloat[$r=5, \alpha=0.15$\label{}]{%
-	\includegraphics[scale=0.2]{flow_length-radius-effect_triangle-r5_summary_flow.eps}
+	\includegraphics[scale=0.2]{flow_length-radius-effect_triangle-r5_summary_flow.pdf}
 	}%
@@
 	\subfloat[$r=5, m=1$\label{}]{%
-	\includegraphics[scale=0.2]{flow_farther-rings_square-r5-l1_summary_flow.eps}
+	\includegraphics[scale=0.2]{flow_farther-rings_square-r5-l1_summary_flow.pdf}
 	}%
@@
 	\subfloat[$r=5, m=3$\label{}]{%
-	\includegraphics[scale=0.2]{flow_farther-rings_square-r5-l3_summary_flow.eps}
+	\includegraphics[scale=0.2]{flow_farther-rings_square-r5-l3_summary_flow.pdf}
 	}%
@@
 	\subfloat[\revision{$r=5, m=5$}\label{}]{%
-	\includegraphics[scale=0.2]{flow_farther-rings_square-r5-l5_summary_flow.eps}
+	\includegraphics[scale=0.2]{flow_farther-rings_square-r5-l5_summary_flow.pdf}
 	}%
@@
 		\subfloat{%
-		\includegraphics[scale=0.2]{flow_grid-radius-effect_triangle_r3-h05_summary_flow.eps}
+		\includegraphics[scale=0.2]{flow_grid-radius-effect_triangle_r3-h05_summary_flow.pdf}
 		}%
@@
 		\subfloat{%
-		\includegraphics[scale=0.15]{flow_grid-radius-effect_square_r3-h05_summary_flow.eps}}%
+		\includegraphics[scale=0.15]{flow_grid-radius-effect_square_r3-h05_summary_flow.pdf}}%
 		\hspace{15pt}
 		\subfloat{%
-\includegraphics[scale=0.2]{flow_grid-radius-effect_flower_r3-h05_summary_flow.eps}}%
+\includegraphics[scale=0.2]{flow_grid-radius-effect_flower_r3-h05_summary_flow.pdf}}%
 		}
@@
 		\subfloat{%
-		\includegraphics[scale=0.2]{flow_grid-radius-effect_triangle_r5-h05_summary_flow.eps}
+		\includegraphics[scale=0.2]{flow_grid-radius-effect_triangle_r5-h05_summary_flow.pdf}
 		}%1
@@
 		\subfloat{%
-		\includegraphics[scale=0.15]{flow_grid-radius-effect_square_r5-h05_summary_flow.eps}}%
+		\includegraphics[scale=0.15]{flow_grid-radius-effect_square_r5-h05_summary_flow.pdf}}%
 		\hspace{15pt}
 		\subfloat{%
-\includegraphics[scale=0.2]{flow_grid-radius-effect_flower_r5-h05_summary_flow.eps}}%
+\includegraphics[scale=0.2]{flow_grid-radius-effect_flower_r5-h05_summary_flow.pdf}}%
 		}\\
 		\subfloat[\revision{Digital elastica evaluation ($r=5,h=0.5$)}]{%
-		\includegraphics[scale=0.5]{flow_elastica-energy-plot_square-flower-triangle.eps}						
+		\includegraphics[scale=0.5]{flow_elastica-energy-plot_square-flower-triangle.pdf}						
 		}
@@
 \subfloat[]{%
-	\includegraphics[scale=0.5]{flow_faster-high-curvature_summary_flow.eps}}\\%
+	\includegraphics[scale=0.5]{flow_faster-high-curvature_summary_flow.pdf}}\\%
 \subfloat[]{%
-		\includegraphics[scale=0.25]{flow_fill-holes_summary_flow.eps}}%%1
+		\includegraphics[scale=0.25]{flow_fill-holes_summary_flow.pdf}}%%1
 \caption{High curvature regions evolves faster than lower ones (a). The flow can handle topological changes (b). }
@@
 \center
-\includegraphics[scale=0.5]{optimization_pairwise-ratio_plot-pairwiseratio-lowerHigher-concavities-probe.eps}
+\includegraphics[scale=0.5]{optimization_pairwise-ratio_plot-pairwiseratio-lowerHigher-concavities-probe.pdf}
 \caption{We plot the ratio of pairwise terms among all $\binom{|X^{(i)}|}{2}$ combinations. The highest ring has roughly half the number of pairwise terms as the lowest ring.}
@@
 \begin{minipage}[b]{0.5\textwidth}
-\subfloat[]{ \includegraphics[scale=0.35]{optimization_unlabeled-iterations_radius-3_plot-model-square-concavities-probe.eps}}\\%
-\subfloat[]{ \includegraphics[scale=0.35]{optimization_unlabeled-iterations_radius-5_plot-model-square-concavities-probe.eps}}\\%
-\subfloat[]{ \includegraphics[scale=0.35]{optimization_unlabeled-iterations_radius-7_plot-model-square-concavities-probe.eps}}%
+\subfloat[]{ \includegraphics[scale=0.35]{optimization_unlabeled-iterations_radius-3_plot-model-square-concavities-probe.pdf}}\\%
+\subfloat[]{ \includegraphics[scale=0.35]{optimization_unlabeled-iterations_radius-5_plot-model-square-concavities-probe.pdf}}\\%
+\subfloat[]{ \includegraphics[scale=0.35]{optimization_unlabeled-iterations_radius-7_plot-model-square-concavities-probe.pdf}}%
 \end{minipage}%
 \begin{minipage}[b]{0.5\textwidth}
-\subfloat[]{ \includegraphics[scale=0.35]{optimization_unlabeled-iterations_radius-3_plot-model-flower-concavities-probe.eps}}\\%
-\subfloat[]{ \includegraphics[scale=0.35]{optimization_unlabeled-iterations_radius-5_plot-model-flower-concavities-probe.eps}}\\%
-\subfloat[]{ \includegraphics[scale=0.35]{optimization_unlabeled-iterations_radius-7_plot-model-flower-concavities-probe.eps}}%
+\subfloat[]{ \includegraphics[scale=0.35]{optimization_unlabeled-iterations_radius-3_plot-model-flower-concavities-probe.pdf}}\\%
+\subfloat[]{ \includegraphics[scale=0.35]{optimization_unlabeled-iterations_radius-5_plot-model-flower-concavities-probe.pdf}}\\%
+\subfloat[]{ \includegraphics[scale=0.35]{optimization_unlabeled-iterations_radius-7_plot-model-flower-concavities-probe.pdf}}%
 \end{minipage}

### 2020-05-20 Revision/R1_latex/manuscript.tex
Replace long filenames to shorter ones

@@
 \center
-\includegraphics[scale=0.5]{optimization_pairwise-ratio_plot-pairwiseratio-lowerHigher-concavities-probe.pdf}
+\includegraphics[scale=0.5]{opt_pairwise_ratio_concavities_probe.pdf}
 \caption{We plot the ratio of pairwise terms among all $\binom{|X^{(i)}|}{2}$ combinations. The highest ring has roughly half the number of pairwise terms as the lowest ring.}
@@
 \begin{minipage}[b]{0.5\textwidth}
-\subfloat[]{ \includegraphics[scale=0.35]{optimization_unlabeled-iterations_radius-3_plot-model-square-concavities-probe.pdf}}\\%
-\subfloat[]{ \includegraphics[scale=0.35]{optimization_unlabeled-iterations_radius-5_plot-model-square-concavities-probe.pdf}}\\%
-\subfloat[]{ \includegraphics[scale=0.35]{optimization_unlabeled-iterations_radius-7_plot-model-square-concavities-probe.pdf}}%
+\subfloat[]{ \includegraphics[scale=0.35]{opt_unlabeled_it_r3_square_concavities_probe.pdf}}\\%
+\subfloat[]{ \includegraphics[scale=0.35]{opt_unlabeled_it_r5_square_concavities_probe.pdf}}\\%
+\subfloat[]{ \includegraphics[scale=0.35]{opt_unlabeled_it_r7_square_concavities_probe.pdf}}%
 \end{minipage}%
 \begin{minipage}[b]{0.5\textwidth}
-\subfloat[]{ \includegraphics[scale=0.35]{optimization_unlabeled-iterations_radius-3_plot-model-flower-concavities-probe.pdf}}\\%
-\subfloat[]{ \includegraphics[scale=0.35]{optimization_unlabeled-iterations_radius-5_plot-model-flower-concavities-probe.pdf}}\\%
-\subfloat[]{ \includegraphics[scale=0.35]{optimization_unlabeled-iterations_radius-7_plot-model-flower-concavities-probe.pdf}}%
+\subfloat[]{ \includegraphics[scale=0.35]{opt_unlabeled_it_r3_flower_concavities_probe.pdf}}\\%
+\subfloat[]{ \includegraphics[scale=0.35]{opt_unlabeled_it_r5_flower_concavities_probe.pdf}}\\%
+\subfloat[]{ \includegraphics[scale=0.35]{opt_unlabeled_it_r7_flower_concavities_probe.pdf}}%
 \end{minipage}
